### 2020-12-20 Manuscript/Manuscript.tex
changed some wording

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\setlength\parindent{0pt}

\title{Knapsack Dynamic Problem}
\author{KV}
\date{December 2020}

\begin{document}

\maketitle

\section{Decision Epochs}
Decisions are made at the beginning of each month

\section{State Space}
State space is defined by current budget for various PPEs for future month, amount of budget already spent on PPEs, current patient waitlist, and expected monthly demand (?)
\[ \vec{s}  = (\vec{bc}, \vec{bu}, \vec{pw}, \vec{pe})\]
\begin{itemize}
    \item $\vec{bc} = bc_{mp}$ - Expected budget for month $m$, and PPE $p$
    \item $\vec{bu} = bc_{mp}$ - Used budget for month $m$, and PPE $p$
    \item $\vec{pw} = pw_{mdc}$ - Number of patients of difficulty $d$, CPU $c$, on a wait list for $m$ months
    \item $\vec{pe} = pe_{dc}$ - Number of patients of difficulty $d$, CPU $c$ expected to arrive this month (Not sure if this is good, because right now, it is assumed this information is know in advance, while in real world this would be realized over the transition)
\end{itemize}

\section{Action Sets}
At the beginning of each month, decision maker must decide how to use the PPE budget, ie how many patients of each group to assign to this month.
\[ \vec{a} = (\vec{s}) \]
\begin{itemize}
    \item $\vec{s} = s_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been in wait list for $m$ month, to schedule in month $t$
\end{itemize}
The actions must satisfy the following constraints:
\begin{itemize}
    \item Total allocated budged must not be exceeded ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
        \[ \sum_{dc}s_{mdc}U_{pdc} >= (bc - bu)\ \quad \forall m, p \]
\end{itemize}

\section{Transition Probabilities}
There are three sources of uncertainty: 
\begin{enumerate}
    \item Number of patients arriving this month - $pe_{dc}$
    \item Transition between patient difficulties within the wait list - $pw_{mdc}$
    \item Amount of resources used during the operation - $U_{pdc}$
\end{enumerate}

Assume $pe_{dc}$ follows some poisson distribution. \\
Assume transition within $pw_{mdc}$ follows some binomial distribution with a probability that patient of difficulty $d$ in CPU $c$ moves to a more difficult category at each state transition. \\
These two sources of uncertainty only deal with $pe_{dc}$ and $pw_{mdc}$ part of the states and must follow the following constraints
\begin{itemize}
	\item Total number of patients on the wait-list must be consistent over time
	\[ \sum_{d} pw'_{m+1,dc} = \sum_{d} pw_{mdc} - \sum_{td} s_{tmdc}\ \quad \forall m, c \]
	\item Patients can only get more difficult over time
	\[ \sum_{di = d}^{D} pw'_{m+1,di,c} \ge \sum_{di = d}^{D} pw_{mdc} - \sum_{t,d=di}^{D} s_{tmdc} \quad \forall m,d,c \]
	\item  Unscheduled expected arrivals are moved into the wait list
	\[ pw'_{m=1, dc} = pe_{dc} -\sum_{t} s_{t, m=0, dc} \quad \forall dc \]
\end{itemize}

\section{Costs}
Cost will come only from one source: the number of people unscheduled after action is performed:
\[ c(\vec{s}, \vec{a}) = \sum_{dc} c_m pw_{mdc} \]
Where $c_m$ is computed as follows (where $val$ is an arbitrary number that would allow us to describe cost growth well):
	\[ c_{m} = val^m \quad \forall m \in \{ 0, ..., M-1 \} \]
	\[ c_{M} = val^m * 100  \]
The reason there is a very high cost at the last month is because patients are essentially removed if they are not scheduled and they are in the last wait month (in order to be able to have a limit on $m$ while modeling). So theoretically, the model should schedule in such a way that people never reach that point.

\end{document}

### 2021-01-17 Manuscript/Manuscript.tex
added some changes
- todo:
   - finalize constraints for action sets
   - make sure costs are correct
   - review transition constraints

@@
 \usepackage{geometry}
+\usepackage{amsmath}
 \geometry{margin=1in}
@@
 
-\title{Knapsack Dynamic Problem}
+\title{Dynamic Knapsack Problem}
 \author{KV}
@@
 \section{Decision Epochs}
-Decisions are made at the beginning of each month
+Decisions are made at the beginning of each time period (will be weeks)
 
 \section{State Space}
-State space is defined by current budget for various PPEs for future month, amount of budget already spent on PPEs, current patient waitlist, and expected monthly demand (?)
-\[ \vec{s}  = (\vec{bc}, \vec{bu}, \vec{pw}, \vec{pe})\]
+State space is defined by current units available for various PPEs for future periods, amount of budget already spent on PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
+\[ \vec{s}  = (\vec{be}, \vec{bu}, \vec{pw}, \vec{pe})\]
 \begin{itemize}
-    \item $\vec{bc} = bc_{mp}$ - Expected budget for month $m$, and PPE $p$
-    \item $\vec{bu} = bc_{mp}$ - Used budget for month $m$, and PPE $p$
-    \item $\vec{pw} = pw_{mdc}$ - Number of patients of difficulty $d$, CPU $c$, on a wait list for $m$ months
-    \item $\vec{pe} = pe_{dc}$ - Number of patients of difficulty $d$, CPU $c$ expected to arrive this month (Not sure if this is good, because right now, it is assumed this information is know in advance, while in real world this would be realized over the transition)
+    \item $\vec{be} = be_{mp}$ - Expected unist for period $m$, and PPE $p$
+    \item $\vec{bu} = bu_{mp}$ - Used units for period $m$, and PPE $p$
+    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
+    \item $\vec{pe} = pe_{dc}$ - Number of patients of complexity $d$, CPU $c$ expected to arrive this period
+    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
 \end{itemize}
@@
 \section{Action Sets}
-At the beginning of each month, decision maker must decide how to use the PPE budget, ie how many patients of each group to assign to this month.
-\[ \vec{a} = (\vec{s}) \]
+At the beginning of each period, decision maker must cancel appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively).
+And decision maker must also schedule patients to surgeries
+\[ \vec{a} = (\vec{sc}, \vec{usc}) \]
 \begin{itemize}
-    \item $\vec{s} = s_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been in wait list for $m$ month, to schedule in month $t$
+    \item $\vec{sc} = sc_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been in wait list for $m$ periods, to schedule in period $t$ ($m$ of 0 stands for people who have just arrived)
+	\item $\vec{usc} = usc_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to cancel from period $t$
 \end{itemize}
@@
     \item Total allocated budged must not be exceeded ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
-        \[ \sum_{dc}s_{mdc}U_{pdc} >= (bc - bu)\ \quad \forall m, p \]
+        \[ \sum_{dc}s_{mdc}U_{pdc} <= (be - bu)\ \quad \forall m, p \]
+	\item Cannot schedule past waitlist horizon limit
+	\item number of people scheduled/cancelled must be consistent
 \end{itemize}
@@
 \begin{enumerate}
-    \item Number of patients arriving this month - $pe_{dc}$
+
+	\item Number of patients arriving this period - $pe_{dc}$
+		\begin{itemize}
+			\item let's assume $pea_{dc}$ - is the random variable that represents the number of patients arrived this period. It follows a poisson distribution.
+		\end{itemize}
+
 	\item Transition between patient difficulties within the wait list - $pw_{mdc}$
-    \item Amount of resources used during the operation - $U_{pdc}$
+		\begin{itemize}
+			\item let's assume $pwfi_{mdc}$ represents an intermediary variable showing the number of patients of complexity $d$, for CPU $c$ entering the waitlist of period $m$ in any way.
+			\item let's assume $pwfo_{mdc}$ represents an intermediary variable showing the number of patients of complexity $d$, for CPU $c$ leaving the waitlist of period $m$  in any way
+			\item let's assume $pwt_{mdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have moved a more complex category.
+It follows binary distribution.
+		\end{itemize}
+
+	\item Amout of expected units of PPE resource for the next time period - $bc_{1dc}$
+		\begin{itemize}
+			\item let's assume $bed_{md}$ is the random variable that represents the deviation of PPE units from the expectation for the next period only. It follows some uniform distribution.
+			\item let's assume $ben_{d}$ is the default value to be used for expected number of PPE units $p$ per period
+		\end{itemize}
 \end{enumerate}
@@
 Assume transition within $pw_{mdc}$ follows some binomial distribution with a probability that patient of difficulty $d$ in CPU $c$ moves to a more difficult category at each state transition. \\
-These two sources of uncertainty only deal with $pe_{dc}$ and $pw_{mdc}$ part of the states and must follow the following constraints
+Assume deviation from expected number of PPE units follows a uniform distribution ($bcd_{p}$)\\
+State transitions have the following constraints:
 \begin{itemize}
-	\item Total number of patients on the wait-list must be consistent over time
-	\[ \sum_{d} pw'_{m+1,dc} = \sum_{d} pw_{mdc} - \sum_{td} s_{tmdc}\ \quad \forall m, c \]
-	\item Patients can only get more difficult over time
-	\[ \sum_{di = d}^{D} pw'_{m+1,di,c} \ge \sum_{di = d}^{D} pw_{mdc} - \sum_{t,d=di}^{D} s_{tmdc} \quad \forall m,d,c \]
-	\item  Unscheduled expected arrivals are moved into the wait list
-	\[ pw'_{m=1, dc} = pe_{dc} -\sum_{t} s_{t, m=0, dc} \quad \forall dc \]
+
+	\item Transition from $\vec{bc}$ to $\vec{bc'}$ - Expected Units of PPE
+		\[ be'_{1p} = be_{2p} + bed_{p}\ \quad \forall p \]
+		\[ be'_{m-1,p} = be_{mp}\ \quad \forall m \in \{3...M\}, p \]
+		\[ be'_{Mp} = ben_{d} \quad \forall p \]
+
+	\item Transition from $\vec{bu}$ to $\vec{bu'}$ - Used Units of PPE
+		\[ bu'_{m-1,p} = bu	_{mp} - \sum_{tdc} ( sc_{t,m-1,dc}U_{pdc} ) + \sum_{tdc} ( usc_{t,m-1,dc}U_{pdc} )  \quad \forall m \in \{2...M\}, p \]
+		\[ bu'_{Mp} = 0 \quad \forall p \]
+
+	\item Transition from $\vec{pe}$ to $\vec{pe'}$ - Expected number of patients for this month
+		\[\ pe_{dc} = pea_{dc} \quad \forall dc \]
+
+	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
+		\[ pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} + \sum_{t} usc_{t0dc} \quad \forall dc \]
+		\[ pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + pwt_{m,d-1,c} - pwt_{m,d,c} \quad \forall m \in \{1...M-1 \}, dc \]
+		\[ pw'_{Mdc} = 0 \quad \forall dc \]
+
+	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patients between difficulties/scheduling/cancelling for scheduled appointments
+		\[ ps'_{t-1,m+1,dc} = ps_{tmdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + inflow - outflow \quad \forall t \in {2 ... T},  m \in \{0... M-1 \}, dc \]
+		\[ ps'_{Tmdc} = 0 \quad \forall mdc \]
+
 \end{itemize}
@@
 \section{Costs}
-Cost will come only from one source: the number of people unscheduled after action is performed:
-\[ c(\vec{s}, \vec{a}) = \sum_{dc} c_m pw_{mdc} \]
-Where $c_m$ is computed as follows (where $val$ is an arbitrary number that would allow us to describe cost growth well):
-	\[ c_{m} = val^m \quad \forall m \in \{ 0, ..., M-1 \} \]
-	\[ c_{M} = val^m * 100  \]
+Cost will come from two source:  
+\begin{itemize} 
+	\item cost of having patients wait ($cw$)
+		\begin{itemize}
+			\item this cost will apply to 2 things: number of patients remaining on the waitlist, and number of patients scheduled in advance
+		\end{itemize}
+	\item cancellation cost ($cc$)
+\end{itemize}
+\[ c(\vec{s}, \vec{a}) = \sum_{dc} cw_{m} pw_{mdc} + \sum_{tdc} cw_{m} ps_{tmdc} + \sum_{tmdc} cc * usc_{tmdc}\]
+Where $cw_{m}$ (wait cost) is computed as follows (where $val$ is an arbitrary number that would allow us to describe cost growth well):
+	\[ cc_{m} = val^m \quad \forall m \in \{ 0, ..., M-1 \} \]
+	\[ cc_{M} = val^m * 100  \]
 The reason there is a very high cost at the last month is because patients are essentially removed if they are not scheduled and they are in the last wait month (in order to be able to have a limit on $m$ while modeling).

### 2021-01-22 Manuscript/Manuscript.tex
finalized updated for friday meeting

@@
 \section{Action Sets}
+
+\subsection{Description}
 At the beginning of each period, decision maker must cancel appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively).
@@
 \end{itemize}
-The actions must satisfy the following constraints:
+
+\subsection{Action Constraints}
 \begin{itemize}
-    \item Total allocated budged must not be exceeded ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
-        \[ \sum_{dc}s_{mdc}U_{pdc} <= (be - bu)\ \quad \forall m, p \]
+    \item Total number of units cannot be exceeded ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
+        \[ \sum_{tdc}(sc_{tmdc} - usc_{tmdc})U_{pdc} <= (be_{mp} - bu_{mp})\ \quad \forall mp \]
 	\item Cannot schedule past waitlist horizon limit
+		\[ sc_{tmdc} = 0 \quad \forall tmdc, \text{where } ((t-1)+m) > T \]
 	\item number of people scheduled/cancelled must be consistent
+		\[ usc_{t0dc} = 0 \quad \forall tdc \]
+		\[ usc_{tmdc} \le ps_{tmdc} \quad \forall t, m \in \{1...M \}, dc \]
+		\[ \sum_{t} sc_{t0dc} \le pe_{dc} \quad \forall dc \]
+		\[ \sum_{t} sc_{tmdc} \le pw_{mdc} + \sum_{t} usc_{tmdc} \quad \forall m \in \{1...M \}, dc \]
 \end{itemize}
@@
 \section{Transition Probabilities}
-There are three sources of uncertainty: 
+
+\subsection{Uncertainty Sources}
 \begin{enumerate}
@@
 		\begin{itemize}
-			\item let's assume $pwfi_{mdc}$ represents an intermediary variable showing the number of patients of complexity $d$, for CPU $c$ entering the waitlist of period $m$ in any way.
-			\item let's assume $pwfo_{mdc}$ represents an intermediary variable showing the number of patients of complexity $d$, for CPU $c$ leaving the waitlist of period $m$  in any way
 			\item let's assume $pwt_{mdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have moved a more complex category.
+It follows binary distribution.
+		\end{itemize}
+
+	\item Transition between patient difficulties within the scheduled list - $ps_{tmdc}$
+		\begin{itemize}
+			\item let's assume $pst_{tmdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have been scheduled into period $t$, that have moved a more complex category.
 It follows binary distribution.
@@
 
-Assume $pe_{dc}$ follows some poisson distribution. \\
-Assume transition within $pw_{mdc}$ follows some binomial distribution with a probability that patient of difficulty $d$ in CPU $c$ moves to a more difficult category at each state transition. \\
-Assume deviation from expected number of PPE units follows a uniform distribution ($bcd_{p}$)\\
-State transitions have the following constraints:
-\begin{itemize}
+\subsection{Transition Constraints}
+\begin{enumerate}
 
@@
 	\item Transition from $\vec{bu}$ to $\vec{bu'}$ - Used Units of PPE
-		\[ bu'_{m-1,p} = bu	_{mp} - \sum_{tdc} ( sc_{t,m-1,dc}U_{pdc} ) + \sum_{tdc} ( usc_{t,m-1,dc}U_{pdc} )  \quad \forall m \in \{2...M\}, p \]
+		\[ bu'_{m-1,p} = bu	_{mp} + \sum_{tdc} ( sc_{t,m-1,dc}U_{pdc} ) - \sum_{tdc} ( usc_{t,m-1,dc}U_{pdc} )  \quad \forall m \in \{2...M\}, p \]
 		\[ bu'_{Mp} = 0 \quad \forall p \]
@@
 		\[ pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} + \sum_{t} usc_{t0dc} \quad \forall dc \]
-		\[ pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + pwt_{m,d-1,c} - pwt_{m,d,c} \quad \forall m \in \{1...M-1 \}, dc \]
-		\[ pw'_{Mdc} = 0 \quad \forall dc \]
+		\[ pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc \]
+		\[ pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} +  \sum_{t, M-1}^{M} usc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}\quad \forall dc \]
 
 	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patients between difficulties/scheduling/cancelling for scheduled appointments
-		\[ ps'_{t-1,m+1,dc} = ps_{tmdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + inflow - outflow \quad \forall t \in {2 ... T},  m \in \{0... M-1 \}, dc \]
+		\[ ps'_{t-1,m+1,dc} = ps_{tmdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc \]
+		\[ ps'_{t-1,Mdc} = \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc} +  \sum_{t, M-1}^{M} usc_{tmdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}\quad \forall t \in \{2...T \}, dc \]
 		\[ ps'_{Tmdc} = 0 \quad \forall mdc \]
-
-\end{itemize}
+\end{enumerate}
 
@@
 \begin{itemize} 
-	\item cost of having patients wait ($cw$)
+	\item cost of waiting ($cw$) (comes from 2 things)
 		\begin{itemize}
-			\item this cost will apply to 2 things: number of patients remaining on the waitlist, and number of patients scheduled in advance
+			\item number of patients remaining on the wait list 
+			\item number of patients scheduled in advance
 		\end{itemize}
-	\item cancellation cost ($cc$)
+	\item cost of canceling ($cc$)
 \end{itemize}
-\[ c(\vec{s}, \vec{a}) = \sum_{dc} cw_{m} pw_{mdc} + \sum_{tdc} cw_{m} ps_{tmdc} + \sum_{tmdc} cc * usc_{tmdc}\]
-Where $cw_{m}$ (wait cost) is computed as follows (where $val$ is an arbitrary number that would allow us to describe cost growth well):
-	\[ cc_{m} = val^m \quad \forall m \in \{ 0, ..., M-1 \} \]
-	\[ cc_{M} = val^m * 100  \]
-The reason there is a very high cost at the last month is because patients are essentially removed if they are not scheduled and they are in the last wait month (in order to be able to have a limit on $m$ while modeling).
-So theoretically, the model should schedule in such a way that people never reach that point.
+\[ c(\vec{s}, \vec{a}) = \sum_{mdc} cw_{m} pw_{mdc} + \sum_{tmdc} cw_{m} (ps_{tmdc} + sc_{tmdc} ) + \sum_{tmdc} cc * usc_{tmdc}\]
+$cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):
+	\[ cw_{m} = val^m \quad \forall m \]
+$cc$ is some arbitrary value
 

### 2021-01-26 Manuscript/Manuscript.tex
updates in model

@@
 \section{State Space}
-State space is defined by current units available for various PPEs for future periods, amount of budget already spent on PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
-\[ \vec{s}  = (\vec{be}, \vec{bu}, \vec{pw}, \vec{pe})\]
+State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
+\[ \vec{s}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})\]
 \begin{itemize}
-    \item $\vec{be} = be_{mp}$ - Expected unist for period $m$, and PPE $p$
-    \item $\vec{bu} = bu_{mp}$ - Used units for period $m$, and PPE $p$
+    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
+    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
     \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
@@
 \subsection{Description}
-At the beginning of each period, decision maker must cancel appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively).
+At the beginning of each period, decision maker must reschedule appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively).
 And decision maker must also schedule patients to surgeries
-\[ \vec{a} = (\vec{sc}, \vec{usc}) \]
+\[ \vec{a} = (\vec{sc}, \vec{rsc}) \]
 \begin{itemize}
     \item $\vec{sc} = sc_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been in wait list for $m$ periods, to schedule in period $t$ ($m$ of 0 stands for people who have just arrived)
-	\item $\vec{usc} = usc_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to cancel from period $t$
+	\item $\vec{rsc} = rsc_{tt'mdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to reschedule from period $t$ to period $t'$
 \end{itemize}
@@
 \begin{itemize}
-    \item Total number of units cannot be exceeded ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
-        \[ \sum_{tdc}(sc_{tmdc} - usc_{tmdc})U_{pdc} <= (be_{mp} - bu_{mp})\ \quad \forall mp \]
-	\item Cannot schedule past waitlist horizon limit
+    \item Total number of PPE units cannot be exceeded  
+    \begin{itemize}
+    	\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
+    	\item ($uv_{tp}$ - goal variable, unit violation for period $t$, of PPE $p$ )
+    \end{itemize}
+        \[ \sum_{mdc}(sc_{tmdc})U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp \]
+	\item Cannot schedule/reschedule past wait list horizon limit
 		\[ sc_{tmdc} = 0 \quad \forall tmdc, \text{where } ((t-1)+m) > T \]
-	\item number of people scheduled/cancelled must be consistent
-		\[ usc_{t0dc} = 0 \quad \forall tdc \]
-		\[ usc_{tmdc} \le ps_{tmdc} \quad \forall t, m \in \{1...M \}, dc \]
+		\[ rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } ((t'-1)+m) > T \]
+	\item Bounds on when reschedules are allowed
+		\[ rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{ 2...T \}, mdc \]
+		\[ rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } t=t' \]
+
+	\item number of people scheduled/rescheduled must be consistent
+		\[ \sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc \]
 		\[ \sum_{t} sc_{t0dc} \le pe_{dc} \quad \forall dc \]
-		\[ \sum_{t} sc_{tmdc} \le pw_{mdc} + \sum_{t} usc_{tmdc} \quad \forall m \in \{1...M \}, dc \]
+		\[ \sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall m \in \{1...M \}, dc \]
 \end{itemize}
@@
 		\begin{itemize}
-			\item let's assume $bed_{md}$ is the random variable that represents the deviation of PPE units from the expectation for the next period only. It follows some uniform distribution.
-			\item let's assume $ben_{d}$ is the default value to be used for expected number of PPE units $p$ per period
+			\item let's assume $ued_{md}$ is the random variable that represents the deviation of PPE units from the expectation for the next period only. It follows some uniform distribution.
+			\item let's assume $uen_{d}$ is the default value to be used for expected number of PPE units $p$ per period
 		\end{itemize}
@@
 	\item Transition from $\vec{bc}$ to $\vec{bc'}$ - Expected Units of PPE
-		\[ be'_{1p} = be_{2p} + bed_{p}\ \quad \forall p \]
-		\[ be'_{m-1,p} = be_{mp}\ \quad \forall m \in \{3...M\}, p \]
-		\[ be'_{Mp} = ben_{d} \quad \forall p \]
+		\[ ue'_{1p} = ue_{2p} + ued_{p}\ \quad \forall p \]
+		\[ ue'_{m-1,p} = ue_{mp}\ \quad \forall m \in \{3...M\}, p \]
+		\[ ue'_{Mp} = uen_{d} \quad \forall p \]
 
-	\item Transition from $\vec{bu}$ to $\vec{bu'}$ - Used Units of PPE
-		\[ bu'_{m-1,p} = bu	_{mp} + \sum_{tdc} ( sc_{t,m-1,dc}U_{pdc} ) - \sum_{tdc} ( usc_{t,m-1,dc}U_{pdc} )  \quad \forall m \in \{2...M\}, p \]
-		\[ bu'_{Mp} = 0 \quad \forall p \]
+	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Units of PPE
+		\[ uu'_{t-1,p} = uu	_{tp} + \sum_{mdc} ( sc_{t-1,mdc}U_{pdc} ) - \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc})  \quad \forall t \in \{2...T\}, p \]
+		\[ uu'_{Tp} = 0 \quad \forall p \]
 
@@
 	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
-		\[ pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} + \sum_{t} usc_{t0dc} \quad \forall dc \]
-		\[ pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc \]
-		\[ pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} +  \sum_{t, M-1}^{M} usc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}\quad \forall dc \]
+		\[ pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} \quad \forall dc \]
+		\[ pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc \]
+		\[ pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}\quad \forall dc \]
 
 	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patients between difficulties/scheduling/cancelling for scheduled appointments
-		\[ ps'_{t-1,m+1,dc} = ps_{tmdc} - \sum_{t} sc_{tmdc} + \sum_{t} usc_{tmdc} + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc \]
-		\[ ps'_{t-1,Mdc} = \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc} +  \sum_{t, M-1}^{M} usc_{tmdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}\quad \forall t \in \{2...T \}, dc \]
+		\[ ps'_{t-1,m+1,dc} = ps_{tmdc} +  \sum_{t} sc_{tmdc} - 
+		\sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) \] 
+		\[+ pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc \]
+		\[ ps'_{t-1,Mdc} = \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc} -
+		\sum_{t',M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) + \sum_{t,M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) \]
+		\[ + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}\quad \forall t \in \{2...T \}, dc \]
 		\[ ps'_{Tmdc} = 0 \quad \forall mdc \]
@@
 	\item cost of waiting ($cw$) (comes from 2 things)
-		\begin{itemize}
-			\item number of patients remaining on the wait list 
-			\item number of patients scheduled in advance
+	\item cost of canceling ($cc$)
+	\item goal variable (to eliminate constraint violation, but still allow it if necessary)
 \end{itemize}
-	\item cost of canceling ($cc$)
-\end{itemize}
-\[ c(\vec{s}, \vec{a}) = \sum_{mdc} cw_{m} pw_{mdc} + \sum_{tmdc} cw_{m} (ps_{tmdc} + sc_{tmdc} ) + \sum_{tmdc} cc * usc_{tmdc}\]
+\[ c(\vec{s}, \vec{a}) = \sum_{mdc} cw_{m} (pw_{mdc}- \sum_{t} sc_{tmdc}) + cc \sum_{tt`mdc} rsc_{tt'mdc} + M (uv_{tp})\]
 $cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):

### 2021-02-01 Manuscript/Manuscript.tex
small change go brrrrrrrrrrrrrrrrrrr
added assumptions

@@
 \author{KV}
-\date{December 2020}
+\date{February 2021}
 
@@
 \maketitle
+
+\section{Assumptions} 
+\begin{itemize}
+	\item Assume all new patients are arriving at the beginning of the period 
+	\begin{itemize}
+		\item Assume arrivals follow poisson distribution
+	\end{itemize}
+
+	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($TL$). 
+	\begin{itemize}
+		\item Let's assume our limit is 10 periods, there is no difference in terms of cost between patients who has been waiting for 1 period and patients waiting 9 period for their appointment (assuming they are the same category).
+		\item However, if a patient waits for 11 period for their appointment there should be some kind of penalty for the wait
+		\item The penalty comes from increasing patient complexity. Higher complexities require more resources and are thus more costly overall in the system
+	\end{itemize}
+
+	\item We assume patient complexity transitions follow binary distribution - each period a patient can become more complex with a certain probability
+		\begin{itemize}
+			\item While patient is waiting less that $TL$, the transition probability is 0.
+			\item After $TL$, transition probability is some arbitrary percentage
+		\end{itemize}
+
+	\item It is assumed if a patient is scheduled in period one, it means they are served "immediately", regardless if in practice the appointment is at the beginning or end of the period.
+	\item We distinguish between two types of reschedules: good and bad reschedules
+	\begin{itemize}
+		\item Good reschedules are reschedules where a patient is rescheduled to an earlier period (they improve cost)
+		\item Bad reschedules are reschedules where a patient is rescheduled to a later period (they worsen cost)
+	\end{itemize}
+
+	\item We assume that only specific reschedules are allowed (to simplify the model, and remove  redundancies)
+		\begin{itemize}
+			\item Good reschedules are allowed from any period after 2 into period 1
+			\item Bad reschedules are only allowed from period 1 to period 2
+		\end{itemize}
+
+	\item It is assumed that there is a certain default expected number of PPE units available for all periods
+		\begin{itemize}
+			\item However, in the period 1, there is some random deviation from the expected number of units
+			\item This random deviation follows some uniform distribution
+		\end{itemize}
+\end{itemize}
 
@@
 And decision maker must also schedule patients to surgeries
-\[ \vec{a} = (\vec{sc}, \vec{rsc}) \]
+\[ \vec{a} = (\vec{sc}, \vec{rsc}, \vec{uv}) \]
 \begin{itemize}
@@
 	\item $\vec{rsc} = rsc_{tt'mdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to reschedule from period $t$ to period $t'$
+	\item $uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
 \end{itemize}
@@
     	\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
-    	\item ($uv_{tp}$ - goal variable, unit violation for period $t$, of PPE $p$ )
     \end{itemize}
         \[ \sum_{mdc}(sc_{tmdc})U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp \]
-	\item Cannot schedule/reschedule past wait list horizon limit
-		\[ sc_{tmdc} = 0 \quad \forall tmdc, \text{where } ((t-1)+m) > T \]
-		\[ rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } ((t'-1)+m) > T \]
 	\item Bounds on when reschedules are allowed
-		\[ rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{ 2...T \}, mdc \]
+		\[ rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \]
+		\[ rsc_{tt'mdc} = 0 \quad \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc \]
 		\[ rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } t=t' \]

### 2021-02-05 Manuscript/Manuscript.tex
minor updates & new documents

@@
 			\item While patient is waiting less that $TL$, the transition probability is 0.
-			\item After $TL$, transition probability is some arbitrary percentage
+			\item After $TL$, transition probability is some arbitrary value
 		\end{itemize}
@@
 	\begin{itemize}
-		\item Good reschedules are reschedules where a patient is rescheduled to an earlier period (they improve cost)
-		\item Bad reschedules are reschedules where a patient is rescheduled to a later period (they worsen cost)
+		\item Good reschedules are reschedules where a patient is rescheduled to an earlier period
+		\item Bad reschedules are reschedules where a patient is rescheduled to a later period
 	\end{itemize}
@@
 \end{itemize}
-\[ c(\vec{s}, \vec{a}) = \sum_{mdc} cw_{m} (pw_{mdc}- \sum_{t} sc_{tmdc}) + cc \sum_{tt`mdc} rsc_{tt'mdc} + M (uv_{tp})\]
+\[ c(\vec{s}, \vec{a}) = \sum_{mdc} cw_{m} (pw_{mdc}- \sum_{t} sc_{tmdc}) + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} 
+- cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + M (uv_{tp})\]
 $cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):

### 2021-02-09 Manuscript/Manuscript.tex
starting on ADP

@@
 \documentclass{article}
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amsmath}
+\usepackage{xcolor}
+
 \geometry{margin=1in}
@@
 
-	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($TL$). 
+	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($Tl$). 
 	\begin{itemize}
@@
 		\begin{itemize}
-			\item While patient is waiting less that $TL$, the transition probability is 0.
-			\item After $TL$, transition probability is some arbitrary value
+			\item While patient is waiting less that $Tl$, the transition probability is 0.
+			\item After $Tl$, transition probability is some arbitrary value
 		\end{itemize}
@@
 
-\section{Decision Epochs}
+\section{MDP Model}
+\subsection{Decision Epochs}
 Decisions are made at the beginning of each time period (will be weeks)
 
-\section{State Space}
+\subsection{State Space}
 State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
-\[ \vec{s}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})\]
+\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \]
 \begin{itemize}
@@
 
-\section{Action Sets}
+\subsection{Action Sets}
 
-\subsection{Description}
+\subsubsection{Description}
 At the beginning of each period, decision maker must reschedule appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively).
 And decision maker must also schedule patients to surgeries
-\[ \vec{a} = (\vec{sc}, \vec{rsc}, \vec{uv}) \]
+\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}) \] 
 \begin{itemize}
@@
 
-\subsection{Action Constraints}
+\subsubsection{Action Constraints}
 \begin{itemize}
@@
     \end{itemize}
-        \[ \sum_{mdc}(sc_{tmdc})U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp \]
+        \begin{equation} 
+			\sum_{mdc}(sc_{tmdc})U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp
+		\end{equation}
+
 	\item Bounds on when reschedules are allowed
-		\[ rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \]
-		\[ rsc_{tt'mdc} = 0 \quad \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc \]
-		\[ rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } t=t' \]
+		\begin{equation}  
+			rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc 
+		\end{equation} 
+		\begin{equation}  
+			rsc_{tt'mdc} = 0 \quad \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc 
+		\end{equation} 
+		\begin{equation}  
+			rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } t=t' 
+		\end{equation}
+
+	\item Cap on max schedule/reschedule wait time
+		\begin{equation}  
+			\sum_{tmdc} sc_{tmdc} = 0 \quad \text{where } t+m-1 > 2Tl 
+		\end{equation} 
+		\begin{equation}  
+			\sum_{tt'mdc} rsc_{tt'mdc} \quad \text{where } t'+m+1 > 2Tl 
+		\end{equation}
 
 	\item number of people scheduled/rescheduled must be consistent
-		\[ \sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc \]
-		\[ \sum_{t} sc_{t0dc} \le pe_{dc} \quad \forall dc \]
-		\[ \sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall m \in \{1...M \}, dc \]
+		\begin{equation}  
+			\sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc 
+		\end{equation} 
+		\begin{equation}  
+			\sum_{t} sc_{t0dc} \le pe_{dc} \quad \forall dc 
+		\end{equation} 
+		\begin{equation}  
+			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall m \in \{1...M \}, dc 
+		\end{equation}
+
 \end{itemize}
 
-\section{Transition Probabilities}
+\subsection{Transition Probabilities}
 
-\subsection{Uncertainty Sources}
+\subsubsection{Uncertainty Sources}
 \begin{enumerate}
@@
 
-\subsection{Transition Constraints}
+\subsubsection{Transition Constraints}
 \begin{enumerate}
 
-	\item Transition from $\vec{bc}$ to $\vec{bc'}$ - Expected Units of PPE
-		\[ ue'_{1p} = ue_{2p} + ued_{p}\ \quad \forall p \]
-		\[ ue'_{m-1,p} = ue_{mp}\ \quad \forall m \in \{3...M\}, p \]
-		\[ ue'_{Mp} = uen_{d} \quad \forall p \]
+	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Units of PPE
+		\begin{equation}  
+			ue'_{1p} = ue_{2p} + ued_{p}\ \quad \forall p 
+		\end{equation} 
+		\begin{equation}  
+			ue'_{m-1,p} = ue_{mp}\ \quad \forall m \in \{3...M\}, p
+		 \end{equation} 
+		\begin{equation}  
+			ue'_{Mp} = uen_{d} \quad \forall p 
+		\end{equation}
 
 	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Units of PPE		
-		\[ uu'_{t-1,p} = uu	_{tp} + \sum_{mdc} ( sc_{t-1,mdc}U_{pdc} ) - \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc})  \quad \forall t \in \{2...T\}, p \]
-		\[ uu'_{Tp} = 0 \quad \forall p \]
+		\begin{align} \begin{split}  
+			uu'_{t-1,p} = &  uu	_{tp} + \sum_{mdc} ( {\color{red} sc_{t-1 \text{ or } tmdc} } U_{pdc} ) - \\ 
+								&	- \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) \quad \forall t \in \{2...T\}, p 
+		\end{split} \end{align}
+		\begin{equation}  
+			uu'_{Tp} = 0 \quad \forall p 
+		\end{equation}
 
 	\item Transition from $\vec{pe}$ to $\vec{pe'}$ - Expected number of patients for this month
-		\[\ pe_{dc} = pea_{dc} \quad \forall dc \]
+		\begin{equation} 
+			\ pe_{dc} = pea_{dc} \quad \forall dc 
+		\end{equation}
 
 	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
-		\[ pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} \quad \forall dc \]
-		\[ pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc \]
-		\[ pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}\quad \forall dc \]
+		\begin{equation}  
+			pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} \quad \forall dc 
+		\end{equation} 
+		\begin{equation}  
+			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc 
+		\end{equation} 
+		\begin{equation}  
+			pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - 
+			\sum_{M-1}^{M} pwt_{mdc}\quad \forall dc 
+		\end{equation}
 
-	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patients between difficulties/scheduling/cancelling for scheduled appointments
-		\[ ps'_{t-1,m+1,dc} = ps_{tmdc} +  \sum_{t} sc_{tmdc} - 
-		\sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) \] 
-		\[+ pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc \]
-		\[ ps'_{t-1,Mdc} = \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc} -
-		\sum_{t',M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) + \sum_{t,M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) \]
-		\[ + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}\quad \forall t \in \{2...T \}, dc \]
-		\[ ps'_{Tmdc} = 0 \quad \forall mdc \]
+	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts between difficulties/scheduling/cancelling for scheduled appointments
+		\begin{align}  \begin{split}
+			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) +\\ 
+										& + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc 
+		\end{split} \end{align} 
+		\begin{align} \begin{split}  
+			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t',M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) + \\
+									& \sum_{t,M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
+									\quad \forall t \in \{2...T \}, dc 
+		\end{split} \end{align}		
+		\begin{equation}  
+			ps'_{Tmdc} = 0 \quad \forall mdc 
+		\end{equation} 
 \end{enumerate}
 
-\section{Costs}
+\subsection{Costs}
 Cost will come from two source:  
@@
 \end{itemize}
-\[ c(\vec{s}, \vec{a}) = \sum_{mdc} cw_{m} (pw_{mdc}- \sum_{t} sc_{tmdc}) + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} 
-- cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + M (uv_{tp})\]
+
+\begin{align} \begin{split}  
+	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = & \sum_{mdc} cw_{m} (pw_{mdc} - \sum_{t} sc_{tmdc}) +  \\
+		& + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} - cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + \\ 
+		& + M (uv_{tp})
+\end{split} \end{align} 
 $cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):
-	\[ cw_{m} = val^m \quad \forall m \]
+	\begin{equation}  cw_{m} = val^m \quad \forall m \end{equation} 
 $cc$ is some arbitrary value
 
+\section{LP Model}
+
+Given a full MDP model, the equivalent LP would look as follows 
+(Note: there is a lot left out.
+$\vec{C}$ is defined above, all states, actions, and next states are all defined above).
+Probability distribution is not explicitly defined, but I am not sure if it is necessary
+\begin{equation}
+	\max_{\vec{v}} \sum \alpha (\vec{S}) v(\vec{S}) 
+\end{equation}
+
+subject to
+\begin{equation}
+	\vec{C} + \gamma \sum_{\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \quad \forall \vec{S} \vec{A}
+\end{equation}
+
+Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
+\begin{align} \begin{split}
+	v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) =  & \beta^0 +
+		\sum_{tp} \beta_{tp}^{ue} ue_{tp} +
+		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + \\
+		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
+		\sum_{dc} \beta_{dc}^{pe} pe_{dc} + 
+		\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
+\end{split} \end{align}
+
+This gives the following LP
+\begin{equation}
+	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
+\end{equation}
+Subject to:
+\begin{align*}
+	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) +  & \\
+	& \gamma \sum_{\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  * &  \\
+		\beta^{0} \quad & v \Bigg( \beta^{0} + \\
+		\beta^{ue} \quad & \sum_{p} \beta_{1p}^{ue} (ue_{2p} + {\color{red} ued_{p}}) + \sum_{m=2,p}^{M-1} \beta_{mp}^{ue} ue_{m+1,p} + \sum_{p} \beta_{Mp} uen_{d} + \\
+		\beta^{uu} \quad & \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - \sum_{t''mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{t''mdc} (rsc_{t,t'+1,mdc} U_{pdc}) \bigg) \\
+		\beta^{uu} \quad & \sum_{p} \beta_{Tp} * 0 + \\
+		\beta^{pe} \quad & \sum_{dc} \beta_{dc}^{pe} {\color{red} pea_{dc}}+ \\
+		\beta^{pw} \quad & \sum_{dc} \beta_{1dc}^{pw} (pe_{dc} - \sum_{t} sc_{t0dc}) + \\
+		\beta^{pw} \quad & \sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} (pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc}) \dots + \\
+		\beta^{ps} \quad & + \\
+		& \Bigg) \\
+	& \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
+\end{align*}
+
 \end{document}

### 2021-02-12 Manuscript/Manuscript.tex
working on expectation equations

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{xcolor}
@@
 \maketitle
+
+\section{Questions/Comments}
+\begin{itemize}
+	\item \textbf{COMMENT}: In constraints for transition between $uu$ and $uu'$ - missing change in usage due to complexity transition
+	\item \textbf{QUESTION}: How to incorporate goal variable $uv$ properly into transition, ADP, etc.?
+	\item \textbf{QUESTION}: Does the ADP look correct to you so far?
+\end{itemize}
 
@@
 \subsubsection{Transition Constraints}
+
+\textit{\textbf{FROM CONSTRAINT SET \#2 MISSING RESOURCE USAGE DUE TO TRANSITION IN DIFFICULTIES}}
 \begin{enumerate}
@@
 		\begin{equation}  
-			ue'_{m-1,p} = ue_{mp}\ \quad \forall m \in \{3...M\}, p
+			ue'_{t-1,p} = ue_{tp}\ \quad \forall t \in \{3...T\}, p
 		 \end{equation} 
 		\begin{equation}  
-			ue'_{Mp} = uen_{d} \quad \forall p 
+			ue'_{Tp} = uen_{d} \quad \forall p 
 		\end{equation}
@@
 		\begin{align} \begin{split}  
-			uu'_{t-1,p} = &  uu	_{tp} + \sum_{mdc} ( {\color{red} sc_{t-1 \text{ or } tmdc} } U_{pdc} ) - \\ 
+			uu'_{t-1,p} = &  uu	_{tp} + \sum_{mdc} ( sc_{tmdc} U_{pdc} ) - \\ 
 								&	- \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) \quad \forall t \in \{2...T\}, p 
@@
 		\begin{align}  \begin{split}
-			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) +\\ 
+			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'} rsc_{tt'mdc} + \sum_{t} rsc_{tt'mdc} +\\ 
 										& + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc 
@@
 		\begin{align} \begin{split}  
-			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t',M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) + \\
-									& \sum_{t,M-1,dc}^M (rsc_{tt'mdc} U_{pdc}) + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
+			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t'M-1}^M rsc_{tt'mdc} + \\
+									& \sum_{t,M-1}^M rsc_{tt'mdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
 									\quad \forall t \in \{2...T \}, dc 
@@
 \begin{align*}
-	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) +  & \\
-	& \gamma \sum_{\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  * &  \\
+	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) +  \\ 
+	& \gamma \sum_{\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
 		\beta^{0} \quad & v \Bigg( \beta^{0} + \\
-		\beta^{ue} \quad & \sum_{p} \beta_{1p}^{ue} (ue_{2p} + {\color{red} ued_{p}}) + \sum_{m=2,p}^{M-1} \beta_{mp}^{ue} ue_{m+1,p} + \sum_{p} \beta_{Mp} uen_{d} + \\
-		\beta^{uu} \quad & \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - \sum_{t''mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{t''mdc} (rsc_{t,t'+1,mdc} U_{pdc}) \bigg) \\
-		\beta^{uu} \quad & \sum_{p} \beta_{Tp} * 0 + \\
-		\beta^{pe} \quad & \sum_{dc} \beta_{dc}^{pe} {\color{red} pea_{dc}}+ \\
-		\beta^{pw} \quad & \sum_{dc} \beta_{1dc}^{pw} (pe_{dc} - \sum_{t} sc_{t0dc}) + \\
-		\beta^{pw} \quad & \sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} (pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc}) \dots + \\
-		\beta^{ps} \quad & + \\
+		\beta^{ue} \quad & 
+				\sum_{p} \beta_{1p}^{ue} (ue_{2p} + ued_{p}) + 
+				\sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
+				\sum_{p} \beta_{Tp}^{ue} uen_{d} + \\
+		\beta^{uu} \quad & 
+				\sum_{tp}^{T-1} \beta_{tp}^{uu} 
+				\bigg( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
+				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc}) \bigg) \\
+		\beta^{uu} \quad & 
+			\sum_{p} \beta_{Tp} * 0 + \\
+		\beta^{pe} \quad & 
+			\sum_{dc} \beta_{dc}^{pe} {\color{red} pea_{dc}}+ \\
+		\beta^{pw} \quad & 
+			\sum_{dc} \beta_{1dc}^{pw} 
+			(pe_{dc} - \sum_{t} sc_{t0dc}) + \\
+		\beta^{pw} \quad & 
+			\sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} 
+			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) + \\
+		\beta^{pw} \quad & 
+			\sum_{dc} \beta_{Mdc}^{pw} 
+			(\sum_{M-1}^{M} pw_{mdc} - \sum_{M-1,t}^{M} sc_{tmdc} + 
+			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) + \\
+		\beta^{ps} \quad & 
+			\sum_{mdc} \beta_{Tmdc}^{ps} * 0 + \\
+		\beta^{ps} \quad & 
+			\sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
+			\bigg( ps_{t+1,m-1,dc} - \sum_{t} sc_{t+1,m-1,dc} + 
+			pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc} - \\ 
+			&- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \bigg) + \\
+			& \text{where }m=0 \text{ is patients who just arrived} \\ 
+		\beta^{ps} \quad & 
+			\sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
+			\bigg( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
+			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} + \\ 
+			&- \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \bigg) \\
+			& \text{where }m=0 \text{ is patients who just arrived} \\ 
 		& \Bigg) \\
-	& \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
+	& \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
 \end{align*}
 
+\newpage 
+Steps for converting the mega constraint $v(\vec{S'})$ into expectation and merging it with $v({\vec{S}})$:
+\begin{itemize}
+	\item $\beta^{0}$ - no adjustments for expectation for $v(\vec{S'})$ 
+	\begin{equation*}
+		\beta^{0} - \gamma \beta^{0} = (1-\gamma) \beta^{0}
+	\end{equation*}
+
+	\item $\beta_{tp}^{ue}$
+	\begin{equation*}
+		E[ued_{p}] = 0 \quad \therefore \quad
+		\sum_{p} \beta_{1p}^{ue} (ue_{2p} + ued_{p}) \rightarrow 
+		\sum_{p} \beta_{1p}^{ue} (ue_{2p}) \rightarrow
+		\sum \beta_{tp}^{ue} uen_{d}
+	\end{equation*}
+	\begin{equation*}
+		\sum_{tp} \beta_{tp}^{ue} ue_{tp} - \gamma (\sum_{tp} \beta_{tp}^{ue} uen_{d}) = 
+		(1-\gamma) \beta_{tp}^{ue} \sum_{tp} (ue_{tp} - uen_{d})
+	\end{equation*}
+
+	\item $\beta_{tp}^{uu}$ - no adjustments for expectation
+	\begin{equation*}
+		uu_{Tp} = 0 \quad \therefore \quad \beta_{Tp}^{uu} uu_{Tp} = 0
+	\end{equation*}
+	\begin{equation*}
+		\sum_{tp}^{T-1} \beta_{tp}^{uu} uu_{tp} - \gamma \sum_{tp}^{T-1} \beta_{tp}^{uu} 
+		\bigg( uu_{t+1p} + \sum_{mdc} (sc_{t+1mdc}U)  - \sum_{tmdc} (rsc_{t+1t'mdc} U) + \sum_{t'mdc} (rsc_{tt'+1mdc} U) \bigg)
+	\end{equation*}
+	\begin{equation*}
+		\sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( 
+			uu_{tp}	 - \gamma uu_{t} - 
+			\gamma U_{pdc} \Big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \Big) 
+		\bigg)
+	\end{equation*}
+
+	\item $\beta_{dc}^{pe}$
+	\begin{equation*}
+		\sum_{dc} \beta_{dc}^{pe} pe_{dc} - \gamma \sum_{dc} \beta_{dc}^{pe} E[pea_{dc}] = 
+		\sum_{dc} \beta_{dc}^{pe} (pe_{dc} - \gamma E[pea_{dc}])
+	\end{equation*}
+
+	\item $\beta_{mdc}^{pw}$ - Let's assume $pwp_{mdc}$ - is the probability of a patient transitioning to a higher complexity
+	\begin{equation*}
+		E[pwt_{mdc}] = pw_{mdc} pwp_{mdc}		
+	\end{equation*}
+
+\end{itemize}
+
 \end{document}

### 2021-02-14 Manuscript/Manuscript.tex
finalized expectation almost done dual

@@
 \usepackage{xcolor}
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks,
+    citecolor=black,
+    filecolor=black,
+    linkcolor=black,
+    urlcolor=black
+}
 
@@
 \maketitle
+\tableofcontents
 
 \section{Questions/Comments}
+
+\subsection{Questions}
 \begin{itemize}
-	\item \textbf{COMMENT}: In constraints for transition between $uu$ and $uu'$ - missing change in usage due to complexity transition
-	\item \textbf{QUESTION}: How to incorporate goal variable $uv$ properly into transition, ADP, etc.?
-	\item \textbf{QUESTION}: Does the ADP look correct to you so far?
+	\item  How to incorporate goal variable $uv$ properly into transition, ADP, etc.?
+	\item Does the ADP look correct to you so far?
+	\item Is it safe to remove $\beta_{Tp}^{uu}$ and $\beta_{Tmdc}^{ps}$ since they are \textit{supposed} to be zero always
+\end{itemize}
+
+\subsection{Comments}
+\begin{itemize}
+	\item In constraints for transition between $uu$ and $uu'$ - missing change in usage due to complexity transition
 \end{itemize}
@@
 			uu'_{t-1,p} = &  uu	_{tp} + \sum_{mdc} ( sc_{tmdc} U_{pdc} ) - \\ 
-								&	- \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) \quad \forall t \in \{2...T\}, p 
+								&	- \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) + \\ 
+								& 	+ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})  \quad \forall t \in \{2...T\}, p  
 		\end{split} \end{align}
@@
 
+\subsection{Full LP} 
 Given a full MDP model, the equivalent LP would look as follows 
@@
 \begin{equation}
-	\vec{C} + \gamma \sum_{\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \quad \forall \vec{S} \vec{A}
+	c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
 \end{equation}
 
+\subsection{Full ADP LP }
 Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
@@
 \begin{align*}
-	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) +  \\ 
-	& \gamma \sum_{\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
-		\beta^{0} \quad & v \Bigg( \beta^{0} + \\
-		\beta^{ue} \quad & 
-				\sum_{p} \beta_{1p}^{ue} (ue_{2p} + ued_{p}) + 
+	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
+		& * \Bigg( \beta^{0} +
+		\bigg( \sum_{p} \beta_{1p}^{ue} (ue_{2p} + ued_{p}) + 
 				\sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
-				\sum_{p} \beta_{Tp}^{ue} uen_{d} + \\
-		\beta^{uu} \quad & 
-				\sum_{tp}^{T-1} \beta_{tp}^{uu} 
-				\bigg( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
-				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc}) \bigg) \\
-		\beta^{uu} \quad & 
-			\sum_{p} \beta_{Tp} * 0 + \\
-		\beta^{pe} \quad & 
-			\sum_{dc} \beta_{dc}^{pe} {\color{red} pea_{dc}}+ \\
-		\beta^{pw} \quad & 
-			\sum_{dc} \beta_{1dc}^{pw} 
-			(pe_{dc} - \sum_{t} sc_{t0dc}) + \\
-		\beta^{pw} \quad & 
-			\sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} 
-			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) + \\
-		\beta^{pw} \quad & 
-			\sum_{dc} \beta_{Mdc}^{pw} 
+				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) +
+		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
+		& \bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
+				\Big( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
+				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc})  + \\ 
+				& \quad \quad \quad \quad \quad \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) \Big) \bigg) +  \\
+		& \bigg( \sum_{dc} \beta_{dc}^{pe} pea_{dc} \bigg) + 
+			\bigg( \sum_{dc} \beta_{1dc}^{pw} (pe_{dc} - \sum_{t} sc_{t0dc}) \bigg) + \\
+		&  \bigg( \sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} 
+			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) \bigg) + \\
+		& \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
 			(\sum_{M-1}^{M} pw_{mdc} - \sum_{M-1,t}^{M} sc_{tmdc} + 
-			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) + \\
-		\beta^{ps} \quad & 
-			\sum_{mdc} \beta_{Tmdc}^{ps} * 0 + \\
-		\beta^{ps} \quad & 
-			\sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
-			\bigg( ps_{t+1,m-1,dc} - \sum_{t} sc_{t+1,m-1,dc} + 
+			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) \bigg) + \\
+		& \bigg( \sum_{mdc} \beta_{Tmdc}^{ps} * 0  \bigg) + \\
+		& \bigg( \sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
+			\Big( ps_{t+1m-1dc} - \sum_{t} sc_{t+1,m-1,dc} + 
 			pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc} - \\
-			&- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \bigg) + \\
-			& \text{where }m=0 \text{ is patients who just arrived} \\ 
-		\beta^{ps} \quad & 
-			\sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
-			\bigg( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
-			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} + \\ 
-			&- \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \bigg) \\
-			& \text{where }m=0 \text{ is patients who just arrived} \\ 
-		& \Bigg) \\
-	& \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
+		& \quad \quad \quad \quad \quad \quad  \quad \quad- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \Big) \bigg) + \\
+		& \bigg( \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
+			\Big( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
+			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} - \\ 
+			& \quad \quad \quad \quad \quad \quad \quad - \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \Big) \bigg) \\
+		& \Bigg) \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
 \end{align*}
+\begin{equation*}
+	\vec{\beta} \ge 0 \quad \forall \beta
+\end{equation*}
 
-\newpage 
+\subsection{Expectation ADP LP}
 Steps for converting the mega constraint $v(\vec{S'})$ into expectation and merging it with $v({\vec{S}})$:
@@
 	\begin{equation*}
-		\beta^{0} - \gamma \beta^{0} = (1-\gamma) \beta^{0}
+		\beta^{0} - \gamma \beta^{0} = \color{red} (1-\gamma) \beta^{0}
 	\end{equation*}
@@
 		\sum_{tp} \beta_{tp}^{ue} ue_{tp} - \gamma (\sum_{tp} \beta_{tp}^{ue} uen_{d}) = 
-		(1-\gamma) \beta_{tp}^{ue} \sum_{tp} (ue_{tp} - uen_{d})
+		\color{red} (1-\gamma) \sum_{tp} \beta_{tp}^{ue} (ue_{tp} - uen_{d})
 	\end{equation*}
@@
 	\begin{equation*}
-		\sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( 
-			uu_{tp}	 - \gamma uu_{t} - 
-			\gamma U_{pdc} \Big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \Big) 
+		\color{red} \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( 
+			uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) + 
+			U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big)
 		\bigg)
@@
 		\sum_{dc} \beta_{dc}^{pe} pe_{dc} - \gamma \sum_{dc} \beta_{dc}^{pe} E[pea_{dc}] = 
-		\sum_{dc} \beta_{dc}^{pe} (pe_{dc} - \gamma E[pea_{dc}])
+		\color{red} \sum_{dc} \beta_{dc}^{pe} (pe_{dc} - \gamma E[pea_{dc}])
 	\end{equation*}
@@
 	\end{equation*}
+	{ \color{red} \begin{align*}
+		\Bigg( \sum _{dc} \beta_{1dc}^{pw}& ( pw_{1dc} - \gamma (pe_{dc} - \sum_{t} sc_{t0dc})) + \\
+		\sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} & ( pw_{mdc} - \gamma 
+			\big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) + \\
+		\sum_{dc} \beta_{Mdc}^{pw} & ( pw_{Mdc} - \gamma \sum_{M-1}^{M}
+			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Bigg)
+	\end{align*} }
+
+	\item $\beta_{mdc}^{pw}$
+	\begin{equation*}
+		E[pst_{tmdc}] = ps_{tmdc} pwp_{mdc}		
+	\end{equation*}
+	{ \color{red} \begin{align*}
+		\Bigg( \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} & 
+			\bigg( ps_{tmdc} - 
+				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} + \\ 
+				&  - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) + \\
+		\sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} & 
+			\bigg( ps_{tMdc} - 
+				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} + \\ 
+				&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \Bigg)
+	\end{align*} }
 
@@
 
+Let's say $E[V]$ is the addition of all the red parts above. In that case the ADP model converted to expectation would look as follows:
+\begin{equation}
+	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + 
+		\sum \beta^{pe} E[pe] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
+\end{equation}
+Subject to:
+\begin{equation}
+	E[V] \le c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) \quad \forall \vec{S} \vec{A} 
+\end{equation}
+
+\subsection{Dual of ADP LP}
+Converting to Dual
+\begin{equation}
+	\min_{w} \sum_{\vec{S} \vec{A}} w(\vec{S} \vec{A}) c(\vec{S} \vec{A})
+\end{equation}
+Subject To:
+	\begin{equation}
+		\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) \ge 1 
+	\end{equation}
+	\begin{equation}
+		\sum_{\vec{S}\vec{A}}\vec{w} \Big( (1-\gamma) (ue_{tp} - uen_{tp}) \Big) \ge E[ue_{tp}] \quad \forall tp
+	\end{equation}	
+	\begin{multline}
+		\sum_{\vec{S}\vec{S}} \vec{w} \bigg( 
+			uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) + \\ 
+			U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big)
+		\bigg) \\
+		\quad \forall T \in \{1...T-1\}p
+	\end{multline}
+	\begin{equation}
+		\sum_{\vec{S}\vec{A}} \vec{w} (pe_{dc} - \gamma E[pea_{dc}])  \ge E[pe_{dc}] \quad \forall dc
+	\end{equation}
+	\begin{equation}
+		w \ge 0 \quad \forall w
+	\end{equation}
+
+\subsection{Finding most violated constraints of ADP LP}
+
 \end{document}

### 2021-03-01 Manuscript/Manuscript.tex
started implementation

@@
     colorlinks,
-    citecolor=black,
-    filecolor=black,
-    linkcolor=black,
-    urlcolor=black
+    linkcolor={red!50!black},
+    citecolor={blue!50!black},
+    urlcolor={blue!80!black}
 }
@@
 \begin{itemize}
-	\item  How to incorporate goal variable $uv$ properly into transition, ADP, etc.?
-	\item Does the ADP look correct to you so far?
-	\item Is it safe to remove $\beta_{Tp}^{uu}$ and $\beta_{Tmdc}^{ps}$ since they are \textit{supposed} to be zero always
+	\item  NEED TO MOVE $uv$ TO STATES AND ADJUST ALL THE RELEVANT EQUATIONS FOR IT
 \end{itemize}
@@
 State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
-\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \]
+\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{pe}, \vec{ps}) \]
 \begin{itemize}
@@
     \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
+    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
     \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
@@
 \subsubsection{Action Constraints}
+\label{action constraints}
 \begin{itemize}
@@
 		\end{equation} 
-
 \end{itemize}
@@
 
-	\item Amout of expected units of PPE resource for the next time period - $bc_{1dc}$
+	\item Amout of expected units of PPE resource for the next time period - $ue_{1p}$
 		\begin{itemize}
-			\item let's assume $ued_{md}$ is the random variable that represents the deviation of PPE units from the expectation for the next period only. It follows some uniform distribution.
+			\item let's assume $ued_{d}$ is the random variable that represents the deviation of PPE units from the expectation for the next period only. It follows some uniform distribution.
 			\item let's assume $uen_{d}$ is the default value to be used for expected number of PPE units $p$ per period
@@
 
-\textit{\textbf{FROM CONSTRAINT SET \#2 MISSING RESOURCE USAGE DUE TO TRANSITION IN DIFFICULTIES}}
 \begin{enumerate}
@@
 		\begin{equation}  
-			ue'_{Tp} = uen_{d} \quad \forall p 
+			ue'_{Tp} = uen_{p} \quad \forall p 
 		\end{equation}
@@
 			uu'_{Tp} = 0 \quad \forall p 
+		\end{equation}
+
+	\item Transition from $\vec{uv}$ to $\vec{uv'}$ - Violation of PPE units
+	\begin{equation}
+		uv'_{tp} \ge uu'_{tp} - ue'_{tp} \quad \forall tp
+	\end{equation}
+	\begin{equation}
+		uv'_{tp} \ge 0 \quad \forall tp
+	\end{equation}
+	\begin{equation}
+		uv'_{tp} = \max \{0, uu'_{tp} - ue'_{tp} \} \quad \forall tp
 	\end{equation}
@@
 		\sum_{p} \beta_{1p}^{ue} (ue_{2p}) \rightarrow
-		\sum \beta_{tp}^{ue} uen_{d}
+		\sum \beta_{tp}^{ue} uen_{p}
 	\end{equation*}
 	\begin{equation*}
-		\sum_{tp} \beta_{tp}^{ue} ue_{tp} - \gamma (\sum_{tp} \beta_{tp}^{ue} uen_{d}) = 
-		\color{red} (1-\gamma) \sum_{tp} \beta_{tp}^{ue} (ue_{tp} - uen_{d})
+		\sum_{tp} \beta_{tp}^{ue} ue_{tp} - \gamma (\sum_{tp} \beta_{tp}^{ue} uen_{p}) = 
+		\color{red} \sum_{tp} \beta_{tp}^{ue} (ue_{tp} - \gamma (uen_{p}))
 	\end{equation*}
@@
 	\end{equation*}
-	\begin{equation*}
-		\sum_{tp}^{T-1} \beta_{tp}^{uu} uu_{tp} - \gamma \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-		\bigg( uu_{t+1p} + \sum_{mdc} (sc_{t+1mdc}U)  - \sum_{tmdc} (rsc_{t+1t'mdc} U) + \sum_{t'mdc} (rsc_{tt'+1mdc} U) \bigg)
-	\end{equation*}
-	\begin{equation*}
-		\color{red} \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( 
-			uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) + 
-			U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big)
-		\bigg)
-	\end{equation*}
+	\begin{align*}
+		\sum_{tp}^{T-1} \beta_{tp}^{uu} uu_{tp} - \gamma \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( 
+					& uu_{t+1p} + \sum_{mdc} (sc_{t+1mdc}U)  - \sum_{tmdc} (rsc_{t+1t'mdc} U) + \sum_{t'mdc} (rsc_{tt'+1mdc} U) + \\ 
+					&\sum_{mdc} ps_{tmdc}pwp_{mdc} (U_{pd+1c} - U_{pdc}) \bigg)
+	\end{align*}
+	{ \color{red} \begin{align*}
+		 \Bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( & 
+		 	uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} ps_{tmdc}pwp_{mdc} (U_{pd+1c} - U_{pdc}) + \\
+			& U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big) \bigg) + \\
+		\beta_{Tp}^{uu} (uu_{Tp}) \Bigg)
+	\end{align*} }
 
@@
 
-	\item $\beta_{mdc}^{pw}$
+	\item $\beta_{mdc}^{ps}$
 	\begin{equation*}
@@
 			\bigg( ps_{tmdc} - 
-				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} + \\ 
+				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
 				&  - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) + \\
@@
 			\bigg( ps_{tMdc} - 
-				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} + \\ 
-				&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \Bigg)
+				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
+				&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) + \\ 
+		\sum_{mdc} \beta_{Tmdc}^{ps} & 
+			\bigg( ps_{Tmdc} \bigg) \Bigg)
 	\end{align*} }
@@
 \subsection{Dual of ADP LP}
+\label{Dual of ADP LP}
 Converting to Dual
@@
 Subject To:
+\begin{itemize}
+	\item $\beta^{0}$ constraints
 	\begin{equation}
-		\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) \ge 1 
+		\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 
 	\end{equation}
+
+	\item $\beta^{ue}$ constraints	
 	\begin{equation}
-		\sum_{\vec{S}\vec{A}}\vec{w} \Big( (1-\gamma) (ue_{tp} - uen_{tp}) \Big) \ge E[ue_{tp}] \quad \forall tp
+		\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - \gamma (uen_{tp}) \Big) \ge E[ue_{tp}] \quad \forall tp
 	\end{equation}
+
+	\item $\beta^{uu}$ constraints
 	\begin{multline}
-		\sum_{\vec{S}\vec{S}} \vec{w} \bigg( 
-			uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) + \\ 
+		\sum_{\vec{S}\vec{A}} \vec{w} \bigg( 
+			uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} ps_{tmdc}pwp (U_{pd+1c} - U_{pdc}) + \\ 
 			U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big)
-		\bigg) \\
+		\bigg) \ge E[uu_{tp}] \\
 		\quad \forall T \in \{1...T-1\}p
@@
 	\begin{equation}
+		\sum_{\vec{S}\vec{A}} \vec{w} (uu_{Tp}) \ge E[uu_{Tp}] \quad \forall p
+	\end{equation}
+
+	\item $\beta^{pe}$ constraints
+	\begin{equation}
 		\sum_{\vec{S}\vec{A}} \vec{w} (pe_{dc} - \gamma E[pea_{dc}])  \ge E[pe_{dc}] \quad \forall dc
 	\end{equation}
+
+	\item $\beta^{pw}$ constraints
+	\begin{equation}
+		  \sum_{\vec{S}\vec{A}}w  ( pw_{1dc} - \gamma (pe_{dc} - \sum_{t} sc_{t0dc})) \ge E[pw_{1dc}] \quad \forall dc
+	\end{equation}
+	\begin{multline}
+		\sum_{\vec{S}\vec{A}}w  \Big( pw_{mdc} - \gamma \big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) \Big) \\ 
+		\ge E[pw_{mdc}]  \quad \forall m \in \{2 ... M-1 \}dc
+	\end{multline}
+	\begin{equation}
+		\sum_{\vec{S}\vec{A}}w  \Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
+			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Big) \ge E[pw_{Mdc}] \quad \forall dc
+	\end{equation}
+
+	\item $\beta^{ps}$ constraints
+	\begin{multline}
+		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
+				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
+				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
+				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} m \in \{1 ... M-1 \} dc
+	\end{multline}
+	\begin{multline}
+		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
+				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
+				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 
+				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} dc
+	\end{multline}
+	\begin{equation}
+		\sum_{\vec{S}\vec{A}} \vec{w} (ps_{Tmdc}) \ge E[ps_{Tmdc}] \quad \forall mdc
+	\end{equation}
+
+	\item State-Action constraints
 	\begin{equation}
@@
 	\end{equation}
+\end{itemize}
 
 \subsection{Finding most violated constraints of ADP LP}
+\label{Pricing Problem}
+\begin{equation}
+	\min_{(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \in S,  (\vec{sc}, \vec{rsc}) \in A } c(\vec{pw},\vec{sc},\vec{rsc},\vec{uv}) - E[V]
+\end{equation}
+Subject to:
+all constraints in section "\nameref{action constraints}"
+
+\subsection{Algorithm for solving}
+To get $\vec{\beta}$ values, which will be used to generate an action follow steps below:
+\begin{enumerate}
+	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pe], E[pw] E[pw]$ (this will only give an approximation as arbitrary policy will likely be different from ADP policy) (if you wanted to, you could resolve for $\vec{\beta}$ again, but replacing $E[ue], E[uu], E[pe], ...$ with the ones that would be generated through the ADP policy)
+	\item Create an initial feasible set of state-action pairs - $\vec{w}$
+	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints
+	\item Solve model in section "\nameref{Pricing Problem}", where duals from problem in step 3  correspond to $\vec{\beta}$ values. 
+		\begin{itemize}
+			\item If objective function is less than 0, add solution as a single state-action pair to $\vec{w}$ and go to step 3
+			\item If objective function is greater than 0, continue to next step
+		\end{itemize}
+	\item Duals from problem in step 3 correspond to final $\vec{\beta}$ values
+\end{enumerate}
+
+\subsection{Generating an Action}
+Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
+\begin{equation}
+	\min_{\vec{A}} c(\vec{S}, \vec{A}) + E[V]
+\end{equation}
+Subject to:
+all constraints in section "\nameref{action constraints}"
 

### 2021-03-16 Implementation/Modules/sub_problem.py
minor changes to manuscript

@@ -27,5 +27,6 @@ class constraint_parameter:
     name:  Dict[ Tuple[str],str ]
 
 
-def generate_sub_problem(beta):
-    pass
+def generate_sub_problem(input_data, beta):
+
+    # Generates Decision Variables

### 2021-03-25 Manuscript/Manuscript.tex
working on sub problem
minor changes to manuscript
new version
- flow conservation of PPE added to all relevant things (model constraints), (MDP constraint updated), (ADP constraint updated), (Dual constraint changed)
- add units violated to states (including transition constraints, MDC constraints, ADP constraints, Dual constraints)

@@
 	\item  NEED TO MOVE $uv$ TO STATES AND ADJUST ALL THE RELEVANT EQUATIONS FOR IT
+	\item Need to change generating an action section (4.7)
 \end{itemize}
@@
 \begin{itemize}
-	\item In constraints for transition between $uu$ and $uu'$ - missing change in usage due to complexity transition
+	\item
 \end{itemize}
@@
 And decision maker must also schedule patients to surgeries
-\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}) \] 
+\[  \vec{A} = (\vec{sc}, \vec{rsc}) \] 
 \begin{itemize}
@@
 	\item $\vec{rsc} = rsc_{tt'mdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to reschedule from period $t$ to period $t'$
-	\item $uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
 \end{itemize}
@@
 	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Units of PPE
+		\begin{align} \begin{split}  
+			ue'_{1p} = & ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \\
+				& - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc} \quad \forall p 
+		\end{split} \end{align} 
 		\begin{equation}  
-			ue'_{1p} = ue_{2p} + ued_{p}\ \quad \forall p 
-		\end{equation} 
-		\begin{equation}  
-			ue'_{t-1,p} = ue_{tp}\ \quad \forall t \in \{3...T\}, p
+			ue'_{t-1,p} = ue_{tp} \quad \forall t \in \{3...T\}, p
 		 \end{equation} 
@@
 		\sum_{tp} \beta_{tp}^{ue} ue_{tp} +
-		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + \\
+		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + 
+		\sum_{tp} \beta_{tp}^{uv} uv_{tp} + \\
 		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
@@
 	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
-		& * \Bigg( \beta^{0} +
-		\bigg( \sum_{p} \beta_{1p}^{ue} (ue_{2p} + ued_{p}) + 
-				\sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
-				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) +
-		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
+		& \Bigg( \beta^{0} + \\ 
+		& \bigg( \sum_{p} \beta_{1p}^{ue} 
+			(ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc}) \bigg)  \\ 
+		& \bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
+				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
+		& \bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
 		& \bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
@@
 				& \quad \quad \quad \quad \quad \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) \Big) \bigg) +  \\
+		& \bigg( \sum_{tp} uv'_{tp} \bigg) + \\ 
 		& \bigg( \sum_{dc} \beta_{dc}^{pe} pea_{dc} \bigg) + 
@@
 	\end{equation*}
-	\begin{equation*}
-		\sum_{tp} \beta_{tp}^{ue} ue_{tp} - \gamma (\sum_{tp} \beta_{tp}^{ue} uen_{p}) = 
-		\color{red} \sum_{tp} \beta_{tp}^{ue} (ue_{tp} - \gamma (uen_{p}))
-	\end{equation*}
+	{ \color{red} \begin{align*}
+		 \Bigg( 
+			& \bigg( \sum_{p} \beta_{1p}^{ue} (ue_{1p} - 
+				\gamma \Big( uen_{p} + ue_{1p} - uu_{1p} - 
+				\sum_{dc} U_{pdc} (\sum_{m} sc_{mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) \bigg) + \\
+			& \bigg(\sum_{t=2p}^{T} \beta_{tp}^{ue} (ue_{tp} - \gamma (uen_{p}) \bigg) \Bigg)
+	\end{align*} }
 
@@
 	\end{align*} }
+
+	\item $\beta_{tp}^{uv}$
+	\begin{equation*}
+		E[uv_{tp}] = 0
+	\end{equation*}
+	\begin{equation*}
+		\sum_{tp} \beta_{tp}^{uv} (uv_{tp} - \gamma (E[uv_{tp}])) = 
+		\color{red} \sum_{tp} \beta_{tp}^{uv} uv_{tp} 
+	\end{equation*}
 
@@
 \begin{equation}
-	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + 
+	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
 		\sum \beta^{pe} E[pe] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
@@
 	\item $\beta^{ue}$ constraints	
+	\begin{multline}
+		\sum_{\vec{S}\vec{A}}\vec{w} \bigg(ue_{1p} - 
+			\gamma \Big( uen_{p} + ue_{1p} - uu_{1p} - 
+			\sum_{dc} U_{pdc} ( \sum_{m} sc_{mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) \bigg) \\ 
+		\ge E[ue_{1p}] \quad \forall p
+	\end{multline}
 	\begin{equation}
-		\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - \gamma (uen_{tp}) \Big) \ge E[ue_{tp}] \quad \forall tp
+		\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - \gamma (uen_{p}) \Big) \ge E[ue_{tp}] \quad \forall t \in (2...T) p
 	\end{equation}
@@
 		\sum_{\vec{S}\vec{A}} \vec{w} (uu_{Tp}) \ge E[uu_{Tp}] \quad \forall p
+	\end{equation}
+
+	\item $\beta^{uv} constraints$
+	\begin{equation}
+		\sum_{\vec{S}\vec{A}} \vec{w} (uv_{tp}) \ge 0 \quad \forall tp
 	\end{equation}

### 2021-04-01 Manuscript/Manuscript.tex
updates
finalized master problem
 - both default and phase 1 model
 - working on subproblem - currently default one

- changes to manuscript
 - modified cost function (removed sc variable, added extra cost)
 - modified an error in a action constraint
 - added uv state

@@
 \begin{itemize}
-	\item  NEED TO MOVE $uv$ TO STATES AND ADJUST ALL THE RELEVANT EQUATIONS FOR IT
 	\item Need to change generating an action section (4.7)
+	\item Priority need to be added
+	\item PPE resources need to include OR time
+	\item Add cost of scheduling past the window
+	\item Evaluate cost of waiting
 \end{itemize}
@@
 
-	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($Tl$). 
+	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($TL$). 
 	\begin{itemize}
-		\item Let's assume our limit is 10 periods, there is no difference in terms of cost between patients who has been waiting for 1 period and patients waiting 9 period for their appointment (assuming they are the same category).
+		\item Let's assume our limit is 10 periods, there is no difference in terms of cost between patients who has been waiting for 1 period and patients waiting 10 period for their appointment (assuming they are the same category).
 		\item However, if a patient waits for 11 period for their appointment there should be some kind of penalty for the wait
@@
 		\begin{itemize}
-			\item While patient is waiting less that $Tl$, the transition probability is 0.
-			\item After $Tl$, transition probability is some arbitrary value
+			\item While patient is waiting less that $TL$, the transition probability is 0.
+			\item After $TL$, transition probability is some arbitrary value
 		\end{itemize}
@@
 \subsection{State Space}
+\subsubsection{Description}
 State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
@@
 \end{itemize}
+\subsubsection{Bounds on States}
+\begin{itemize}
+	\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
+	\item $uu_{tp} \le 2(uen_{p} + max(ued_p)) \quad \forall tp$
+	\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
+	\item $pe_{dc} \le pea_{dc} * 4 \quad \forall dc$
+	\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
+	\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
+\end{itemize}
 
 \subsection{Action Sets}
-
 \subsubsection{Description}
@@
         \begin{equation} 
-			\sum_{mdc}(sc_{tmdc})U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp
+			( \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp
 		\end{equation}
@@
 		\begin{itemize}
-			\item let's assume $ued_{d}$ is the random variable that represents the deviation of PPE units from the expectation for the next period only. It follows some uniform distribution.
-			\item let's assume $uen_{d}$ is the default value to be used for expected number of PPE units $p$ per period
+			\item let's assume $ued_{p}$ is the random variable that represents the deviation of PPE units $p$ from the expectation for the next period only. It follows some uniform distribution.
+			\item let's assume $uen_{p}$ is the default value to be used for expected number of PPE units $p$ per period
 		\end{itemize}
@@
 \begin{align} \begin{split}  
-	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = & \sum_{mdc} cw_{m} (pw_{mdc} - \sum_{t} sc_{tmdc}) +  \\
+	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = 
+		& \sum_{mdc} cw_{m} (pw_{mdc}) +  \\
+		& \sum_{tdc} cw_{M} (ps_{tMdc}) (\text{ to prevent infinite rescheduling })+ \\
 		& + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} - cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + \\ 
@@
 				\gamma \Big( uen_{p} + ue_{1p} - uu_{1p} - 
-				\sum_{dc} U_{pdc} (\sum_{m} sc_{mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) \bigg) + \\
+				\sum_{dc} U_{pdc} (\sum_{m} sc_{1mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) \bigg) + \\
 			& \bigg(\sum_{t=2p}^{T} \beta_{tp}^{ue} (ue_{tp} - \gamma (uen_{p}) \bigg) \Bigg)

### 2021-04-01 Implementation/Modules/sub_problem.py

@@ -26,8 +26,7 @@ class constraint_parameter:
     sign: Dict[ Tuple[str],str ]
     name:  Dict[ Tuple[str],str ]
 
-
-def generate_sub_problem(input_data, betas):
+def generate_sub_model(input_data, betas):
     indices = input_data.indices
     arrival = input_data.arrival
     ppe_data = input_data.ppe_data
@@ -39,7 +38,7 @@ def generate_sub_problem(input_data, betas):
     gamma = model_param.gamma
 
     # Initializes model
-    sub_model = gp.Model('SubproblemKnapsack')
+    sub_model = gp.Model('SubmodelKnapsack')
 
     var_ue = {}
     var_uu = {}
@@ -49,30 +48,139 @@ def generate_sub_problem(input_data, betas):
     var_ps = {}
     var_sc = {}
     var_rsc = {}
+    variables = {
+        
+    }
 
     # Decision Variables
-        # States
+    # States / Upper Bounds
     for tp in itertools.product(indices['t'], indices['p']):
-        var_ue[tp] = sub_model.addVar(name=f's_ue_{tp}')
-        var_uu[tp] = sub_model.addVar(name=f's_uu_{tp}')
-        var_uv[tp] = sub_model.addVar(name=f's_uv_{tp}')
+        ppe_upper_bounds = ppe_data[tp[1]].expected_units + ppe_data[tp[1]].deviation[1]
+        var_ue[tp] = sub_model.addVar(name=f's_ue_{tp}', ub=ppe_upper_bounds)
+        var_uu[tp] = sub_model.addVar(name=f's_uu_{tp}', ub=ppe_upper_bounds*2)
+        var_uv[tp] = sub_model.addVar(name=f's_uv_{tp}', ub=ppe_upper_bounds)
     for dc in itertools.product(indices['d'], indices['c']):
-        var_pe[dc] = sub_model.addVar(name='s_pe_{dc}')
+        var_pe[dc] = sub_model.addVar(name=f's_pe_{dc}', ub=4*arrival[dc])
     for mdc in itertools.product(indices['m'], indices['d'], indices['c']):
         if mdc[0] == 0: continue
-        var_pw[mdc] = sub_model.addVar(name='s_pw_{mdc}')
+        var_pw[mdc] = sub_model.addVar(name=f's_pw_{mdc}', ub=4*arrival[(mdc[1],mdc[2])])
[…]

### 2021-04-01 Implementation/main.py

@@ -1,6 +1,7 @@
 # %% Packages
 from Modules.data_import import *
 from Modules.master_model import *
+from Modules.sub_problem import *
 from Modules.decorators import timer
 import os.path
 
@@ -9,11 +10,17 @@ my_path = os.path.dirname(__file__)
 read_data = timer(read_data)
 input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
 
-# %% Generate Initial States (Phase 1)
+# %% Generate Master Model (Phase 1)
 init_state, init_action = generate_initial_state_action(input_data)
 state_action_list = [(init_state, init_action)]
 p1_mast_model, p1_variables, p1_constraints = generate_phase1_master_model(input_data, state_action_list)
 p1_mast_model.write('mast_p1.lp')
+
+p1_mast_model.optimize()
+betas = generate_beta_values(input_data, p1_constraints)
+# %% Generate Sub Model (Phase 2)
+sub_model = generate_sub_model(input_data, betas)
+sub_model.write('sub_prob.lp')
 
 
 # %% Solve the problem (Phase 2?)

### 2021-04-03 Manuscript/Manuscript.tex
initial implementation done
- but I am sure there are bugs, as it is unable to even find an initial feasible solution

@@
 		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
-				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
+				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - sc_{t+1m-1dc} \\ 
 				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
@@
 		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
-				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
+				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - sc_{t+1mdc} \\ 
 				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 

### 2021-04-03 Implementation/main.py

@@ -10,17 +10,36 @@ my_path = os.path.dirname(__file__)
 read_data = timer(read_data)
 input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
 
-# %% Generate Master Model (Phase 1)
+# %% Generate Initial Feasible Set
 init_state, init_action = generate_initial_state_action(input_data)
 state_action_list = [(init_state, init_action)]
-p1_mast_model, p1_variables, p1_constraints = generate_phase1_master_model(input_data, state_action_list)
-p1_mast_model.write('mast_p1.lp')
 
-p1_mast_model.optimize()
-betas = generate_beta_values(input_data, p1_constraints)
+count = 0
+while True:
+    # Adjusted Master Model
+    p1_mast_model, p1_mast_var, p1_mast_const = generate_phase1_master_model(input_data, state_action_list)
+    p1_mast_model.Params.LogToConsole = 0
+    p1_mast_model.optimize()
+    print(f'iteration {count}, {p1_mast_model.getObjective().getValue()}')
+    count += 1
+    betas = generate_beta_values(input_data, p1_mast_const)
+    if p1_mast_model.getObjective().getValue() <= 0:
+        break
+    # Adjusted Subproblem
+    p1_sub_model, p1_sub_var = generate_sub_model(input_data, betas, True)
+    p1_sub_model.Params.LogToConsole = 0
+    p1_sub_model.optimize()
+    state_action = generate_state_action(p1_sub_var)
+    # Adjusts state action set
+    state_action_list.append(state_action)
+
 # %% Generate Sub Model (Phase 2)
-sub_model = generate_sub_model(input_data, betas)
-sub_model.write('sub_prob.lp')
+sub_model, sub_variables = generate_sub_model(input_data, betas)
+sub_model.write('sub_prob_p2.lp')
+
+# %% Generate Master Model (Phase 2)
+mast_model, variables, constraints = generate_master_model(input_data, state_action_list)
+mast_model.write('mast_p2.lp')
 
 
 # %% Solve the problem (Phase 2?)

### 2021-04-09 Manuscript/Manuscript.tex
trying to find the bugs
updates go brrrr

@@
 	\item PPE resources need to include OR time
-	\item Add cost of scheduling past the window
-	\item Evaluate cost of waiting
+	\item When generating a new state for master (section 4.5), do I need to ensure the states are consistent, etc?
 \end{itemize}
@@
 \end{itemize}
-\subsubsection{Bounds on States}
+\subsubsection{States Constraints}
+\begin{itemize}
+	\item PPE Usage Constraint
+	\begin{equation}
+		uu_{tp} = ue_{tp}+uv_{tp} \quad \forall tp
+	\end{equation}
+	\item Bounds on states
 	\begin{itemize}
 		\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
-	\item $uu_{tp} \le 2(uen_{p} + max(ued_p)) \quad \forall tp$
+		\item $uu_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
 		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
@@
 		\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-    \item Total number of PPE units cannot be exceeded  
+    \item Tracks PPE Usage  
     \begin{itemize}
@@
         \begin{equation} 
-			( \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} <= (ue_{tp} - uu_{tp}) + uv_{tp}\ \quad \forall tp
+			(\sum_{mdc}ps_{tmdc} \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
 		\end{equation}

### 2021-04-09 Implementation/Modules/master_model.py

@@ -36,11 +36,11 @@ def generate_initial_state_action(input_data):
     # Patient States
     pe = {}
     for dc in itertools.product(indices['d'], indices['c']):
-        pe[dc] = 0
+        pe[dc] = arrival[dc] * 4
     pw = {}
     for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
         if mdc[0] == 0: continue
-        pw[mdc] = 0
+        pw[mdc] = arrival[(mdc[1], mdc[2])] * 4
     ps = {}
     for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
         if tmdc[1] == 0: continue
@@ -51,9 +51,11 @@ def generate_initial_state_action(input_data):
     uu = {}
     uv = {}
     for tp in itertools.product(indices['t'], indices['p']):
-        ue[tp] = ppe_data[tp[1]].expected_units
-        uu[tp] = 0
-        uv[tp] = np.max((0, uu[tp] - ue[tp]))
+        ub = ppe_data[tp[1]].expected_units + ppe_data[tp[1]].deviation[1] 
+        ue[tp] = ub
+        uv[tp] = ub
+        if tp[0] == 1: uu[tp] = ub*2
+        else: uu[tp] = 0
 
     # Actions
     sc = {}
@@ -70,10 +72,10 @@ def generate_initial_state_action(input_data):
     return test_state, test_action
 
 # Generate Phase 1 Master Model (finding initial feasible solution)
-def generate_phase1_master_model(input_data,state_action_data):
+def generate_phase1_master_model(input_data, model):
     indices = input_data.indices    
-    mast_model, variables, constraints = generate_master_model(input_data, state_action_data)
 
+    mast_model = model.copy()
     # Resets objective function
     obj_expr = gp.LinExpr()
     mast_model.setObjective(obj_expr, GRB.MINIMIZE)
@@ -87,42 +89,70 @@ def generate_phase1_master_model(input_data,state_action_data):
     gv_pe = {}
     gv_ps = {}
 
+    # Constraints 
+    b0_constr = {}
+    ue_constr = {}
+    uu_constr = {}
+    uv_constr = {}
+    pe_constr = {}
+    pw_constr = {}
+    ps_constr = {}
+
     # Adds variables to model, updates constraints, and adds to objective function
         # Beta 0
[…]

### 2021-04-09 Implementation/Modules/sub_problem.py

@@ -79,20 +79,30 @@ def generate_sub_model(input_data, betas, phase1 = False):
     sub_vars = variables( var_ue, var_uu, var_uv, var_pe, var_pw, var_ps, var_sc, var_rsc)
 
     # Constraints
-    # 1) PPE Capacity
+    # 1) PPE Usage Constraint
     for tp in itertools.product(indices['t'], indices['p']):
         expr = gp.LinExpr()
+        for mdc in itertools.product(indices['m'], indices['d'], indices['c']):
+            if mdc[0] == 0: continue
+            expr.addTerms(-usage[(tp[1],mdc[1],mdc[2])], var_ps[(tp[0], mdc[0],mdc[1],mdc[2])])
         for mdc in itertools.product(indices['m'], indices['d'], indices['c']):
             expr.addTerms(-usage[(tp[1],mdc[1],mdc[2])], var_sc[(tp[0], mdc[0],mdc[1],mdc[2])])
         for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
             if tmdc[1] == 0: continue
             expr.addTerms(-usage[(tp[1],tmdc[2],tmdc[3])], var_rsc[(tmdc[0], tp[0], tmdc[1],tmdc[2],tmdc[3])])
-        expr.addTerms(1, var_ue[tp])
-        expr.addTerms(-1, var_uu[tp])
-        expr.addTerms(1, var_uv[tp])
-        sub_model.addConstr(expr >= 0, name=f'ppe_capacity_{tp}')
+        expr.addTerms(1, var_uu[tp])
+        sub_model.addConstr(expr == 0, name=f'tracks_usage{tp}')
 
-    # 2) Bounds on Reschedules
+
+    # 2) PPE Capacity
+    for tp in itertools.product(indices['t'], indices['p']):
+        expr = gp.LinExpr()
+        expr.addTerms(-1, var_ue[tp])
+        expr.addTerms(1, var_uu[tp])
+        expr.addTerms(-1, var_uv[tp])
+        sub_model.addConstr(expr <= 0, name=f'ppe_capacity_constraint_{tp}')
+
+    # 3) Bounds on Reschedules
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
         if ttpmdc[2] == 0: continue
         if ttpmdc[0] == ttpmdc[1]:
[…]

### 2021-04-09 Implementation/main.py

@@ -6,74 +6,101 @@ from Modules.sub_problem import *
 from Modules.decorators import timer
 import os.path
 
-# %% Reads Data
+# read_data = timer(read_data)
+# generate_master_model = timer(generate_master_model)
+# generate_phase1_master_model = timer(generate_phase1_master_model)
+# generate_sub_model = timer(generate_sub_model)
+# update_master_model = timer(update_master_model)
+
 my_path = os.path.dirname(__file__)
-read_data = timer(read_data)
 input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
 
-# %% Generate Initial Feasible Set
+# %% Generate Initial Feasible Set (Phase 1)
 init_state, init_action = generate_initial_state_action(input_data)
 state_action_list = [(init_state, init_action)]
 
 count = 0
-for i in range(4):
-    # Adjusted Master Model
-    p1_mast_model, p1_mast_var, p1_mast_const = generate_phase1_master_model(input_data, state_action_list)
+mast_model, mast_var, mast_const = generate_master_model(input_data, state_action_list)
+
+while True:
+    
+    # Generates and Solves Master
+    p1_mast_model, p1_mast_const = generate_phase1_master_model(input_data, mast_model)
     p1_mast_model.Params.LogToConsole = 0
     p1_mast_model.optimize()
-    print(f'iteration {count}, {p1_mast_model.getObjective().getValue()}')
-    count += 1
     betas = generate_beta_values(input_data, p1_mast_const)
+
+    p1_mast_model.write('mast_p1.lp')
+    mast_model.write('mast_p2.lp')
+        
+    # Debugging
+    print(f'Phase 1 - iteration {count+1}, Mast Objective {p1_mast_model.getObjective().getValue()}')
+    count += 1
+
+    # Stops if necessary
     if p1_mast_model.getObjective().getValue() <= 0:
+        print('Found Feasible Set')
         break
-    # Adjusted Subproblem
+    
+    # Generates and solves Subproblem 
     p1_sub_model, p1_sub_var = generate_sub_model(input_data, betas, True)
     p1_sub_model.Params.LogToConsole = 0
     p1_sub_model.optimize()
+    
+    # Update State-Actions
     state_action = generate_state_action(p1_sub_var)
-    # Adjusts state action set
     state_action_list.append(state_action)
[…]

### 2021-04-25 Manuscript/Manuscript.tex
adjusted the model

@@
 State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
-\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{pe}, \vec{ps}) \]
+\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{ps}) \]
 \begin{itemize}
@@
     \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
-    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods
-    \item $\vec{pe} = pe_{dc}$ - Number of patients of complexity $d$, CPU $c$ expected to arrive this period
+    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0, stands for people who just arrived)
     \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
@@
 		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
-		\item $pe_{dc} \le pea_{dc} * 4 \quad \forall dc$
 		\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
@@
         \begin{equation} 
-			(\sum_{mdc}ps_{tmdc} \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
+			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
 		\end{equation}
@@
 		\begin{equation}  
-			\sum_{t} sc_{t0dc} \le pe_{dc} \quad \forall dc 
-		\end{equation} 
-		\begin{equation}  
-			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall m \in \{1...M \}, dc 
+			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall mdc 
 		\end{equation} 
@@
 
-	\item Transition from $\vec{pe}$ to $\vec{pe'}$ - Expected number of patients for this month
-		\begin{equation} 
-			\ pe_{dc} = pea_{dc} \quad \forall dc 
-		\end{equation}
-
 	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
 		\begin{equation}  
-			pw'_{1dc} = pe_{dc} - \sum_{t} sc_{t0dc} \quad \forall dc 
+			pw'_{0dc} = pea_{dc} \quad \forall dc 
 		\end{equation} 
 		\begin{equation}  
-			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{1...M-2 \}, dc 
+			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{0...M-2 \}, dc 
 		\end{equation} 
@@
 	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts between difficulties/scheduling/cancelling for scheduled appointments
+		\begin{equation}
+			ps'_{t0dc} = 0 \quad \forall tdc
+		\end{equation}
 		\begin{align}  \begin{split}
@@
 		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
-		\sum_{dc} \beta_{dc}^{pe} pe_{dc} + 
 		\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
@@
 		& \bigg( \sum_{tp} uv'_{tp} \bigg) + \\ 
-		& \bigg( \sum_{dc} \beta_{dc}^{pe} pea_{dc} \bigg) + 
-			\bigg( \sum_{dc} \beta_{1dc}^{pw} (pe_{dc} - \sum_{t} sc_{t0dc}) \bigg) + \\
-		&  \bigg( \sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} 
+			& \bigg( \sum_{dc} \beta_{0dc}^{pw} (pea_{dc}) \bigg) + \\
+		&  \bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
 			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) \bigg) + \\
@@
 
-	\item $\beta_{dc}^{pe}$
-	\begin{equation*}
-		\sum_{dc} \beta_{dc}^{pe} pe_{dc} - \gamma \sum_{dc} \beta_{dc}^{pe} E[pea_{dc}] = 
-		\color{red} \sum_{dc} \beta_{dc}^{pe} (pe_{dc} - \gamma E[pea_{dc}])
-	\end{equation*}
-
 	\item $\beta_{mdc}^{pw}$ - Let's assume $pwp_{mdc}$ - is the probability of a patient transitioning to a higher complexity
@@
 	{ \color{red} \begin{align*}
-		\Bigg( \sum _{dc} \beta_{1dc}^{pw}& ( pw_{1dc} - \gamma (pe_{dc} - \sum_{t} sc_{t0dc})) + \\
-		\sum_{m=2,dc}^{M-1} \beta_{mdc}^{pw} & ( pw_{mdc} - \gamma 
+		\Bigg( \sum_{dc} \beta_{0dc}^{pw} & (pw_{0dc} - \gamma E[pea_{dc}]) + \\
+		\sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} & ( pw_{mdc} - \gamma 
 			\big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) + \\
@@
 	{ \color{red} \begin{align*}
-		\Bigg( \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} & 
+		\Bigg( \sum_{tdc} \beta_{t0dc}^{ps} & * ps_{Tmdc} + \\
+			\sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} & 
 				\bigg( ps_{tmdc} - 
@@
 	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
-		\sum \beta^{pe} E[pe] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
+		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
 \end{equation}
@@
 	\begin{equation}
-		\sum_{\vec{S}\vec{A}} \vec{w} (uv_{tp}) \ge 0 \quad \forall tp
-	\end{equation}
-
-	\item $\beta^{pe}$ constraints
-	\begin{equation}
-		\sum_{\vec{S}\vec{A}} \vec{w} (pe_{dc} - \gamma E[pea_{dc}])  \ge E[pe_{dc}] \quad \forall dc
+		\sum_{\vec{S}\vec{A}} \vec{w} (uv_{tp}) \ge E[uv_{tp}] \quad \forall tp
 	\end{equation}
@@
 	\begin{equation}
-		  \sum_{\vec{S}\vec{A}}w  ( pw_{1dc} - \gamma (pe_{dc} - \sum_{t} sc_{t0dc})) \ge E[pw_{1dc}] \quad \forall dc
+		  \sum_{\vec{S}\vec{A}}w  ( pw_{0dc} - \gamma E[pea_{dc}]) \ge E[pw_{0dc}] \quad \forall dc
 	\end{equation}
@@
 		\sum_{\vec{S}\vec{A}}w  \Big( pw_{mdc} - \gamma \big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) \Big) \\ 
-		\ge E[pw_{mdc}]  \quad \forall m \in \{2 ... M-1 \}dc
+		\ge E[pw_{mdc}]  \quad \forall m \in \{1 ... M-1 \}dc
 	\end{multline}
@@
 	\item $\beta^{ps}$ constraints
+	\begin{equation}
+		 \sum_{\vec{S}\vec{A}}w (ps_{t0dc}) \ge E[ps_{t0dc}] \quad \forall tdc 
+	\end{equation}
 	\begin{multline}

### 2021-04-25 Implementation/Modules/data_classes.py

@@ -1,0 +1,58 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+import gurobipy as gp
+
+# Data Import Classes
+@dataclass(frozen=True)
+class ppe_data_class:
+    ppe_type: str
+    expected_units: int
+    deviation: List[int]
+@dataclass(frozen=True)
+class model_param_class:
+    cw: float
+    cc: float
+    M: float
+    gamma: float
+@dataclass(frozen=True)
+class input_data_class:
+    indices: Dict[ str, List[int] ]
+    ppe_data: Dict[ str,ppe_data_class ]
+    usage: Dict[ Tuple[str], List[int] ]
+    arrival: Dict[ Tuple[str], List[int] ]
+    transition: Dict[ Tuple[str], List[int] ]
+    model_param: model_param_class
+    expected_state_values: Dict[ str, Dict[Tuple[str], float] ]
+
+# Data Export Classes
+
+# State Action 
+@dataclass(frozen=True)
+class state:
+    ue_tp: Dict[ Tuple[str],float ] # units expected on time t, ppe p
+    uu_tp: Dict[ Tuple[str],float ] # units used on time t, ppe p
+    uv_tp: Dict[ Tuple[str],float ] # units violated on time t, ppe p
+    # pe_dc: Dict[ Tuple[str],float ] # new patient arrivals of complexity d, cpu c
+    pw_mdc: Dict[ Tuple[str],float ] # patients waiting for m periods, of complexity d, cpu c
+    ps_tmdc: Dict[ Tuple[str],float ] # patients scheduled into time t, who have waited for m periods, of complexity d, cpu c
+@dataclass(frozen=True)
+class action:
+    sc_tmdc: Dict[ Tuple[str],float ] # patients of complexity d, cpu c, waiting for m periods to schedule into t (m of 0 corresponds to pe)
+    rsc_ttpmdc: Dict[ Tuple[str],float ] # patients of complexity d, cpu c, waiting for m periods, to reschedule from t to tp 
+
+# Gurobi Relevant Objects
+@dataclass(frozen=True)
+class constraint_parameter:
+    lhs_param: Dict[ Tuple[str],float ]
+    rhs_param: Dict[ Tuple[str],float ]
+    sign: Dict[ Tuple[str],str ]
[…]

### 2021-04-25 Implementation/Modules/data_import.py

@@ -1,28 +1,8 @@
 # Imports packages
 import openpyxl
 from dataclasses import dataclass
+from Modules.data_classes import ppe_data_class, model_param_class, input_data_class
 from typing import Dict, Tuple, List, Callable
-
-@dataclass(frozen=True)
-class ppe_data_class:
-    ppe_type: str
-    expected_units: int
-    deviation: List[int]
-@dataclass(frozen=True)
-class model_param_class:
-    cw: float
-    cc: float
-    M: float
-    gamma: float
-@dataclass(frozen=True)
-class input_data_class:
-    indices: Dict[ str, List[int] ]
-    ppe_data: Dict[ str,ppe_data_class ]
-    usage: Dict[ Tuple[str], List[int] ]
-    arrival: Dict[ Tuple[str], List[int] ]
-    transition: Dict[ Tuple[str], List[int] ]
-    model_param: model_param_class
-    expected_state_values: Dict[ str, Dict[Tuple[str], float] ]
 
 # Reads All data
 def read_data(data_file_path):
@@ -40,7 +20,7 @@ def read_data(data_file_path):
         if t_row[0] == None: break
         t.append(t_row[0])
     # Generates M
-    m = [0]
+    m = []
     for m_row in indices_sheet.iter_rows(min_row=2, min_col=2, max_col=2, values_only=True):
         if m_row[0] == None: break
         m.append(m_row[0])
@@ -142,23 +122,16 @@ def read_data(data_file_path):
         key = (row[1], row[0])
         value = float(row[2])
         expected_state_values['uv'][key] = value
-    # pe
-    expected_state_values['pe'] = {}
-    for row in expected_state_sheet.iter_rows(min_row=3, min_col=10,max_col=12, values_only=True):
-        if row[0] == None: break
-        key = (row[0], row[1])
-        value = float(row[2])
-        expected_state_values['pe'][key] = value
     # pw
     expected_state_values['pw'] = {}
-    for row in expected_state_sheet.iter_rows(min_row=3, min_col=13,max_col=16, values_only=True):
+    for row in expected_state_sheet.iter_rows(min_row=3, min_col=10,max_col=13, values_only=True):
         if row[0] == None: break
         key = (row[0], row[1], row[2])
         value = float(row[3])
         expected_state_values['pw'][key] = value
     # ps
     expected_state_values['ps'] = {}
-    for row in expected_state_sheet.iter_rows(min_row=3, min_col=17,max_col=21, values_only=True):
[…]

### 2021-04-25 Implementation/Modules/master_model.py

@@ -1,4 +1,5 @@
 from dataclasses import dataclass
+from Modules.data_classes import state, action, constraint_parameter, input_data_class
 from typing import Dict, Tuple, List, Callable
 
 import itertools
@@ -6,27 +7,7 @@ import numpy as np
 import gurobipy as gp
 from gurobipy import GRB
 
-# Data Classes
-@dataclass(frozen=True)
-class state:
-    ue_tp: Dict[ Tuple[str],float ] # units expected on time t, ppe p
-    uu_tp: Dict[ Tuple[str],float ] # units used on time t, ppe p
-    uv_tp: Dict[ Tuple[str],float ] # units violated on time t, ppe p
-    pe_dc: Dict[ Tuple[str],float ] # new patient arrivals of complexity d, cpu c
-    pw_mdc: Dict[ Tuple[str],float ] # patients waiting for m periods, of complexity d, cpu c
-    ps_tmdc: Dict[ Tuple[str],float ] # patients scheduled into time t, who have waited for m periods, of complexity d, cpu c
-@dataclass(frozen=True)
-class action:
-    sc_tmdc: Dict[ Tuple[str],float ] # patients of complexity d, cpu c, waiting for m periods to schedule into t (m of 0 corresponds to pe)
-    rsc_ttpmdc: Dict[ Tuple[str],float ] # patients of complexity d, cpu c, waiting for m periods, to reschedule from t to tp 
-@dataclass(frozen=True)
-class constraint_parameter:
-    lhs_param: Dict[ Tuple[str],float ]
-    rhs_param: Dict[ Tuple[str],float ]
-    sign: Dict[ Tuple[str],str ]
-    name:  Dict[ Tuple[str],str ]
-
-# Initialization
+# Initialization 
 def generate_initial_state_action(input_data):
     # Input Data
     indices = input_data.indices
@@ -34,16 +15,16 @@ def generate_initial_state_action(input_data):
     ppe_data = input_data.ppe_data
 
     # Patient States
-    pe = {}
-    for dc in itertools.product(indices['d'], indices['c']):
-        pe[dc] = arrival[dc] * 4
+    # pe = {}
+    # for dc in itertools.product(indices['d'], indices['c']):
+    #     pe[dc] = arrival[dc] * 4
     pw = {}
     for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
-        if mdc[0] == 0: continue
[…]

### 2021-04-25 Implementation/Modules/simulation.py

@@ -1,0 +1,263 @@
+# %% 
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import state, action, variables
+
+from copy import deepcopy
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+# %%
+
+# Initializes State ( Everything Empty )
+def initial_state(input_data) -> state:
+    # Input Data
+    indices = input_data.indices
+    arrival = input_data.arrival
+    ppe_data = input_data.ppe_data
+
+    # Patient States
+    pw = {}
+    for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
+        pw[mdc] = 0
+    ps = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        ps[tmdc] = 0
+
+    # Unit States
+    ue = {}
+    uu = {}
+    uv = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        ue[tp] = ppe_data[tp[1]].expected_units
+        uv[tp] = 0
+        uu[tp] = 0
+
+    init_state = state(ue, uu, uv, pw, ps)
+
+    return init_state
+# Initializes Action ( Everything Empty )
+def initial_action(input_data) -> action:
+    indices = input_data.indices
+
+    sc = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        sc[tmdc] = 0
+    rsc = {}
+    for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
+        rsc[ttpmdc] = 0
+
+    # Returns
+    init_action = action(sc, rsc)
+    return(init_action)
+
+# Executes Action
+def execute_action(input_data, state, action) -> state:
+    
+    new_state = deepcopy(state)
+
+    # Handles Reschedules
+
+    # Handles Schedules
+    for m in input_data.indices['m']:
+        for d in input_data.indices['d']:
+            for c in input_data.indices['c']:
+
+                # Adjusts PS
+                total_sched = 0
+                for t in input_data.indices['t']:
+                    new_state.ps_tmdc[(t,m,d,c)] += action.sc_tmdc[(t, m, d, c)]
+                    total_sched += action.sc_tmdc[(t, m, d, c)]
+
+                # Adjusts PW
+                new_state.pw_mdc[(m,d,c)] -= total_sched
[…]

### 2021-04-25 Implementation/main.py

@@ -44,7 +44,7 @@ while True:
     p1_sub_model, p1_sub_var = generate_sub_model(input_data, betas, True)
     p1_sub_model.Params.LogToConsole = 0
     # p1_sub_model.setParam('Presolve', 0)
-    p1_sub_model.setParam('MIPGap', 0)
+    # p1_sub_model.setParam('MIPGap', 0)
     p1_sub_model.optimize()
     
     # Update State-Actions
@@ -78,9 +78,9 @@ while True:
     count += 1
 
     # Stops if necessary
-    # if sub_model.ObjVal >= 0:
-    #     print('Found Optimal Solution')
-    #     break
+    if sub_model.ObjVal >= 0:
+        print('Found Optimal Solution')
+        break
 
     # Update State-Actions
     state_action = generate_state_action(sub_var)

### 2021-04-30 Manuscript/Manuscript.tex
working on simulation - there are some issues with timeline

@@
         \begin{equation} 
-			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
+			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + 
+			\sum_{tmdc} rsc_{tt'mdc} - \sum_{t'mdc} rsc_{tt'mdc})U_{pdc} = uu_{tp}\ \quad \forall tp
 		\end{equation}
@@
 	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = 
-		& \sum_{mdc} cw_{m} (pw_{mdc}) +  \\
+		& \sum_{mdc} cw_{m} (pw_{mdc} - \sum_{t} sc_{tmdc}) +  \\
 		& \sum_{tdc} cw_{M} (ps_{tMdc}) (\text{ to prevent infinite rescheduling })+ \\
@@
 Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
-\begin{equation}
-	\min_{\vec{A}} c(\vec{S}, \vec{A}) + E[V]
-\end{equation}
+\begin{equation*}
+	\min_{\vec{A}} c(\vec{S}, \vec{A}) - \gamma v(S')
+\end{equation*}	
+\begin{align*}
+	v(S') = \bigg(  & \beta^0 + \sum_{t=2p}^{T} \beta_{tp}^{ue} uen_{p} + \\ 
+	& \sum_{p} \beta_{1p}^{ue} \Big( uen_{p} + ue_{1p} - uu_{1p} - 
+		\sum_{dc} U_{pdc} (\sum_{m} sc_{1mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) + \\
+	& \sum_{tp}^{T-1} \beta_{tp}^{uu} \Big( uu_{t+1p} + 
+		\sum_{mdc} ps_{tmdc}pwp_{} (U_{pd+1c} - U_{pdc}) + 
+		U_{pdc} \big( \sum_{mdc} sc_{t+1}  - \sum_{t'mdc} rsc_{t+1t'} + 
+		\sum_{tmdc} rsc_{tt'+1} \big) \Big) + \\
+	& \sum_{dc} \beta_{0dc}^{pw} E[pea_{dc}]) + \\
+	& \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} \Big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \Big) + \\
+	& \sum_{dc} \beta_{Mdc}^{pw} \sum_{M-1}^{M} \Big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \Big) + \\
+	& \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} 
+		\Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} - \\
+		& - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) + \\
+	& \sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
+	&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg)
+	& \bigg)
+\end{align*}
 Subject to:

### 2021-04-30 Implementation/Modules/simulation.py

@@ -1,15 +1,13 @@
-# %% 
 from dataclasses import dataclass
 from typing import Dict, Tuple, List, Callable
 from Modules.data_classes import state, action, variables
 
+from tqdm import tqdm, trange
 from copy import deepcopy
 import itertools
 import numpy as np
 import gurobipy as gp
 from gurobipy import GRB
-
-# %%
 
 # Initializes State ( Everything Empty )
 def initial_state(input_data) -> state:
@@ -59,7 +57,18 @@ def execute_action(input_data, state, action) -> state:
     new_state = deepcopy(state)
 
     # Handles Reschedules
+    for t in input_data.indices['t']:
+        for tp in input_data.indices['t']:
+            for mdc in itertools.product(input_data.indices['m'], input_data.indices['d'], input_data.indices['c']):
 
+                # Change
+                rescheduled_number = action.rsc_ttpmdc[(t, tp, mdc[0], mdc[1], mdc[2])]
+
+                # Reschedules Out
+                new_state.ps_tmdc[(t, mdc[0], mdc[1], mdc[2])] -= rescheduled_number
+                # Schedules into
+                new_state.ps_tmdc[(tp, mdc[0], mdc[1], mdc[2])] += rescheduled_number
+                
     # Handles Schedules
     for m in input_data.indices['m']:
         for d in input_data.indices['d']:
@@ -115,60 +124,141 @@ def execute_transition(input_data, state) -> state:
 
     indices = input_data.indices
     new_state = deepcopy(state)
+
+    # UE
+    for tp in itertools.product(indices['t'], indices['p']):
+        if tp[0] == 1:
+            deviation = np.random.uniform(
+                input_data.ppe_data[tp[1]].deviation[0],
+                input_data.ppe_data[tp[1]].deviation[1]
+            )
+            new_state.ue_tp[tp] = state.ue_tp[(tp[0]+1, tp[1])] + deviation
+        elif tp[0] == indices['t'][-1]:
+            new_state.ue_tp[tp] = input_data.ppe_data[tp[1]].expected_units
+        else:
+            new_state.ue_tp[tp] = state.ue_tp[(tp[0]+1, tp[1])]
+
+
+    # UU
+    for tp in itertools.product(indices['t'], indices['p']):
+        if tp[0] == indices['t'][-1]:
+            new_state.uu_tp[tp] = 0
+        else:
[…]

### 2021-04-30 Implementation/main.py

@@ -3,6 +3,7 @@ from Modules.data_import import *
 from Modules.data_export import *
 from Modules.master_model import *
 from Modules.sub_problem import *
+from Modules.simulation import *
 from Modules.decorators import timer
 import os.path
 
@@ -16,6 +17,52 @@ import os.path
 my_path = os.path.dirname(__file__)
 input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
 
+def non_zero_state(state: state):
+    for key,value in state.ue_tp.items():
+        if state.ue_tp[key] >= 0.1: print(f'\tUnits Expected - {key} - {state.ue_tp[key]}')
+        if state.uu_tp[key] >= 0.1: print(f'\tUnits Used - {key} - {state.uu_tp[key]}')
+        if state.uv_tp[key] >= 0.1: print(f'\tUnits Violated - {key} - {state.uv_tp[key]}')
+    for key,value in state.pw_mdc.items(): 
+        if value >= 0.1: print(f'\tPatients Waiting- {key} - {value}')
+    for key,value in state.ps_tmdc.items(): 
+        if value >= 0.1: print(f'\tPatients Scheduled- {key} - {value}')
+def non_zero_action(action: action):
+    for key,value in action.sc_tmdc.items():
+        if value >= 0.1: print(f'\tPatients Schedule - {key} - {value}')
+    for key,value in action.rsc_ttpmdc.items(): 
+        if value >= 0.1: print(f'\tPatients Reschedule- {key} - {value}')
+# %% Simulation
+# cost_data = generate_expected_values(input_data, 30, 1000)
+# fas_costs = simulation(input_data, 10, 600, 300, fas_policy)
+# myopic_cost = simulation(input_data, 10, 600, 300, myopic_policy)
+# fas_cost_total = 0
+# myopic_cost_total = 0
+# for repl in fas_costs:
+#     for day in repl:
+#         fas_cost_total += day
+# for repl in myopic_cost:
+#     for day in repl:
+#         myopic_cost_total += day
+# print(fas_cost_total)
+# print(myopic_cost_total)
+curr_state = initial_state(input_data)
+for i in range(10):
+    print()
+    print(f'Replication {i} - Initial State')
+    non_zero_state(curr_state)
+
+    print('Myopic Action')
+    new_action = myopic_policy(input_data, curr_state)
+    non_zero_action(new_action)
+
+    print(f'Post Action State')
[…]

### 2021-05-16 Manuscript/Manuscript.tex
things todo
todo:
- move uv to action
- change cost to be post-action states
- add auxiliary post-action states
- add carry over in the simulation
Finalized Model Update and Myopic and MDP Simulation
to finish - FAS simulation

@@
+%%%~~~~~~~~~~~~~~~~~ Preamble ~~~~~~~~~~~~~~~~~~~~~~
 \documentclass{article}
@@
 \usepackage[utf8]{inputenc}
-\usepackage{geometry}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{xcolor}
+\usepackage{amsmath, amssymb}
 
-\usepackage{hyperref}
+\usepackage{xcolor, hyperref}
 \hypersetup{
@@
 
-\geometry{margin=1in}
+\usepackage{geometry}
+\geometry{margin=0.65in}
 \setlength\parindent{0pt}
@@
 \title{Dynamic Knapsack Problem}
-\author{KV}
-\date{February 2021}
+\author{AS, WM, KV}
+\date{\today}
 
+\allowdisplaybreaks
+
+%%%~~~~~~~~~~~~~~~~~ Document ~~~~~~~~~~~~~~~~~~~~~~
 \begin{document}
@@
 \tableofcontents
+\newpage
 
@@
 \begin{itemize}
-	\item Need to change generating an action section (4.7)
 	\item Priority need to be added
-	\item PPE resources need to include OR time
-	\item When generating a new state for master (section 4.5), do I need to ensure the states are consistent, etc?
 \end{itemize}
@@
 	\end{itemize}
+	\item We allow some violation of PPE units, in rare cases (with high cost), in order to accomodate changes due to variability.
+	\begin{itemize}
+		\item If we have violation of PPE units - it reduces capacity in the future (Meaning violations are borrowed from future capacity)
+	\end{itemize}
 \end{itemize}
@@
 \subsection{Decision Epochs}
-Decisions are made at the beginning of each time period (will be weeks)
+Decisions are made at the beginning of each time period. There are 3 relevant time intervals to look at:
+\begin{itemize}
+	\item Pre-decision state ($S$)
+	\begin{itemize}
+		\item Pre-decision state defines the initial state on which a decision is required
+		\item This information drives decision making
+	\end{itemize}
+
+	\item Post-decision state ($\hat{S}$)
+	\begin{itemize}
+		\item Post-decision state is the time when the decision has been executed, but no new info came in
+		\item This state defines the immediate cost of an action
+	\end{itemize}
+
+	\item Post-transition state ($S'$)
+	\begin{itemize}
+		\item This is the state when new information has come in (transition randomness). Defines next pre decision state
+		\item It is primarily used to generate expectation for the ADP
+	\end{itemize}
+\end{itemize}
 
@@
 \subsubsection{Description}
-State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
-\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{ps}) \]
+State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
+\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) \]
 \begin{itemize}
-    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
-    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
-    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
-    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0, stands for people who just arrived)
-    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
-\end{itemize}
-\subsubsection{States Constraints}
-\begin{itemize}
-	\item PPE Usage Constraint
-	\begin{equation}
-		uu_{tp} = ue_{tp}+uv_{tp} \quad \forall tp
-	\end{equation}
-	\item Bounds on states
-	\begin{itemize}
-		\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
-		\item $uu_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
-		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
-		\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
-		\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
-	\end{itemize}
+    \item $\vec{ue} = ue_{tp}$ - Expected unist for  period $t$, and resource $p$
+    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and resource $p$
+    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
+    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
 \end{itemize}
@@
 \subsubsection{Description}
-At the beginning of each period, decision maker must reschedule appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively).
-And decision maker must also schedule patients to surgeries
-\[  \vec{A} = (\vec{sc}, \vec{rsc}) \] 
+Decision consists of rescheduling currently scheduled patients, and scheduling patients on waitlist. There are also some goal and auxiliary variables
+\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}, \text{auxiliary variables}) \] 
 \begin{itemize}
-    \item $\vec{sc} = sc_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been in wait list for $m$ periods, to schedule in period $t$ ($m$ of 0 stands for people who have just arrived)
-	\item $\vec{rsc} = rsc_{tt'mdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to reschedule from period $t$ to period $t'$
+    \item $\vec{sc} = sc_{tmdc}$ - Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to schedule in period $t$
+	\item $\vec{rsc} = rsc_{tt'mdc}$ -Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to reschedule from period $t$ to period $t'$
+	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
 \end{itemize}
 
-\subsubsection{Action Constraints}
-\label{action constraints}
+\subsubsection{Auxiliary Variables}
 \begin{itemize}
-    \item Tracks PPE Usage  
+	\item $\hat{uu}_{tp}$ - post-decision units used
+	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
+	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
+\end{itemize}
+\subsubsection{Auxiliary Variable Definition}
+\label{auxiliary constraints}
+\begin{alignat}{10}
+	& \hat{uu}_{tp} 
+		&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
+		&& \forall tp \\ 
+	& \hat{pw}_{mdc} 
+		&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
+		&& \forall mdc \\ 
+	& \hat{ps}_{tmdc} 
+		&& = ps_{tmdc} + sc_{tmdc} + 
+			\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
+		&& \forall tmdc
+\end{alignat}
+
+\subsubsection{State-Action Constraints}
+\label{state-action constraints}
 \begin{itemize}
-    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
-    \end{itemize}
+
+	\item Consistency Constraint
 	\begin{equation}
-			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + 
-			\sum_{tmdc} rsc_{tt'mdc} - \sum_{t'mdc} rsc_{tt'mdc})U_{pdc} = uu_{tp}\ \quad \forall tp
+		uu_{tp} = \sum_{mdc} U_{pdc} ps_{tmdc} \quad \forall tp
+	\end{equation}
+	\item Resource Usage Constraint
+	\begin{equation}
+		\hat{uu}_{tp} \le ue_{tp}+uv_{tp} \quad \forall tp
 	\end{equation}
 
-	\item Bounds on when reschedules are allowed
-		\begin{equation}  
-			rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc 
-		\end{equation} 
-		\begin{equation}  
-			rsc_{tt'mdc} = 0 \quad \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc 
-		\end{equation} 
-		\begin{equation}  
-			rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } t=t' 
-		\end{equation}
+	\item Custom bounds on when reschedules are allowed
+	\begin{alignat}{10}
+		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
+		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
+		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t' 
+	\end{alignat}
 
-	\item Cap on max schedule/reschedule wait time
-		\begin{equation}  
-			\sum_{tmdc} sc_{tmdc} = 0 \quad \text{where } t+m-1 > 2Tl 
-		\end{equation} 
-		\begin{equation}  
-			\sum_{tt'mdc} rsc_{tt'mdc} \quad \text{where } t'+m+1 > 2Tl 
-		\end{equation}
+	\item Bounds on Schedules/Reschedules
+	\begin{alignat}{10}
+		& \sum_{t'} rsc_{tt'mdc} 	&& \le ps_{tmdc} \quad  && \forall tmdc  \\
+		& \sum_{t} sc_{tmdc} 		&& \le pw_{mdc} \quad 	&& \forall mdc 
+	\end{alignat}
 
-	\item number of people scheduled/rescheduled must be consistent
-		\begin{equation}  
-			\sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc 
-		\end{equation} 
-		\begin{equation}  
-			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall mdc 
-		\end{equation} 
+	\item Bounds on states
+	\begin{alignat}{10}
+		& ue_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
+		& uu_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
+		& pw_{mdc} 	&& \le pea_{dc} * 4 \quad 			&& \forall mdc \\
+		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
+	\end{alignat}
 \end{itemize}
@@
 
-	\item Number of patients arriving this period - $pe_{dc}$
+	\item Number of patients arriving this period - $pw_{0dc}$
 		\begin{itemize}
-			\item let's assume $pea_{dc}$ - is the random variable that represents the number of patients arrived this period. It follows a poisson distribution.
+			\item $pea_{dc}$ - represents the random number of patients arriving. Follows a poisson distribution.
 		\end{itemize}
 
-	\item Transition between patient difficulties within the wait list - $pw_{mdc}$
+	\item Transition between patient complexities within the wait list - $pw_{m>=1,dc}$
 		\begin{itemize}
-			\item let's assume $pwt_{mdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have moved a more complex category.
-It follows binary distribution.
+			\item $pwt_{mdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, who became more complex. Follows binomial distribution.
+			\item $ptp_{mdc}$ represents transition probability to a higher complexity
 		\end{itemize}
 
-	\item Transition between patient difficulties within the scheduled list - $ps_{tmdc}$
+	\item Transition between patient complexities within the scheduled list - $ps_{tmdc}$
 		\begin{itemize}
-			\item let's assume $pst_{tmdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have been scheduled into period $t$, that have moved a more complex category.
-It follows binary distribution.
+			\item $pst_{tmdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, scheduled into $t$ period, who became more complex. Follows binomial distribution.
 		\end{itemize}
@@
 		\begin{itemize}
-			\item let's assume $ued_{p}$ is the random variable that represents the deviation of PPE units $p$ from the expectation for the next period only. It follows some uniform distribution.
-			\item let's assume $uen_{p}$ is the default value to be used for expected number of PPE units $p$ per period
+			\item $ued_{p}$ represents the random deviation of resource $p$ from the expectation. Follows uniform distribution.
+			\item $uen_{p}$ expected units of resource $p$ per period
 		\end{itemize}
@@
 \begin{enumerate}
+	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Resources
+	\begin{alignat}{10}
+		& ue'_{1p} 
+			&& 	= \overbrace{ ue_{2p} + ued_{p} }^\text{deviation}
+				+ \overbrace{ ue_{1p} - \hat{uu}_{1p} }^\text{unused} \quad
+			&& \forall p \in \{ \text{Carry Over Resources} \} \\
+		& ue'_{1p} 
+			&& 	= ue_{2p} + ued_{p} \quad
+			&& \forall p \in \{ \text{Non Carry Over Resources} \} \\
+		& ue'_{tp} 
+			&& = ue_{t+1,p} \quad 
+			&& \forall t \in \{2...T-1\} p \\
+		& ue'_{Tp} 
+			&& = uen_{p} \quad
+			&& \forall p
+	\end{alignat}
 
-	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Units of PPE
-		\begin{align} \begin{split}  
-			ue'_{1p} = & ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \\
-				& - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc} \quad \forall p 
-		\end{split} \end{align} 
-		\begin{equation}  
-			ue'_{t-1,p} = ue_{tp} \quad \forall t \in \{3...T\}, p
-		 \end{equation} 
-		\begin{equation}  
-			ue'_{Tp} = uen_{p} \quad \forall p 
-		\end{equation}
+	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Resources	
+	\begin{alignat}{10}
+		& uu'_{tp}
+			&& = \hat{uu}_{t+1,p} + 
+				\overbrace{ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) }^\text{
+					change in complexities} \quad
+			&& \forall t \in \{1...T-1\} \\
+		& uu'_{Tp}
+			&& = 0 \quad
+			&& \forall p
+	\end{alignat}
 
-	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Units of PPE		
-		\begin{align} \begin{split}  
-			uu'_{t-1,p} = &  uu	_{tp} + \sum_{mdc} ( sc_{tmdc} U_{pdc} ) - \\ 
-								&	- \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) + \\ 
-								& 	+ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})  \quad \forall t \in \{2...T\}, p  
-		\end{split} \end{align}
-		\begin{equation}  
-			uu'_{Tp} = 0 \quad \forall p 
-		\end{equation}
+	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients on waitlist
+		\begin{alignat}{10}
+			& pw'_{0dc} 
+				&& = pea_{dc} \quad
+				&& \forall dc \\  
+			& pw'_{mdc} 
+				&& = \hat{pw}_{m-1,dc} + 
+				\overbrace{pwt_{m-1,d-1,c} - pwt_{m-1,dc}}^\text{
+					change in complexities} \quad
+				&& \forall m \in \{ 1...M-1 \} dc \\  
+			& pw'_{Mdc} 
+				&& = \sum_{M-1}^{M} \big( 
+					\hat{pw}_{mdc} + 
+					\overbrace{pwt_{md-1,c} - pwt_{mdc}}^\text{
+						change in complexities} \big) \quad
+				&& \forall dc
+		\end{alignat}
 
-	\item Transition from $\vec{uv}$ to $\vec{uv'}$ - Violation of PPE units
-	\begin{equation}
-		uv'_{tp} \ge uu'_{tp} - ue'_{tp} \quad \forall tp
-	\end{equation}
-	\begin{equation}
-		uv'_{tp} \ge 0 \quad \forall tp
-	\end{equation}
-	\begin{equation}
-		uv'_{tp} = \max \{0, uu'_{tp} - ue'_{tp} \} \quad \forall tp
-	\end{equation}
-
-	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
-		\begin{equation}  
-			pw'_{0dc} = pea_{dc} \quad \forall dc 
-		\end{equation} 
-		\begin{equation}  
-			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{0...M-2 \}, dc 
-		\end{equation} 
-		\begin{equation}  
-			pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - 
-			\sum_{M-1}^{M} pwt_{mdc}\quad \forall dc 
-		\end{equation}
-
-	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts between difficulties/scheduling/cancelling for scheduled appointments
-		\begin{equation}
-			ps'_{t0dc} = 0 \quad \forall tdc
-		\end{equation}
-		\begin{align}  \begin{split}
-			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'} rsc_{tt'mdc} + \sum_{t} rsc_{tt'mdc} +\\ 
-										& + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc 
-		\end{split} \end{align} 
-		\begin{align} \begin{split}  
-			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t'M-1}^M rsc_{tt'mdc} + \\
-									& \sum_{t,M-1}^M rsc_{tt'mdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
-									\quad \forall t \in \{2...T \}, dc 
-		\end{split} \end{align}		
-		\begin{equation}  
-			ps'_{Tmdc} = 0 \quad \forall mdc 
-		\end{equation} 
+	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts scheduled
+		\begin{alignat}{10}
+			& ps'_{t0dc} 
+				&& = 0 \quad
+				&& \forall tdc \\  
+			& ps'_{Tmdc} 
+				&& = 0 \quad
+				&& \forall mdc \\  
+			& ps'_{tmdc} 
+				&& = \hat{ps}_{t+1,m-1,dc} + 
+				\overbrace{pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc}}^\text{
+					change in complexities} \quad
+				&& \forall t \in \{1...T-1\} m \in \{ 1...M-1 \} dc \\  
+			& ps'_{tMdc} 
+				&& = \sum_{M-1}^{M} \big( 
+				\hat{ps}_{t+1mdc} + 
+				\overbrace{pst_{t+1,md-1,c} - pst_{t+1,mdc}}^\text{
+					change in complexities} \big) \quad
+				&& \forall t \in \{1...T-1\} dc
+		\end{alignat}
 \end{enumerate}
@@
 \subsection{Costs}
-Cost will come from two source:  
+Cost will come from 3 sources:  
 \begin{itemize} 
-	\item cost of waiting ($cw$) (comes from 2 things)
-	\item cost of canceling ($cc$)
-	\item goal variable (to eliminate constraint violation, but still allow it if necessary)
+	\item waiting ($cw$)
+	\item rescheduling ($cc = \lceil cw^M \rceil$)
+	\item resource violation ($M$)
 \end{itemize}
 
-\begin{align} \begin{split}  
-	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = 
-		& \sum_{mdc} cw_{m} (pw_{mdc} - \sum_{t} sc_{tmdc}) +  \\
-		& \sum_{tdc} cw_{M} (ps_{tMdc}) (\text{ to prevent infinite rescheduling })+ \\
-		& + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} - cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + \\ 
-		& + M (uv_{tp})
-\end{split} \end{align} 
-$cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):
-	\begin{equation}  cw_{m} = val^m \quad \forall m \end{equation} 
-$cc$ is some arbitrary value
+\begin{equation}\begin{alignedat}{10}
+	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
+		&& 
+			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
+				cost of waiting}  + 
+			\overbrace{ \sum_{tdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
+				prevent infinite reschedules} + \\
+	&	&&  +
+			\overbrace{
+				cc \sum_{
+				\substack{tt`mdc \\ t' > t}} 
+				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
+			\overbrace{ 
+				cc \sum_{
+				\substack{tt`mdc \\ t' < t}}
+				rsc_{tt'mdc}}^\text{Good Reschedule} + 
+			M \sum_{tp} uv_{tp}
+\end{alignedat}\end{equation}
 
@@
 \subsection{Full LP} 
-Given a full MDP model, the equivalent LP would look as follows 
-(Note: there is a lot left out.
-$\vec{C}$ is defined above, all states, actions, and next states are all defined above).
-Probability distribution is not explicitly defined, but I am not sure if it is necessary
+Given a full MDP model, the equivalent LP would look as follows:
 \begin{equation}
@@
 \begin{equation}
-	c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
+	c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
 \end{equation}
 
-\subsection{Full ADP LP }
+\section{Aproximate Dynamic Programming Model}
+\subsection{Full ADP Model}
 Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
-\begin{align} \begin{split}
-	v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) =  & \beta^0 +
-		\sum_{tp} \beta_{tp}^{ue} ue_{tp} +
-		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + 
-		\sum_{tp} \beta_{tp}^{uv} uv_{tp} + \\
-		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
+\begin{equation}\begin{alignedat}{10}
+	& v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) 
+		&& =  \beta^0 + \sum_{tp} \beta_{tp}^{ue} ue_{tp} +
+			\sum_{tp} \beta_{tp}^{uu} uu_{tp} + \\
+		& && + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
 			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
-\end{split} \end{align}
+\end{alignedat} \end{equation}
 
@@
 Subject to:
-\begin{align*}
-	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
-		& \Bigg( \beta^{0} + \\ 
+\begin{equation}\begin{alignedat}{10}
+\label{full-adp-equation}
+	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
+		\beta^0 + \\
 	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
-			(ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc}) \bigg)  \\ 
-		& \bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
-				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
-		& \bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
+			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
+		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
+		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
 	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-				\Big( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
-				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc})  + \\ 
-				& \quad \quad \quad \quad \quad \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) \Big) \bigg) +  \\
-		& \bigg( \sum_{tp} uv'_{tp} \bigg) + \\ 
-			& \bigg( \sum_{dc} \beta_{0dc}^{pw} (pea_{dc}) \bigg) + \\
-		&  \bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
-			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) \bigg) + \\
-		& \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
-			(\sum_{M-1}^{M} pw_{mdc} - \sum_{M-1,t}^{M} sc_{tmdc} + 
-			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) \bigg) + \\
-		& \bigg( \sum_{mdc} \beta_{Tmdc}^{ps} * 0  \bigg) + \\
-		& \bigg( \sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
-			\Big( ps_{t+1m-1dc} - \sum_{t} sc_{t+1,m-1,dc} + 
-			pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc} - \\
-		& \quad \quad \quad \quad \quad \quad  \quad \quad- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \Big) \bigg) + \\
-		& \bigg( \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
-			\Big( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
-			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} - \\ 
-			& \quad \quad \quad \quad \quad \quad \quad - \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \Big) \bigg) \\
-		& \Bigg) \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
-\end{align*}
-\begin{equation*}
+			( \hat{uu}_{t+1,p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})) \bigg) +
+		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
+	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
+		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
+			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
+	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
+			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
+	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
+		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
+		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
+			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
+	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
+			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
+	\Bigg) \ge v(\vec{ue}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
+\end{alignedat} \end{equation}
+\begin{equation}
 	\vec{\beta} \ge 0 \quad \forall \beta
-\end{equation*}
+\end{equation}
+And all auxiliary constraints in "\nameref{auxiliary constraints}"
 
-\subsection{Expectation ADP LP}
-Steps for converting the mega constraint $v(\vec{S'})$ into expectation and merging it with $v({\vec{S}})$:
+\subsection{Expectation ADP Model}
+Steps for rearranging and converting the constraint (\ref{full-adp-equation}) into expectation:
 \begin{itemize}
-	\item $\beta^{0}$ - no adjustments for expectation for $v(\vec{S'})$ 
-	\begin{equation*}
-		\beta^{0} - \gamma \beta^{0} = \color{red} (1-\gamma) \beta^{0}
-	\end{equation*}
-
-	\item $\beta_{tp}^{ue}$
-	\begin{equation*}
-		E[ued_{p}] = 0 \quad \therefore \quad
-		\sum_{p} \beta_{1p}^{ue} (ue_{2p} + ued_{p}) \rightarrow 
-		\sum_{p} \beta_{1p}^{ue} (ue_{2p}) \rightarrow
-		\sum \beta_{tp}^{ue} uen_{p}
-	\end{equation*}
-	{ \color{red} \begin{align*}
-		 \Bigg( 
-			& \bigg( \sum_{p} \beta_{1p}^{ue} (ue_{1p} - 
-				\gamma \Big( uen_{p} + ue_{1p} - uu_{1p} - 
-				\sum_{dc} U_{pdc} (\sum_{m} sc_{1mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) \bigg) + \\
-			& \bigg(\sum_{t=2p}^{T} \beta_{tp}^{ue} (ue_{tp} - \gamma (uen_{p}) \bigg) \Bigg)
-	\end{align*} }
-
-	\item $\beta_{tp}^{uu}$ - no adjustments for expectation
-	\begin{equation*}
-		uu_{Tp} = 0 \quad \therefore \quad \beta_{Tp}^{uu} uu_{Tp} = 0
-	\end{equation*}
-	\begin{align*}
-		\sum_{tp}^{T-1} \beta_{tp}^{uu} uu_{tp} - \gamma \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( 
-					& uu_{t+1p} + \sum_{mdc} (sc_{t+1mdc}U)  - \sum_{tmdc} (rsc_{t+1t'mdc} U) + \sum_{t'mdc} (rsc_{tt'+1mdc} U) + \\ 
-					&\sum_{mdc} ps_{tmdc}pwp_{mdc} (U_{pd+1c} - U_{pdc}) \bigg)
-	\end{align*}
-	{ \color{red} \begin{align*}
-		 \Bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} \bigg( & 
-		 	uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} ps_{tmdc}pwp_{mdc} (U_{pd+1c} - U_{pdc}) + \\
-			& U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big) \bigg) + \\
-		\beta_{Tp}^{uu} (uu_{Tp}) \Bigg)
-	\end{align*} }
-
-	\item $\beta_{tp}^{uv}$
-	\begin{equation*}
-		E[uv_{tp}] = 0
-	\end{equation*}
-	\begin{equation*}
-		\sum_{tp} \beta_{tp}^{uv} (uv_{tp} - \gamma (E[uv_{tp}])) = 
-		\color{red} \sum_{tp} \beta_{tp}^{uv} uv_{tp} 
-	\end{equation*}
-
-	\item $\beta_{mdc}^{pw}$ - Let's assume $pwp_{mdc}$ - is the probability of a patient transitioning to a higher complexity
-	\begin{equation*}
-		E[pwt_{mdc}] = pw_{mdc} pwp_{mdc}		
-	\end{equation*}
-	{ \color{red} \begin{align*}
-		\Bigg( \sum_{dc} \beta_{0dc}^{pw} & (pw_{0dc} - \gamma E[pea_{dc}]) + \\
-		\sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} & ( pw_{mdc} - \gamma 
-			\big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) + \\
-		\sum_{dc} \beta_{Mdc}^{pw} & ( pw_{Mdc} - \gamma \sum_{M-1}^{M}
-			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Bigg)
-	\end{align*} }
-
-	\item $\beta_{mdc}^{ps}$
-	\begin{equation*}
-		E[pst_{tmdc}] = ps_{tmdc} pwp_{mdc}		
-	\end{equation*}
-	{ \color{red} \begin{align*}
-		\Bigg( \sum_{tdc} \beta_{t0dc}^{ps} & * ps_{Tmdc} + \\
-			\sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} & 
-				\bigg( ps_{tmdc} - 
-					\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
-				&  - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) + \\
-		\sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} & 
-			\bigg( ps_{tMdc} - 
-				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
-				&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) + \\ 
-		\sum_{mdc} \beta_{Tmdc}^{ps} & 
-			\bigg( ps_{Tmdc} \bigg) \Bigg)
-	\end{align*} }
-
+	\item $E[ued_p] = 0$
+	\item $E[pwt_{mdc}] = ptp_{mdc} * \hat{pw}_{mdc}$ 
+	\item $E[pst_{tmdc}] = ptp_{mdc} * \hat{ps}_{tmdc}$ 
 \end{itemize}
 
-Let's say $E[V]$ is the addition of all the red parts above. In that case the ADP model converted to expectation would look as follows:
 \begin{equation}
-	\max_{\vec{\beta}} \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
-		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps]
+	\beta^{0}: \qquad (1-\gamma) \beta^{0}
+\end{equation}
+\begin{equation}
+\beta^{ue}_{tp}: \qquad 
+	\sum_{p} \beta_{1p}^{ue} \Big( ue_{1p} - \gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p}) \Big) + \sum_{t=2p}^{T} \beta_{tp}^{ue} \Big( ue_{tp} - \gamma (uen_{p}) \Big)
+\end{equation}
+\begin{equation}
+\beta^{uu}_{tp}: \qquad \sum_{tp}^{T-1} \beta_{tp}^{uu} 
+	\Big(uu_{tp} - \gamma 
+	(\hat{uu}_{t+1p} + \sum_{mdc} E[pst_{t+1mdc}] (U_{pd+1c} - U_{pdc})) \Big) +
+	\sum_{p} \beta_{Tp}^{uu} \Big( uu_{Tp} \Big)
+\end{equation}
+\begin{equation}\begin{alignedat}{10}
+& \beta^{pw}_{mdc}: \qquad 
+	&& \sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) + 
+	\sum_{m=1dc}^{M-1} \beta_{mdc}^{pw} 
+	\Big( pw_{mdc} - \gamma 
+		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
+&	&& \sum_{dc} \beta_{Mdc}^{pw} 
+	\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
+		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
+\end{alignedat} \end{equation}
+\begin{equation}\begin{alignedat}{10}
+& \beta^{ps}_{tmdc}: \qquad 
+	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
+	\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + \\
+&	&& 
+	\sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
+	\Big( ps_{tmdc} - \gamma 
+		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
+&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
+	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
+		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
+\end{alignedat} \end{equation}
+
+Let's say $E[V]$ is the addition of all parts above. Then the ADP model converted to expectation would look as follows:
+\begin{equation}
+	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
+		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
 \end{equation}
@@
 
-\subsection{Dual of ADP LP}
+\subsection{ADP Master Problem}
 \label{Dual of ADP LP}
@@
 Subject To:
-\begin{itemize}
-	\item $\beta^{0}$ constraints
+
+\begin{alignat}{10}
+	& \beta^{0}: 
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
+	& \beta^{ue}: 
+		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{1p} - 
+			\gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p}) \Big) \ge E[ue_{tp}]
+		&&	\forall p \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - 
+			\gamma (uen_{p}) \Big) \ge E[ue_{tp}] 
+		&& 	\forall t \in (2...T) p \\ 
+	& \beta^{uu}: 
+		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(uu_{tp} - 
+		\gamma (\hat{uu}_{t+1p} + \sum_{mdc} E[pst_{t+1mdc}] (U_{pd+1c} - U_{pdc}) ) \Big) 
+		\ge E[uu_{tp}]
+		&&	\forall t \in \{1...T-1\}p \\
+	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(uu_{Tp} \Big) \ge E[uu_{Tp}]
+		&&	\forall p \\
+	&	\beta^{pw}: 
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
+		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
+		&&	\forall dc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
+		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
+		&&	\forall m \in \{1...M-1\} dc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
+			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
+		&&	\forall dc \\ 
+	&	\beta^{ps}: 
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
+		&&	\forall tdc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
+		&&	\forall mdc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
+			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
+		&&	\forall \{1...T-1\} \{1...M-1\}dc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
+		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
+		&&	\forall \{1...T-1\} dc
+\end{alignat}
+
 \begin{equation}
-		\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 
+	\text{State Action Bounds:} \qquad w \ge 0 \qquad \forall w
 \end{equation}
 
-	\item $\beta^{ue}$ constraints	
-	\begin{multline}
-		\sum_{\vec{S}\vec{A}}\vec{w} \bigg(ue_{1p} - 
-			\gamma \Big( uen_{p} + ue_{1p} - uu_{1p} - 
-			\sum_{dc} U_{pdc} ( \sum_{m} sc_{mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) \bigg) \\ 
-		\ge E[ue_{1p}] \quad \forall p
-	\end{multline}
-	\begin{equation}
-		\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - \gamma (uen_{p}) \Big) \ge E[ue_{tp}] \quad \forall t \in (2...T) p
-	\end{equation}
-
-	\item $\beta^{uu}$ constraints
-	\begin{multline}
-		\sum_{\vec{S}\vec{A}} \vec{w} \bigg( 
-			uu_{tp}	 - \gamma \Big( uu_{t+1p} + \sum_{mdc} ps_{tmdc}pwp (U_{pd+1c} - U_{pdc}) + \\ 
-			U_{pdc} \big( \sum_{mdc} sc_{t+1mdc}  - \sum_{t'mdc} rsc_{t+1t'mdc} + \sum_{tmdc} rsc_{tt'+1mdc} \big) \Big)
-		\bigg) \ge E[uu_{tp}] \\
-		\quad \forall T \in \{1...T-1\}p
-	\end{multline}
-	\begin{equation}
-		\sum_{\vec{S}\vec{A}} \vec{w} (uu_{Tp}) \ge E[uu_{Tp}] \quad \forall p
-	\end{equation}
-
-	\item $\beta^{uv} constraints$
-	\begin{equation}
-		\sum_{\vec{S}\vec{A}} \vec{w} (uv_{tp}) \ge E[uv_{tp}] \quad \forall tp
-	\end{equation}
-
-	\item $\beta^{pw}$ constraints
-	\begin{equation}
-		  \sum_{\vec{S}\vec{A}}w  ( pw_{0dc} - \gamma E[pea_{dc}]) \ge E[pw_{0dc}] \quad \forall dc
-	\end{equation}
-	\begin{multline}
-		\sum_{\vec{S}\vec{A}}w  \Big( pw_{mdc} - \gamma \big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \big) \Big) \\ 
-		\ge E[pw_{mdc}]  \quad \forall m \in \{1 ... M-1 \}dc
-	\end{multline}
-	\begin{equation}
-		\sum_{\vec{S}\vec{A}}w  \Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
-			\big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \big) \Big) \ge E[pw_{Mdc}] \quad \forall dc
-	\end{equation}
-
-	\item $\beta^{ps}$ constraints
-	\begin{equation}
-		 \sum_{\vec{S}\vec{A}}w (ps_{t0dc}) \ge E[ps_{t0dc}] \quad \forall tdc 
-	\end{equation}
-	\begin{multline}
-		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
-				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - sc_{t+1m-1dc} \\ 
-				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
-				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} m \in \{1 ... M-1 \} dc
-	\end{multline}
-	\begin{multline}
-		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
-				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - sc_{t+1mdc} \\ 
-				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 
-				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} dc
-	\end{multline}
-	\begin{equation}
-		\sum_{\vec{S}\vec{A}} \vec{w} (ps_{Tmdc}) \ge E[ps_{Tmdc}] \quad \forall mdc
-	\end{equation}
-
-	\item State-Action constraints
-	\begin{equation}
-		w \ge 0 \quad \forall w
-	\end{equation}
-\end{itemize}
-
-\subsection{Finding most violated constraints of ADP LP}
+\subsection{ADP Pricing Problem}
 \label{Pricing Problem}
@@
 Subject to:
-all constraints in section "\nameref{action constraints}"
+constraints in sections "\nameref{state-action constraints}" and "\nameref{auxiliary constraints}"
 
+\section{Solution Explanation}
 \subsection{Algorithm for solving}
@@
 \begin{enumerate}
-	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pe], E[pw] E[pw]$ (this will only give an approximation as arbitrary policy will likely be different from ADP policy) (if you wanted to, you could resolve for $\vec{\beta}$ again, but replacing $E[ue], E[uu], E[pe], ...$ with the ones that would be generated through the ADP policy)
+	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pw] E[pw]$
 	\item Create an initial feasible set of state-action pairs - $\vec{w}$
-	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints
+	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints for a specific action.
 	\item Solve model in section "\nameref{Pricing Problem}", where duals from problem in step 3  correspond to $\vec{\beta}$ values. 
@@
 Subject to:
-all constraints in section "\nameref{action constraints}"
+constraints in section "\nameref{state-action constraints}"
 

### 2021-05-16 Implementation/Modules/simulation.py

@@ -27,68 +27,62 @@ def initial_state(input_data) -> state:
     # Unit States
     ue = {}
     uu = {}
-    uv = {}
     for tp in itertools.product(indices['t'], indices['p']):
         ue[tp] = ppe_data[tp[1]].expected_units
-        uv[tp] = 0
         uu[tp] = 0
 
-    init_state = state(ue, uu, uv, pw, ps)
+    init_state = state(ue, uu, pw, ps)
 
     return init_state
 # Initializes Action ( Everything Empty )
 def initial_action(input_data) -> action:
     indices = input_data.indices
 
+    # Action
     sc = {}
     for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
         sc[tmdc] = 0
     rsc = {}
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
         rsc[ttpmdc] = 0
+    
+    # Violation
+    uv = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uv[tp] = 0
+    
+    # Auxiliary variables
+    uu_p = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uu_p[tp] = 0
+    pw_p = {}
+    for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
+        pw_p[mdc] = 0
+    ps_p = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        ps_p[tmdc] = 0
 
     # Returns
-    init_action = action(sc, rsc)
+    init_action = action(sc, rsc, uv, uu_p, pw_p, ps_p)
     return(init_action)
 
 # Executes Action
 def execute_action(input_data, state, action) -> state:
     
+    indices = input_data.indices
     new_state = deepcopy(state)
 
-    # Handles Reschedules
-    for t in input_data.indices['t']:
-        for tp in input_data.indices['t']:
-            for mdc in itertools.product(input_data.indices['m'], input_data.indices['d'], input_data.indices['c']):
-
-                # Change
-                rescheduled_number = action.rsc_ttpmdc[(t, tp, mdc[0], mdc[1], mdc[2])]
-
-                # Reschedules Out
[…]

### 2021-05-16 Implementation/main.py

@@ -1,152 +1,0 @@
-# %% Packages
-from Modules.data_import import *
-from Modules.data_export import *
-from Modules.master_model import *
-from Modules.sub_problem import *
-from Modules.simulation import *
-from Modules.decorators import timer
-import os.path
-
-# read_data = timer(read_data)
-# generate_master_model = timer(generate_master_model)
-# generate_phase1_master_model = timer(generate_phase1_master_model)
-# generate_sub_model = timer(generate_sub_model)
-# update_master_model = timer(update_master_model)
-# gp.Model.optimize = timer(gp.Model.optimize)
-
-my_path = os.path.dirname(__file__)
-input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
-
-def non_zero_state(state: state):
-    for key,value in state.ue_tp.items():
-        if state.ue_tp[key] >= 0.1: print(f'\tUnits Expected - {key} - {state.ue_tp[key]}')
-        if state.uu_tp[key] >= 0.1: print(f'\tUnits Used - {key} - {state.uu_tp[key]}')
-        if state.uv_tp[key] >= 0.1: print(f'\tUnits Violated - {key} - {state.uv_tp[key]}')
-    for key,value in state.pw_mdc.items(): 
-        if value >= 0.1: print(f'\tPatients Waiting- {key} - {value}')
-    for key,value in state.ps_tmdc.items(): 
-        if value >= 0.1: print(f'\tPatients Scheduled- {key} - {value}')
-def non_zero_action(action: action):
-    for key,value in action.sc_tmdc.items():
-        if value >= 0.1: print(f'\tPatients Schedule - {key} - {value}')
-    for key,value in action.rsc_ttpmdc.items(): 
-        if value >= 0.1: print(f'\tPatients Reschedule- {key} - {value}')
-# %% Simulation
-# cost_data = generate_expected_values(input_data, 30, 1000)
-# fas_costs = simulation(input_data, 10, 600, 300, fas_policy)
-# myopic_cost = simulation(input_data, 10, 600, 300, myopic_policy)
-# fas_cost_total = 0
-# myopic_cost_total = 0
-# for repl in fas_costs:
-#     for day in repl:
-#         fas_cost_total += day
-# for repl in myopic_cost:
-#     for day in repl:
-#         myopic_cost_total += day
-# print(fas_cost_total)
-# print(myopic_cost_total)
-curr_state = initial_state(input_data)
-for i in range(10):
-    print()
-    print(f'Day {i} - Initial State')
[…]

### 2021-05-16 Implementation/optimization.py

@@ -1,0 +1,114 @@
+# %% Packages
+from Modules.data_import import *
+from Modules.data_export import *
+from Modules.master_model import *
+from Modules.sub_problem import *
+# from Modules.decorators import timer
+import os.path
+
+# read_data = timer(read_data)
+# generate_master_model = timer(generate_master_model)
+# generate_phase1_master_model = timer(generate_phase1_master_model)
+# generate_sub_model = timer(generate_sub_model)
+# update_master_model = timer(update_master_model)
+# gp.Model.optimize = timer(gp.Model.optimize)
+
+my_path = os.path.dirname(__file__)
+input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
+    
+
+
+    
+# %% Generate Initial Feasible Set (Phase 1)
+init_state, init_action = generate_initial_state_action(input_data)
+state_action_list = [(init_state, init_action)]
+
+count = 0
+mast_model, mast_var, mast_const = generate_master_model(input_data, state_action_list)
+
+while True:
+    
+    # Generates and Solves Master
+    p1_mast_model, p1_mast_const = generate_phase1_master_model(input_data, mast_model)
+    p1_mast_model.Params.LogToConsole = 0
+    p1_mast_model.optimize()
+    betas = generate_beta_values(input_data, p1_mast_const)
+        
+    # Debugging
+    print(f'Phase 1 - iteration {count+1}, Mast Objective {p1_mast_model.getObjective().getValue()}')
+    count += 1
+
+    # Stops if necessary
+    if p1_mast_model.getObjective().getValue() <= 0:
+        print('Found Feasible Set')
+        break
+    
+    # Generates and solves Subproblem 
+    p1_sub_model, p1_sub_var = generate_sub_model(input_data, betas, True)
+    p1_sub_model.Params.LogToConsole = 0
+    p1_sub_model.optimize()
+    
+    # Update State-Actions
+    state_action = generate_state_action(p1_sub_var)
+    state_action_list.append(state_action)
+    mast_model, mast_var, mast_const = update_master_model(input_data, mast_model, mast_var, mast_const, state_action, count)
+    
+    # Stops if necessary
+    if state_action_list[-1] == state_action_list[-2]:
+        print('Unable to find feasible set')
+        break
+
[…]

### 2021-05-18 Manuscript/Manuscript.tex
fixed a few mistakes with simulation
- Added ability for resources to be carried over
- Changed how action is generated to be correct (exclude current state value)

TODO:
- fas simulation

@@
 		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
-		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
+		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{p} \bigg) + \\
 	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
@@
 \end{equation*}
-\begin{align*}
-	v(S') = \bigg(  & \beta^0 + \sum_{t=2p}^{T} \beta_{tp}^{ue} uen_{p} + \\ 
-	& \sum_{p} \beta_{1p}^{ue} \Big( uen_{p} + ue_{1p} - uu_{1p} - 
-		\sum_{dc} U_{pdc} (\sum_{m} sc_{1mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) + \\
-	& \sum_{tp}^{T-1} \beta_{tp}^{uu} \Big( uu_{t+1p} + 
-		\sum_{mdc} ps_{tmdc}pwp_{} (U_{pd+1c} - U_{pdc}) + 
-		U_{pdc} \big( \sum_{mdc} sc_{t+1}  - \sum_{t'mdc} rsc_{t+1t'} + 
-		\sum_{tmdc} rsc_{tt'+1} \big) \Big) + \\
-	& \sum_{dc} \beta_{0dc}^{pw} E[pea_{dc}]) + \\
-	& \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} \Big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \Big) + \\
-	& \sum_{dc} \beta_{Mdc}^{pw} \sum_{M-1}^{M} \Big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \Big) + \\
-	& \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} 
-		\Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} - \\
-		& - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) + \\
-	& \sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
-	&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg)
-	& \bigg)
-\end{align*}
+
+\begin{equation}\begin{alignedat}{10}
+	&	v(S') = \Bigg( 
+		&& 	\beta^0 + 
+			\bigg( \sum_{p} \beta_{1p}^{ue} 
+				(uen_{d} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
+			\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\
+	&	&& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
+				( \hat{uu}_{t+1,p} + \sum_{mdc} E[pst_{tmdc}] (U_{pd+1c} - U_{pdc})) \bigg) + \\
+	&	&&	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
+			\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
+				(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \bigg) + \\
+	&	&&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
+				(\sum_{M-1}^{M} \hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}])\bigg) + \\
+	& 	&&	\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
+				(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \bigg) + \\	
+	&	&&	\qquad \qquad \bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
+				(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}])) \bigg)
+			\Bigg)
+\end{alignedat}
+\end{equation}
+
 Subject to:

### 2021-05-18 Implementation/simulation.py

@@ -79,3 +79,4 @@ for i in range(5):
     # print(f'\t Cost: {state_action_cost(input_data, curr_state, new_action)}')
 
     curr_state = execute_transition(input_data, curr_state)
+# %%

### 2021-05-24 Manuscript/Manuscript.tex
fixing bugs and testing things

@@
 	\begin{itemize}
-		\item If we have violation of PPE units - it reduces capacity in the future (Meaning violations are borrowed from future capacity)
+		\item If we have violation of PPE units - the extra capacity comes from external source
 	\end{itemize}
@@
 		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
-		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
+		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
 		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t' 
@@
 			&& 	= \overbrace{ ue_{2p} + ued_{p} }^\text{deviation}
-				+ \overbrace{ ue_{1p} - \hat{uu}_{1p} }^\text{unused} \quad
+				+ \overbrace{ ue_{1p} - \hat{uu}_{1p} }^\text{unused} + uv_{1p} \quad
 			&& \forall p \in \{ \text{Carry Over Resources} \} \\
@@
 				cost of waiting}  + 
-			\overbrace{ \sum_{tdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
+			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
 				prevent infinite reschedules} + \\
@@
 				\overbrace{
-				cc \sum_{
+					\sum_{tmdc} cw^{m} * t * (1/M)  (sc_{tmdc})
+				}^\text{Prefer earlier appointments} \\ 
+	&	&&  +
+			\overbrace{
+				(1.5cc+cw^{m}) \sum_{
 				\substack{tt`mdc \\ t' > t}} 
@@
 			\overbrace{ 
-				cc \sum_{
+				(0.5cc) \sum_{
 				\substack{tt`mdc \\ t' < t}}
@@
 	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
-			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
+			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
 		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
@@
 \beta^{ue}_{tp}: \qquad 
-	\sum_{p} \beta_{1p}^{ue} \Big( ue_{1p} - \gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p}) \Big) + \sum_{t=2p}^{T} \beta_{tp}^{ue} \Big( ue_{tp} - \gamma (uen_{p}) \Big)
+	\sum_{p} \beta_{1p}^{ue} \Big( ue_{1p} - \gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{tp}) \Big) + \sum_{t=2p}^{T} \beta_{tp}^{ue} \Big( ue_{tp} - \gamma (uen_{p}) \Big)
 \end{equation}
@@
 \begin{equation}
-	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu] + \sum \beta^{uv} E[uv] 
+	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu]
 		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
@@
 		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{1p} - 
-			\gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p}) \Big) \ge E[ue_{tp}]
+			\gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \Big) \ge E[ue_{tp}]
 		&&	\forall p \\
@@
 			\bigg( \sum_{p} \beta_{1p}^{ue} 
-				(uen_{d} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
+				(uen_{d} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
 			\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\

### 2021-05-24 Implementation/Modules/data_export.py

@@ -91,3 +91,43 @@ def export_betas(betas, data_file_path):
 
     # Saves
     wb.save(data_file_path)
+def export_expected_vals(data_file_path, state):
+    wb = openpyxl.load_workbook(data_file_path, data_only=True)
+    ws = wb["Expected State Values"]
+
+    # UE
+    count = 3
+    for tp, v in state.ue_tp.items():
+        ws.cell(row=count, column=1).value = tp[1]
+        ws.cell(row=count, column=2).value = tp[0]
+        ws.cell(row=count, column=3).value = v
+        count += 1
+
+    # UU
+    count = 3
+    for tp, v in state.uu_tp.items():
+        ws.cell(row=count, column=4).value = tp[1]
+        ws.cell(row=count, column=5).value = tp[0]
+        ws.cell(row=count, column=6).value = v
+        count += 1
+
+    # PW
+    count = 3
+    for mdc, v in state.pw_mdc.items():
+        ws.cell(row=count, column=7).value = mdc[0]
+        ws.cell(row=count, column=8).value = mdc[1]
+        ws.cell(row=count, column=9).value = mdc[2]
+        ws.cell(row=count, column=10).value = v
+        count += 1
+
+    # UE
+    count = 3
+    for tmdc, v in state.ps_tmdc.items():
+        ws.cell(row=count, column=11).value = tmdc[0]
+        ws.cell(row=count, column=12).value = tmdc[1]
+        ws.cell(row=count, column=13).value = tmdc[2]
+        ws.cell(row=count, column=14).value = tmdc[3]
+        ws.cell(row=count, column=15).value = v
+        count += 1
+        
+    wb.save(data_file_path)

### 2021-05-24 Implementation/Modules/master_model.py

@@ -73,12 +73,16 @@ def cost_function(input_data: input_data_class, state: state, action: action):
     for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
         cost += model_param.cw**indices['m'][-1] * ( action.ps_p_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
 
-    # Cost of Cancelling
+    # Prefer Earlier Appointments
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        cost += model_param.cw**tmdc[1] * tmdc[0] * 1/input_data.model_param.M * ( action.sc_tmdc[(tmdc[0],tmdc[1],tmdc[2],tmdc[3])] )
+
+    # Cost of Rescheduling
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
         if ttpmdc[0] > ttpmdc[1]: #good schedule
-            cost -= model_param.cc * action.rsc_ttpmdc[ttpmdc]
+            cost -= (model_param.cc-model_param.cw) * action.rsc_ttpmdc[ttpmdc]
         elif ttpmdc[1] > ttpmdc[0]: #bad schedule
-            cost += model_param.cc * action.rsc_ttpmdc[ttpmdc]
+            cost += (model_param.cc+model_param.cw) * action.rsc_ttpmdc[ttpmdc]
 
     # Violating unit bounds
     for tp in itertools.product(indices['t'], indices['p']):
@@ -111,7 +115,7 @@ def b_ue_constraint(input_data: input_data_class, state: state, action: action) 
     # Creates Data
     for tp in itertools.product(indices['t'], indices['p']):
         if tp[0] == 1:
-            lhs[tp] = state.ue_tp[tp] - gamma*( ppe_data[tp[1]].expected_units + state.ue_tp[tp] - action.uu_p_tp[tp])
+            lhs[tp] = state.ue_tp[tp] - gamma*( ppe_data[tp[1]].expected_units + state.ue_tp[tp] - action.uu_p_tp[tp] + action.uv_tp[tp])
        
         elif tp[0] >= 2:
             lhs[tp] = state.ue_tp[tp] - gamma*(ppe_data[tp[1]].expected_units)
@@ -157,11 +161,11 @@ def b_uu_constraint(input_data: input_data_class, state: state, action: action) 
                         
                     # Otherwise
                     else:
[…]

### 2021-05-24 Implementation/Modules/simulation.py

@@ -19,7 +19,10 @@ def initial_state(input_data) -> state:
     # Patient States
     pw = {}
     for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
-        pw[mdc] = 0
+        if mdc[0] == 0:
+            pw[mdc] = arrival[(mdc[1], mdc[2])] 
+        else:
+            pw[mdc] = 0
     ps = {}
     for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
         ps[tmdc] = 0
@@ -95,18 +98,22 @@ def state_action_cost(input_data, state, action) -> float:
 
     # Cost of Waiting
     for mdc in itertools.product(indices['m'], indices['d'], indices['c']):            
-        cost += model_param.cw**mdc[0] * ( state.pw_mdc[mdc] )
+        cost += model_param.cw**mdc[0] * ( action.pw_p_mdc[mdc] )
 
     # Cost of Waiting - Last Period
     for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
-        cost += model_param.cw**indices['m'][-1] * ( state.ps_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
+        cost += model_param.cw**indices['m'][-1] * ( action.ps_p_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
+
+    # Cost of Later Schedulings
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        cost += (model_param.cw**tmdc[1] * tmdc[0] * 1/M) * ( action.sc_tmdc[(tmdc[0],tmdc[1],tmdc[2],tmdc[3])] )
 
     # Cost of Cancelling
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
         if ttpmdc[0] > ttpmdc[1]: #good schedule
-            cost -= model_param.cc * action.rsc_ttpmdc[ttpmdc]
+            cost -= (model_param.cc-model_param.cw) * action.rsc_ttpmdc[ttpmdc]
         elif ttpmdc[1] > ttpmdc[0]: #bad schedule
-            cost += model_param.cc * action.rsc_ttpmdc[ttpmdc]
+            cost += (model_param.cc+model_param.cw) * action.rsc_ttpmdc[ttpmdc]
 
     # Violating unit bounds
[…]

### 2021-05-24 Implementation/optimization.py

@@ -3,103 +3,131 @@ from Modules.data_import import *
 from Modules.data_export import *
 from Modules.master_model import *
 from Modules.sub_problem import *
-# from Modules.decorators import timer
+from Modules.decorators import timer
 import os.path
-
-# read_data = timer(read_data)
-# generate_master_model = timer(generate_master_model)
-# generate_phase1_master_model = timer(generate_phase1_master_model)
-# generate_sub_model = timer(generate_sub_model)
-# update_master_model = timer(update_master_model)
-# gp.Model.optimize = timer(gp.Model.optimize)
+import time
 
 my_path = os.path.dirname(__file__)
 input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
     
 
-
-    
 # %% Generate Initial Feasible Set (Phase 1)
+@timer
+def generate_feasible_sa_list(input_data, init_state_actions):
+    state_action_list = init_state_actions
+    
+    # Initializes
+    count = len(state_action_list)-1
+    mast_model, mast_var, mast_const = generate_master_model(input_data, state_action_list)
+
+    # Generates
+    while True:
+    
+        # Generates and Solves Master
+        p1_mast_model, p1_mast_const = generate_phase1_master_model(input_data, mast_model)
+        p1_mast_model.Params.LogToConsole = 0
+        p1_mast_model.optimize()
+        betas = generate_beta_values(input_data, p1_mast_const)
+            
+        # Debugging
+        print(f'Phase 1 - iteration {count+1}, Mast Objective {p1_mast_model.getObjective().getValue()}')
+        count += 1
+
+        # Stops if necessary
+        if p1_mast_model.getObjective().getValue() <= 0.00000000001:
+            print('Found Feasible Set')
+            break
+        
+        # Generates and solves Subproblem 
+        p1_sub_model, p1_sub_var = generate_sub_model(input_data, betas, True)
+        p1_sub_model.Params.LogToConsole = 0
+        p1_sub_model.optimize()
+        
+        # Update State-Actions
+        state_action = generate_state_action(p1_sub_var)
+        state_action_list.append(state_action)
+        mast_model, mast_var, mast_const = update_master_model(input_data, mast_model, mast_var, mast_const, state_action, count)
+        
+        # Stops if necessary
+        if state_action_list[-1] == state_action_list[-2]:
+            print('Unable to find feasible set')
+            break
+
[…]

### 2021-05-24 Implementation/simulation.py

@@ -4,11 +4,44 @@ from Modules.data_export import *
 from Modules.simulation import *
 import os.path
 
+import pandas as pd
+import numpy as np
+import matplotlib.pylab as plt
+import seaborn as sns
+
+
 my_path = os.path.dirname(__file__)
 input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
 betas = read_betas(os.path.join(my_path, 'Data', 'Optimal-Betas.xlsx'))
 
-# %% Checking Logic
+
+# %% Expected Values Simulation
+expected_values = generate_expected_values(input_data, 5, 1000, 500)
+export_expected_vals(os.path.join(my_path, 'Data', 'Data.xlsx'), expected_values)
+
+# %% Comparison of Policies
+repls = 1
+total_days = 505
+warm_up = 500
+# Myopic Policy (FAS)
+np.random.seed(10)
+myopic_cost = simulation(input_data, repls, total_days, warm_up, myopic_policy)
+# MDP Policy
+# np.random.seed(10)
+# mdp_cost = simulation(input_data, repls, total_days, warm_up, mdp_policy, betas=betas)
+
+# Visualization
+# myopic_cost_avg = pd.DataFrame(myopic_cost).transpose().mean(axis=1)
+# myopic_cost_avg = pd.DataFrame(myopic_cost_avg, columns=['Myopic'])
+# mdp_cost_avg = pd.DataFrame(mdp_cost).transpose().mean(axis=1)
+# mdp_cost_avg = pd.DataFrame(mdp_cost_avg, columns=['MDP'])
+# cost_frame = pd.concat([myopic_cost_avg, mdp_cost_avg], axis=1)
+# cost_frame['Day'] = cost_frame.index
+
+# sns.lineplot(data=cost_frame, x="Day", y="Myopic", label='Myopic')
+# sns.lineplot(data=cost_frame, x="Day", y="MDP", label='MDP')
+
+# %% Writing Out Things
 def non_zero_state(state: state):
     for key,value in state.ue_tp.items():
         if state.ue_tp[key] >= 0.1: print(f'\tUnits Expected - {key} - {state.ue_tp[key]}')
@@ -31,52 +64,23 @@ def non_zero_action(action: action):
     for key,value in action.ps_p_tmdc.items(): 
         if value >= 0.1: print(f'\tPatients Scheduled - Post Decision - {key} - {value}')
 
-# %% Expected Values Simulation
-cost_data = generate_expected_values(input_data, 30, 1000)
[…]

### 2021-06-26 v2-Manuscript/Manuscript.tex
working on a new version with streamlined model

--- 2021-05-24 Manuscript/Manuscript.tex
@@
 \begin{itemize}
-	\item Priority need to be added
+	\item Should $ul$ definition include units violated?? it seems a constraint might be violated otherwise
 \end{itemize}
@@
 
-	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($TL$). 
+	\item It is assumed that patients do not change complexities within some limit ($TL$). 
 	\begin{itemize}
-		\item Let's assume our limit is 10 periods, there is no difference in terms of cost between patients who has been waiting for 1 period and patients waiting 10 period for their appointment (assuming they are the same category).
-		\item However, if a patient waits for 11 period for their appointment there should be some kind of penalty for the wait
-		\item The penalty comes from increasing patient complexity. Higher complexities require more resources and are thus more costly overall in the system
+		\item Let's assume our limit is 10 periods, patients will never change complexities within the 10 periods.  
+		\item However, if a patient waits for 11 periods there is a possibility they increase complexity
 	\end{itemize}
@@
 		\item Good reschedules are allowed from any period after 2 into period 1
-		\item Bad reschedules are only allowed from period 1 to period 2
+		\item Bad reschedules are only allowed from period 1 to any period after 2
 	\end{itemize}
@@
 State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
-\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) \]
+\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
 \begin{itemize}
-    \item $\vec{ue} = ue_{tp}$ - Expected unist for  period $t$, and resource $p$
-    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and resource $p$
+	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1
     \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
@@
 \begin{itemize}
+	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
+	\item $\hat{ul}_{p}$ - post-decision unit leftover at period 1
+	\item $ulb_{p}$ - binary variable to enforce $ul$ variable without objective function
 	\item $\hat{uu}_{tp}$ - post-decision units used
@@
 
+\begin{itemize}
+
+	\item Define Resource Violation Variable
+	\begin{alignat}{10}
+			& \hat{uv}_{tp} 
+				&& \le  M(uvb_{tp}) \quad
+				&& \forall tp \\
+			& \hat{uv}_{1p} 
+				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
+				&& \forall p \\
+			& \hat{uv}_{tp} 
+				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
+				&& \forall t \in \{ 2..T \} p \\
+	\end{alignat}
+
+	\item Define Units Left Over Variable
+	\begin{alignat}{10}
+			& \hat{ul}_{p} 
+				&& \ge 0 \quad 
+				&& \forall p \\
+			& \hat{ul}_{p} 
+				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
+				&& \forall p \\
+			& \hat{ul}_{p} 
+				&& \le M (ulb_{p}) \quad 
+				&& \forall p \\
+			& \hat{ul}_{p} 
+				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
+				&& \forall p
+	\end{alignat}
+\end{itemize}
+
 \subsubsection{State-Action Constraints}
@@
 
-	\item Consistency Constraint
-	\begin{equation}
-		uu_{tp} = \sum_{mdc} U_{pdc} ps_{tmdc} \quad \forall tp
-	\end{equation}
 	\item Resource Usage Constraint
-	\begin{equation}
-		\hat{uu}_{tp} \le ue_{tp}+uv_{tp} \quad \forall tp
-	\end{equation}
+	\begin{alignat}{10}
+			& \hat{uu}_{1p} 
+			&& \le uen_{1p} + ul_{p} + uv_{1p} \quad 
+			&& \forall p \\
+		& \hat{uu}_{tp} 
+			&& \le uen_{tp} + uv_{tp} \quad
+			&& \forall t \in \{ 2..T \}p 
+	\end{alignat}
 
@@
 		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
-		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t' 
+		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t'=1 
 	\end{alignat}
@@
 	\begin{alignat}{10}
-		& ue_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
-		& uu_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
-		& pw_{mdc} 	&& \le pea_{dc} * 4 \quad 			&& \forall mdc \\
+		& ul_{p} 	&& \le uen_{p} * 3 \quad 	&& \forall p \\
+		& pw_{mdc} 	&& \le pea_{dc} * 20 \quad 			&& \forall mdc \\
 		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
@@
 \begin{enumerate}
-	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Resources
+	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
 	\begin{alignat}{10}
-		& ue'_{1p} 
-			&& 	= \overbrace{ ue_{2p} + ued_{p} }^\text{deviation}
-				+ \overbrace{ ue_{1p} - \hat{uu}_{1p} }^\text{unused} + uv_{1p} \quad
-			&& \forall p \in \{ \text{Carry Over Resources} \} \\
-		& ue'_{1p} 
-			&& 	= ue_{2p} + ued_{p} \quad
-			&& \forall p \in \{ \text{Non Carry Over Resources} \} \\
-		& ue'_{tp} 
-			&& = ue_{t+1,p} \quad 
-			&& \forall t \in \{2...T-1\} p \\
-		& ue'_{Tp} 
-			&& = uen_{p} \quad
-			&& \forall p
-	\end{alignat}
-
-	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Resources	
-	\begin{alignat}{10}
-		& uu'_{tp}
-			&& = \hat{uu}_{t+1,p} + 
-				\overbrace{ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) }^\text{
-					change in complexities} \quad
-			&& \forall t \in \{1...T-1\} \\
-		& uu'_{Tp}
-			&& = 0 \quad
+		& ul'_{p} 
+			&& = \hat{ul}_{p} + ued_{p} \quad 
 			&& \forall p
@@
 \subsection{Costs}
-Cost will come from 3 sources:  
+Cost will come from 4 sources:  
 \begin{itemize} 
 	\item waiting ($cw$)
-	\item rescheduling ($cc = \lceil cw^M \rceil$)
+	\item rescheduling ($cc$)
+	\item scheduling ($cs$)
 	\item resource violation ($M$)
@@
 				\overbrace{
-					\sum_{tmdc} cw^{m} * t * (1/M)  (sc_{tmdc})
+					\sum_{tmdc} cs^{t} (sc_{tmdc})
 				}^\text{Prefer earlier appointments} \\ 
@@
 			\overbrace{
-				(1.5cc+cw^{m}) \sum_{
+				(1.5cc) \sum_{
 				\substack{tt`mdc \\ t' > t}} 
@@
 \begin{equation}\begin{alignedat}{10}
-	& v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) 
-		&& =  \beta^0 + \sum_{tp} \beta_{tp}^{ue} ue_{tp} +
-			\sum_{tp} \beta_{tp}^{uu} uu_{tp} + \\
-		& && + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
+	& v(\vec{ul}, \vec{pw}, \vec{ps}) 
+		&& =  \beta^0 + \sum_{p} \beta_{p}^{ul} ul_{p} +
+			\sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
 			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
@@
 \begin{equation}
-	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
+	\max_{\vec{\beta}} \sum \alpha (\vec{ul}, \vec{pw}, \vec{ps}) v(\vec{ul}, \vec{pw}, \vec{ps})
 \end{equation}
@@
 	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
-		\beta^0 + \\
-	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
-			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
-		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
-		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{p} \bigg) + \\
-	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-			( \hat{uu}_{t+1,p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})) \bigg) +
-		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
+		\beta^0 +
+		\bigg( \beta^{ul}_{p} (\hat{ul}_{p} + uen_{d}) \bigg) + \\  
 	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
@@
 			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
-	\Bigg) \ge v(\vec{ue}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
+	\Bigg) \ge v(\vec{ul}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
 \end{alignedat} \end{equation}
@@
 \begin{equation}
-\beta^{ue}_{tp}: \qquad 
-	\sum_{p} \beta_{1p}^{ue} \Big( ue_{1p} - \gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{tp}) \Big) + \sum_{t=2p}^{T} \beta_{tp}^{ue} \Big( ue_{tp} - \gamma (uen_{p}) \Big)
-\end{equation}
-\begin{equation}
-\beta^{uu}_{tp}: \qquad \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-	\Big(uu_{tp} - \gamma 
-	(\hat{uu}_{t+1p} + \sum_{mdc} E[pst_{t+1mdc}] (U_{pd+1c} - U_{pdc})) \Big) +
-	\sum_{p} \beta_{Tp}^{uu} \Big( uu_{Tp} \Big)
+\beta^{ul}_{p}: \qquad 
+	\sum_{p} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big)
 \end{equation}
@@
 \begin{equation}
-	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu]
-		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
+	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ut} E[ut] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
 \end{equation}
@@
 		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
-	& \beta^{ue}: 
-		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{1p} - 
-			\gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \Big) \ge E[ue_{tp}]
-		&&	\forall p \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - 
-			\gamma (uen_{p}) \Big) \ge E[ue_{tp}] 
-		&& 	\forall t \in (2...T) p \\ 
-	& \beta^{uu}: 
-		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(uu_{tp} - 
-		\gamma (\hat{uu}_{t+1p} + \sum_{mdc} E[pst_{t+1mdc}] (U_{pd+1c} - U_{pdc}) ) \Big) 
-		\ge E[uu_{tp}]
-		&&	\forall t \in \{1...T-1\}p \\
-	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(uu_{Tp} \Big) \ge E[uu_{Tp}]
+	& \beta^{ul}: 
+		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
+			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}]
 		&&	\forall p \\

### 2021-06-26 Implementation/simulation.py

@@ -1,89 +1,0 @@
-# %% Imports
-from Modules.data_import import *
-from Modules.data_export import *
-from Modules.simulation import *
-import os.path
-import pandas as pd
-import numpy as np
-import seaborn as sns
-
-
-# %% Expected Values Simulation
-def expected_val_sim(input_data, path):
-    expected_values = generate_expected_values(input_data, 5, 1000, 500)
-    export_expected_vals(os.path.join(path, 'Data', 'Data.xlsx'), expected_values)
-
-# %% Comparison of Policies
-def compare_policies(input_data, betas, repls, days, warm_up, axes):
-    repls = repls
-    total_days = days
-    warm_up = warm_up
-
-    # Myopic Policy (FAS)
-    np.random.seed(10)
-    myopic_cost, myopic_disc_c, myopic_state = simulation(input_data, repls, total_days, warm_up, myopic_policy)
-    # MDP Policy
-    np.random.seed(10)
-    mdp_cost, mdp_disc_c, mdp_state = simulation(input_data, repls, total_days, warm_up, mdp_policy, betas=betas)
-    
-    # Visualization
-    myopic_cost_avg = pd.DataFrame(myopic_cost).transpose().mean(axis=1)
-    myopic_cost_avg = pd.DataFrame(myopic_cost_avg, columns=['Myopic'])
-    mdp_cost_avg = pd.DataFrame(mdp_cost).transpose().mean(axis=1)
-    mdp_cost_avg = pd.DataFrame(mdp_cost_avg, columns=['MDP'])
-    cost_frame = pd.concat([myopic_cost_avg, mdp_cost_avg], axis=1)
-    cost_frame['Day'] = cost_frame.index
-
-    sns.lineplot(data=cost_frame, x="Day", y="Myopic", label='Myopic', ax=axes)
-    sns.lineplot(data=cost_frame, x="Day", y="MDP", label='MDP', ax=axes)
-
-    print(f"Myopic Discounted Cost - {np.average(myopic_disc_c)}")
-    print(f"MDP Discounted Cost - {np.average(mdp_disc_c)}")
-
-    res = {'myopic': np.average(myopic_disc_c), 'mdp': np.average(mdp_disc_c)}
-    return res
-
-# %% Writing Out Things
-def non_zero_state(state: state):
-    for key,value in state.ue_tp.items():
[…]

### 2021-06-26 v1-Implementation/Modules/simulation.py

@@ -1,0 +1,862 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import state, action, variables
+
+from multiprocessing import Pool
+from tqdm import tqdm, trange
+from copy import deepcopy
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+# Initializes State ( Everything Empty )
+def initial_state(input_data) -> state:
+    # Input Data
+    indices = input_data.indices
+    arrival = input_data.arrival
+    ppe_data = input_data.ppe_data
+
+    # Patient States
+    pw = {}
+    for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
+        if mdc[0] == 0:
+            pw[mdc] = arrival[(mdc[1], mdc[2])] 
+        else:
+            pw[mdc] = 0
+    ps = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        ps[tmdc] = 0
+
+    # Unit States
+    ue = {}
+    uu = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        ue[tp] = ppe_data[tp[1]].expected_units
+        uu[tp] = 0
+
+    init_state = state(ue, uu, pw, ps)
+
+    return init_state
+# Initializes Action ( Everything Empty )
+def initial_action(input_data) -> action:
+    indices = input_data.indices
+
+    # Action
+    sc = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        sc[tmdc] = 0
+    rsc = {}
+    for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
+        rsc[ttpmdc] = 0
+    
+    # Violation
+    uv = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uv[tp] = 0
+    
+    # Auxiliary variables
+    uu_p = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uu_p[tp] = 0
+    pw_p = {}
+    for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
+        pw_p[mdc] = 0
+    ps_p = {}
[…]

### 2021-06-26 v1-Implementation/Modules/sub_problem.py

@@ -1,0 +1,409 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import state, action, variables
+
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+# Generate sub problem model
+def generate_sub_model(input_data, betas, phase1 = False):
+    indices = input_data.indices
+    arrival = input_data.arrival
+    ppe_data = input_data.ppe_data
+    model_param = input_data.model_param
+    transition = input_data.transition
+    usage = input_data.usage
+
+    M = model_param.M
+    gamma = model_param.gamma
+
+    # Initializes model
+    sub_model = gp.Model('SubmodelKnapsack')
+
+    # Decision Variables
+    var_ue = {}
+    var_uu = {}
+    var_pw = {}
+    var_ps = {}
+
+    var_sc = {}
+    var_rsc = {}
+    var_uv = {}
+    var_uu_p = {}
+    var_pw_p = {}
+    var_ps_p = {}
+
+    # States / Upper Bounds
+    # UE, UU
+    for tp in itertools.product(indices['t'], indices['p']):
+        ppe_upper_bounds = ppe_data[tp[1]].expected_units + ppe_data[tp[1]].deviation[1]
+        var_ue[tp] = sub_model.addVar(name=f's_ue_{tp}', ub=4*ppe_upper_bounds, vtype=GRB.CONTINUOUS)
+        var_uu[tp] = sub_model.addVar(name=f's_uu_{tp}', ub=4*ppe_upper_bounds, vtype=GRB.CONTINUOUS)
+    # PW
+    for mdc in itertools.product(indices['m'], indices['d'], indices['c']):
+        var_pw[mdc] = sub_model.addVar(name=f's_pw_{mdc}', ub=4*arrival[(mdc[1],mdc[2])], vtype=GRB.INTEGER)
+    # PS
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        var_ps[tmdc] = sub_model.addVar(name=f's_ps_{tmdc}', ub=4*arrival[(tmdc[2],tmdc[3])], vtype=GRB.INTEGER)
+
+    # Actions
+    # SC
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        var_sc[tmdc] = sub_model.addVar(name=f'a_sc_{tmdc}', vtype=GRB.INTEGER)
+    # RSC
[…]

### 2021-06-26 v1-Implementation/main.py

@@ -1,0 +1,79 @@
+# %%
+from Implementation.Modules.simulation import mdp_policy
+from optimization import *
+from simulation import *
+import os.path
+import sys
+from matplotlib import pyplot as plt
+
+# Read Data
+my_path = os.path.dirname(__file__)
+input_data = read_data(os.path.join(my_path, 'Data', 'Data.xlsx'))
+# %% Optimization
+# No need to do an expected state simulation, 
+# because setting values to extremes gives same results
+
+# for cw_p in [1, 1.25, 1.5]:
+#     for cs_p in [1, 1.25, 1.5]:
+#         for cc_p in [1, 25, 50]:
+
+            # if cw_p == 1.0 and cs_p == 1.0:
+            #     continue
+            # input_data.model_param.cw = cw_p
+            # input_data.model_param.cs = cs_p
+            # input_data.model_param.cc = cc_p
+
+# print(f"\t\tcw {cw_p}-cs {cs_p}-cc {cc_p}")
+# print(input_data.)
+
+# Phase 1
+init_state, init_action = generate_initial_state_action(input_data)
+state_action_list = [(init_state, init_action)]
+feasible_list = generate_feasible_sa_list(input_data, state_action_list)
+
+# Phase 2
+optimal_list, betas = generate_optimal_sa_list(input_data, feasible_list)
+export_betas(betas, os.path.join(my_path, 'Data', f'Optimal-Betas-ZeroVariation.xlsx'))
+            
+
+
+# %% Compare Policies
+# Import betas
+fig, axes = plt.subplots(1, 1)
+# fig.set_size_inches()
+# fig.subplots_adjust(top = 1.5)
+
+# counter = 0
+# for cw_p in [1, 1.25, 1.5]:
+#     for cs_p in [1, 1.25, 1.5]:
+#         for cc_p in [1, 25, 50]: 
+betas = read_betas(os.path.join(my_path, 'Data', f'Optimal-Betas-ZeroVariation.xlsx'))
+
+# input_data.model_param.cw = cw_p
+# input_data.model_param.cs = cs_p
+# input_data.model_param.cc = cc_p
+
+# print(f'COSTS: cw - {cw_p}, cs - {cs_p}, cc - {cc_p}')
+# betas = read_betas(os.path.join(my_path, 'Data', 'Optimal-Betas.xlsx'))
+
+# Compare Policies
[…]

### 2021-06-26 v2-Implementation/Modules/simulation.py

@@ -1,0 +1,862 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import state, action, variables
+
+from multiprocessing import Pool
+from tqdm import tqdm, trange
+from copy import deepcopy
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+# Initializes State ( Everything Empty )
+def initial_state(input_data) -> state:
+    # Input Data
+    indices = input_data.indices
+    arrival = input_data.arrival
+    ppe_data = input_data.ppe_data
+
+    # Patient States
+    pw = {}
+    for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
+        if mdc[0] == 0:
+            pw[mdc] = arrival[(mdc[1], mdc[2])] 
+        else:
+            pw[mdc] = 0
+    ps = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        ps[tmdc] = 0
+
+    # Unit States
+    ul = {}
+    for p in itertools.product(indices['p']):
+        ul[p] = 0
+
+    init_state = state(ul, pw, ps)
+
+    return init_state
+# Initializes Action ( Everything Empty )
+def initial_action(input_data) -> action:
+    indices = input_data.indices
+
+    # Action
+    sc = {}
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        sc[tmdc] = 0
+    rsc = {}
+    for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
+        rsc[ttpmdc] = 0
+    
+    # Violation
+    uv = {}
+    uvb = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uv[tp] = 0
+        uvb[tp] = 0
+
+    # Units left over 
+    ul_p = {}
+    ulb = {}
+    for p in itertools.product(indices['p']):
+        ul_p[p] = 0
+        ulb[p] = 0
+
+    # Auxiliary variables
+    uu_p = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uu_p[tp] = 0
+    pw_p = {}
[…]

### 2021-06-26 v2-Implementation/Modules/sub_problem.py

@@ -1,0 +1,402 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import state, action, variables
+
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+# Generate sub problem model
+def generate_sub_model(input_data, betas, phase1 = False):
+    indices = input_data.indices
+    arrival = input_data.arrival
+    ppe_data = input_data.ppe_data
+    model_param = input_data.model_param
+    transition = input_data.transition
+    usage = input_data.usage
+
+    M = model_param.M
+    gamma = model_param.gamma
+
+    # Initializes model
+    sub_model = gp.Model('SubmodelKnapsack')
+
+    # Decision Variables
+    # State
+    var_ul = {}
+    var_pw = {}
+    var_ps = {}
+
+    # Action
+    var_sc = {}
+    var_rsc = {}
+    var_uv = {}
+
+    var_uvb = {}
+    var_ul_p = {}
+    var_ulb = {}
+    var_uu_p = {}
+    var_pw_p = {}
+    var_ps_p = {}
+
+    # States / Upper Bounds
+    # UL
+    for p in itertools.product(indices['p']):
+        var_ul[p] = sub_model.addVar(name=f's_ul_{p}', ub=3*ppe_data[p[0]].expected_units, vtype=GRB.CONTINUOUS)
+    # PW
+    for mdc in itertools.product(indices['m'], indices['d'], indices['c']):
+        var_pw[mdc] = sub_model.addVar(name=f's_pw_{mdc}', ub=4*arrival[(mdc[1],mdc[2])], vtype=GRB.INTEGER)
+    # PS
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        var_ps[tmdc] = sub_model.addVar(name=f's_ps_{tmdc}', ub=4*arrival[(tmdc[2],tmdc[3])], vtype=GRB.INTEGER)
+
+    # Actions
+    # SC
+    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
+        var_sc[tmdc] = sub_model.addVar(name=f'a_sc_{tmdc}', vtype=GRB.INTEGER)
+    # RSC
+    for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
[…]

### 2021-06-26 v2-Implementation/optimization.py

@@ -1,0 +1,122 @@
+# %% Packages
+from Modules.data_import import *
+from Modules.data_export import *
+from Modules.master_model import *
+from Modules.sub_problem import *    
+
+# %% Generate Initial Feasible Set (Phase 1)
+def generate_feasible_sa_list(input_data, init_state_actions):
+    state_action_list = init_state_actions
+    
+    # Initializes
+    count = len(state_action_list)-1
+    mast_model, mast_var, mast_const = generate_master_model(input_data, state_action_list)
+
+    # Generates
+    while True:
+    
+        # Generates and Solves Master
+        p1_mast_model, p1_mast_const = generate_phase1_master_model(input_data, mast_model)
+        p1_mast_model.Params.LogToConsole = 0
+        p1_mast_model.optimize()
+        betas = generate_beta_values(input_data, p1_mast_const)
+            
+        # Debugging
+        print(f'Phase 1 - iteration {count+1}, Mast Objective {p1_mast_model.getObjective().getValue()}')
+        count += 1
+
+        # Stops if necessary
+        if p1_mast_model.getObjective().getValue() <= 0.00000000001:
+            print('Found Feasible Set')
+            break
+        
+        # Generates and solves Subproblem 
+        p1_sub_model, p1_sub_var = generate_sub_model(input_data, betas, True)
+        p1_sub_model.Params.LogToConsole = 0
+        p1_sub_model.optimize()
+        
+        # Update State-Actions
+        state_action = generate_state_action(p1_sub_var)
+        state_action_list.append(state_action)
+        mast_model, mast_var, mast_const = update_master_model(input_data, mast_model, mast_var, mast_const, state_action, count)
+        
+        # Stops if necessary
+        if state_action_list[-1] == state_action_list[-2]:
+            print('Unable to find feasible set')
+            break
+
+    return(state_action_list)
+
+# %% Solve the problem (Phase 2)
+def generate_optimal_sa_list(input_data, init_state_actions):
+
+    # Initializes
+    state_action_list = init_state_actions
+    count = len(state_action_list)
+    count_without_removal = 0
+    mast_model, mast_var, mast_const = generate_master_model(input_data, state_action_list)
+
+    while True:
+
+        # Generates and Solves Master
+        mast_model.Params.LogToConsole = 0
+        mast_model.optimize()
+        betas = generate_beta_values(input_data, mast_const)
+
+        # Drops state action pairs as needed
[…]

### 2021-06-26 v2-Implementation/simulation.py

@@ -1,0 +1,86 @@
+# %% Imports
+from Modules.data_import import *
+from Modules.data_export import *
+from Modules.simulation import *
+import os.path
+import pandas as pd
+import numpy as np
+import seaborn as sns
+
+
+# %% Expected Values Simulation
+def expected_val_sim(input_data, path):
+    expected_values = generate_expected_values(input_data, 5, 1000, 500)
+    export_expected_vals(os.path.join(path, 'Data', 'Data.xlsx'), expected_values)
+
+# %% Comparison of Policies
+def compare_policies(input_data, betas, repls, days, warm_up, axes):
+    repls = repls
+    total_days = days
+    warm_up = warm_up
+
+    # Myopic Policy (FAS)
+    np.random.seed(10)
+    myopic_cost, myopic_disc_c, myopic_state = simulation(input_data, repls, total_days, warm_up, myopic_policy)
+    # MDP Policy
+    np.random.seed(10)
+    mdp_cost, mdp_disc_c, mdp_state = simulation(input_data, repls, total_days, warm_up, mdp_policy, betas=betas)
+    
+    # Visualization
+    myopic_cost_avg = pd.DataFrame(myopic_cost).transpose().mean(axis=1)
+    myopic_cost_avg = pd.DataFrame(myopic_cost_avg, columns=['Myopic'])
+    mdp_cost_avg = pd.DataFrame(mdp_cost).transpose().mean(axis=1)
+    mdp_cost_avg = pd.DataFrame(mdp_cost_avg, columns=['MDP'])
+    cost_frame = pd.concat([myopic_cost_avg, mdp_cost_avg], axis=1)
+    cost_frame['Day'] = cost_frame.index
+
+    sns.lineplot(data=cost_frame, x="Day", y="Myopic", label='Myopic', ax=axes)
+    sns.lineplot(data=cost_frame, x="Day", y="MDP", label='MDP', ax=axes)
+
+    print(f"Myopic Discounted Cost - {np.average(myopic_disc_c)}")
+    print(f"MDP Discounted Cost - {np.average(mdp_disc_c)}")
+
+# %% Writing Out Things
+def non_zero_state(state: state):
+    for key,value in state.ue_tp.items():
+        if state.ue_tp[key] >= 0.1: print(f'\tUnits Expected - {key} - {state.ue_tp[key]}')
[…]

### 2021-07-06 v2-Manuscript/Manuscript.tex
testing version 2

@@
 \begin{itemize}
-	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1
+	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1. This is only for resources that can be carried over
     \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
@@
 				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
-				&& \forall p \\
+				&& \forall p \in \{\text{Carry Over}\} \\
+			& \hat{uv}_{1p} 
+				&& \le  (\hat{uu}_{1p} - uen_{1p}) + M(1-uvb_{tp}) \quad
+				&& \forall p \in \{\text{Non Carry Over}\} \\
 			& \hat{uv}_{tp} 
@@
 				&& \ge 0 \quad 
-				&& \forall p \\
+				&& \forall p \in \{\text{Non Carry Over}\} \\
 			& \hat{ul}_{p} 
 				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
-				&& \forall p \\
+				&& \forall p \in \{\text{Non Carry Over}\} \\
 			& \hat{ul}_{p} 
 				&& \le M (ulb_{p}) \quad 
-				&& \forall p \\
+				&& \forall p \in \{\text{Non Carry Over}\} \\
 			& \hat{ul}_{p} 
 				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
-				&& \forall p
+				&& \forall p \in \{\text{Non Carry Over}\}
 	\end{alignat}
@@
 			&& = \hat{ul}_{p} + ued_{p} \quad 
-			&& \forall p
+			&& \forall p \in \{ \text{Carry Over}\} \\
 	\end{alignat}
@@
 		&& 
-			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
+			\overbrace{ \sum_{mdc} cw^{m+1} (\hat{pw}_{mdc}) }^\text{
 				cost of waiting}  + 
-			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
+			\overbrace{ \sum_{tmdc} cw^{M+1} (\hat{ps}_{tMdc})}^\text{
 				prevent infinite reschedules} + \\
@@
 \begin{equation*}
-	\min_{\vec{A}} c(\vec{S}, \vec{A}) - \gamma v(S')
+	\min_{\vec{A}} c(\vec{S}, \vec{A}) + \gamma v(S')
 \end{equation*}

### 2021-07-06 v2-Implementation/Modules/master_model.py

@@ -45,7 +45,7 @@ def generate_initial_state_action(input_data):
     ulb = {}
     for p in itertools.product(indices['p']):
         ul_p[p] = 0
-        ulb[p] = 1
+        ulb[p] = 0
     uvb = {}
     uu_p = {}
     for tp in itertools.product(indices['t'], indices['p']):
@@ -72,19 +72,19 @@ def cost_function(input_data: input_data_class, state: state, action: action):
     cost = 0
     # Cost of Waiting
     for mdc in itertools.product(indices['m'], indices['d'], indices['c']):            
-        cost += model_param.cw**mdc[0] * ( action.pw_p_mdc[mdc] )
+        cost += model_param.cw**(mdc[0]+1) * ( action.pw_p_mdc[mdc] )
     
     # Cost of Waiting - Last Period
     for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
-        cost += model_param.cw**indices['m'][-1] * ( action.ps_p_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
+        cost += model_param.cw**(indices['m'][-1]+1) * ( action.ps_p_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
 
     # Prefer Earlier Appointments
     for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
-        cost += model_param.cs**tmdc[0] * ( action.sc_tmdc[(tmdc[0],tmdc[1],tmdc[2],tmdc[3])] )
+        cost += model_param.cs**tmdc[0] * ( action.sc_tmdc[tmdc] )
 
     # Cost of Rescheduling
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
-        if ttpmdc[0] > ttpmdc[1]: #good schedule
+        if ttpmdc[0] > ttpmdc[1]: # good schedule
             cost -= (0.5*model_param.cc) * action.rsc_ttpmdc[ttpmdc]
         elif ttpmdc[1] > ttpmdc[0]: #bad schedule
             cost += (1.5*model_param.cc) * action.rsc_ttpmdc[ttpmdc]
@@ -93,7 +93,7 @@ def cost_function(input_data: input_data_class, state: state, action: action):
     for tp in itertools.product(indices['t'], indices['p']):
         cost += action.uv_tp[tp] * model_param.M
 
-    return(cost)
+    return cost
[…]

### 2021-07-06 v2-Implementation/simulation.py

@@ -41,28 +41,7 @@ def compare_policies(input_data, betas, repls, days, warm_up, axes):
     print(f"MDP Discounted Cost - {np.average(mdp_disc_c)}")
 
 # %% Writing Out Things
-def non_zero_state(state: state):
-    for key,value in state.ue_tp.items():
-        if state.ue_tp[key] >= 0.1: print(f'\tUnits Expected - {key} - {state.ue_tp[key]}')
-        if state.uu_tp[key] >= 0.1: print(f'\tUnits Used - {key} - {state.uu_tp[key]}')
-    for key,value in state.pw_mdc.items(): 
-        if value >= 0.1: print(f'\tPatients Waiting- {key} - {value}')
-    for key,value in state.ps_tmdc.items(): 
-        if value >= 0.1: print(f'\tPatients Scheduled- {key} - {value}')
-def non_zero_action(action: action):
-    for key,value in action.sc_tmdc.items():
-        if value >= 0.1: print(f'\tPatients Schedule - {key} - {value}')
-    for key,value in action.rsc_ttpmdc.items(): 
-        if value >= 0.1: print(f'\tPatients Reschedule- {key} - {value}')
-    for key,value in action.uv_tp.items(): 
-        if value >= 0.1: print(f'\tUnits Violated- {key} - {value}')
-    for key,value in action.uu_p_tp.items(): 
-        if value >= 0.1: print(f'\tUnits Used - Post Decision - {key} - {value}')
-    for key,value in action.pw_p_mdc.items(): 
-        if value >= 0.1: print(f'\ttPatients Waiting - Post Decision - {key} - {value}')
-    for key,value in action.ps_p_tmdc.items(): 
-        if value >= 0.1: print(f'\tPatients Scheduled - Post Decision - {key} - {value}')
-def test_out_policy(input_data, duration, policy, policy_name, betas):
+def test_out_policy(input_data, duration, policy, policy_name, betas=False):
 
     curr_state = initial_state(input_data)
 

### 2021-07-23 v2-Manuscript/Manuscript.tex
adjusting pricing

--- 2021-06-26 v2-Manuscript/Manuscript.tex
@@
 			&& = \hat{ul}_{p} + ued_{p} \quad 
-			&& \forall p
+			&& \forall p \in \{ \text{Carry Over}\} \\
+		& ul'_{p} 
+			&& = ued_{p} \quad 
+			&& \forall p \in \{ \text{Non Carry Over}\} 
 	\end{alignat}
@@
 	\item rescheduling ($cc$) 
-	\item scheduling ($cs$)
+	\item scheduling ($cs_{t} = \sum_{t}cw^{t}$)
 	\item resource violation ($M$)
@@
 		&& 
-			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
+			\overbrace{ \sum_{mdc} cw (\hat{pw}_{mdc}) }^\text{
 				cost of waiting}  + 
-			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
-				prevent infinite reschedules} + \\
-	&	&&	+
 			\overbrace{
-					\sum_{tmdc} cs^{t} (sc_{tmdc})
+				\sum_{tmdc} cs_{t} (sc_{tmdc})
 			}^\text{Prefer earlier appointments} \\ 
@@
 			\overbrace{
-				(1.5cc) \sum_{
+				\sum_{
 				\substack{tt`mdc \\ t' > t}} 
-				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
+				(cs_{t'-t} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
 			\overbrace{ 
-				(0.5cc) \sum_{
+				\sum_{
 				\substack{tt`mdc \\ t' < t}}
-				rsc_{tt'mdc}}^\text{Good Reschedule} + 
+				(cs_{t-t'} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
 			M \sum_{tp} uv_{tp}

### 2021-07-23 v2-Implementation/Modules/data_classes.py

@@ -13,7 +13,7 @@ class ppe_data_class:
 class model_param_class:
     cw: float
     cc: float
-    cs: float
+    cs: List[float]
     M: float
     gamma: float
 @dataclass()

### 2021-07-23 v2-Implementation/Modules/master_model.py

@@ -72,22 +72,24 @@ def cost_function(input_data: input_data_class, state: state, action: action):
     cost = 0
     # Cost of Waiting
     for mdc in itertools.product(indices['m'], indices['d'], indices['c']):            
-        cost += model_param.cw**(mdc[0]+1) * ( action.pw_p_mdc[mdc] )
+        cost += model_param.cw * ( action.pw_p_mdc[mdc] )
     
     # Cost of Waiting - Last Period
-    for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
-        cost += model_param.cw**(indices['m'][-1]+1) * ( action.ps_p_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
+    # for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
+    #     cost += model_param.cw**(indices['m'][-1]+1) * ( action.ps_p_tmdc[(tdc[0],indices['m'][-1],tdc[1],tdc[2])] )
 
     # Prefer Earlier Appointments
     for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
-        cost += model_param.cs**tmdc[0] * ( action.sc_tmdc[tmdc] )
+        cost += model_param.cs[tmdc[0]] * ( action.sc_tmdc[tmdc] )
 
     # Cost of Rescheduling
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
         if ttpmdc[0] > ttpmdc[1]: # good schedule
-            cost -= (0.5*model_param.cc) * action.rsc_ttpmdc[ttpmdc]
+            difference = ttpmdc[0] - ttpmdc[1]
+            cost -= (model_param.cs[difference] - model_param.cc) * action.rsc_ttpmdc[ttpmdc]
         elif ttpmdc[1] > ttpmdc[0]: #bad schedule
-            cost += (1.5*model_param.cc) * action.rsc_ttpmdc[ttpmdc]
+            difference = ttpmdc[1] - ttpmdc[0]
+            cost += (model_param.cs[difference] + model_param.cc) * action.rsc_ttpmdc[ttpmdc]
 
     # Violating unit bounds
     for tp in itertools.product(indices['t'], indices['p']):

### 2021-07-23 v2-Implementation/Modules/sub_problem.py

@@ -145,12 +145,10 @@ def generate_sub_model(input_data, betas, phase1 = False):
 
     # 2) Bounds on Reschedules
     for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
-        # if ttpmdc[0] == ttpmdc[1] == 1:
-        #     sub_model.addConstr(var_rsc[ttpmdc] == 0, f'resc_bound_{ttpmdc}')
-        # elif ttpmdc[0] >= 2 and ttpmdc[1] >= 2:
-        #     sub_model.addConstr(var_rsc[ttpmdc] == 0, f'resc_bound_{ttpmdc}')
-        # elif ttpmdc[0] == 1 and ttpmdc[1] >= 3:
-        sub_model.addConstr(var_rsc[ttpmdc] == 0, f'resc_bound_{ttpmdc}')
+        if ttpmdc[0] == ttpmdc[1] == 1:
+            sub_model.addConstr(var_rsc[ttpmdc] == 0, f'resc_bound_{ttpmdc}')
+        elif ttpmdc[0] >= 2 and ttpmdc[1] >= 2:
+            sub_model.addConstr(var_rsc[ttpmdc] == 0, f'resc_bound_{ttpmdc}')
 
     # 3) Number of people schedules/reschedules must be consistent
         # Reschedules
@@ -175,11 +173,11 @@ def generate_sub_model(input_data, betas, phase1 = False):
 
         # Cost of Waiting
         for mdc in itertools.product(indices['m'], indices['d'], indices['c']):  
-            expr.addTerms(model_param.cw**(mdc[0]+1), var.a_pw_p[mdc])                    
+            expr.addTerms(model_param.cw, var.a_pw_p[mdc])                    
         
         # Cost of Waiting - Last Period
-        for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
-            expr.addTerms(model_param.cw**(indices['m'][-1]+1), var.a_ps_p[(tdc[0],indices['m'][-1],tdc[1],tdc[2])])     
+        # for tdc in itertools.product(indices['t'], indices['d'], indices['c']):
+        #     expr.addTerms(model_param.cw**(indices['m'][-1]+1), var.a_ps_p[(tdc[0],indices['m'][-1],tdc[1],tdc[2])])     
 
         return expr
     def pref_earlier_appointment(var: variables, betas) -> gp.LinExpr:
[…]

### 2021-07-26 v2-Manuscript/Manuscript.tex
added non - carry over option

@@
 		\beta^0 +
-		\bigg( \beta^{ul}_{p} (\hat{ul}_{p} + uen_{d}) \bigg) + \\  
+		\bigg( \beta^{ul}_{p \in \text{co}} (\hat{ul}_{p} + uen_{d}) \bigg) + 
+		\bigg( \beta^{ul}_{p \in \text{nco}} (uen_{d}) \bigg) + \\  
 	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
@@
 \beta^{ul}_{p}: \qquad 
-	\sum_{p} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big)
+	\sum_{p \in \text{co}} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big) + 
+	\sum_{p \in \text{nco}} \beta_{p}^{ul} ( ul_{p}) 
 \end{equation}
@@
 			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
-		&&	\forall p \\
+		&&	\forall p \in \{ \text{carry over} \} \\ 
+	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
+		&&	\forall p \in \{ \text{non carry over} \}\\
 	&	\beta^{pw}: 

### 2021-07-26 v2-Implementation/Modules/sub_problem.py

@@ -212,15 +212,18 @@ def generate_sub_model(input_data, betas, phase1 = False):
     def b0_cost(var: variables, betas) -> gp.LinExpr:
         expr = gp.LinExpr()
         expr.addConstant((1-gamma) * betas['b0']['b_0'])
-        return(expr)
+        return expr
     def b_ul_cost(var: variables, betas) -> gp.LinExpr:
         expr = gp.LinExpr()
         
-        for p in itertools.product(indices['p']):
-            expr.addTerms(betas['ul'][p], var.s_ul[p])
-            expr.addTerms(- (betas['ul'][p] * gamma), var.a_ul_p[p])
+        for p in itertools.product(indices['p']):    
+            if ppe_data[p[0]].ppe_type == 'carry-over':
+                expr.addTerms(betas['ul'][p], var.s_ul[p])
+                expr.addTerms(- (betas['ul'][p] * gamma), var.a_ul_p[p])    
+            elif ppe_data[p[0]].ppe_type == 'non-carry-over':
+                expr.addTerms(betas['ul'][p], var.s_ul[p])
                     
-        return(expr)
+        return expr
     def b_pw_costs(var: variables, betas) -> gp.LinExpr:
         expr = gp.LinExpr()
 

### 2021-07-26 v2-Implementation/main.py

@@ -27,7 +27,7 @@ input_data = read_data(os.path.join(my_path, 'Data', 'Data-complex-newcost.xlsx'
 # Import betas
 fig, axes = plt.subplots(1, 1)
 betas = read_betas(os.path.join(my_path, 'Data', f'Optimal-Betas-complex-newcost.xlsx'))
-compare_policies(input_data, betas, 1, 10000, 5000, axes)
+compare_policies(input_data, betas, 3, 10000, 5000, axes)
 fig.savefig(os.path.join(my_path, 'Data', f'Optimal-Betas-complex-newcost-long.pdf'))
 
 # # %% Test out policies

### 2021-07-27 v2-Manuscript/Manuscript.tex
working on modifying transitions

@@
 		\item Let's assume our limit is 10 periods, patients will never change complexities within the 10 periods.  
-		\item However, if a patient waits for 11 periods there is a possibility they increase complexity
+		\item However, on their 10th period, they can increase complexity
 	\end{itemize}
 
-	\item We assume patient complexity transitions follow binary distribution - each period a patient can become more complex with a certain probability
+	\item We assume patient complexity transitions follow binary distribution - each period a patient can become more complex with a static probability
 	\begin{itemize}
 		\item While patient is waiting less that $TL$, the transition probability is 0.
-		\item After $TL$, transition probability is some arbitrary value
+		\item After $TL$, a patient has some probability they move to a higher complexity in that period
 	\end{itemize}
@@
 
-	\item Transition between patient complexities within the wait list - $pw_{m>=1,dc}$
+	\item Transition between patient complexities within the wait list - $pw_{mdc}$
 		\begin{itemize}
 			\item $pwt_{mdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, who became more complex. Follows binomial distribution.
-			\item $ptp_{mdc}$ represents transition probability to a higher complexity
+			\item $ptp_{dc}$ represents transition probability to a higher complexity
+			\item $TL_{dc}$ represents the time at which this transition probability starts to have an effect (must be less than M)
 		\end{itemize}
@@
 			& pw'_{mdc} 
+				&& = \hat{pw}_{m-1,dc}
+				&& \forall m \in \{ 1...(TL_{dc}-1) \} dc \\  
+			& pw'_{mdc} 
 				&& = \hat{pw}_{m-1,dc} + 
@@
 					change in complexities} \quad
-				&& \forall m \in \{ 1...M-1 \} dc \\  
+				&& \forall m \in \{ TL_{dc}...M-1 \} dc \\  
 			& pw'_{Mdc} 
@@
 			& ps'_{tmdc} 
+				&& = \hat{ps}_{t+1,m-1,dc} \quad 
+				&& \forall t \in \{1...T-1\} m \in \{ 1... (TL_{dc}-1) \} dc \\ 
+			& ps'_{tmdc} 
 				&& = \hat{ps}_{t+1,m-1,dc} + 
@@
 					change in complexities} \quad
-				&& \forall t \in \{1...T-1\} m \in \{ 1...M-1 \} dc \\  
+				&& \forall t \in \{1...T-1\} m \in \{ TL_{dc}...M-1 \} dc \\  
 			& ps'_{tMdc} 

### 2021-07-28 v2-Manuscript/Manuscript.tex
finished changing complexity transitions

@@
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath, amssymb}
+\usepackage{amsmath, amssymb, nccmath}
 
@@
 \begin{equation}
-	c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
+\label{full-adp-equation}
+	c(\vec{S}, \vec{A}) + \gamma \sum_{\vec{p}} p * v( \vec{S'}) 
+		\ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
 \end{equation}
 
+And all auxiliary constraints in "\nameref{auxiliary constraints}"
+
 \section{Aproximate Dynamic Programming Model}
-\subsection{Full ADP Model}
+\subsection{Expectation ADP Model}
 Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
@@
 
-This gives the following LP
-\begin{equation}
-	\max_{\vec{\beta}} \sum \alpha (\vec{ul}, \vec{pw}, \vec{ps}) v(\vec{ul}, \vec{pw}, \vec{ps})
-\end{equation}
-Subject to:
-\begin{equation}\begin{alignedat}{10}
-\label{full-adp-equation}
-	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
-		\beta^0 +
-		\bigg( \beta^{ul}_{p \in \text{co}} (\hat{ul}_{p} + uen_{d}) \bigg) + 
-		\bigg( \beta^{ul}_{p \in \text{nco}} (uen_{d}) \bigg) + \\  
-	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
-		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
-			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
-	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
-			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
-	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
-		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
-		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
-			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
-	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
-			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
-	\Bigg) \ge v(\vec{ul}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
-\end{alignedat} \end{equation}
-\begin{equation}
-	\vec{\beta} \ge 0 \quad \forall \beta
-\end{equation}
-And all auxiliary constraints in "\nameref{auxiliary constraints}"
+Next we need to convert a part of equation \ref{full-adp-equation} into expectation. \\ 
+(To make it easier later, we will format is as $v(\vec{S}) - E[v(\vec{S}')]$)
 
-\subsection{Expectation ADP Model}
-Steps for rearranging and converting the constraint (\ref{full-adp-equation}) into expectation:
 \begin{itemize}
 	\item $E[ued_p] = 0$
-	\item $E[pwt_{mdc}] = ptp_{mdc} * \hat{pw}_{mdc}$ 
-	\item $E[pst_{tmdc}] = ptp_{mdc} * \hat{ps}_{tmdc}$ 
+	\item $E[pwt_{mdc}] = ptp_{dc} * \hat{pw}_{mdc}$ 
+	\item $E[pst_{tmdc}] = ptp_{dc} * \hat{ps}_{tmdc}$ 
 \end{itemize}
 
+\begin{fleqn}[\parindent]
 \begin{equation}
@@
 \end{equation}
+\end{fleqn}
+
+\begin{fleqn}[\parindent]
 \begin{equation}
@@
 \end{equation}
+\end{fleqn}
+
+\begin{fleqn}[\parindent]
 \begin{equation}\begin{alignedat}{10}
@@
 	&& 	\sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) +
-	\sum_{m=1dc}^{M-1} \beta_{mdc}^{pw} 
+	\sum_{m=1dc}^{TL_{dc}-1} \beta_{mdc}^{pw} 
+	\Big( pw_{mdc} - \gamma 
+		(\hat{pw}_{m-1dc}) \Big) + \\
+	& && \sum_{m=TL_{dc}dc}^{M-1} \beta_{mdc}^{pw} 
 		\Big( pw_{mdc} - \gamma 
@@
 \end{alignedat} \end{equation}
+\end{fleqn}
+
+\begin{fleqn}[\parindent]
 \begin{equation}\begin{alignedat}{10}
@@
 	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
-	\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + \\
+\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + 
+	\sum_{t=1m=1dc}^{T-1, TL_{dc}-1} \beta_{tmdc}^{ps} 
+	\Big( ps_{tmdc} - \gamma 
+	(\hat{ps}_{t+1m-1dc}) \Big) + \\
 &	&& 
-	\sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
+	\sum_{t=1m=TL_{dc}dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
 	\Big( ps_{tmdc} - \gamma 
@@
 \end{alignedat} \end{equation}
+\end{fleqn}
 
-Let's say $E[V]$ is the addition of all parts above. Then the ADP model converted to expectation would look as follows:
+Using the numbers above we rearrange the original equation as follows:
 \begin{equation}
@@
 \begin{equation}
-	E[V] \le c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) \quad \forall \vec{S} \vec{A} 
+	v(\vec{S}) - E[v(\vec{S}')] \le c(\vec{S}, \vec{A}) \quad \forall \vec{S} \vec{A} 
 \end{equation}
@@
 	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
+		\gamma (\hat{pw}_{m-1dc}) \Big) \ge E[pw_{mdc}]
+		&&	\forall m \in \{1...TL_{dc}-1\} dc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
 		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
-		&&	\forall m \in \{1...M-1\} dc \\
+		&&	\forall m \in \{TL_{dc}...M-1\} dc \\
 	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
@@
 	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
+		(\hat{ps}_{t+1m-1dc}) \Big) \ge E[ps_{tmdc}] \;
+		&&	\forall \{1...T-1\} \{1...TL_{dc}-1\}dc \\
+	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
 			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
-		&&	\forall \{1...T-1\} \{1...M-1\}dc \\
+		&&	\forall \{1...T-1\} \{TL_{dc}...M-1\}dc \\
 	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
@@
 \begin{equation}
-	\min_{(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \in S,  (\vec{sc}, \vec{rsc}) \in A } c(\vec{pw},\vec{sc},\vec{rsc},\vec{uv}) - E[V]
+	\min_{(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \in S,  (\vec{sc}, \vec{rsc}) \in A } c(\vec{pw},\vec{sc},\vec{rsc},\vec{uv}) - \Big(v(\vec{S}) - E[v(\vec{S}')] \Big)
 \end{equation}

### 2021-07-28 v2-Implementation/Modules/data_import.py

@@ -84,7 +84,6 @@ def read_data(data_file_path):
     transition = {}
     for row in transition_sheet.iter_rows(min_row=2, min_col=1, max_col=4, values_only=True):
         if row[0] == None: break
-        print(row)
         transition[(row[1], row[0])] = transition_data_class(row[2], row[3])
 
 

### 2021-07-28 v2-Implementation/main.py

@@ -2,37 +2,38 @@
 from optimization import *
 from simulation import *
 import Modules.decorators
+
 import os.path
 import sys
 from matplotlib import pyplot as plt
 
 # Read Data
 my_path = os.path.dirname(__file__)
-input_data = read_data(os.path.join(my_path, 'Data', 'Data-complex-newcost.xlsx'))
+input_data = read_data(os.path.join(my_path, 'Data', 'Data-full-newcost.xlsx'))
 # generate_optimal_sa_list = Modules.decorators.timer(generate_optimal_sa_list)
-# # %% Optimization
-# # Phase 1
-# init_state, init_action = generate_initial_state_action(input_data)
-# state_action_list = [(init_state, init_action)]
-# feasible_list = generate_feasible_sa_list(input_data, state_action_list)
-
-# # Phase 2
-# stabilization_parameter = 0.3
-# optimal_list, betas = generate_optimal_sa_list(input_data, feasible_list,stabilization_parameter)
-# export_betas(betas, os.path.join(my_path, 'Data', f'Optimal-Betas-complex-newcost.xlsx'))
+# %% Optimization
+# Phase 1
+init_state, init_action = generate_initial_state_action(input_data)
+state_action_list = [(init_state, init_action)]
+feasible_list = generate_feasible_sa_list(input_data, state_action_list)
+ 
+# Phase 2
+stabilization_parameter = 0.3
+optimal_list, betas = generate_optimal_sa_list(input_data, feasible_list,stabilization_parameter)
+export_betas(betas, os.path.join(my_path, 'Data', f'Optimal-Betas-full-newcost.xlsx'))
 
 
 
 # %% Compare Policies
 # Import betas
 fig, axes = plt.subplots(1, 1)
-betas = read_betas(os.path.join(my_path, 'Data', f'Optimal-Betas-complex-newcost.xlsx'))
+betas = read_betas(os.path.join(my_path, 'Data', f'Optimal-Betas-full-newcost.xlsx'))
 compare_policies(input_data, betas, 3, 10000, 5000, axes)
-fig.savefig(os.path.join(my_path, 'Data', f'Optimal-Betas-complex-newcost-long.pdf'))
+fig.savefig(os.path.join(my_path, 'Data', f'Optimal-Betas-full-newcost-long.pdf'))
 
 # # %% Test out policies
 # input_data.arrival[('Complexity 1', 'CPU 1')] = 20
[…]

### 2021-08-12 v2-Manuscript/sections/adp_model.tex
Tuned solve parameters & started adding priority

--- 2021-07-28 v2-Manuscript/Manuscript.tex
@@
-%%%~~~~~~~~~~~~~~~~~ Preamble ~~~~~~~~~~~~~~~~~~~~~~
-\documentclass{article}
-
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath, amssymb, nccmath}
-
-\usepackage{xcolor, hyperref}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\usepackage{geometry}
-\geometry{margin=0.65in}
-\setlength\parindent{0pt}
-
-\title{Dynamic Knapsack Problem}
-\author{AS, WM, KV}
-\date{\today}
-
-\allowdisplaybreaks
-
-%%%~~~~~~~~~~~~~~~~~ Document ~~~~~~~~~~~~~~~~~~~~~~
-\begin{document}
-
-\maketitle
-\tableofcontents
-\newpage
-
-\section{Questions/Comments}
-
-\subsection{Questions}
-\begin{itemize}
-	\item Should $ul$ definition include units violated?? it seems a constraint might be violated otherwise
-\end{itemize}
-
-\subsection{Comments}
-\begin{itemize}
-	\item
-\end{itemize}
-
-\section{Assumptions} 
-\begin{itemize}
-	\item Assume all new patients are arriving at the beginning of the period 
-	\begin{itemize}
-		\item Assume arrivals follow poisson distribution
-	\end{itemize}
-
-	\item It is assumed that patients do not change complexities within some limit ($TL$). 
-	\begin{itemize}
-		\item Let's assume our limit is 10 periods, patients will never change complexities within the 10 periods.  
-		\item However, on their 10th period, they can increase complexity
-	\end{itemize}
-
-	\item We assume patient complexity transitions follow binary distribution - each period a patient can become more complex with a static probability
-	\begin{itemize}
-		\item While patient is waiting less that $TL$, the transition probability is 0.
-		\item After $TL$, a patient has some probability they move to a higher complexity in that period
-	\end{itemize}
-
-	\item It is assumed if a patient is scheduled in period one, it means they are served "immediately", regardless if in practice the appointment is at the beginning or end of the period.
-	\item We distinguish between two types of reschedules: good and bad reschedules
-	\begin{itemize}
-		\item Good reschedules are reschedules where a patient is rescheduled to an earlier period
-		\item Bad reschedules are reschedules where a patient is rescheduled to a later period
-	\end{itemize}
-
-	\item We assume that only specific reschedules are allowed (to simplify the model, and remove  redundancies)
-	\begin{itemize}
-		\item Good reschedules are allowed from any period after 2 into period 1
-		\item Bad reschedules are only allowed from period 1 to any period after 2
-	\end{itemize}
-
-	\item It is assumed that there is a certain default expected number of PPE units available for all periods
-	\begin{itemize}
-		\item However, in the period 1, there is some random deviation from the expected number of units
-		\item This random deviation follows some uniform distribution
-	\end{itemize}
-	\item We allow some violation of PPE units, in rare cases (with high cost), in order to accomodate changes due to variability.
-	\begin{itemize}
-		\item If we have violation of PPE units - the extra capacity comes from external source
-	\end{itemize}
-\end{itemize}
-
-\section{MDP Model}
-\subsection{Decision Epochs}
-Decisions are made at the beginning of each time period. There are 3 relevant time intervals to look at:
-\begin{itemize}
-	\item Pre-decision state ($S$)
-	\begin{itemize}
-		\item Pre-decision state defines the initial state on which a decision is required
-		\item This information drives decision making
-	\end{itemize}
-
-	\item Post-decision state ($\hat{S}$)
-	\begin{itemize}
-		\item Post-decision state is the time when the decision has been executed, but no new info came in
-		\item This state defines the immediate cost of an action
-	\end{itemize}
-
-	\item Post-transition state ($S'$)
-	\begin{itemize}
-		\item This is the state when new information has come in (transition randomness). Defines next pre decision state
-		\item It is primarily used to generate expectation for the ADP
-	\end{itemize}
-\end{itemize}
-
-\subsection{State Space}
-\subsubsection{Description}
-State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
-\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
-\begin{itemize}
-	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1. This is only for resources that can be carried over
-    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
-    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
-\end{itemize}
-
-\subsection{Action Sets}
-\subsubsection{Description}
-Decision consists of rescheduling currently scheduled patients, and scheduling patients on waitlist. There are also some goal and auxiliary variables
-\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}, \text{auxiliary variables}) \] 
-\begin{itemize}
-    	\item $\vec{sc} = sc_{tmdc}$ - Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to schedule in period $t$
-	\item $\vec{rsc} = rsc_{tt'mdc}$ -Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to reschedule from period $t$ to period $t'$
-	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
-\end{itemize}
-
-\subsubsection{Auxiliary Variables}
-\begin{itemize}
-	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
-	\item $\hat{ul}_{p}$ - post-decision unit leftover at period 1
-	\item $ulb_{p}$ - binary variable to enforce $ul$ variable without objective function
-	\item $\hat{uu}_{tp}$ - post-decision units used
-	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
-	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
-\end{itemize}
-\subsubsection{Auxiliary Variable Definition}
-\label{auxiliary constraints}
-\begin{alignat}{10}
-	& \hat{uu}_{tp} 
-		&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
-		&& \forall tp \\ 
-	& \hat{pw}_{mdc} 
-		&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
-		&& \forall mdc \\ 
-	& \hat{ps}_{tmdc} 
-		&& = ps_{tmdc} + sc_{tmdc} + 
-			\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
-		&& \forall tmdc
-\end{alignat}
-
-\begin{itemize}
-
-	\item Define Resource Violation Variable
-	\begin{alignat}{10}
-			& \hat{uv}_{tp} 
-				&& \le  M(uvb_{tp}) \quad
-				&& \forall tp \\
-			& \hat{uv}_{1p} 
-				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
-				&& \forall p \\
-			& \hat{uv}_{tp} 
-				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
-				&& \forall t \in \{ 2..T \} p \\
-	\end{alignat}
-
-	\item Define Units Left Over Variable
-	\begin{alignat}{10}
-			& \hat{ul}_{p} 
-				&& \ge 0 \quad 
-				&& \forall p \\
-			& \hat{ul}_{p} 
-				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
-				&& \forall p \\
-			& \hat{ul}_{p} 
-				&& \le M (ulb_{p}) \quad 
-				&& \forall p \\
-			& \hat{ul}_{p} 
-				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
-				&& \forall p 
-	\end{alignat}
-\end{itemize}
-
-\subsubsection{State-Action Constraints}
-\label{state-action constraints}
-\begin{itemize}
-
-	\item Resource Usage Constraint
-	\begin{alignat}{10}
-			& \hat{uu}_{1p} 
-			&& \le uen_{1p} + ul_{p} + uv_{1p} \quad 
-			&& \forall p \\
-		& \hat{uu}_{tp} 
-			&& \le uen_{tp} + uv_{tp} \quad
-			&& \forall t \in \{ 2..T \}p 
-	\end{alignat}
-
-	\item Custom bounds on when reschedules are allowed
-	\begin{alignat}{10}
-		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
-		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
-		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t'=1 
-	\end{alignat}
-
-	\item Bounds on Schedules/Reschedules
-	\begin{alignat}{10}
-		& \sum_{t'} rsc_{tt'mdc} 	&& \le ps_{tmdc} \quad  && \forall tmdc  \\
-		& \sum_{t} sc_{tmdc} 		&& \le pw_{mdc} \quad 	&& \forall mdc 
-	\end{alignat}
-
-	\item Bounds on states
-	\begin{alignat}{10}
-		& ul_{p} 	&& \le uen_{p} * 3 \quad 	&& \forall p \\
-		& pw_{mdc} 	&& \le pea_{dc} * 20 \quad 			&& \forall mdc \\
-		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
-	\end{alignat}
-\end{itemize}
-
-\subsection{Transition Probabilities}
-
-\subsubsection{Uncertainty Sources}
-\begin{enumerate}
-
-	\item Number of patients arriving this period - $pw_{0dc}$
-		\begin{itemize}
-			\item $pea_{dc}$ - represents the random number of patients arriving. Follows a poisson distribution.
-		\end{itemize}
-
-	\item Transition between patient complexities within the wait list - $pw_{mdc}$
-		\begin{itemize}
-			\item $pwt_{mdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, who became more complex. Follows binomial distribution.
-			\item $ptp_{dc}$ represents transition probability to a higher complexity
-			\item $TL_{dc}$ represents the time at which this transition probability starts to have an effect (must be less than M)
-		\end{itemize}
-
-	\item Transition between patient complexities within the scheduled list - $ps_{tmdc}$
-		\begin{itemize}
-			\item $pst_{tmdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, scheduled into $t$ period, who became more complex. Follows binomial distribution.
-		\end{itemize}
-
-	\item Amout of expected units of PPE resource for the next time period - $ue_{1p}$
-		\begin{itemize}
-			\item $ued_{p}$ represents the random deviation of resource $p$ from the expectation. Follows uniform distribution.
-			\item $uen_{p}$ expected units of resource $p$ per period
-		\end{itemize}
-\end{enumerate}
-
-\subsubsection{Transition Constraints}
-
-\begin{enumerate}
-	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
-	\begin{alignat}{10}
-		& ul'_{p} 
-			&& = \hat{ul}_{p} + ued_{p} \quad 
-			&& \forall p \in \{ \text{Carry Over}\} \\
-		& ul'_{p} 
-			&& = ued_{p} \quad 
-			&& \forall p \in \{ \text{Non Carry Over}\} 
-	\end{alignat}
-
-	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients on waitlist
-		\begin{alignat}{10}
-			& pw'_{0dc} 
-				&& = pea_{dc} \quad
-				&& \forall dc \\  
-			& pw'_{mdc} 
-				&& = \hat{pw}_{m-1,dc}
-				&& \forall m \in \{ 1...(TL_{dc}-1) \} dc \\  
-			& pw'_{mdc} 
-				&& = \hat{pw}_{m-1,dc} + 
-				\overbrace{pwt_{m-1,d-1,c} - pwt_{m-1,dc}}^\text{
-					change in complexities} \quad
-				&& \forall m \in \{ TL_{dc}...M-1 \} dc \\  
-			& pw'_{Mdc} 
-				&& = \sum_{M-1}^{M} \big( 
-					\hat{pw}_{mdc} + 
-					\overbrace{pwt_{md-1,c} - pwt_{mdc}}^\text{
-						change in complexities} \big) \quad
-				&& \forall dc
-		\end{alignat}
-
-	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts scheduled
-		\begin{alignat}{10}
-			& ps'_{t0dc} 
-				&& = 0 \quad
-				&& \forall tdc \\  
-			& ps'_{Tmdc} 
-				&& = 0 \quad
-				&& \forall mdc \\  
-			& ps'_{tmdc} 
-				&& = \hat{ps}_{t+1,m-1,dc} \quad 
-				&& \forall t \in \{1...T-1\} m \in \{ 1... (TL_{dc}-1) \} dc \\ 
-			& ps'_{tmdc} 
-				&& = \hat{ps}_{t+1,m-1,dc} + 
-				\overbrace{pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc}}^\text{
-					change in complexities} \quad
-				&& \forall t \in \{1...T-1\} m \in \{ TL_{dc}...M-1 \} dc \\  
-			& ps'_{tMdc} 
-				&& = \sum_{M-1}^{M} \big( 
-				\hat{ps}_{t+1mdc} + 
-				\overbrace{pst_{t+1,md-1,c} - pst_{t+1,mdc}}^\text{
-					change in complexities} \big) \quad
-				&& \forall t \in \{1...T-1\} dc
-		\end{alignat}
-\end{enumerate}
-
-\subsection{Costs}
-Cost will come from 4 sources:  
-\begin{itemize} 
-	\item waiting ($cw$)
-	\item rescheduling ($cc$) 
-	\item scheduling ($cs_{t} = \sum_{t}cw^{t}$)
-	\item resource violation ($M$)
-\end{itemize}
-
-\begin{equation}\begin{alignedat}{10}
-	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
-		&& 
-			\overbrace{ \sum_{mdc} cw (\hat{pw}_{mdc}) }^\text{
-				cost of waiting}  + 
-			\overbrace{
-				\sum_{tmdc} cs_{t} (sc_{tmdc})
-			}^\text{Prefer earlier appointments} \\ 
-	&	&&  +
-			\overbrace{
-				\sum_{
-				\substack{tt`mdc \\ t' > t}} 
-				(cs_{t'-t} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
-			\overbrace{ 
-				\sum_{
-				\substack{tt`mdc \\ t' < t}}
-				(cs_{t-t'} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
-			M \sum_{tp} uv_{tp}
-\end{alignedat}\end{equation}
-
-\section{LP Model}
-
-\subsection{Full LP} 
-Given a full MDP model, the equivalent LP would look as follows:
-\begin{equation}
-	\max_{\vec{v}} \sum \alpha (\vec{S}) v(\vec{S}) 
-\end{equation}
-
-subject to
-\begin{equation}
-\label{full-adp-equation}
-	c(\vec{S}, \vec{A}) + \gamma \sum_{\vec{p}} p * v( \vec{S'}) 
-		\ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
-\end{equation}
-
-And all auxiliary constraints in "\nameref{auxiliary constraints}"
-
 \section{Aproximate Dynamic Programming Model}
@@
 constraints in section "\nameref{state-action constraints}"
-
-\end{document}

### 2021-08-12 v2-Manuscript/sections/assumptions.tex
Tuned solve parameters & started adding priority

--- 2021-07-28 v2-Manuscript/Manuscript.tex
@@
-%%%~~~~~~~~~~~~~~~~~ Preamble ~~~~~~~~~~~~~~~~~~~~~~
-\documentclass{article}
+\section{Assumptions} 
+\begin{enumerate}
+	\item Assume arrivals follow poisson distribution and all arrivals are at the beginning of the period
 
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath, amssymb, nccmath}
-
-\usepackage{xcolor, hyperref}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\usepackage{geometry}
-\geometry{margin=0.65in}
-\setlength\parindent{0pt}
-
-\title{Dynamic Knapsack Problem}
-\author{AS, WM, KV}
-\date{\today}
-
-\allowdisplaybreaks
-
-%%%~~~~~~~~~~~~~~~~~ Document ~~~~~~~~~~~~~~~~~~~~~~
-\begin{document}
-
-\maketitle
-\tableofcontents
-\newpage
-
-\section{Questions/Comments}
-
-\subsection{Questions}
-\begin{itemize}
-	\item Should $ul$ definition include units violated?? it seems a constraint might be violated otherwise
-\end{itemize}
-
-\subsection{Comments}
-\begin{itemize}
-	\item
-\end{itemize}
-
-\section{Assumptions} 
-\begin{itemize}
-	\item Assume all new patients are arriving at the beginning of the period 
-	\begin{itemize}
-		\item Assume arrivals follow poisson distribution
-	\end{itemize}
-
-	\item It is assumed that patients do not change complexities within some limit ($TL$). 
-	\begin{itemize}
-		\item Let's assume our limit is 10 periods, patients will never change complexities within the 10 periods.  
-		\item However, on their 10th period, they can increase complexity
-	\end{itemize}
-
-	\item We assume patient complexity transitions follow binary distribution - each period a patient can become more complex with a static probability
-	\begin{itemize}
-		\item While patient is waiting less that $TL$, the transition probability is 0.
-		\item After $TL$, a patient has some probability they move to a higher complexity in that period
-	\end{itemize}
+	\item It is assumed that patients do not change complexities/priorities within some limit ($TL$). 	
+	\item We assume patient complexity/priority transitions follow binary distribution
 
 	\item It is assumed if a patient is scheduled in period one, it means they are served "immediately", regardless if in practice the appointment is at the beginning or end of the period.
+
 	\item We distinguish between two types of reschedules: good and bad reschedules
@@
 	\begin{itemize}
-		\item Good reschedules are allowed from any period after 2 into period 1
-		\item Bad reschedules are only allowed from period 1 to any period after 2
+		\item Good reschedules are allowed from any period after 1 into period 1
+		\item Bad reschedules are only allowed from period 1 to any period after 1
 	\end{itemize}
@@
 	\end{itemize}
-\end{itemize}
-
-\section{MDP Model}
-\subsection{Decision Epochs}
-Decisions are made at the beginning of each time period. There are 3 relevant time intervals to look at:
-\begin{itemize}
-	\item Pre-decision state ($S$)
-	\begin{itemize}
-		\item Pre-decision state defines the initial state on which a decision is required
-		\item This information drives decision making
-	\end{itemize}
-
-	\item Post-decision state ($\hat{S}$)
-	\begin{itemize}
-		\item Post-decision state is the time when the decision has been executed, but no new info came in
-		\item This state defines the immediate cost of an action
-	\end{itemize}
-
-	\item Post-transition state ($S'$)
-	\begin{itemize}
-		\item This is the state when new information has come in (transition randomness). Defines next pre decision state
-		\item It is primarily used to generate expectation for the ADP
-	\end{itemize}
-\end{itemize}
-
-\subsection{State Space}
-\subsubsection{Description}
-State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
-\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
-\begin{itemize}
-	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1. This is only for resources that can be carried over
-    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
-    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
-\end{itemize}
-
-\subsection{Action Sets}
-\subsubsection{Description}
-Decision consists of rescheduling currently scheduled patients, and scheduling patients on waitlist. There are also some goal and auxiliary variables
-\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}, \text{auxiliary variables}) \] 
-\begin{itemize}
-    	\item $\vec{sc} = sc_{tmdc}$ - Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to schedule in period $t$
-	\item $\vec{rsc} = rsc_{tt'mdc}$ -Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to reschedule from period $t$ to period $t'$
-	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
-\end{itemize}
-
-\subsubsection{Auxiliary Variables}
-\begin{itemize}
-	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
-	\item $\hat{ul}_{p}$ - post-decision unit leftover at period 1
-	\item $ulb_{p}$ - binary variable to enforce $ul$ variable without objective function
-	\item $\hat{uu}_{tp}$ - post-decision units used
-	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
-	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
-\end{itemize}
-\subsubsection{Auxiliary Variable Definition}
-\label{auxiliary constraints}
-\begin{alignat}{10}
-	& \hat{uu}_{tp} 
-		&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
-		&& \forall tp \\ 
-	& \hat{pw}_{mdc} 
-		&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
-		&& \forall mdc \\ 
-	& \hat{ps}_{tmdc} 
-		&& = ps_{tmdc} + sc_{tmdc} + 
-			\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
-		&& \forall tmdc
-\end{alignat}
-
-\begin{itemize}
-
-	\item Define Resource Violation Variable
-	\begin{alignat}{10}
-			& \hat{uv}_{tp} 
-				&& \le  M(uvb_{tp}) \quad
-				&& \forall tp \\
-			& \hat{uv}_{1p} 
-				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
-				&& \forall p \\
-			& \hat{uv}_{tp} 
-				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
-				&& \forall t \in \{ 2..T \} p \\
-	\end{alignat}
-
-	\item Define Units Left Over Variable
-	\begin{alignat}{10}
-			& \hat{ul}_{p} 
-				&& \ge 0 \quad 
-				&& \forall p \\
-			& \hat{ul}_{p} 
-				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
-				&& \forall p \\
-			& \hat{ul}_{p} 
-				&& \le M (ulb_{p}) \quad 
-				&& \forall p \\
-			& \hat{ul}_{p} 
-				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
-				&& \forall p 
-	\end{alignat}
-\end{itemize}
-
-\subsubsection{State-Action Constraints}
-\label{state-action constraints}
-\begin{itemize}
-
-	\item Resource Usage Constraint
-	\begin{alignat}{10}
-			& \hat{uu}_{1p} 
-			&& \le uen_{1p} + ul_{p} + uv_{1p} \quad 
-			&& \forall p \\
-		& \hat{uu}_{tp} 
-			&& \le uen_{tp} + uv_{tp} \quad
-			&& \forall t \in \{ 2..T \}p 
-	\end{alignat}
-
-	\item Custom bounds on when reschedules are allowed
-	\begin{alignat}{10}
-		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
-		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
-		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t'=1 
-	\end{alignat}
-
-	\item Bounds on Schedules/Reschedules
-	\begin{alignat}{10}
-		& \sum_{t'} rsc_{tt'mdc} 	&& \le ps_{tmdc} \quad  && \forall tmdc  \\
-		& \sum_{t} sc_{tmdc} 		&& \le pw_{mdc} \quad 	&& \forall mdc 
-	\end{alignat}
-
-	\item Bounds on states
-	\begin{alignat}{10}
-		& ul_{p} 	&& \le uen_{p} * 3 \quad 	&& \forall p \\
-		& pw_{mdc} 	&& \le pea_{dc} * 20 \quad 			&& \forall mdc \\
-		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
-	\end{alignat}
-\end{itemize}
-
-\subsection{Transition Probabilities}
-
-\subsubsection{Uncertainty Sources}
-\begin{enumerate}
-
-	\item Number of patients arriving this period - $pw_{0dc}$
-		\begin{itemize}
-			\item $pea_{dc}$ - represents the random number of patients arriving. Follows a poisson distribution.
-		\end{itemize}
-
-	\item Transition between patient complexities within the wait list - $pw_{mdc}$
-		\begin{itemize}
-			\item $pwt_{mdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, who became more complex. Follows binomial distribution.
-			\item $ptp_{dc}$ represents transition probability to a higher complexity
-			\item $TL_{dc}$ represents the time at which this transition probability starts to have an effect (must be less than M)
-		\end{itemize}
-
-	\item Transition between patient complexities within the scheduled list - $ps_{tmdc}$
-		\begin{itemize}
-			\item $pst_{tmdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, scheduled into $t$ period, who became more complex. Follows binomial distribution.
-		\end{itemize}
-
-	\item Amout of expected units of PPE resource for the next time period - $ue_{1p}$
-		\begin{itemize}
-			\item $ued_{p}$ represents the random deviation of resource $p$ from the expectation. Follows uniform distribution.
-			\item $uen_{p}$ expected units of resource $p$ per period
-		\end{itemize}
 \end{enumerate}
-
-\subsubsection{Transition Constraints}
-
-\begin{enumerate}
-	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
-	\begin{alignat}{10}
-		& ul'_{p} 
-			&& = \hat{ul}_{p} + ued_{p} \quad 
-			&& \forall p \in \{ \text{Carry Over}\} \\
-		& ul'_{p} 
-			&& = ued_{p} \quad 
-			&& \forall p \in \{ \text{Non Carry Over}\} 
-	\end{alignat}
-
-	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients on waitlist
-		\begin{alignat}{10}
-			& pw'_{0dc} 
-				&& = pea_{dc} \quad
-				&& \forall dc \\  
-			& pw'_{mdc} 
-				&& = \hat{pw}_{m-1,dc}
-				&& \forall m \in \{ 1...(TL_{dc}-1) \} dc \\  
-			& pw'_{mdc} 
-				&& = \hat{pw}_{m-1,dc} + 
-				\overbrace{pwt_{m-1,d-1,c} - pwt_{m-1,dc}}^\text{
-					change in complexities} \quad
-				&& \forall m \in \{ TL_{dc}...M-1 \} dc \\  
-			& pw'_{Mdc} 
-				&& = \sum_{M-1}^{M} \big( 
-					\hat{pw}_{mdc} + 
-					\overbrace{pwt_{md-1,c} - pwt_{mdc}}^\text{
-						change in complexities} \big) \quad
-				&& \forall dc
-		\end{alignat}
-
-	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts scheduled
-		\begin{alignat}{10}
-			& ps'_{t0dc} 
-				&& = 0 \quad
-				&& \forall tdc \\  
-			& ps'_{Tmdc} 
-				&& = 0 \quad
-				&& \forall mdc \\  
-			& ps'_{tmdc} 
-				&& = \hat{ps}_{t+1,m-1,dc} \quad 
-				&& \forall t \in \{1...T-1\} m \in \{ 1... (TL_{dc}-1) \} dc \\ 
-			& ps'_{tmdc} 
-				&& = \hat{ps}_{t+1,m-1,dc} + 
-				\overbrace{pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc}}^\text{
-					change in complexities} \quad
-				&& \forall t \in \{1...T-1\} m \in \{ TL_{dc}...M-1 \} dc \\  
-			& ps'_{tMdc} 
-				&& = \sum_{M-1}^{M} \big( 
-				\hat{ps}_{t+1mdc} + 
-				\overbrace{pst_{t+1,md-1,c} - pst_{t+1,mdc}}^\text{
-					change in complexities} \big) \quad
-				&& \forall t \in \{1...T-1\} dc
-		\end{alignat}
-\end{enumerate}
-
-\subsection{Costs}
-Cost will come from 4 sources:  
-\begin{itemize} 
-	\item waiting ($cw$)
-	\item rescheduling ($cc$) 
-	\item scheduling ($cs_{t} = \sum_{t}cw^{t}$)
-	\item resource violation ($M$)
-\end{itemize}
-
-\begin{equation}\begin{alignedat}{10}
-	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
-		&& 
-			\overbrace{ \sum_{mdc} cw (\hat{pw}_{mdc}) }^\text{
-				cost of waiting}  + 
-			\overbrace{
-				\sum_{tmdc} cs_{t} (sc_{tmdc})
-			}^\text{Prefer earlier appointments} \\ 
-	&	&&  +
-			\overbrace{
-				\sum_{
-				\substack{tt`mdc \\ t' > t}} 
-				(cs_{t'-t} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
-			\overbrace{ 
-				\sum_{
-				\substack{tt`mdc \\ t' < t}}
-				(cs_{t-t'} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
-			M \sum_{tp} uv_{tp}
-\end{alignedat}\end{equation}
-
-\section{LP Model}
-
-\subsection{Full LP} 
-Given a full MDP model, the equivalent LP would look as follows:
-\begin{equation}
-	\max_{\vec{v}} \sum \alpha (\vec{S}) v(\vec{S}) 
-\end{equation}
-
-subject to
-\begin{equation}
-\label{full-adp-equation}
-	c(\vec{S}, \vec{A}) + \gamma \sum_{\vec{p}} p * v( \vec{S'}) 
-		\ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
-\end{equation}
-
-And all auxiliary constraints in "\nameref{auxiliary constraints}"
-
-\section{Aproximate Dynamic Programming Model}
-\subsection{Expectation ADP Model}
-Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
-\begin{equation}\begin{alignedat}{10}
-	& v(\vec{ul}, \vec{pw}, \vec{ps}) 
-		&& =  \beta^0 + \sum_{p} \beta_{p}^{ul} ul_{p} +
-			\sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
-			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
-\end{alignedat} \end{equation}
-
-Next we need to convert a part of equation \ref{full-adp-equation} into expectation. \\ 
-(To make it easier later, we will format is as $v(\vec{S}) - E[v(\vec{S}')]$)
-
-\begin{itemize}
-	\item $E[ued_p] = 0$
-	\item $E[pwt_{mdc}] = ptp_{dc} * \hat{pw}_{mdc}$ 
-	\item $E[pst_{tmdc}] = ptp_{dc} * \hat{ps}_{tmdc}$ 
-\end{itemize}
-
-\begin{fleqn}[\parindent]
-\begin{equation}
-	\beta^{0}: \qquad (1-\gamma) \beta^{0}
-\end{equation}
-\end{fleqn}
-
-\begin{fleqn}[\parindent]
-\begin{equation}
-\beta^{ul}_{p}: \qquad 
-	\sum_{p \in \text{co}} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big) + 
-	\sum_{p \in \text{nco}} \beta_{p}^{ul} ( ul_{p}) 
-\end{equation}
-\end{fleqn}
-
-\begin{fleqn}[\parindent]
-\begin{equation}\begin{alignedat}{10}
-& \beta^{pw}_{mdc}: \qquad 
-	&& 	\sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) +
-	\sum_{m=1dc}^{TL_{dc}-1} \beta_{mdc}^{pw} 
-	\Big( pw_{mdc} - \gamma 
-		(\hat{pw}_{m-1dc}) \Big) + \\
-	& && \sum_{m=TL_{dc}dc}^{M-1} \beta_{mdc}^{pw} 
-		\Big( pw_{mdc} - \gamma 
-		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
-	& && \sum_{dc} \beta_{Mdc}^{pw} 
-		\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
-		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
-\end{alignedat} \end{equation}
-\end{fleqn}
-
-\begin{fleqn}[\parindent]
-\begin{equation}\begin{alignedat}{10}
-& \beta^{ps}_{tmdc}: \qquad 
-	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
-\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + 
-	\sum_{t=1m=1dc}^{T-1, TL_{dc}-1} \beta_{tmdc}^{ps} 
-	\Big( ps_{tmdc} - \gamma 
-	(\hat{ps}_{t+1m-1dc}) \Big) + \\
-&	&& 
-	\sum_{t=1m=TL_{dc}dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
-	\Big( ps_{tmdc} - \gamma 
-		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
-&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
-	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
-		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
-\end{alignedat} \end{equation}
-\end{fleqn}
-
-Using the numbers above we rearrange the original equation as follows:
-\begin{equation}
-	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ut} E[ut] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
-\end{equation}
-Subject to:
-\begin{equation}
-	v(\vec{S}) - E[v(\vec{S}')] \le c(\vec{S}, \vec{A}) \quad \forall \vec{S} \vec{A} 
-\end{equation}
-
-\subsection{ADP Master Problem}
-\label{Dual of ADP LP}
-Converting to Dual
-\begin{equation}
-	\min_{w} \sum_{\vec{S} \vec{A}} w(\vec{S} \vec{A}) c(\vec{S} \vec{A})
-\end{equation}
-Subject To:
-
-\begin{alignat}{10}
-	& \beta^{0}: 
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
-	& \beta^{ul}: 
-		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
-			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
-		&&	\forall p \in \{ \text{carry over} \} \\ 
-	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
-		&&	\forall p \in \{ \text{non carry over} \}\\
-	&	\beta^{pw}: 
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
-		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
-		&&	\forall dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
-		\gamma (\hat{pw}_{m-1dc}) \Big) \ge E[pw_{mdc}]
-		&&	\forall m \in \{1...TL_{dc}-1\} dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
-		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
-		&&	\forall m \in \{TL_{dc}...M-1\} dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
-			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
-		&&	\forall dc \\ 
-	&	\beta^{ps}: 
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
-		&&	\forall tdc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
-		&&	\forall mdc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
-		(\hat{ps}_{t+1m-1dc}) \Big) \ge E[ps_{tmdc}] \;
-		&&	\forall \{1...T-1\} \{1...TL_{dc}-1\}dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
-			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
-		&&	\forall \{1...T-1\} \{TL_{dc}...M-1\}dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
-		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
-		&&	\forall \{1...T-1\} dc
-\end{alignat}
-
-\begin{equation}
-	\text{State Action Bounds:} \qquad w \ge 0 \qquad \forall w
-\end{equation}
-
-\subsection{ADP Pricing Problem}
-\label{Pricing Problem}
-\begin{equation}
-	\min_{(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \in S,  (\vec{sc}, \vec{rsc}) \in A } c(\vec{pw},\vec{sc},\vec{rsc},\vec{uv}) - \Big(v(\vec{S}) - E[v(\vec{S}')] \Big)
-\end{equation}
-Subject to:
-constraints in sections "\nameref{state-action constraints}" and "\nameref{auxiliary constraints}"
-
-\section{Solution Explanation}
-\subsection{Algorithm for solving}
-To get $\vec{\beta}$ values, which will be used to generate an action follow steps below:
-\begin{enumerate}
-	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pw] E[pw]$
-	\item Create an initial feasible set of state-action pairs - $\vec{w}$
-	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints for a specific action.
-	\item Solve model in section "\nameref{Pricing Problem}", where duals from problem in step 3  correspond to $\vec{\beta}$ values. 
-		\begin{itemize}
-			\item If objective function is less than 0, add solution as a single state-action pair to $\vec{w}$ and go to step 3
-			\item If objective function is greater than 0, continue to next step
-		\end{itemize}
-	\item Duals from problem in step 3 correspond to final $\vec{\beta}$ values
-\end{enumerate}
-
-\subsection{Generating an Action}
-Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
-\begin{equation*}
-	\min_{\vec{A}} c(\vec{S}, \vec{A}) + \gamma v(S')
-\end{equation*}
-
-\begin{equation}\begin{alignedat}{10}
-	&	v(S') = \Bigg( 
-		&& 	\beta^0 + 
-			\bigg( \sum_{p} \beta_{1p}^{ue} 
-				(uen_{d} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
-			\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\
-	&	&& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-				( \hat{uu}_{t+1,p} + \sum_{mdc} E[pst_{tmdc}] (U_{pd+1c} - U_{pdc})) \bigg) + \\
-	&	&&	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
-			\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
-				(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \bigg) + \\
-	&	&&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
-				(\sum_{M-1}^{M} \hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}])\bigg) + \\
-	& 	&&	\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
-				(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \bigg) + \\	
-	&	&&	\qquad \qquad \bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
-				(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}])) \bigg)
-			\Bigg)
-\end{alignedat}
-\end{equation}
-
-Subject to:
-constraints in section "\nameref{state-action constraints}"
-
-\end{document}

### 2021-08-12 v2-Manuscript/sections/data.tex
Tuned solve parameters & started adding priority

\section{Data}

\subsection{Sets}
\begin{itemize}
	\item $\vec{m}$ - 
		period defining how long a patient has been waiting so far. 0 represents patients who have arrived. 
		$m \in \{0 ... M\}$
	\item $\vec{t}$ - 
		denotes time of various things - scheduled into, waitlist period, rescheduled from. 
		$t \in \{1 ... T\}$
	\item $\vec{d}$ - 
		denotes complexity of a patient. 
		$d \in \{ 1 ... D \}$
	\item $\vec{k}$ - 
		denotes priority of a patient. 
		$d \in \{ 1 ... K \}$
	\item $\vec{c}$ - 
		denotes surgery type of a patient. 
		$c \in \{ 1 ... C \}$
	\item $\vec{p}$ - 
		denotes resource type. 
		$p \in \{ 1 ... P \}$
\end{itemize}

\subsection{Input Data}
\begin{itemize}
	\item $p\_co_{p}$ - set of resources that carries over between periods
	\item $p\_nco_{p}$ - set of resources that doesn't carry over between periods
	\item $p\_ue_{p}$ - amount of resources expected each period
	\item $p\_ued_{p}$ - Deviation from $p\_ue$. Uniform, defined by lower and upper value. The mean must be zero
	\item $U_{pdc}$ - Usage of resource $p$, of complexity $d$, surgery type $c$
	\item $pea_{dc}$ - Patient Expected Arrival
	\item $TL\_d_{dc}$ - Time Limit after which patient can transition in complexity
	\item $TL\_k_{kc}$ - Time Limit after which patient can transition in priority
	\item $ptp\_c_{dc}$ - Probability to transition to higher complexity
	\item $ptp\_p_{kc}$ - Probability to transition to higher priority
\end{itemize}

\subsection{Model Parameters}
\begin{itemize}
	\item $cw_{d}$ - defines cost of waiting, by priority $d$
	\item $cc$ - additional cost of rescheduling 
	\item $\alpha$ - discount factor to be used in the model
\end{itemize}

### 2021-08-12 v2-Manuscript/sections/mdp_model.tex
Tuned solve parameters & started adding priority

--- 2021-07-28 v2-Manuscript/Manuscript.tex
@@
-%%%~~~~~~~~~~~~~~~~~ Preamble ~~~~~~~~~~~~~~~~~~~~~~
-\documentclass{article}
+\section{MDP Model}
 
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath, amssymb, nccmath}
-
-\usepackage{xcolor, hyperref}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\usepackage{geometry}
-\geometry{margin=0.65in}
-\setlength\parindent{0pt}
-
-\title{Dynamic Knapsack Problem}
-\author{AS, WM, KV}
-\date{\today}
-
-\allowdisplaybreaks
-
-%%%~~~~~~~~~~~~~~~~~ Document ~~~~~~~~~~~~~~~~~~~~~~
-\begin{document}
-
-\maketitle
-\tableofcontents
-\newpage
-
-\section{Questions/Comments}
-
-\subsection{Questions}
-\begin{itemize}
-	\item Should $ul$ definition include units violated?? it seems a constraint might be violated otherwise
-\end{itemize}
-
-\subsection{Comments}
-\begin{itemize}
-	\item
-\end{itemize}
-
-\section{Assumptions} 
-\begin{itemize}
-	\item Assume all new patients are arriving at the beginning of the period 
-	\begin{itemize}
-		\item Assume arrivals follow poisson distribution
-	\end{itemize}
-
-	\item It is assumed that patients do not change complexities within some limit ($TL$). 
-	\begin{itemize}
-		\item Let's assume our limit is 10 periods, patients will never change complexities within the 10 periods.  
-		\item However, on their 10th period, they can increase complexity
-	\end{itemize}
-
-	\item We assume patient complexity transitions follow binary distribution - each period a patient can become more complex with a static probability
-	\begin{itemize}
-		\item While patient is waiting less that $TL$, the transition probability is 0.
-		\item After $TL$, a patient has some probability they move to a higher complexity in that period
-	\end{itemize}
-
-	\item It is assumed if a patient is scheduled in period one, it means they are served "immediately", regardless if in practice the appointment is at the beginning or end of the period.
-	\item We distinguish between two types of reschedules: good and bad reschedules
-	\begin{itemize}
-		\item Good reschedules are reschedules where a patient is rescheduled to an earlier period
-		\item Bad reschedules are reschedules where a patient is rescheduled to a later period
-	\end{itemize}
-
-	\item We assume that only specific reschedules are allowed (to simplify the model, and remove  redundancies)
-	\begin{itemize}
-		\item Good reschedules are allowed from any period after 2 into period 1
-		\item Bad reschedules are only allowed from period 1 to any period after 2
-	\end{itemize}
-
-	\item It is assumed that there is a certain default expected number of PPE units available for all periods
-	\begin{itemize}
-		\item However, in the period 1, there is some random deviation from the expected number of units
-		\item This random deviation follows some uniform distribution
-	\end{itemize}
-	\item We allow some violation of PPE units, in rare cases (with high cost), in order to accomodate changes due to variability.
-	\begin{itemize}
-		\item If we have violation of PPE units - the extra capacity comes from external source
-	\end{itemize}
-\end{itemize}
-
-\section{MDP Model}
 \subsection{Decision Epochs}
@@
 \subsubsection{Description}
-State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
+State is defined by carried over resources, deviation from expected resources,, patient waitlist/demand, and patients already scheduled
 \[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
@@
 	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1. This is only for resources that can be carried over
-    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
-    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
+	\item $\vec{pw} = pw_{mdkc}$ - Patients of complexity $d$, priority $k$, surgery type $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
+	\item $\vec{ps} = ps_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
 \end{itemize}
@@
 \begin{itemize}
-    	\item $\vec{sc} = sc_{tmdc}$ - Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to schedule in period $t$
-	\item $\vec{rsc} = rsc_{tt'mdc}$ -Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to reschedule from period $t$ to period $t'$
-	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
+	\item $\vec{sc} = sc_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, waiting for $m$ periods, to schedule in period $t$
+	\item $\vec{rsc} = rsc_{tt'mdkc}$ -Patients of complexity $d$, priority $k$, surgery type $c$, waiting for $m$ periods, to reschedule from $t$ to $t'$
 \end{itemize}
@@
 \begin{itemize}
+	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
 	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
@@
 		& \hat{uv}_{1p} 
-				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
+		&& \le  (\hat{uu}_{1p} - p\_ue_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
 		&& \forall p \\
 		& \hat{uv}_{tp} 
-				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
+		&& \le  (\hat{uu}_{tp} - p\_ue_{tp}) + M(1-uvb_{tp}) \quad
 		&& \forall t \in \{ 2..T \} p \\
@@
 		& \hat{ul}_{p} 
-				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
+		&& \ge p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
 		&& \forall p \\
@@
 		& \hat{ul}_{p} 
-				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
+		&& \le (p\_ue_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
 		&& \forall p 
@@
 		& \hat{uu}_{1p} 
-			&& \le uen_{1p} + ul_{p} + uv_{1p} \quad 
+		&& \le p\_ue_{1p} + ul_{p} + uv_{1p} \quad 
 		&& \forall p \\
 		& \hat{uu}_{tp} 
-			&& \le uen_{tp} + uv_{tp} \quad
+		&& \le p\_ue_{tp} + uv_{tp} \quad
 		&& \forall t \in \{ 2..T \}p 
@@
 	\begin{alignat}{10}
-		& ul_{p} 	&& \le uen_{p} * 3 \quad 	&& \forall p \\
+		& ul_{p} 	&& \le p\_ue_{p} * 3 \quad 			&& \forall p \\
 		& pw_{mdc} 	&& \le pea_{dc} * 20 \quad 			&& \forall mdc \\
@@
 
-\subsection{Transition Probabilities}
-
-\subsubsection{Uncertainty Sources}
-\begin{enumerate}
-
-	\item Number of patients arriving this period - $pw_{0dc}$
-		\begin{itemize}
-			\item $pea_{dc}$ - represents the random number of patients arriving. Follows a poisson distribution.
-		\end{itemize}
-
-	\item Transition between patient complexities within the wait list - $pw_{mdc}$
-		\begin{itemize}
-			\item $pwt_{mdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, who became more complex. Follows binomial distribution.
-			\item $ptp_{dc}$ represents transition probability to a higher complexity
-			\item $TL_{dc}$ represents the time at which this transition probability starts to have an effect (must be less than M)
-		\end{itemize}
-
-	\item Transition between patient complexities within the scheduled list - $ps_{tmdc}$
-		\begin{itemize}
-			\item $pst_{tmdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, scheduled into $t$ period, who became more complex. Follows binomial distribution.
-		\end{itemize}
-
-	\item Amout of expected units of PPE resource for the next time period - $ue_{1p}$
-		\begin{itemize}
-			\item $ued_{p}$ represents the random deviation of resource $p$ from the expectation. Follows uniform distribution.
-			\item $uen_{p}$ expected units of resource $p$ per period
-		\end{itemize}
-\end{enumerate}
-
-\subsubsection{Transition Constraints}
+\subsection{Transition}
 
 \begin{enumerate}
-	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
+	\item Transition from $\vec{ul}$ to $\vec{ul'}$ - Resource Carry Over
 	\begin{alignat}{10}
 		& ul'_{p} 
-			&& = \hat{ul}_{p} + ued_{p} \quad 
-			&& \forall p \in \{ \text{Carry Over}\} \\
+		&& = \hat{ul}_{p} + p\_ued_{p} \quad 
+		&& \forall p \in \{ p\_co \} \\
 		& ul'_{p} 
-			&& = ued_{p} \quad 
-			&& \forall p \in \{ \text{Non Carry Over}\} 
+		&& = p\_ued_{p} \quad 
+		&& \forall p \in \{ p\_nco \} 
 	\end{alignat}
@@
 \subsection{Costs}
-Cost will come from 4 sources:  
-\begin{itemize} 
-	\item waiting ($cw$)
-	\item rescheduling ($cc$) 
-	\item scheduling ($cs_{t} = \sum_{t}cw^{t}$)
-	\item resource violation ($M$)
-\end{itemize}
-
 \begin{equation}\begin{alignedat}{10}
@@
 \end{alignedat}\end{equation}
-
-\section{LP Model}
-
-\subsection{Full LP} 
-Given a full MDP model, the equivalent LP would look as follows:
-\begin{equation}
-	\max_{\vec{v}} \sum \alpha (\vec{S}) v(\vec{S}) 
-\end{equation}
-
-subject to
-\begin{equation}
-\label{full-adp-equation}
-	c(\vec{S}, \vec{A}) + \gamma \sum_{\vec{p}} p * v( \vec{S'}) 
-		\ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
-\end{equation}
-
-And all auxiliary constraints in "\nameref{auxiliary constraints}"
-
-\section{Aproximate Dynamic Programming Model}
-\subsection{Expectation ADP Model}
-Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
-\begin{equation}\begin{alignedat}{10}
-	& v(\vec{ul}, \vec{pw}, \vec{ps}) 
-		&& =  \beta^0 + \sum_{p} \beta_{p}^{ul} ul_{p} +
-			\sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
-			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
-\end{alignedat} \end{equation}
-
-Next we need to convert a part of equation \ref{full-adp-equation} into expectation. \\ 
-(To make it easier later, we will format is as $v(\vec{S}) - E[v(\vec{S}')]$)
-
-\begin{itemize}
-	\item $E[ued_p] = 0$
-	\item $E[pwt_{mdc}] = ptp_{dc} * \hat{pw}_{mdc}$ 
-	\item $E[pst_{tmdc}] = ptp_{dc} * \hat{ps}_{tmdc}$ 
-\end{itemize}
-
-\begin{fleqn}[\parindent]
-\begin{equation}
-	\beta^{0}: \qquad (1-\gamma) \beta^{0}
-\end{equation}
-\end{fleqn}
-
-\begin{fleqn}[\parindent]
-\begin{equation}
-\beta^{ul}_{p}: \qquad 
-	\sum_{p \in \text{co}} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big) + 
-	\sum_{p \in \text{nco}} \beta_{p}^{ul} ( ul_{p}) 
-\end{equation}
-\end{fleqn}
-
-\begin{fleqn}[\parindent]
-\begin{equation}\begin{alignedat}{10}
-& \beta^{pw}_{mdc}: \qquad 
-	&& 	\sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) +
-	\sum_{m=1dc}^{TL_{dc}-1} \beta_{mdc}^{pw} 
-	\Big( pw_{mdc} - \gamma 
-		(\hat{pw}_{m-1dc}) \Big) + \\
-	& && \sum_{m=TL_{dc}dc}^{M-1} \beta_{mdc}^{pw} 
-		\Big( pw_{mdc} - \gamma 
-		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
-	& && \sum_{dc} \beta_{Mdc}^{pw} 
-		\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
-		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
-\end{alignedat} \end{equation}
-\end{fleqn}
-
-\begin{fleqn}[\parindent]
-\begin{equation}\begin{alignedat}{10}
-& \beta^{ps}_{tmdc}: \qquad 
-	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
-\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + 
-	\sum_{t=1m=1dc}^{T-1, TL_{dc}-1} \beta_{tmdc}^{ps} 
-	\Big( ps_{tmdc} - \gamma 
-	(\hat{ps}_{t+1m-1dc}) \Big) + \\
-&	&& 
-	\sum_{t=1m=TL_{dc}dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
-	\Big( ps_{tmdc} - \gamma 
-		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
-&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
-	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
-		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
-\end{alignedat} \end{equation}
-\end{fleqn}
-
-Using the numbers above we rearrange the original equation as follows:
-\begin{equation}
-	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ut} E[ut] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
-\end{equation}
-Subject to:
-\begin{equation}
-	v(\vec{S}) - E[v(\vec{S}')] \le c(\vec{S}, \vec{A}) \quad \forall \vec{S} \vec{A} 
-\end{equation}
-
-\subsection{ADP Master Problem}
-\label{Dual of ADP LP}
-Converting to Dual
-\begin{equation}
-	\min_{w} \sum_{\vec{S} \vec{A}} w(\vec{S} \vec{A}) c(\vec{S} \vec{A})
-\end{equation}
-Subject To:
-
-\begin{alignat}{10}
-	& \beta^{0}: 
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
-	& \beta^{ul}: 
-		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
-			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
-		&&	\forall p \in \{ \text{carry over} \} \\ 
-	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
-		&&	\forall p \in \{ \text{non carry over} \}\\
-	&	\beta^{pw}: 
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
-		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
-		&&	\forall dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
-		\gamma (\hat{pw}_{m-1dc}) \Big) \ge E[pw_{mdc}]
-		&&	\forall m \in \{1...TL_{dc}-1\} dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
-		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
-		&&	\forall m \in \{TL_{dc}...M-1\} dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
-			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
-		&&	\forall dc \\ 
-	&	\beta^{ps}: 
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
-		&&	\forall tdc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
-		&&	\forall mdc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
-		(\hat{ps}_{t+1m-1dc}) \Big) \ge E[ps_{tmdc}] \;
-		&&	\forall \{1...T-1\} \{1...TL_{dc}-1\}dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
-			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
-		&&	\forall \{1...T-1\} \{TL_{dc}...M-1\}dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
-		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
-		&&	\forall \{1...T-1\} dc
-\end{alignat}
-
-\begin{equation}
-	\text{State Action Bounds:} \qquad w \ge 0 \qquad \forall w
-\end{equation}
-
-\subsection{ADP Pricing Problem}
-\label{Pricing Problem}
-\begin{equation}
-	\min_{(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \in S,  (\vec{sc}, \vec{rsc}) \in A } c(\vec{pw},\vec{sc},\vec{rsc},\vec{uv}) - \Big(v(\vec{S}) - E[v(\vec{S}')] \Big)
-\end{equation}
-Subject to:
-constraints in sections "\nameref{state-action constraints}" and "\nameref{auxiliary constraints}"
-
-\section{Solution Explanation}
-\subsection{Algorithm for solving}
-To get $\vec{\beta}$ values, which will be used to generate an action follow steps below:
-\begin{enumerate}
-	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pw] E[pw]$
-	\item Create an initial feasible set of state-action pairs - $\vec{w}$
-	\item Solve model in section "\nameref{Dual of ADP LP}" where each state-action pairs in $\vec{w}$ corresponds to a variable and parameters for all the constraints for a specific action.
-	\item Solve model in section "\nameref{Pricing Problem}", where duals from problem in step 3  correspond to $\vec{\beta}$ values. 
-		\begin{itemize}
-			\item If objective function is less than 0, add solution as a single state-action pair to $\vec{w}$ and go to step 3
-			\item If objective function is greater than 0, continue to next step
-		\end{itemize}
-	\item Duals from problem in step 3 correspond to final $\vec{\beta}$ values
-\end{enumerate}
-
-\subsection{Generating an Action}
-Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
-\begin{equation*}
-	\min_{\vec{A}} c(\vec{S}, \vec{A}) + \gamma v(S')
-\end{equation*}
-
-\begin{equation}\begin{alignedat}{10}
-	&	v(S') = \Bigg( 
-		&& 	\beta^0 + 
-			\bigg( \sum_{p} \beta_{1p}^{ue} 
-				(uen_{d} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
-			\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\
-	&	&& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-				( \hat{uu}_{t+1,p} + \sum_{mdc} E[pst_{tmdc}] (U_{pd+1c} - U_{pdc})) \bigg) + \\
-	&	&&	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
-			\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
-				(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \bigg) + \\
-	&	&&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
-				(\sum_{M-1}^{M} \hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}])\bigg) + \\
-	& 	&&	\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
-				(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \bigg) + \\	
-	&	&&	\qquad \qquad \bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
-				(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}])) \bigg)
-			\Bigg)
-\end{alignedat}
-\end{equation}
-
-Subject to:
-constraints in section "\nameref{state-action constraints}"
-
-\end{document}

### 2021-08-12 v2-Implementation/main.py

@@ -19,7 +19,8 @@ state_action_list = [(init_state, init_action)]
 feasible_list = generate_feasible_sa_list(input_data, state_action_list)
  
 # Phase 2
-stabilization_parameter = 0
+stabilization_parameter = 0.7
+# start_betas = read_betas(os.path.join(my_path, 'Data', f'Intermediate-Betas.xlsx'))
 optimal_list, betas = generate_optimal_sa_list(input_data, feasible_list,stabilization_parameter)
 export_betas(betas, os.path.join(my_path, 'Data', f'Optimal-Betas-full-newcost.xlsx'))
 

### 2021-08-16 v2-Manuscript/sections/adp_model.tex
finalized adding priority

@@
 		&& =  \beta^0 + \sum_{p} \beta_{p}^{ul} ul_{p} +
-		\sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
-		\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
+		\sum_{mdkc} \beta_{mdkc}^{pw} pw_{mdkc}  + 
+		\sum_{tmdkc} \beta_{tmdkc}^{ps} ps_{tmdkc}
 \end{alignedat} \end{equation}
@@
 \begin{itemize}
-	\item $E[ued_p] = 0$
-	\item $E[pwt_{mdc}] = ptp_{dc} * \hat{pw}_{mdc}$ 
-	\item $E[pst_{tmdc}] = ptp_{dc} * \hat{ps}_{tmdc}$ 
+	\item $E[p\_ued_p] = 0$
+	\item $E[pwt_{mdkc}] = ptp\_d_{dc} * \hat{pw}_{mdkc}$ 
+	\item $E[pst_{tmdkc}] = ptp\_k_{kc} * \hat{ps}_{tmdkc}$ 
 \end{itemize}
@@
 		\beta^{ul}_{p}: \qquad 
-		\sum_{p \in \text{co}} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big) + 
-		\sum_{p \in \text{nco}} \beta_{p}^{ul} ( ul_{p}) 
+		\sum_{p \in \text{p\_co}} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big) + 
+		\sum_{p \in \text{p\_nco}} \beta_{p}^{ul} ( ul_{p}) 
 	\end{equation}
@@
 	\begin{equation}\begin{alignedat}{10}
-			& \beta^{pw}_{mdc}: \qquad 
-			&& 	\sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) +
-			\sum_{m=1dc}^{TL_{dc}-1} \beta_{mdc}^{pw} 
-			\Big( pw_{mdc} - \gamma 
-			(\hat{pw}_{m-1dc}) \Big) + \\
-			& && \sum_{m=TL_{dc}dc}^{M-1} \beta_{mdc}^{pw} 
-			\Big( pw_{mdc} - \gamma 
-			(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
-			& && \sum_{dc} \beta_{Mdc}^{pw} 
-			\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
-			(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
+			& \beta^{pw}_{mdkc}: \qquad 
+				&& 	\sum_{dkc} \beta_{0dkc}^{pw} \Big( pw_{0dkc} - \gamma (pea_{dkc}) \Big) +
+					\sum_{m=1dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
+					\Big( pw_{mdkc} - \gamma 
+					(\hat{pw}_{m-1dkc}) \Big) + \\
+			& 
+				&& \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
+					\Big( pw_{mdkc} - \gamma 
+					(\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - + E[pwt\_k_{k}]) \Big) + \\
+			& 
+				&& \sum_{dc} \beta_{Mdkc}^{pw} 
+					\Big( pw_{Mdkc} - \gamma \sum_{M-1}^{M}
+					(\hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big)
 	\end{alignedat} \end{equation}
@@
 	\begin{equation}\begin{alignedat}{10}
-			& \beta^{ps}_{tmdc}: \qquad 
-			&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
-			\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + 
-			\sum_{t=1m=1dc}^{T-1, TL_{dc}-1} \beta_{tmdc}^{ps} 
-			\Big( ps_{tmdc} - \gamma 
-			(\hat{ps}_{t+1m-1dc}) \Big) + \\
-			&	&& 
-			\sum_{t=1m=TL_{dc}dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
-			\Big( ps_{tmdc} - \gamma 
-			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
-			&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
-			\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
-			(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
+			& \beta^{ps}_{tmdkc}: \qquad 
+				&& \sum_{tdkc} \beta_{t0dkc}^{ps} \Big( ps_{t0dkc}) \Big) + 
+					\sum_{mdkc} \beta_{Tmdkc}^{ps} \Big( ps_{Tmdkc}) \Big) + 
+					\sum_{t=1m=1dkc}^{T-1, TL_{c}-1} \beta_{tmdkc}^{ps} 
+					\Big( ps_{tmdkc} - \gamma 
+					(\hat{ps}_{t+1m-1dkc}) \Big) + \\
+			&	
+				&& 
+					\sum_{t=1m=TL_{c}dkc}^{T-1,M-1} \beta_{tmdkc}^{ps} 
+					\Big( ps_{tmdkc} - \gamma 
+					(\hat{ps}_{t+1m-1dkc} + E[pst\_d_{t+1m-1d-1c}] - E[pst\_d_{d}]  + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) + \\
+			&	
+				&& 
+					\sum_{t=1dkc}^{T-1} \beta_{tMdkc}^{ps} 
+					\Big( ps_{tMdkc} - \gamma \sum_{M-1}^{M}
+					(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big)
 	\end{alignedat} \end{equation}
@@
 \label{Dual of ADP LP}
-Converting to Dual
+The equation above has a reasonable amount of decision variables, but an uncountable amount of constraints. Let's use column generation to solve it. First converting to dual
 \begin{equation}
@@
 		\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}] 
-	&&	\forall p \in \{ \text{carry over} \} \\ 
-	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
-	&&	\forall p \in \{ \text{non carry over} \}\\
+		&&	\forall p \in p\_co \\ 
+	&	
+		&& 	\sum_{\vec{S}\vec{A}}\vec{w} ( ul_{p}) \ge E[ul_{p}]
+		&&	\forall p \in p\_nco \\
 	&	\beta^{pw}: 
-	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
-	\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
-	&&	\forall dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
-	\gamma (\hat{pw}_{m-1dc}) \Big) \ge E[pw_{mdc}]
-	&&	\forall m \in \{1...TL_{dc}-1\} dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
-	\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
-	&&	\forall m \in \{TL_{dc}...M-1\} dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
-	\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
-	&&	\forall dc \\ 
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dkc} - 
+		\gamma (pea_{dkc}) \Big) \ge E[ps_{0dkc}]
+		&&	\forall dkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdkc} - 
+		\gamma (\hat{pw}_{m-1dkc}) \Big) \ge E[pw_{mdkc}]
+		&&	\forall m \in \{1...TL_{c}-1\} dkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdkc} - 
+		\gamma (\hat{pw}_{m-1dkc}  + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] +\\ 
+		& && \qquad + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big) \ge E[pw_{mdkc}]
+		&&	\forall m \in \{TL_{c}...M-1\} dkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
+		\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + \\
+		&	&& \qquad  + E[pwt\_k_{k-1k}] - E[pwt\_k_{k}] )  \Big) \ge E[pw_{Mdc}]
+		&&	\forall dkc \\ 
 	&	\beta^{ps}: 
-	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
-	&&	\forall tdc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
-	&&	\forall mdc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
-	(\hat{ps}_{t+1m-1dc}) \Big) \ge E[ps_{tmdc}] \;
-	&&	\forall \{1...T-1\} \{1...TL_{dc}-1\}dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
-	(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
-	&&	\forall \{1...T-1\} \{TL_{dc}...M-1\}dc \\
-	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
-	(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
-	&&	\forall \{1...T-1\} dc
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dkc} \Big) \ge E[ps_{t0dkc}]
+		&&	\forall tdkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdkc} \Big) \ge E[ps_{Tmdkc}]
+		&&	\forall mdkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdkc} - \gamma 
+				(\hat{ps}_{t+1m-1dkc}) \Big) \ge E[ps_{tmdkc}] \;
+		&&	\forall \{1...T-1\} \{1...TL_{c}-1\}dkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdkc} - \gamma 
+				(\hat{ps}_{t+1m-1dc} + E[pst\_d_{t+1m-1d-1c}] - E[pst\_d_{d}] + \\
+		& &&	+ E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) \ge E[ps_{tmdkc}] 
+		&&	\forall \{1...T-1\} \{TL_{c}...M-1\}dkc \\
+	&	
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdkc} - \gamma \sum_{M-1}^{M}
+				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - E[pst\_d_{d}] + \\
+		& &&	+ E[pst\_k_{k-1}] - E[pst\_k_{k}]) \Big) \ge E[ps_{tMdkc}]
+		&&	\forall \{1...T-1\} dkc
 \end{alignat}

### 2021-08-16 v2-Manuscript/sections/data.tex
finalized adding priority

@@
 	\item $U_{pdc}$ - Usage of resource $p$, of complexity $d$, surgery type $c$
-	\item $pea_{dc}$ - Patient Expected Arrival
-	\item $TL\_d_{dc}$ - Time Limit after which patient can transition in complexity
-	\item $TL\_k_{kc}$ - Time Limit after which patient can transition in priority
-	\item $ptp\_c_{dc}$ - Probability to transition to higher complexity
+	\item $pea_{dkc}$ - Patient Expected Arrival
+	\item $TL_{c}$ - Time Limit after which patient can transition in complexity/priority
+	\item $ptp\_d_{dc}$ - Probability to transition to higher complexity
 	\item $ptp\_p_{kc}$ - Probability to transition to higher priority
@@
 \begin{itemize}
-	\item $cw_{d}$ - defines cost of waiting, by priority $d$
-	\item $cc$ - additional cost of rescheduling 
+	\item $cw_{k}$ - defines cost of waiting, by priority $k$
+	\item $cc_{k}$ - additional cost of rescheduling, by priority $k$ 
 	\item $\alpha$ - discount factor to be used in the model

### 2021-08-16 v2-Manuscript/sections/mdp_model.tex
finalized adding priority

@@
 \begin{itemize}
-	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1. This is only for resources that can be carried over
+	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1.
 	\item $\vec{pw} = pw_{mdkc}$ - Patients of complexity $d$, priority $k$, surgery type $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
@@
 	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
-	\item $\hat{ul}_{p}$ - post-decision unit leftover at period 1
-	\item $ulb_{p}$ - binary variable to enforce $ul$ variable without objective function
+	\item $\hat{ul}_{p \in p\_co}$ - post-decision unit leftover at period 1
+	\item $ulb_{p \in p\_co}$ - binary variable to enforce $ul$ variable without objective function
 	\item $\hat{uu}_{tp}$ - post-decision units used
-	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
-	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
+	\item $\hat{pw}_{mdkc}$ - post-decision patients waiting
+	\item $\hat{ps}_{tmdkc}$ - post-decision patients scheduled
 \end{itemize}
@@
 	& \hat{uu}_{tp} 
-	&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
+	&& =  \sum_{mdkc} U_{pdc} \hat{ps}_{tmdkc} \quad
 	&& \forall tp \\ 
-	& \hat{pw}_{mdc} 
-	&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
-	&& \forall mdc \\ 
-	& \hat{ps}_{tmdc} 
-	&& = ps_{tmdc} + sc_{tmdc} + 
-	\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
-	&& \forall tmdc
+	& \hat{pw}_{mdkc} 
+	&& = pw_{mdkc} - \sum_{t} sc_{tmdkc} \quad 
+	&& \forall mdkc \\ 
+	& \hat{ps}_{tmdkc} 
+	&& = ps_{tmdkc} + sc_{tmdkc} + 
+	\sum_{t} rsc_{tt'mdkc} - \sum_{t'} rsc_{tt'mdkc} \quad 
+	&& \forall tmdkc
 \end{alignat}
@@
 		&& \ge 0 \quad 
-		&& \forall p \\
+		&& \forall p  \in p\_co \\
 		& \hat{ul}_{p} 
 		&& \ge p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
-		&& \forall p \\
+		&& \forall p  \in p\_co\\
 		& \hat{ul}_{p} 
 		&& \le M (ulb_{p}) \quad 
-		&& \forall p \\
+		&& \forall p  \in p\_co\\
 		& \hat{ul}_{p} 
 		&& \le (p\_ue_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
-		&& \forall p 
+		&& \forall p  \in p\_co
 	\end{alignat}
@@
 			&& \le p\_ue_{1p} + ul_{p} + uv_{1p} \quad 
-		&& \forall p \\
+			&& \forall p \in p\_co \\
+		& \hat{uu}_{1p} 
+			&& \le p\_ue_{1p} + uv_{1p} \quad 
+			&& \forall p \in p\_nco \\
 		& \hat{uu}_{tp} 
@@
 	\begin{alignat}{10}
-		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
-		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
-		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t'=1 
+		& rsc_{tt'mdkc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdkc \\
+		% & rsc_{tt'mdkc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdkc  \\
+		& rsc_{tt'mdkc} && = 0 \quad && \forall tt'mdkc, \text{where } t=t'=1 
 	\end{alignat}
@@
 	\begin{alignat}{10}
-		& \sum_{t'} rsc_{tt'mdc} 	&& \le ps_{tmdc} \quad  && \forall tmdc  \\
-		& \sum_{t} sc_{tmdc} 		&& \le pw_{mdc} \quad 	&& \forall mdc 
+		& \sum_{t'} rsc_{tt'mdkc} 	&& \le ps_{tmdkc} \quad  && \forall tmdkc  \\
+		& \sum_{t} sc_{tmdkc} 		&& \le pw_{mdkc} \quad 	&& \forall mdkc 
 	\end{alignat}
@@
 	\begin{alignat}{10}
-		& ul_{p} 	&& \le p\_ue_{p} * 3 \quad 			&& \forall p \\
-		& pw_{mdc} 	&& \le pea_{dc} * 20 \quad 			&& \forall mdc \\
-		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
+		& ul_{p} 	&& \le p\_ue_{p} \quad 			&& \forall p \\
+		& pw_{mdkc} 	&& \le pea_{dkc} * 2 \quad 			&& \forall mdkc \\
+		& ps_{tmdkc} && \le pea_{dkc} \quad 			&& \forall tmdkc
 	\end{alignat}
@@
 \subsection{Transition}
+
+In this section we will have the following:
+\begin{itemize}
+	\item $p\_ued$ will represent the random variable from $p\_ued$ distribution 
+	\item $pea$ will represent the random variable from $pea$ distribution. 
+	\item $pwt$ and $pst$, will represent number transitioned in complexity/priority on waitlist and currently scheduled list.
+\end{itemize}
 
@@
 	\begin{alignat}{10}
-		& pw'_{0dc} 
-		&& = pea_{dc} \quad
+		& pw'_{0dkc} 
+			&& = pea_{dkc} \quad
 			&& \forall dc \\  
-		& pw'_{mdc} 
-		&& = \hat{pw}_{m-1,dc}
-		&& \forall m \in \{ 1...(TL_{dc}-1) \} dc \\  
-		& pw'_{mdc} 
-		&& = \hat{pw}_{m-1,dc} + 
-		\overbrace{pwt_{m-1,d-1,c} - pwt_{m-1,dc}}^\text{
-			change in complexities} \quad
-		&& \forall m \in \{ TL_{dc}...M-1 \} dc \\  
+		& pw'_{mdkc} 
+			&& = \hat{pw}_{m-1,dkc}
+			&& \forall m \in \{ 1...(TL_{c}-1) \} dkc \\  
+		& pw'_{mdkc} 
+			&& = \hat{pw}_{m-1,dkc} + 
+				\overbrace{pwt\_d_{m-1,d-1,c} - pwt\_d_{d}}^\text{
+				change in complexities} +  
+				\overbrace{pwt\_k_{k-1} - pwt\_k_{k}}^\text{
+				change in priorities}\quad 
+			&& \forall m \in \{ TL_{c}...M-1 \} dkc \\  
 		& pw'_{Mdc} 
@@
 				\hat{pw}_{mdc} + 
-		\overbrace{pwt_{md-1,c} - pwt_{mdc}}^\text{
-			change in complexities} \big) \quad
+				\overbrace{pwt\_d_{md-1,c} - pwt\_d_{d}}^\text{
+				change in complexities} +  
+				\overbrace{pwt\_k_{k-1} - pwt\_k_{k}}^\text{
+				change in priorities} \big) \quad
 			&& \forall dc
@@
 	\begin{alignat}{10}
-		& ps'_{t0dc} 
+		& ps'_{t0dkc} 
 			&& = 0 \quad
-		&& \forall tdc \\  
-		& ps'_{Tmdc} 
+			&& \forall tdkc \\  
+		& ps'_{Tmdkc} 
 			&& = 0 \quad
-		&& \forall mdc \\  
-		& ps'_{tmdc} 
-		&& = \hat{ps}_{t+1,m-1,dc} \quad 
-		&& \forall t \in \{1...T-1\} m \in \{ 1... (TL_{dc}-1) \} dc \\ 
-		& ps'_{tmdc} 
-		&& = \hat{ps}_{t+1,m-1,dc} + 
-		\overbrace{pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc}}^\text{
-			change in complexities} \quad
-		&& \forall t \in \{1...T-1\} m \in \{ TL_{dc}...M-1 \} dc \\  
-		& ps'_{tMdc} 
+			&& \forall mdkc \\  
+		& ps'_{tmdkc} 
+			&& = \hat{ps}_{t+1,m-1,dkc} \quad 
+			&& \forall t \ne T m \in \{ 1... TL-1 \} dkc \\ 
+		& ps'_{tmdkc} 
+			&& = \hat{ps}_{t+1,m-1,dkc} + 
+			\overbrace{pst\_d_{t+1,m-1,d-1,c} - pst\_d_{d}}^\text{
+				change in complexities}  + 
+			\overbrace{pst\_k_{k-1} - pst\_k_{k}}^\text{
+				change in priorities} \quad 
+			&& \forall t \ne T m \in \{ TL_{c}...M-1 \} dkc \\  
+		& ps'_{tMdkc} 
 			&& = \sum_{M-1}^{M} \big( 
 			\hat{ps}_{t+1mdc} + 
-		\overbrace{pst_{t+1,md-1,c} - pst_{t+1,mdc}}^\text{
-			change in complexities} \big) \quad
-		&& \forall t \in \{1...T-1\} dc
+			\overbrace{pst\_d_{t+1,md-1,c} - pst\_d_{d}}^\text{
+				change in complexities} + 
+			\overbrace{pst\_k_{k-1} - pst\_k_{k}}^\text{
+				change in priorities} \big) \quad
+			&& \forall t \ne T dkc
 	\end{alignat}
@@
 \subsection{Costs}
+
+\begin{itemize}
+	\item $cs_{tk} = \sum_t (\alpha^t * cw_{k})$
+\end{itemize}
+
 \begin{equation}\begin{alignedat}{10}
@@
 		&& 
-		\overbrace{ \sum_{mdc} cw (\hat{pw}_{mdc}) }^\text{
+		\overbrace{ \sum_{mdc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
 			cost of waiting}  + 
 		\overbrace{
-			\sum_{tmdc} cs_{t} (sc_{tmdc})
+			\sum_{tmdc} cs_{tk} (sc_{tmdkc})
 		}^\text{Prefer earlier appointments} \\ 
@@
 				\substack{tt`mdc \\ t' > t}} 
-			(cs_{t'-t} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
+			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
 		\overbrace{ 
@@
 				\substack{tt`mdc \\ t' < t}}
-			(cs_{t-t'} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
+			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
 		M \sum_{tp} uv_{tp}

### 2021-08-25 v2-Manuscript/sections/adp_model.tex
working on adding a priority index

@@
 	&	
-		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
-		\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + \\
-		&	&& \qquad  + E[pwt\_k_{k-1k}] - E[pwt\_k_{k}] )  \Big) \ge E[pw_{Mdc}]
+		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdkc} - \gamma 
+		\sum_{M-1}^{M} (\hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + \\
+		&	&& \qquad  + E[pwt\_k_{k-1k}] - E[pwt\_k_{k}] )  \Big) \ge E[pw_{Mdkc}]
 		&&	\forall dkc \\ 
@@
 \begin{enumerate}
-	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ue], E[uu], E[pw] E[pw]$
+	\item Perform a monte-carlo simulation (following some arbitrary policy) to get $E[ul], E[pw] E[pw]$
 	\item Create an initial feasible set of state-action pairs - $\vec{w}$

### 2021-08-25 v2-Implementation/Modules/data_classes.py

@@ -3,30 +3,31 @@ from typing import Dict, Tuple, List, Callable
 import gurobipy as gp
 
 # Data Import Classes
-@dataclass(frozen=True)
+@dataclass()
 class ppe_data_class:
     ppe_type: str
     expected_units: int
     deviation: List[int]
 
-@dataclass(frozen=False)
+@dataclass()
 class model_param_class:
     cw: Dict[ str, float ]
     cc: Dict[ str, float ]
     cs: Dict[ str, List[float] ]
     M: float
     gamma: float
-@dataclass(frozen=False)
+@dataclass()
 class transition_data_class:
-    wait_limit: int
-    transition_rate: float
+    wait_limit: Dict[ Tuple[str], float ]
+    transition_rate_comp: Dict[ Tuple[str], float ]
+    transition_rate_pri: Dict[ Tuple[str], float ]
 @dataclass()
 class input_data_class:
     indices: Dict[ str, List[int] ]
     ppe_data: Dict[ str,ppe_data_class ]
     usage: Dict[ Tuple[str], List[int] ]
     arrival: Dict[ Tuple[str], List[int] ]
-    transition: Dict[ Tuple[str], transition_data_class ]
+    transition: transition_data_class
     model_param: model_param_class
     expected_state_values: Dict[ str, Dict[Tuple[str], float] ]
 
@@ -36,20 +37,20 @@ class input_data_class:
 @dataclass(frozen=True)
 class state:
     ul_p: Dict[ Tuple[str],float ] # units left over on time 1, ppe p
-    pw_mdc: Dict[ Tuple[str],float ] # patients waiting for m periods, of complexity d, cpu c
-    ps_tmdc: Dict[ Tuple[str],float ] # patients scheduled into time t, who have waited for m periods, of complexity d, cpu c
+    pw_mdkc: Dict[ Tuple[str],float ] # patients waiting for m periods, of complexity d, cpu c
+    ps_tmdkc: Dict[ Tuple[str],float ] # patients scheduled into time t, who have waited for m periods, of complexity d, cpu c
 @dataclass(frozen=True)
 class action:
-    sc_tmdc: Dict[ Tuple[str],float ] # patients of complexity d, cpu c, waiting for m periods to schedule into t (m of 0 corresponds to pe)
-    rsc_ttpmdc: Dict[ Tuple[str],float ] # patients of complexity d, cpu c, waiting for m periods, to reschedule from t to tp 
[…]

### 2021-08-25 v2-Implementation/Modules/sub_problem.py

@@ -1,11 +1,255 @@
 from dataclasses import dataclass
 from typing import Dict, Tuple, List, Callable
-from Modules.data_classes import state, action, variables
+from Modules.data_classes import input_data_class, state, action, variables
 
 import itertools
 import numpy as np
 import gurobipy as gp
 from gurobipy import GRB
+
+
+    # Objective Function
+    # Cost Function
+def wait_cost(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
+    # Initialization
+    indices = input_data.indices
+    model_param = input_data.model_param
+    expr = gp.LinExpr()
+
+    # Cost of Waiting
+    for mdkc in itertools.product(indices['m'], indices['d'], indices['k'], indices['c']):  
+        expr.addTerms(model_param.cw[mdkc[2]], var.a_pw_p[mdkc])                     
+
+    return expr
+def pref_earlier_appointment(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
+    # Initialization
+    indices = input_data.indices
+    model_param = input_data.model_param
+    expr = gp.LinExpr()
+    
+    # Prefer Earlier Appointments
+    for tmdkc in itertools.product(indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        expr.addTerms(model_param.cs[tmdkc[3]][tmdkc[0]], var.a_sc[tmdkc])
+
+    return expr
+def reschedule_cost(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
+    # Initialization
+    indices = input_data.indices
+    model_param = input_data.model_param
+    expr = gp.LinExpr()
+
+    # Cost of Rescheduling                
+    for ttpmdkc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        if ttpmdkc[0] > ttpmdkc[1]: # Good Reschedule
+            difference = ttpmdkc[0] - ttpmdkc[1]
+            expr.addTerms(-(model_param.cs[ttpmdkc[4]][difference] - model_param.cc[ttpmdkc[4]]), var.a_rsc[ttpmdkc])
+        elif ttpmdkc[0] < ttpmdkc[1]: # Bad Reschedule
+            difference = ttpmdkc[1] - ttpmdkc[0]
[…]

### 2021-11-07 New-Manuscript/sections/adp_model.tex
completed simulation

--- 2021-08-25 v2-Manuscript/sections/adp_model.tex
@@
 					\Big( pw_{mdkc} - \gamma 
-					(\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - + E[pwt\_k_{k}]) \Big) + \\
+					(\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big) + \\
 			& 
@@
 		&& 	\beta^0 + 
-		\bigg( \sum_{p} \beta_{1p}^{ue} 
-		(uen_{d} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
-		\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\
-		&	&& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
-		( \hat{uu}_{t+1,p} + \sum_{mdc} E[pst_{tmdc}] (U_{pd+1c} - U_{pdc})) \bigg) + \\
-		&	&&	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
-		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
-		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \bigg) + \\
-		&	&&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
-		(\sum_{M-1}^{M} \hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}])\bigg) + \\
-		& 	&&	\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
-		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \bigg) + \\	
-		&	&&	\qquad \qquad \bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
-		(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}])) \bigg)
+		\bigg( \sum_{p \in p\_co} \beta_{p}^{ul} (\hat{ul_{p}}) \bigg) +
+			\bigg( \sum_{dc} \beta_{0dkc}^{pw} pea_{dkc} \bigg) +
+			\bigg( \sum_{m=1,dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
+				(\hat{pw}_{m-1dkc} \bigg) + \\
+		&	&&	\qquad \qquad \bigg( \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
+		(	\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] 
+			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
+		&	&&	\qquad \qquad \bigg( \sum_{dkc} \beta_{Mdkc}^{pw} 
+		\sum_{M-1}^{M} ( \hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] 
+			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
+		& 	&&	\bigg( \sum_{t=1m=1dkc}^{T-1, TL_{c}-1} \beta_{tmdkc}^{ps} 
+				(\hat{ps}_{t+1m-1dkc}) \bigg) + \\
+		&	&&	\qquad \bigg( \sum_{t=1m=TL_{c}dkc}^{T-1M-1} \beta_{tmdkc}^{ps} 
+				(\hat{ps}_{t+1m-1dkc} + E[pst\_d_{t+1m-1d-1c}] - 
+				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg)  + \\
+		&	&&	\qquad \bigg( \sum_{t=1dkc}^{T-1} \beta_{tmdkc}^{ps} \sum_{M-1}^{M}
+				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - 
+				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg) 
 		\Bigg)

### 2021-11-07 New-Manuscript/sections/mdp_model.tex
completed simulation

--- 2021-08-16 v2-Manuscript/sections/mdp_model.tex
@@
 \subsubsection{Description}
-State is defined by carried over resources, deviation from expected resources,, patient waitlist/demand, and patients already scheduled
+State is defined by carried over resources, deviation from expected resources, patient waitlist/demand, and patients already scheduled
 \[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
@@
 	\item $\vec{pw} = pw_{mdkc}$ - Patients of complexity $d$, priority $k$, surgery type $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
-	\item $\vec{ps} = ps_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
+	\item $\vec{ps} = ps_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, scheduled to period $t$, waiting for $m$ periods
 \end{itemize}
@@
 \subsubsection{Description}
-Decision consists of rescheduling currently scheduled patients, and scheduling patients on waitlist. There are also some goal and auxiliary variables
-\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}, \text{auxiliary variables}) \] 
+Actions consist of rescheduling currently scheduled patients, and scheduling patients on wait list. There are also some goal and auxiliary variables
+\[  \vec{A} = (\vec{sc}, \vec{rsc}, \text{auxiliary variables}) \] 
 \begin{itemize}
-	\item $\vec{sc} = sc_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, waiting for $m$ periods, to schedule in period $t$
-	\item $\vec{rsc} = rsc_{tt'mdkc}$ -Patients of complexity $d$, priority $k$, surgery type $c$, waiting for $m$ periods, to reschedule from $t$ to $t'$
+	\item $\vec{sc} = sc_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, waiting for $m$, to schedule in period $t$
+	\item $\vec{rsc} = rsc_{tt'mdkc}$ -Patients of complexity $d$, priority $k$, surgery type $c$, waiting for $m$, reschedule from $t$ to $t'$
 \end{itemize}
@@
 		&& 
-		\overbrace{ \sum_{mdc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
+		\overbrace{ \sum_{mdkc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
 			cost of waiting}  + 
 		\overbrace{
-			\sum_{tmdc} cs_{tk} (sc_{tmdkc})
+			\sum_{tmdkc} cs_{tk} (sc_{tmdkc})
 		}^\text{Prefer earlier appointments} \\ 
@@
 			\sum_{
-				\substack{tt`mdc \\ t' > t}} 
+				\substack{tt`mdkc \\ t' > t}} 
 			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
@@
 			\sum_{
-				\substack{tt`mdc \\ t' < t}}
+				\substack{tt`mdkc \\ t' < t}}
 			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 

### 2021-11-07 New-Implementation/Modules/data_import.py

@@ -1,0 +1,172 @@
+# Imports packages
+import openpyxl
+from typing import Dict, Tuple, List, Callable
+from dataclasses import dataclass
+
+from Modules.data_classes import ppe_data_class, model_param_class, transition_data_class, input_data_class
+
+# Reads All input data from excel
+def read_data(data_file_path):
+
+    #Opens the excel book
+    book = openpyxl.load_workbook(data_file_path, data_only=True)
+
+
+    # Generates Indices
+    indices_sheet = book.get_sheet_by_name('Indices Data')
+
+    # Generates T
+    t = []
+    for t_row in indices_sheet.iter_rows(min_row=2, min_col=1, max_col=1, values_only=True):
+        if t_row[0] == None: break
+        t.append(t_row[0])
+    # Generates M
+    m = []
+    for m_row in indices_sheet.iter_rows(min_row=2, min_col=2, max_col=2, values_only=True):
+        if m_row[0] == None: break
+        m.append(m_row[0])
+    # Generates P
+    p = []
+    for ppe_row in indices_sheet.iter_rows(min_row=2, min_col=3, max_col=3, values_only=True):
+        if ppe_row[0] == None: break
+        p.append(ppe_row[0])
+    # Generates D
+    d = []
+    for comp_row in indices_sheet.iter_rows(min_row=2, min_col=4, max_col=4, values_only=True):
+        if comp_row[0] == None: break
+        d.append(comp_row[0])
+    # Generates K
+    k = []
+    for prio_row in indices_sheet.iter_rows(min_row=2, min_col=5, max_col=5, values_only=True):
+        if prio_row[0] == None: break
+        k.append(prio_row[0])
+    # Generates C
+    c = []
+    for cpu_row in indices_sheet.iter_rows(min_row=2, min_col=6, max_col=6, values_only=True):
+        if cpu_row[0] == None: break
+        c.append(cpu_row[0])
+
+    # Saves Indices
+    indices = {'t': t, 'm': m, 'p': p, 'd': d, 'k': k, 'c': c }
+    
+
+    # PPE Data
+    ppe_data_sheet = book.get_sheet_by_name('PPE Data')
+
+    ppe_data = {}
+    for ppe_row in ppe_data_sheet.iter_rows(min_row=2, min_col=1, max_col=4, values_only=True):
+        if ppe_row[0] == None: break
+        ppe_type = ""
+        if ppe_row[1] == True: ppe_type = "carry-over"
[…]

### 2021-11-07 New-Implementation/Modules/simulation.py

@@ -1,0 +1,996 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import state, action, variables
+
+from multiprocessing import Pool
+from tqdm import tqdm, trange
+from copy import deepcopy
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+# Initializes State ( Everything Empty )
+def initial_state(input_data) -> state:
+    # Input Data
+    indices = input_data.indices
+    arrival = input_data.arrival
+    ppe_data = input_data.ppe_data
+
+    # Patient States
+    pw = {}
+    for mdkc in itertools.product(indices['m'],indices['d'], indices['k'], indices['c']):
+        if mdkc[0] == 0:
+            pw[mdkc] = round(arrival[(mdkc[1], mdkc[2], mdkc[3])]) 
+        else:
+            pw[mdkc] = 0
+    ps = {}
+    for tmdkc in itertools.product(indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        ps[tmdkc] = 0
+
+    # Unit States
+    ul = {}
+    for p in itertools.product(indices['p']):
+        ul[p] = 0
+
+    init_state = state(ul, pw, ps)
+
+    return init_state
+# Initializes Action ( Everything Empty )
+def initial_action(input_data) -> action:
+    indices = input_data.indices
+
+    # Action
+    sc = {}
+    for tmdkc in itertools.product(indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        sc[tmdkc] = 0
+    rsc = {}
+    for ttpmdkc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        rsc[ttpmdkc] = 0
+    
+    # Violation
+    uv = {}
+    uvb = {}
+    for tp in itertools.product(indices['t'], indices['p']):
+        uv[tp] = 0
+        uvb[tp] = 0
+
+    # Units left over 
+    ul_p = {}
+    ulb = {}
+    for p in itertools.product(indices['p']):
+        ul_p[p] = 0
+        ulb[p] = 0
+
+    # Auxiliary variables
+    uu_p = {}
+    for tp in itertools.product(indices['t'], indices['p']):
[…]

### 2021-11-07 New-Implementation/Modules/sub_problem.py

@@ -1,0 +1,517 @@
+from dataclasses import dataclass
+from typing import Dict, Tuple, List, Callable
+from Modules.data_classes import input_data_class, state, action, variables
+
+import itertools
+import numpy as np
+import gurobipy as gp
+from gurobipy import GRB
+
+
+    # Objective Function
+    # Cost Function
+def wait_cost(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
+    # Initialization
+    indices = input_data.indices
+    model_param = input_data.model_param
+    expr = gp.LinExpr()
+
+    # Cost of Waiting
+    for mdkc in itertools.product(indices['m'], indices['d'], indices['k'], indices['c']):  
+        expr.addTerms(model_param.cw[mdkc[2]], var.a_pw_p[mdkc])                     
+
+    return expr
+def pref_earlier_appointment(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
+    # Initialization
+    indices = input_data.indices
+    model_param = input_data.model_param
+    expr = gp.LinExpr()
+    
+    # Prefer Earlier Appointments
+    for tmdkc in itertools.product(indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        expr.addTerms(model_param.cs[tmdkc[3]][tmdkc[0]], var.a_sc[tmdkc])
+
+    return expr
+def reschedule_cost(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
+    # Initialization
+    indices = input_data.indices
+    model_param = input_data.model_param
+    expr = gp.LinExpr()
+
+    # Cost of Rescheduling                
+    for ttpmdkc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
+        if ttpmdkc[0] > ttpmdkc[1]: # Good Reschedule
+            difference = ttpmdkc[0] - ttpmdkc[1]
+            expr.addTerms(-(model_param.cs[ttpmdkc[4]][difference] - model_param.cc[ttpmdkc[4]]), var.a_rsc[ttpmdkc])
+        elif ttpmdkc[0] < ttpmdkc[1]: # Bad Reschedule
+            difference = ttpmdkc[1] - ttpmdkc[0]
[…]

### 2021-11-07 New-Implementation/optimization.py

@@ -1,0 +1,266 @@
+# Packages
+from Modules.data_import import *
+from Modules.data_export import *
+from Modules import master_model
+from Modules import sub_problem
+import itertools
+import gurobipy as gp
+import os.path
+import numpy as np
+from Modules.decorators import timer
+
+# gp.Model.write = timer(gp.Model.write)
+
+# Generate Initial Feasible Set (Phase 1)
+def p1_algo(input_data, init_state_actions):
+    
+    # Initializes
+    state_action_list = init_state_actions
+    count = len(state_action_list)-1
+    mast_model, mast_var, mast_const = master_model.master_p2(input_data, state_action_list)
+
+    # Initialize Sub model
+    p1_mast_model, p1_mast_const = master_model.master_p1(input_data, mast_model)
+    p1_mast_model.Params.LogToConsole = 0
+    p1_mast_model.optimize()
+
+    betas = master_model.get_betas(input_data, p1_mast_const)
+    p1_sub_model, p1_sub_var = sub_problem.subproblem(input_data, betas, True)
+    
+    # Algorithm
+    while True:
+    
+        # Generates and Solves Master
+        p1_mast_model, p1_mast_const = master_model.master_p1(input_data, mast_model)
+        p1_mast_model.Params.LogToConsole = 0
+        p1_mast_model.write('p1_m.lp')
+        p1_mast_model.optimize()
+        # p1_mast_model.write('m_p1.lp')
+        betas = master_model.get_betas(input_data, p1_mast_const)
+            
+        # Debugging
+        print(f'Phase 1 - iteration {count+1}, Mast Objective {p1_mast_model.getObjective().getValue()}')
+        count += 1
+
+        # Stops if successful
+        if p1_mast_model.getObjective().getValue() <= 0.00000000001:
+            p1_mast_model.optimize()
+            betas = master_model.get_betas(input_data, p1_mast_const)
+            print('Found Feasible Set')
+            break
+
+        # Trims
+        if (count%100) == 0:
+            state_action_list, p1_mast_model, p1_mast_const = trim_sa_list_p1(input_data, state_action_list, p1_mast_model)
+        
+        # Generates and solves Subproblem 
+        p1_sub_model, p1_sub_var = sub_problem.update_sub(input_data, p1_sub_model, p1_sub_var, betas, True)
+        p1_sub_model.Params.LogToConsole = 0
+        p1_sub_model.write('p1_s.lp')
[…]

### 2021-11-07 v2-Implementation/Modules/data_import.py

@@ -1,172 +1,0 @@
-# Imports packages
-import openpyxl
-from typing import Dict, Tuple, List, Callable
-from dataclasses import dataclass
-
-from Modules.data_classes import ppe_data_class, model_param_class, transition_data_class, input_data_class
-
-# Reads All input data from excel
-def read_data(data_file_path):
-
-    #Opens the excel book
-    book = openpyxl.load_workbook(data_file_path, data_only=True)
-
-
-    # Generates Indices
-    indices_sheet = book.get_sheet_by_name('Indices Data')
-
-    # Generates T
-    t = []
-    for t_row in indices_sheet.iter_rows(min_row=2, min_col=1, max_col=1, values_only=True):
-        if t_row[0] == None: break
-        t.append(t_row[0])
-    # Generates M
-    m = []
-    for m_row in indices_sheet.iter_rows(min_row=2, min_col=2, max_col=2, values_only=True):
-        if m_row[0] == None: break
-        m.append(m_row[0])
-    # Generates P
-    p = []
-    for ppe_row in indices_sheet.iter_rows(min_row=2, min_col=3, max_col=3, values_only=True):
-        if ppe_row[0] == None: break
-        p.append(ppe_row[0])
-    # Generates D
-    d = []
-    for comp_row in indices_sheet.iter_rows(min_row=2, min_col=4, max_col=4, values_only=True):
-        if comp_row[0] == None: break
-        d.append(comp_row[0])
-    # Generates K
-    k = []
-    for prio_row in indices_sheet.iter_rows(min_row=2, min_col=5, max_col=5, values_only=True):
-        if prio_row[0] == None: break
-        k.append(prio_row[0])
-    # Generates C
-    c = []
-    for cpu_row in indices_sheet.iter_rows(min_row=2, min_col=6, max_col=6, values_only=True):
-        if cpu_row[0] == None: break
-        c.append(cpu_row[0])
-
-    # Saves Indices
-    indices = {'t': t, 'm': m, 'p': p, 'd': d, 'k': k, 'c': c }
-    
-
-    # PPE Data
-    ppe_data_sheet = book.get_sheet_by_name('PPE Data')
-
-    ppe_data = {}
-    for ppe_row in ppe_data_sheet.iter_rows(min_row=2, min_col=1, max_col=4, values_only=True):
-        if ppe_row[0] == None: break
-        ppe_type = ""
-        if ppe_row[1] == True: ppe_type = "carry-over"
[…]

### 2021-11-07 v2-Implementation/Modules/simulation.py

@@ -1,926 +1,0 @@
-from dataclasses import dataclass
-from typing import Dict, Tuple, List, Callable
-from Modules.data_classes import state, action, variables
-
-from multiprocessing import Pool
-from tqdm import tqdm, trange
-from copy import deepcopy
-import itertools
-import numpy as np
-import gurobipy as gp
-from gurobipy import GRB
-
-# Initializes State ( Everything Empty )
-def initial_state(input_data) -> state:
-    # Input Data
-    indices = input_data.indices
-    arrival = input_data.arrival
-    ppe_data = input_data.ppe_data
-
-    # Patient States
-    pw = {}
-    for mdc in itertools.product(indices['m'],indices['d'], indices['c']):
-        if mdc[0] == 0:
-            pw[mdc] = arrival[(mdc[1], mdc[2])] 
-        else:
-            pw[mdc] = 0
-    ps = {}
-    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
-        ps[tmdc] = 0
-
-    # Unit States
-    ul = {}
-    for p in itertools.product(indices['p']):
-        ul[p] = 0
-
-    init_state = state(ul, pw, ps)
-
-    return init_state
-# Initializes Action ( Everything Empty )
-def initial_action(input_data) -> action:
-    indices = input_data.indices
-
-    # Action
-    sc = {}
-    for tmdc in itertools.product(indices['t'], indices['m'], indices['d'], indices['c']):
-        sc[tmdc] = 0
-    rsc = {}
-    for ttpmdc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['c']):
-        rsc[ttpmdc] = 0
-    
-    # Violation
-    uv = {}
-    uvb = {}
-    for tp in itertools.product(indices['t'], indices['p']):
-        uv[tp] = 0
-        uvb[tp] = 0
-
-    # Units left over 
-    ul_p = {}
-    ulb = {}
-    for p in itertools.product(indices['p']):
-        ul_p[p] = 0
-        ulb[p] = 0
-
-    # Auxiliary variables
-    uu_p = {}
-    for tp in itertools.product(indices['t'], indices['p']):
-        uu_p[tp] = 0
-    pw_p = {}
[…]

### 2021-11-07 v2-Implementation/Modules/sub_problem.py

@@ -1,519 +1,0 @@
-from dataclasses import dataclass
-from typing import Dict, Tuple, List, Callable
-from Modules.data_classes import input_data_class, state, action, variables
-
-import itertools
-import numpy as np
-import gurobipy as gp
-from gurobipy import GRB
-
-
-    # Objective Function
-    # Cost Function
-def wait_cost(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
-    # Initialization
-    indices = input_data.indices
-    model_param = input_data.model_param
-    expr = gp.LinExpr()
-
-    # Cost of Waiting
-    for mdkc in itertools.product(indices['m'], indices['d'], indices['k'], indices['c']):  
-        expr.addTerms(model_param.cw[mdkc[2]], var.a_pw_p[mdkc])                     
-
-    return expr
-def pref_earlier_appointment(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
-    # Initialization
-    indices = input_data.indices
-    model_param = input_data.model_param
-    expr = gp.LinExpr()
-    
-    # Prefer Earlier Appointments
-    for tmdkc in itertools.product(indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
-        expr.addTerms(model_param.cs[tmdkc[3]][tmdkc[0]], var.a_sc[tmdkc])
-
-    return expr
-def reschedule_cost(input_data:input_data_class, var: variables, betas) -> gp.LinExpr:
-    # Initialization
-    indices = input_data.indices
-    model_param = input_data.model_param
-    expr = gp.LinExpr()
-
-    # Cost of Rescheduling                
-    for ttpmdkc in itertools.product(indices['t'], indices['t'], indices['m'], indices['d'], indices['k'], indices['c']):
-        if ttpmdkc[0] > ttpmdkc[1]: # Good Reschedule
-            difference = ttpmdkc[0] - ttpmdkc[1]
-            expr.addTerms(-(model_param.cs[ttpmdkc[4]][difference] - model_param.cc[ttpmdkc[4]]), var.a_rsc[ttpmdkc])
-        elif ttpmdkc[0] < ttpmdkc[1]: # Bad Reschedule
-            difference = ttpmdkc[1] - ttpmdkc[0]
-            expr.addTerms((model_param.cs[ttpmdkc[4]][difference] - model_param.cc[ttpmdkc[4]]), var.a_rsc[ttpmdkc])
-
[…]

### 2021-12-10 New-Manuscript/sections/mdp_model.tex
working on gurobi like implementation

@@
 	\item $\hat{ps}_{tmdkc}$ - post-decision patients scheduled
+	\item $pwt\_d_{mdkc}$ - patients waiting transitioned in complexity
+	\item $pwt\_k_{mdkc}$ - patients waiting transitioned in priority
+	\item $pst\_d_{tmdkc}$ - patients scheduled transitioned in complexity
+	\item $pst\_k_{tmdkc}$ - patients scheduled transitioned in priority
 \end{itemize}
@@
 		\sum_{t} rsc_{tt'mdkc} - \sum_{t'} rsc_{tt'mdkc} \quad 
+		&& \forall tmdkc \\
+	& pwt\_d_{mdkc} 
+		&& = ptp\_{dc} * \hat{pw}_{mdkc} \quad
+		&& \forall mdkc \\
+	& pwt\_k_{mdkc} 
+		&& = ptp\_{kc} * \hat{pw}_{mdkc} \quad
+		&& \forall mdkc \\
+	& pst\_d_{tmdkc} 
+		&& = ptp\_{dc} * \hat{ps}_{tmdkc} \quad
+		&& \forall tmdkc \\
+	& pst\_k_{tmdkc} 
+		&& = ptp\_{kc} * \hat{ps}_{tmdkc} \quad
 		&& \forall tmdkc
@@
 	\begin{alignat}{10}
-		& \hat{uv}_{tp} 
+		& uv_{tp} 
+			&& = max\{0 , \hat{uu}_{1p} - p\_{ue}_{1p} - ul_{p}\} \quad 
+			&& \forall p \\ 
+		& uv_{tp} 
+			&& = max\{0 , \hat{uu}_{tp} - p\_{ue}_{tp}\} \quad
+			&& \forall t \in \{2..T\} p \\ \\
+		& uv_{tp} 
+			&&\ge 0 \quad
+			&& \forall tp \\
+		& uv_{tp} 
 			&& \le  M(uvb_{tp}) \quad
 			&& \forall tp \\
-		& \hat{uv}_{1p} 
+		& uv_{1p} 
+			&&\ge \hat{uu}_{1p} - p\_ue_{1p} - ul_{p} \quad
+			&& \forall p \\
+		& uv_{1p} 
 		&& \le  (\hat{uu}_{1p} - p\_ue_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
 		&& \forall p \\
-		& \hat{uv}_{tp} 
+		& uv_{tp} 
+			&&\ge \hat{uu}_{tp} - p\_ue_{tp} \quad
+			&& \forall t \in \{2..T \} p \\
+		& uv_{tp} 
 		&& \le  (\hat{uu}_{tp} - p\_ue_{tp}) + M(1-uvb_{tp}) \quad
@@
 		& \hat{ul}_{p} 
+			&& = max \{0, p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \}
+			&& \forall p \in \{p_co\} \\ \\
+		& \hat{ul}_{p} 
 			&& \ge 0 \quad 
@@
 		& \hat{ul}_{p} 
-		&& \ge p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
+			&& \le M (ulb_{p}) \quad 
 			&& \forall p  \in p\_co\\
 		& \hat{ul}_{p} 
-		&& \le M (ulb_{p}) \quad 
+			&& \ge p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
 			&& \forall p  \in p\_co\\
@@
 			&& \le p\_ue_{1p} + ul_{p} + uv_{1p} \quad 
-			&& \forall p \in p\_co \\
-		& \hat{uu}_{1p} 
-			&& \le p\_ue_{1p} + uv_{1p} \quad 
-			&& \forall p \in p\_nco \\
+			&& \forall p \\
 		& \hat{uu}_{tp} 

### 2021-12-10 New-Implementation/Modules/data_import.py

@@ -111,7 +111,7 @@ def read_data(data_file_path):
         cc[row[0]] = row[2]
         cs[row[0]] = [0]
     
-    M = model_param_sheet['D2'].value
+    cv = model_param_sheet['D2'].value
     gamma = model_param_sheet['E2'].value
 
     # Cost of Scheduling
@@ -119,7 +119,7 @@ def read_data(data_file_path):
         for time in t:
             cs[prior].append(cs[prior][-1] + cw[prior] * (gamma**time) )
     
-    model_param = model_param_class(cw, cc, cs, M, gamma)
+    model_param = model_param_class(cw, cc, cs, cv, gamma)
 
     # Expected Data
     expected_vals_sheet = book.get_sheet_by_name('Expected State Values')
@@ -127,7 +127,7 @@ def read_data(data_file_path):
     expected_vals['ul'] = {}
     for row in expected_vals_sheet.iter_rows(min_row=3, min_col=1, max_col=2, values_only=True):
         if row[0] == None: break
-        expected_vals['ul'][(row[0],)] = row[1]
+        expected_vals['ul'][row[0]] = row[1]
     expected_vals['pw'] = {}
     for row in expected_vals_sheet.iter_rows(min_row=3, min_col=3, max_col=7, values_only=True):
         if row[0] == None: break

### 2021-12-16 New-Implementation/optimization_new.py
phase 1 works phase 2 doesnt

@@ -1,13 +1,15 @@
 #%%
 ##### Initialization #####
-from typing import MutableMapping
-from Modules import master_model, data_import
+#region
+from Modules import data_import
 
 from gurobipy import *
-import pandas as pd
+import itertools
 import os.path
+#endregion
 
 ##### Read Data #####
+#region
 my_path = os.getcwd()
 input_data = data_import.read_data(os.path.join(my_path, 'Data', 'simple-data.xlsx'))
 
@@ -20,6 +22,10 @@ pea = input_data.arrival
 gam = input_data.model_param.gamma
 ptp_d = input_data.transition.transition_rate_comp
 ptp_k = input_data.transition.transition_rate_pri
+cw = input_data.model_param.cw
+cs = input_data.model_param.cs
+cc = input_data.model_param.cc
+cv = input_data.model_param.cv
 
 ##### Generating Sets #####
 T = input_data.indices['t']
@@ -45,12 +51,13 @@ tTLMdkc = [(t, m, d, k, c) for t in T[:-1] for c in C for m in M[input_data.tran
 E_UL = input_data.expected_state_values['ul']
 E_PW = input_data.expected_state_values['pw']
 E_PS = input_data.expected_state_values['ps']
-
-
+#endregion
 
 #%%
 ##### Master Phase 1 #####
+#region
 master = Model("Master problem")
+master.params.LogToConsole = 0
 
 # Goal Variables
 ma_var_b0 = master.addVar(vtype = GRB.CONTINUOUS, lb=0, name='var_beta_0')
@@ -102,13 +109,13 @@ ma_obj_bps_M = quicksum(ma_var_bps_M[t, M[-1], d, k, c] for t in T[:-1] for d in
 ma_obj_bps_T = quicksum(ma_var_bps_T[T[-1], m, d, k, c] for m in M for d in D for k in K for c in C)
 
[…]

### 2022-01-14 New-Manuscript/sections/mdp_model.tex
phase 1 works phase 2 doesnt
modifications

@@
 	& pwt\_k_{mdkc} 
-		&& = ptp\_{kc} * \hat{pw}_{mdkc} \quad
+		&& = ptp\_{kc} * ( \hat{pw}_{mdkc} + pwt\_d_{md-1kc} - pwt\_d_{mdkc} )  \quad
 		&& \forall mdkc \\
@@
 	& pst\_k_{tmdkc} 
-		&& = ptp\_{kc} * \hat{ps}_{tmdkc} \quad
+		&& = ptp\_{kc} * ( \hat{ps}_{tmdkc} + pst\_d_{tmd-1kc} - pst\_d_{tmdkc} )  \quad
 		&& \forall tmdkc
@@
 			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
-		M \sum_{tp} uv_{tp}
+		cv \sum_{tp} uv_{tp}
 \end{alignedat}\end{equation}

### 2022-01-14 New-Implementation/simulation_new.py

@@ -1,18 +1,37 @@
 #%%
-##### Initialization #####
+##### Initialization & Changeable Parameters #####
 #region
 from os import linesep
+
+from numpy.core.fromnumeric import prod
 from Modules import data_import
 
 from gurobipy import *
 import itertools
 import os.path
+import pickle
+from copy import deepcopy
+import numpy as np
+from tqdm.auto import trange
+import plotly.express as px
+from plotly.subplots import make_subplots
+import plotly.graph_objects as go
+
+# Changeable Parameters
+replications = 3
+warm_up = 2000
+duration = 6000
+show_policy = False
+# replications = 1
+# warm_up = 0
+# duration = 100
+# show_policy = True
 #endregion
 
 ##### Read Data #####
 #region
 my_path = os.getcwd()
-input_data = data_import.read_data(os.path.join(my_path, 'Data', 'simple-data.xlsx'))
+input_data = data_import.read_data(os.path.join(my_path, 'Data', 'complex-data.xlsx'))
 
 # Quick Assess to Various Parameters
 TL = input_data.transition.wait_limit
@@ -54,10 +73,68 @@ E_UL = input_data.expected_state_values['ul']
 E_PW = input_data.expected_state_values['pw']
 E_PS = input_data.expected_state_values['ps']
 
+# Initial State
+init_state = {'ul': E_UL, 'pw': E_PW, 'ps': E_PS}
+init_state_strm =  np.random.default_rng(199725)
+for i in itertools.product(M,D,K,C): init_state['pw'][i] = init_state_strm.poisson(E_PW[i])
+for i in itertools.product(T,M,D,K,C): init_state['ps'][i] = init_state_strm.poisson(E_PS[i])
+
 # Betas
+with open(os.path.join(my_path, 'Data', 'complex-optimal.pkl'), 'rb') as handle:
+    betas = pickle.load(handle)
 #endregion
 
-#%%
+##### Various Functions #####
+#region
[…]

### 2022-02-22 New-Manuscript/sections/adp_model.tex
added more "full" scenarios

@@
 
-\begin{equation}\begin{alignedat}{10}
+\begin{equation}
+	\begin{alignedat}{10}
 		&	v(S') = \Bigg( 
@@
 constraints in section "\nameref{state-action constraints}"
+
+\subsection{Representation in terms of actions only}
+
+\begin{equation}
+	\begin{alignedat}{10}
+		& \beta_{ul} && \text{if } ul_{p} >0: && sc_{1mdkc} * \beta_{p}^{ul}  && \forall pmdkc \\
+		& \beta_{pw} \text{ part 1 } && all && - sc_{tm-1dkc} * \beta_{mdkc}^{pw} && \forall tm\in\{1...M-1\}dkc \\
+		& \beta_{pw} \text{ part 1 } && all && - sc_{tM-1dkc} * \beta_{Mdkc}^{pw} && \forall tdkc \\
+		& \beta_{pw} \text{ part 1 } && all && - sc_{tMdkc} * \beta_{Mdkc}^{pw} && \forall tdkc \\
+		& \beta_{pw} \text{ part 2 } && all && - sc_{tm-1d-1kc} * (\beta_{mdkc}^{pw} * ptp\_dc_{d-1c}) && \forall tdkc, m \in \{TL_{c} ... M-1 \} \\
+		& \beta_{pw} \text{ part 2 } && all && - sc_{tM-1d-1kc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{d-1c}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 2 } && all && - sc_{tMd-1kc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
+		& \beta_{pw} \text{ part 3 } && all && sc_{tm-1dkc} * (\beta_{mdkc}^{pw} * ptp\_dc_{dc}) && \forall tdkc, m \in \{TL_{c} ... M-1 \} \\
+		& \beta_{pw} \text{ part 3 } && all && sc_{tM-1dkc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{dc}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 3 } && all && sc_{tMdkc} * (\beta_{Mdkc}^{pw} * ptp\_dc_{dc}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 4 } && all && -sc_{tm-1dk-1c} * (\beta_{mdkc}^{pw} * ptp\_kc_{k-1c}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
+		& \beta_{pw} \text{ part 4 } && all && -sc_{tm-1d-1k-1c} * (\beta_{mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{d-1c}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\ 
+		& \beta_{pw} \text{ part 4 } && all && sc_{tm-1dk-1c} * (\beta_{mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{dc}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
+		& \beta_{pw} \text{ part 4 } && all && -sc_{tM-1dk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 4 } && all && -sc_{tM-1d-1k-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
+		& \beta_{pw} \text{ part 4 } && all && sc_{tM-1dk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{dc}) && \forall tdkc  \\
+		& \beta_{pw} \text{ part 4 } && all && -sc_{tMdk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 4 } && all && -sc_{tMd-1k-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
+		& \beta_{pw} \text{ part 4 } && all && sc_{tMdk-1c} * (\beta_{Mdkc}^{pw} * ptp\_kc_{k-1c} * ptp\_dc_{dc}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 5 } && all && sc_{tm-1dkc} * (\beta_{mdkc}^{pw} * ptp\_kc_{kc}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
+		& \beta_{pw} \text{ part 5 } && all && sc_{tm-1d-1kc} * (\beta_{mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{d-1c}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\ 
+		& \beta_{pw} \text{ part 5 } && all && -sc_{tm-1dkc} * (\beta_{mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{dc}) && \forall tdkc, m \in \{ TL_{c} ... M-1 \} \\
+		& \beta_{pw} \text{ part 5 } && all && sc_{tM-1dkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 5 } && all && sc_{tM-1d-1kc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
+		& \beta_{pw} \text{ part 5 } && all && -sc_{tM-1dkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{dc}) && \forall tdkc  \\
+		& \beta_{pw} \text{ part 5 } && all && sc_{tMdkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc}) && \forall tdkc \\
+		& \beta_{pw} \text{ part 5 } && all && sc_{tMd-1kc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{d-1c}) && \forall tdkc \\ 
+		& \beta_{pw} \text{ part 5 } && all && -sc_{tMdkc} * (\beta_{Mdkc}^{pw} * ptp\_kc_{kc} * ptp\_dc_{dc}) && \forall tdkc \\
+		& \beta_{ps} \text{ part 1 } && all && sc_{t+1m-1dkc} * \beta_{tmdkc}^{ps} && \forall t \in \{1...T-1 \} m \in \{ 1...M-1 \} dkc \\
+		& \beta_{ps} \text{ part 1 } && all && sc_{t+1M-1dkc} * \beta_{tMdkc}^{ps} && \forall t \in \{1...T-1 \} m \in \{ 1...M-1 \} dkc \\
+		& \beta_{ps} \text{ part 1 } && all && sc_{t+1Mdkc} * \beta_{tMdkc}^{ps} && \forall t \in \{1...T-1 \} dkc \\
+		& \beta_{ps} \text{ part 2 } && all && sc_{t+1m-1d-1kc} * (\beta_{tmdkc}^{ps} * ptp\_dc_{d-1c}) && \forall t \in \{1...T-1 \} dkc, m \in \{TL_{c} ... M-1 \} \\
+		& \beta_{ps} \text{ part 2 } && all && sc_{t+1M-1d-1kc} * (\beta_{tMdkc}^{ps} * ptp\_dc_{d-1c}) && \forall t \in \{1...T-1 \} dkc \\
+		& \beta_{ps} \text{ part 2 } && all && sc_{t+1Md-1kc} * (\beta_{tMdkc}^{ps} * ptp\_dc_{d-1c}) && \forall t \in \{1...T-1 \} dkc \\ 
+	\end{alignedat}
+\end{equation}

### 2022-02-22 New-Implementation/job-full-all.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+sbatch job-full1.sh
+sbatch job-full2.sh
+sbatch job-full3.sh
+sbatch job-full4.sh
+sbatch job-full5.sh
+sbatch job-full6.sh
+sbatch job-full7.sh
+sbatch job-full8.sh
+sbatch job-full9.sh
+sbatch job-full10.sh

### 2022-02-22 New-Implementation/main-full1.py

@@ -3,7 +3,7 @@ import simulation_new
 import time
 
 # Test Type
-test_modifier = "cw1-cc5-cv1000-gam95-"
+test_modifier = "cw1-cc5-cv100-gam95-"
 data_type = "full"
 
 # Optimization Paramers
@@ -32,7 +32,7 @@ export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_
 
 # Execute
 start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2)
+optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
 end_time_opt = time.time()
 # simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
 end_time_sim = time.time()

### 2022-02-22 New-Implementation/main-full2.py

@@ -3,7 +3,7 @@ import simulation_new
 import time
 
 # Test Type
-test_modifier = "cw1-cc5-cv1000-gam99-"
+test_modifier = "cw1-cc5-cv100-gam99-"
 data_type = "full"
 
 # Optimization Paramers
@@ -32,7 +32,7 @@ export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_
 
 # Execute
 start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2)
+optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
 end_time_opt = time.time()
 # simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
 end_time_sim = time.time()

### 2022-02-22 New-Implementation/main-full3.py

@@ -3,7 +3,7 @@ import simulation_new
 import time
 
 # Test Type
-test_modifier = "cw1-cc5-cv1000-gam999-"
+test_modifier = "cw1-cc5-cv100-gam999-"
 data_type = "full"
 
 # Optimization Paramers
@@ -32,7 +32,7 @@ export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_
 
 # Execute
 start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2)
+optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
 end_time_opt = time.time()
 # simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
 end_time_sim = time.time()

### 2022-02-22 New-Implementation/main-full5.py

@@ -4,7 +4,7 @@ import simulation_new
 import time
 
 # Test Type
-test_modifier = "exp-zero-cw1-cc5-cv1000-gam95-"
+test_modifier = "exp-zero-cw1-cc5-cv100-gam95-"
 data_type = "full"
 
 # Optimization Paramers
@@ -33,7 +33,7 @@ export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_
 
 # Execute
 start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2)
+optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
 end_time_opt = time.time()
 # simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
 end_time_sim = time.time()

### 2022-02-22 New-Implementation/main-full8.py

@@ -3,7 +3,7 @@ import simulation_new
 import time
 
 # Test Type
-test_modifier = "exp-full-cw1-cc5-cv100-gam95-"
+test_modifier = "cw1-cc5-cv1000-gam999-"
 data_type = "full"
 
 # Optimization Paramers

### 2022-02-22 New-Implementation/simulation_new.py

@@ -248,7 +248,7 @@ def main_func(replications, warm_up, duration, show_policy, import_data, import_
 
     ##### MDP Model #####
     #region
-    MDP = Model('Myopic')
+    MDP = Model('MDP')
     MDP.params.LogToConsole = 0
 
     # State Action & Auxiliary Variables

### 2022-07-16 New-Manuscript/sections/mdp_model.tex
R3

@@
 	\item $pst\_k_{tmdkc}$ - patients scheduled transitioned in priority
+	\item (R3) $uu_{tp}, \quad \forall p \in {\text{Admission}}$ - units underutilized for resource p, time t
+	\item (R3) $uub_{tp}, \quad \forall p \in {\text{Admission}}$ - binary variable to enforce $uu$ without using objective function
 \end{itemize}
@@
 	\begin{alignat}{10}
-		& uv_{tp} 
+		& uv_{1p} 
 			&& = max\{0 , \hat{uu}_{1p} - p\_{ue}_{1p} - ul_{p}\} \quad 
@@
 			&& \forall p  \in p\_co
+	\end{alignat}
+
+	\item(R3) Define Resource Underutilized
+	\begin{alignat}{10}
+		& uu_{1p} 
+			&& = max\{0 , p\_{ue}_{1p} + ul_{p} - \hat{uu}_{1p}\} \quad 
+			&& \forall p \in {\text{Admissions}} \\ 
+		& uu_{tp} 
+			&& = max\{0 , p\_{ue}_{tp} - \hat{uu}_{tp}\} \quad
+			&& \forall t \in \{2..T\} p \in {\text{Admissions}} \\ \\
+		& uu_{tp} 
+			&&\ge 0 \quad
+			&& \forall tp \\
+		& uu_{tp} 
+			&& \le  M(uub_{tp}) \quad
+			&& \forall tp \\
+		& uu_{1p} 
+			&&\ge p\_{ue}_{1p} + ul_{p} - \hat{uu}_{1p} \quad
+			&& \forall p \\
+		& uu_{1p} 
+		&& \le  (p\_{ue}_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-uub_{tp}) \quad
+		&& \forall p \\
+		& uu_{tp} 
+			&&\ge p\_{ue}_{tp} - \hat{uu}_{tp}\ \quad
+			&& \forall t \in \{2..T \} p \\
+		& uu_{tp} 
+		&& \le  (p\_{ue}_{tp} - \hat{uu}_{tp}\ + M(1-uub_{tp}) \quad
+		&& \forall t \in \{ 2..T \} p \\
 	\end{alignat}
@@
 			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
-		cv \sum_{tp} uv_{tp}
+		cv \sum_{tp} uv_{tp} \\ 
+		& && + \overbrace{
+			M (cuu) \sum_{tp} (uu_{tp})}^\text{(R3) Underutilization}
 \end{alignedat}\end{equation}

### 2022-07-16 New-Implementation/optimization_new.py

@@ -32,6 +32,7 @@ def main_func(iter_lims, beta_fun, sub_mip_gap, import_data, export_data, export
     cs = input_data.model_param.cs
     cc = input_data.model_param.cc
     cv = input_data.model_param.cv
+    cuu = 1000
 
     ##### Generating Sets #####
     T = input_data.indices['t']
@@ -147,6 +148,9 @@ def main_func(iter_lims, beta_fun, sub_mip_gap, import_data, export_data, export
     sv_aux_pst_d = sub_prob.addVars(T,M,D,K,C, vtype=GRB.CONTINUOUS, lb = 0, name='var_auxiliary_pst_d')
     sv_aux_pst_k = sub_prob.addVars(T,M,D,K,C, vtype=GRB.CONTINUOUS, lb = 0, name='var_auxiliary_pst_k')
 
+    sv_aux_uu = sub_prob.addVars(T, vtype=GRB.CONTINUOUS, lb=0, name='var_auxiliary_uu')
+    sv_aux_uub = sub_prob.addVars(T, vtype=GRB.BINARY, lb=0, name='var_auxiliary_uub')
+
     # Definition of auxiliary variables
     sc_uup = sub_prob.addConstrs((sv_aux_uup[(t,p)] == quicksum( U[(p,d,c)] * sv_aux_psp[(t,m,d,k,c)] for m in M for d in D for k in K for c in C) for t in T for p in P), name='con_auxiliary_uup')
     sc_pwp = sub_prob.addConstrs((sv_aux_pwp[(m,d,k,c)] == sv_st_pw[(m,d,k,c)] - quicksum( sv_ac_sc[(t,m,d,k,c)] for t in T) for m in M for d in D for k in K for c in C), name='con_auxiliary_pwp')
@@ -175,6 +179,13 @@ def main_func(iter_lims, beta_fun, sub_mip_gap, import_data, export_data, export
     sc_aux_pst_k_i = sub_prob.addConstrs((sv_aux_pst_k[(t,m,d,k,c)] == ptp_k[(k,c)] * (sv_aux_psp[(t,m,d,k,c)] + sv_aux_pst_d[(t,m,D[D.index(d)-1],k,c)] - sv_aux_pst_d[(t,m,d,k,c)]) for t in T for m in M for d in D for k in K for c in C if d != D[0] and d != D[-1]), name='con_auxiliary_pwt_k')
[…]

### 2022-10-02 New-Implementation/Report.Rmd
report

---
title: "Dynamic Knapsack Model Report"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
    toc_depth: 3
    lightbox: TRUE
    gallery: TRUE
---

```{r setup, include=FALSE, cache=FALSE}
## Global options
library(reticulate)
library(knitr)

library(scales)
library(here)
library(tidyverse)
library(readr)
library(plotly)
library(tidyverse)

knitr::opts_chunk$set(cache = TRUE)
reticulate::use_condaenv('uOttawa-dyn-knap-R', required=TRUE)
source_python("z_factor.py")
source(here('Report_Stuff/data_funcs.R'))

### Generate Data
warm <- 250
dur <- 1250
repl <- 30

# path <- "R1R2"
# R1R2 <- generate_summary(path, dur, warm, repl)
R1R2_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2.pkl"
return_data(R1R2_beta_file, FALSE, FALSE)
return_data(R1R2_beta_file, FALSE, TRUE)

# path <- "R1R2R3"
# R1R2R3 <- generate_summary(path, dur, warm, repl)
R1R2R3_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2R3.pkl"
return_data(R1R2R3_beta_file, TRUE, FALSE)
return_data(R1R2R3_beta_file, TRUE, TRUE)

arrival_rate <- data.frame(
  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 4', 'Surgery 4', 'Surgery 6', 'Surgery 6'),
  Complexity = c('Complexity 1', 'Complexity 2', 'Complexity 1', 'Complexity 2', 'Complexity 1', 'Complexity 2'),
  "Arrival_Adjusted" = c(1.231988473, 0.615994236, 0.143731988, 0.102665706, 1.231988473, 0.615994236),
  "Arrival_Original" = c(1, 0.5, 0.0833, 0.0625, 1, 0.5), 
  Rationale = c("once per week", "once per two weeks", "once per 3 months", "once per 4 months", "once per week", "once per 2 weeks")
)

resource_usage <- data.frame(
  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 6', 'Surgery 6', 'Surgery 6', 'Surgery 6'),
  Complexity = c('Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2', 'Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2', 'Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2'),
  Resource_Type = c('Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time'), 
  Usage = c(0, 3, 1,4,1,4,1,5.5,0,1.5,0,2.5)
)

resource_capacity <- data.frame(
  Resouce = c('Admissions', 'OR_Time'),
  Capacity_Weekly = c(1.5, 11.25),
  Unit = c("Patients Admitted per week", "OR Hours per week")
)

temp1 <- read_csv("Report_Stuff/R2_basic.csv") %>% mutate(type = 'basic')
temp2 <- read_csv("Report_Stuff/R2_prio.csv") %>% mutate(type = 'prio')
R1R2_beta_data <- bind_rows(temp1, temp2)

temp1 <- read_csv("Report_Stuff/R2_basic_myopic.csv") %>% mutate(type = 'basic')
temp2 <- read_csv("Report_Stuff/R2_prio_myopic.csv") %>% mutate(type = 'prio')
R1R2_beta_data_myopic <- bind_rows(temp1, temp2)

### Generate Plots
R1R2_policy <- (ggplot(R1R2_beta_data %>% filter(M == 0), aes(x=T, y=Val, color=C, shape=D, linetype=D)) +
    geom_line() + geom_point() +
    facet_wrap(. ~ type, scales='free') +
    scale_x_continuous(breaks=seq(0,10), limits = c(1,10))) %>% ggplotly()
R1R2_policy_myopic <- (ggplot(R1R2_beta_data_myopic %>% filter(M == 0), aes(x=T, y=Val, color=C, shape=D, linetype=D)) +
    geom_line() + geom_point() +
    facet_wrap(. ~ type, scales='free') +
    scale_x_continuous(breaks=seq(0,10), limits = c(1,10))) %>% ggplotly()
```

# Parameters

## Model Parameters
This model is a smaller instance of the full problem:

* Planning horizon is decreased from 24 weeks to 10 weeks
* Maximum tracked wait is decreased from 6 weeks to 4 weeks
* There are 3 surgeries instead of 6 surgeries
* Number of priorities is set to 1

## Simulation Parameters
* 30 Replications
* 1250 weeks duration
* 250 weeks warm up

## Surgeries
1) **Surgery 1** - 1. SPINE POSTERIOR DECOMPRESSION/LAMINECTOMY LUMBAR
2) **Surgery 4** - 4. SPINE POST CERV DECOMPRESSION AND FUSION W INSTR
3) **Surgery 6** - 6. SPINE POSTERIOR DISCECTOMY LUMBAR

## Arrival Rate
It was set to be 95% of the capacity, however due to transitions, the resource usage should be higher than 95%

``` {r echo=FALSE, cache=FALSE}
kable(arrival_rate)
```

## Resource Usage

Usage of the resources
```{r echo=FALSE, cache=FALSE}
kable(resource_usage)
```

## Resource Capacity
```{r echo=FALSE, cache=FALSE}
kable(resource_capacity)
```

# R1R2 Report
This model is the default model that does not penalize bed under utilization

## Policy Description

The description will be based on the following graphs (both of them are for M of 0 only):

```{r echo=FALSE, cache=FALSE}
R1R2_policy
```
```{r echo=FALSE, xcache=FALSE}
R1R2_policy_myopic
```

The graph on the left shows in which days the MDP policy will allow scheduling. If the value is below 0 - the model will allow scheduling, otherwise the model will keep patients in the waitlist. Thus this policy **will only schedule into week 1 and week 2**

The plot on the right shows the approximate priority of different surgeries. The lower the surgery is on the list the more likely it is to be scheduled first.

## Policy Results

# R1R2R3 Report
In addition to the parameters above, this model penalizes bed under utilization in the first period

## Policy Description

The description will be based on the following graphs:

```{r echo=FALSE, cache=FALSE}
R1R2_policy
```

## Policy Results

The policy description is based on the following graphs.

### 2022-10-02 New-Implementation/Report_Stuff/data_funcs.R

@@ -1,0 +1,335 @@
+library(tidyverse)
+library(here)
+
+path <- "R1R2"
+dur <- 1250
+warm <- 250
+repl <- 30
+
+generate_summary <- function(path, dur, warm, repl) {
+  
+  # Data
+  data <- read_data(path)
+  
+  # Generate Wait Time
+  avg_pw <- analyse_wait(data, dur, warm, repl)
+  # Generate Wait List
+  avg_wtl <- analyse_wait_list(data, dur, warm, repl)
+  # Generate Utilization
+  avg_util <- analyse_util(data, dur, warm, repl)
+  # Generate Reschedules
+  avg_rsc <- analyse_resch(data, dur, warm, repl)
+  # Generate Transitions
+  avg_tr <- analyse_trans(data, dur, warm, repl)
+  
+  results <- list(
+    'data' = data,
+    'results' = list(
+      'pw' = avg_pw, 
+      'wtl' = avg_wtl, 
+      'util' = avg_util, 
+      'rsc' = avg_rsc,
+      'tr' = avg_tr
+    )
+  )
+  
+  return (results)
+}
+
+
+
+### Reads all relevant data
+read_data <- function(path) {
+  
+  # Patient Transition Data
+  state_md <- read_csv(here("simulation_data",paste0('STATE-md-',path,'.txt')), col_types = cols(
+    id = col_double(), repl=col_double(), period=col_double(), arrived_on=col_double(), 
+    sched_to=col_double(), resch_from=col_double(), resch_to=col_double())) %>% filter(!is.na(id))
+  state_my <- read_csv(here("simulation_data",paste0('STATE-my-',path,'.txt')), col_types = cols(
+    id = col_double(), repl=col_double(), period=col_double(), arrived_on=col_double(), 
+    sched_to=col_double(), resch_from=col_double(), resch_to=col_double())) %>% filter(!is.na(id))
+  state <- bind_rows(state_md, state_my)
+
+  # Cost Data
+  cost_md <- read_csv(here("simulation_data",paste0('COST-md-',path,'.txt'))) %>% mutate(policy = 'MDP')
+  cost_my <- read_csv(here("simulation_data",paste0('COST-my-',path,'.txt'))) %>% mutate(policy = 'myopic')
[…]

### 2022-10-02 New-Implementation/data_analysis.R

@@ -1,114 +1,0 @@
-library(tidyverse)
-library(readr)
-library(gridExtra)
-library(here)
-library(scales)
-library(gridExtra)
-library(plotly)
-
-source(here('data_funcs.R'))
-
-warm <- 250
-dur <- 1250
-repl <- 30
-
-my_dat <- read_csv(here("simulation_data/SA-my-R1R2R3.txt")) %>% mutate(policy = 'my')
-md_dat <- read_csv(here("simulation_data/SA-md-R1R2R3.txt")) %>% mutate(policy = 'md')
-dat <- my_dat %>% bind_rows(md_dat)
-
-# Scheduling
-sched_dat <- dat %>% filter(`state-aciton` == 'action' & value == 'sc') %>%
-  filter(period >= warm) %>%
-  mutate(t = as.numeric(t)) %>%
-  group_by(repl, policy, t, c, d) %>% 
-  summarize(count = sum(val) / (dur-warm)) %>% 
-  group_by(policy, t,c,d) %>%
-  summarize(mean = mean(count), sd = sd(count)) %>%
-  mutate(mean_log = log(mean)) %>%
-  separate(c, sep=" ", into=c('c'))
-
-ggplot(sched_dat) +
-  geom_bar(aes(x=t, y=mean, fill=c), stat='identity') +
-  geom_text(aes(x=t, y=mean, label=round(mean,1)), size=2) +
-  facet_grid(c+d ~ policy, scales="fixed") + 
-  labs(x='Time (Week)', y='Count (Sched)', title='Average Scheduling Numbers')
-
-# Rescheduling
-rsc_dat <- dat %>% filter(value == 'rsc') %>%
-  filter(period >= warm) %>%
-  group_by(policy, repl, c, d,t ,tp) %>%
-  summarize(avg = sum(val)) %>%
-  group_by(policy, c, d, t, tp) %>%
-  summarize(mean = mean(avg), sd = sd(avg)) %>%
-  separate(c, sep=' ', into=c('c')) %>%
-  mutate(t = as.numeric(t), tp = as.numeric(tp))
-
-(ggplot(rsc_dat %>% filter(t == 1)) +
-  geom_bar(aes(x=t, y=mean, fill=tp), stat = 'identity', position='dodge2') +
-  facet_grid(c+d ~ policy, scales='free') + 
[…]

### 2022-10-02 New-Implementation/data_funcs.R

@@ -1,335 +1,0 @@
-library(tidyverse)
-library(here)
-
-path <- "R1R2"
-dur <- 1250
-warm <- 250
-repl <- 30
-
-generate_summary <- function(path, dur, warm, repl) {
-  
-  # Data
-  data <- read_data(path)
-  
-  # Generate Wait Time
-  avg_pw <- analyse_wait(data, dur, warm, repl)
-  # Generate Wait List
-  avg_wtl <- analyse_wait_list(data, dur, warm, repl)
-  # Generate Utilization
-  avg_util <- analyse_util(data, dur, warm, repl)
-  # Generate Reschedules
-  avg_rsc <- analyse_resch(data, dur, warm, repl)
-  # Generate Transitions
-  avg_tr <- analyse_trans(data, dur, warm, repl)
-  
-  results <- list(
-    'data' = data,
-    'results' = list(
-      'pw' = avg_pw, 
-      'wtl' = avg_wtl, 
-      'util' = avg_util, 
-      'rsc' = avg_rsc,
-      'tr' = avg_tr
-    )
-  )
-  
-  return (results)
-}
-
-
-
-### Reads all relevant data
-read_data <- function(path) {
-  
-  # Patient Transition Data
-  state_md <- read_csv(here("simulation_data",paste0('STATE-md-',path,'.txt')), col_types = cols(
-    id = col_double(), repl=col_double(), period=col_double(), arrived_on=col_double(), 
-    sched_to=col_double(), resch_from=col_double(), resch_to=col_double())) %>% filter(!is.na(id))
-  state_my <- read_csv(here("simulation_data",paste0('STATE-my-',path,'.txt')), col_types = cols(
-    id = col_double(), repl=col_double(), period=col_double(), arrived_on=col_double(), 
-    sched_to=col_double(), resch_from=col_double(), resch_to=col_double())) %>% filter(!is.na(id))
-  state <- bind_rows(state_md, state_my)
-
-  # Cost Data
-  cost_md <- read_csv(here("simulation_data",paste0('COST-md-',path,'.txt'))) %>% mutate(policy = 'MDP')
-  cost_my <- read_csv(here("simulation_data",paste0('COST-my-',path,'.txt'))) %>% mutate(policy = 'myopic')
[…]

### 2022-10-02 New-Implementation/job-complex2.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=02-00
-#SBATCH --mem-per-cpu=8G
-#SBATCH --job-name=complex2
-#SBATCH --output=optim-complex2.out
-python3 main-complex2.py

### 2022-10-02 New-Implementation/job-complex4.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=02-00
-#SBATCH --mem-per-cpu=8G
-#SBATCH --job-name=complex4
-#SBATCH --output=optim-complex4.out
-python3 main-complex4.py

### 2022-10-02 New-Implementation/job-complex5.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=02-00
-#SBATCH --mem-per-cpu=8G
-#SBATCH --job-name=complex5
-#SBATCH --output=optim-complex5.out
-python3 main-complex5.py

### 2022-10-02 New-Implementation/job-full-all.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-sbatch job-full1.sh
-sbatch job-full2.sh
-sbatch job-full3.sh
-sbatch job-full4.sh
-sbatch job-full5.sh
-sbatch job-full6.sh
-sbatch job-full7.sh
-sbatch job-full8.sh
-sbatch job-full9.sh
-sbatch job-full10.sh

### 2022-10-02 New-Implementation/job-full3.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=full3
-#SBATCH --output=optim-full3.out
-python3 main-full3.py

### 2022-10-02 New-Implementation/job-full6.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=full6
-#SBATCH --output=optim-full6.out
-python3 main-full6.py

### 2022-10-02 New-Implementation/job-full8.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=full8
-#SBATCH --output=optim-full8.out
-python3 main-full8.py

### 2022-10-02 New-Implementation/job-smaller-full10.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full10
-#SBATCH --output=optim-smaller-full10.out
-python3 main-smaller-full10.py

### 2022-10-02 New-Implementation/job-smaller-full12.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full12
-#SBATCH --output=optim-smaller-full12.out
-python3 main-smaller-full12.py

### 2022-10-02 New-Implementation/job-smaller-full14.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full14
-#SBATCH --output=optim-smaller-full14.out
-python3 main-smaller-full14.py

### 2022-10-02 New-Implementation/job-smaller-full2.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full2
-#SBATCH --output=optim-smaller-full2.out
-python3 main-smaller-full2.py

### 2022-10-02 New-Implementation/job-smaller-full4.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full4
-#SBATCH --output=optim-smaller-full4.out
-python3 main-smaller-full4.py

### 2022-10-02 New-Implementation/job-smaller-full7.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full7
-#SBATCH --output=optim-smaller-full7.out
-python3 main-smaller-full7.py

### 2022-10-02 New-Implementation/job-smaller-full8.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full8
-#SBATCH --output=optim-smaller-full8.out
-python3 main-smaller-full8.py

### 2022-10-02 New-Implementation/main-complex3.py

@@ -1,38 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv100-gam999-"
-data_type = "complex"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.9)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 10
-warm_up = 1500
-duration = 5000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-complex5.py

@@ -1,38 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "exp-zero-cw1-cc5-cv100-gam95-"
-data_type = "complex"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.9)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 10
-warm_up = 1500
-duration = 5000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-full2.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv100-gam99-"
-data_type = "full"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.9)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 1
-warm_up = 2000
-duration = 10000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-# simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-full3.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv100-gam999-"
-data_type = "full"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.9)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 1
-warm_up = 2000
-duration = 10000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-# simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-full7.py

@@ -1,41 +1,0 @@
-
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv1000-gam99-"
-data_type = "full"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.9)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 1
-warm_up = 2000
-duration = 10000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-# simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-smaller-full1.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv100-gam99-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 1000000
-beta_fun = [
-    (0,0.75),
-    (10000,0.8)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 2000
-duration = 6000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-smaller-full12.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv10-gam99-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.95)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 2000
-duration = 6000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-smaller-full13.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv10-gam999-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 300000
-beta_fun = [
-    (0,0.75),
-    (10000,0.95)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 2000
-duration = 6000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-smaller-full14.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "exp-full-cw1-cc5-cv10-gam95-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 100000
-beta_fun = [
-    (0,0.75),
-    (10000,0.95)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 2000
-duration = 6000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-smaller-full4.py

@@ -1,42 +1,0 @@
-from doctest import FAIL_FAST
-from math import fabs
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "exp-full-cw1-cc5-cv100-gam95-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 1000000
-beta_fun = [
-    (0,0.75),
-    (10000,0.8)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 2000
-duration = 6000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2022-10-02 New-Implementation/main-smaller-full8.py

@@ -1,40 +1,0 @@
-import optimization_new
-import simulation_new    
-import time
-
-# Test Type
-test_modifier = "cw1-cc5-cv1000-gam999-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 1000000
-beta_fun = [
-    (0,0.75),
-    (10000,0.8)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 2000
-duration = 6000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md)
-end_time_sim = time.time()
-print(f'{test_modifier}{data_type}\tOptimization: {end_time_opt-start_time_opt} sec \tSimulation: {end_time_sim-end_time_opt} sec')
-print(f'{beta_fun}')

### 2023-05-06 implementation/Report.Rmd
Refactoring code
- adjusted folder names
- moved modules into various folders
- refactored simulation and optimization code to be class based rather than function based

---
title: "Dynamic Knapsack Model Report"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
    toc_depth: 3
    lightbox: TRUE
    gallery: TRUE
---

```{r setup, include=FALSE, cache=FALSE}
## Global options
library(reticulate)
library(knitr)

library(scales)
library(here)
library(tidyverse)
library(readr)
library(plotly)
library(tidyverse)

knitr::opts_chunk$set(cache = TRUE)
reticulate::use_condaenv('uOttawa-dyn-knap-R', required=TRUE)
source_python("z_factor.py")
source(here('Report_Stuff/data_funcs.R'))

### Generate Data
warm <- 250
dur <- 1250
repl <- 30

path <- "R1R2"
R1R2 <- generate_summary(path, dur, warm, repl)
R1R2_sa <- generate_summary_sa(path, dur, warm, repl)
R1R2_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2.pkl"
return_data(R1R2_beta_file, FALSE, FALSE)
return_data(R1R2_beta_file, FALSE, TRUE)
temp1 <- read_csv("Report_Stuff/R2_basic.csv") %>% mutate(type = 'basic')
temp2 <- read_csv("Report_Stuff/R2_prio.csv") %>% mutate(type = 'prio')
R1R2_beta_data_mdp <- bind_rows(temp1, temp2) %>% mutate(pol = 'mdp')
temp1 <- read_csv("Report_Stuff/R2_basic_myopic.csv") %>% mutate(type = 'basic')
temp2 <- read_csv("Report_Stuff/R2_prio_myopic.csv") %>% mutate(type = 'prio')
R1R2_beta_data_myopic <- bind_rows(temp1, temp2) %>% mutate(pol = 'myopic')
R1R2_beta_data <- bind_rows(R1R2_beta_data_mdp, R1R2_beta_data_myopic)

path <- "R1R2R3"
R1R2R3 <- generate_summary(path, dur, warm, repl)
R1R2R3_sa <- generate_summary_sa(path, dur, warm, repl)
R1R2R3_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2R3.pkl"
return_data(R1R2R3_beta_file, TRUE, FALSE)
return_data(R1R2R3_beta_file, TRUE, TRUE)
temp1 <- read_csv("Report_Stuff/R3_basic.csv") %>% mutate(type = 'basic')
temp2 <- read_csv("Report_Stuff/R3_prio.csv") %>% mutate(type = 'prio')
R1R2R3_beta_data_mdp <- bind_rows(temp1, temp2) %>% mutate(pol = 'mdp')
temp1 <- read_csv("Report_Stuff/R3_basic_myopic.csv") %>% mutate(type = 'basic')
temp2 <- read_csv("Report_Stuff/R3_prio_myopic.csv") %>% mutate(type = 'prio')
R1R2R3_beta_data_myopic <- bind_rows(temp1, temp2) %>% mutate(pol = 'myopic')
R1R2R3_beta_data <- bind_rows(R1R2R3_beta_data_mdp, R1R2R3_beta_data_myopic)

arrival_rate <- data.frame(
  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 4', 'Surgery 4', 'Surgery 6', 'Surgery 6'),
  Complexity = c('Complexity 1', 'Complexity 2', 'Complexity 1', 'Complexity 2', 'Complexity 1', 'Complexity 2'),
  "Arrival_Adjusted" = c(1.231988473, 0.615994236, 0.143731988, 0.102665706, 1.231988473, 0.615994236),
  "Arrival_Original" = c(1, 0.5, 0.0833, 0.0625, 1, 0.5), 
  Rationale = c("once per week", "once per two weeks", "once per 3 months", "once per 4 months", "once per week", "once per 2 weeks")
)

resource_usage <- data.frame(
  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 6', 'Surgery 6', 'Surgery 6', 'Surgery 6'),
  Complexity = c('Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2', 'Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2', 'Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2'),
  Resource_Type = c('Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time'), 
  Usage = c(0, 3, 1,4,1,4,1,5.5,0,1.5,0,2.5)
)

resource_capacity <- data.frame(
  Resouce = c('Admissions', 'OR_Time'),
  Capacity_Weekly = c(1.5, 11.25),
  Unit = c("Patients Admitted per week", "OR Hours per week")
)

### Generate Plots
R1R2_policy <- (ggplot(R1R2_beta_data %>% filter(M == 0), aes(x=T, y=Val, color=C, shape=D, linetype=D)) +
    geom_line() + geom_point() +
    facet_wrap(pol ~ type, scales='free') +
    scale_x_continuous(breaks=seq(0,10), limits = c(1,10))) %>% ggplotly()

R1R2R3_policy <- (ggplot(R1R2R3_beta_data %>% filter(M == 0), aes(x=T, y=Val, color=C, shape=D, linetype=D)) +
    geom_line() + geom_point() +
    facet_wrap(pol ~ type, scales='free') +
    scale_x_continuous(breaks=seq(0,10), limits = c(1,10))) %>% ggplotly()
```

# Parameters

## Model Parameters
This model is a smaller instance of the full problem:

* Planning horizon is decreased from 24 weeks to 10 weeks
* Maximum tracked wait is decreased from 6 weeks to 4 weeks
* There are 3 surgeries instead of 6 surgeries
* Number of priorities is set to 1

## Simulation Parameters
* 30 Replications
* 1250 weeks duration
* 250 weeks warm up

## Surgeries
1) **Surgery 1** - 1. SPINE POSTERIOR DECOMPRESSION/LAMINECTOMY LUMBAR
2) **Surgery 4** - 4. SPINE POST CERV DECOMPRESSION AND FUSION W INSTR
3) **Surgery 6** - 6. SPINE POSTERIOR DISCECTOMY LUMBAR

## Arrival Rate
It was set to be 95% of the capacity, however due to transitions, the resource usage should be higher than 95% 
``` {r echo=FALSE, cache=FALSE}
kable(arrival_rate)
```

## Resource Usage
Usage of the resources
```{r echo=FALSE, cache=FALSE}
kable(resource_usage)
```

## Resource Capacity
```{r echo=FALSE, cache=FALSE}
kable(resource_capacity)
```

# R1R2 Report
This model is the default model that does not penalize bed under utilization

## Policy Description
The description will be based on the following graphs (both of them are for M of 0 only):
```{r echo=FALSE, cache=FALSE}
R1R2_policy
```

The top graphs show MDP policy, and the graphs below show Myopic policy.

The graph on the left shows in which days the policy will allow scheduling. If the value is below 0 - the model will allow scheduling, otherwise the model will keep patients in the waitlist. Thus this policy **will only schedule into week 1 and week 2**. The plot on the right shows the approximate priority of different surgeries. The lower the surgery is on the list the more likely it is to be scheduled first. The following is the order:

- Surgery 6, Complexity 2
- Surgery 6, Complexity 1
- Surgery 1, Complexity 1
- Surgery 1, Complexity 2
- Surgery 4, Complexity 1
- Surgery 4, Complexity 2

For Myopic, it is changed such that the entire horizon is filled. And the graph on the right shows the approximate order of scheduling priority. It appears to be very similar to MDP.

Additionally the following graphs give some insights on how the policy makes decision
```{r echo=FALSE, cache=FALSE}
R1R2_sa$res_plot$sched_plt
```

## Policy Results
### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(R1R2$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(R1R2$results$wtl)
```
```{r echo=FALSE, cache=FALSE}
R1R2_sa$res_plot$waitlist_plt
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(R1R2$results$util)
```

### Reschedules as percentage of arrivals & Total Reschedules
```{r echo=FALSE, cache=FALSE}
kable(R1R2$results$rsc)
```
```{r echo=FALSE, cache=FALSE}
R1R2_sa$res_plot$rsc_plt %>% ggplotly()
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(R1R2$results$tr)
```

# R1R2R3 Report
In addition to the parameters above, this model penalizes bed under utilization in the first period

## Policy Description
<!-- The description will be based on the following graphs: -->
```{r echo=FALSE, cache=FALSE}
R1R2R3_policy
```

Additionally the following graphs give some insights on how the policy makes decision
```{r echo=FALSE, cache=FALSE}
R1R2R3_sa$res_plot$sched_plt
```

## Policy Results

### Wait Times in weeks
```{r echo=FALSE, cache=FALSE}
kable(R1R2R3$results$pw)
```

### Wait List Size
```{r echo=FALSE, cache=FALSE}
kable(R1R2R3$results$wtl)
```
```{r echo=FALSE, cache=FALSE}
R1R2R3_sa$res_plot$waitlist_plt
```

### Utilization
```{r echo=FALSE, cache=FALSE}
kable(R1R2R3$results$util)
```

### Reschedules as percentage of arrivals & Total Reschedules
```{r echo=FALSE, cache=FALSE}
kable(R1R2R3$results$rsc)
```
```{r echo=FALSE, cache=FALSE}
R1R2R3_sa$res_plot$rsc_plt %>% ggplotly()
```

### Transitions per week
```{r echo=FALSE, cache=FALSE}
kable(R1R2R3$results$tr)
```

### 2023-05-06 manuscript/sections/introduction.tex
Refactoring code
- adjusted folder names
- moved modules into various folders
- refactored simulation and optimization code to be class based rather than function based

\section{Introduction}

\subsection{Goals}
The goal of this paper is to describe a patient surgery scheduling policy. This policy should consider the following items:
\begin{itemize}
	\item Different surgery types
	\item Usage of various resources
	\item Consider changes in patient complexity and patient priority
	\item Consider randomness in various aspects
	\item Take into account long term impact of scheduling
	\item Modeling of the wait list 
	\item It should allow for rescheduling
\end{itemize}

\subsection{Outcomes}
The outcomes of the model should be the following:
\begin{itemize}
	\item The model should optimize overall system metrics
	\item It should provide suggested schedule times for an input
\end{itemize}

\subsection{Model Description}
The model's decisions will be done at the beginning of each period (in our case weekly). At the beginning of the period the model will take the current number of patients waiting, current waitlist, and current resource into account to make a decision. The model will output how many of each patient type to schedule into which period. And it will also say how many of each patient type to reschedule to which period.

### 2023-05-06 manuscript/sections/mdp_model.tex
Refactoring code
- adjusted folder names
- moved modules into various folders
- refactored simulation and optimization code to be class based rather than function based

--- 2021-12-10 New-Manuscript/sections/mdp_model.tex
@@
 	\item $pst\_k_{tmdkc}$ - patients scheduled transitioned in priority
+	\item $uu_{tp}, \quad \forall p \in {\text{Admission}}$ - units underutilized for resource p, time t
+	\item $uub_{tp}, \quad \forall p \in {\text{Admission}}$ - binary variable to enforce $uu$ without using objective function
 \end{itemize}
@@
 	& pwt\_d_{mdkc} 
-		&& = ptp\_{dc} * \hat{pw}_{mdkc} \quad
+		&& = ptp\_d_{dc} * \hat{pw}_{mdkc} \quad
 		&& \forall mdkc \\
 	& pwt\_k_{mdkc} 
-		&& = ptp\_{kc} * \hat{pw}_{mdkc} \quad
+		&& = ptp\_k_{kc} * ( \hat{pw}_{mdkc} + pwt\_d_{md-1kc} - pwt\_d_{mdkc} )  \quad
 		&& \forall mdkc \\
 	& pst\_d_{tmdkc} 
-		&& = ptp\_{dc} * \hat{ps}_{tmdkc} \quad
+		&& = ptp\_d_{dc} * \hat{ps}_{tmdkc} \quad
 		&& \forall tmdkc \\
 	& pst\_k_{tmdkc} 
-		&& = ptp\_{kc} * \hat{ps}_{tmdkc} \quad
+		&& = ptp\_k_{kc} * ( \hat{ps}_{tmdkc} + pst\_d_{tmd-1kc} - pst\_d_{tmdkc} )  \quad
 		&& \forall tmdkc
@@
 \begin{itemize}
-
 	\item Define Resource Violation Variable
 	\begin{alignat}{10}
-		& uv_{tp} 
-			&& = max\{0 , \hat{uu}_{1p} - p\_{ue}_{1p} - ul_{p}\} \quad 
+		& uv_{1p} 
+			&& = max\{0 , \hat{uu}_{1p} - p\_ue_{p} - ul_{p}\} \quad 
 			&& \forall p \\ 
 		& uv_{tp} 
-			&& = max\{0 , \hat{uu}_{tp} - p\_{ue}_{tp}\} \quad
+			&& = max\{0 , \hat{uu}_{tp} - p\_ue_{p}\} \quad
 			&& \forall t \in \{2..T\} p \\ \\
@@
 		& uv_{1p} 
-			&&\ge \hat{uu}_{1p} - p\_ue_{1p} - ul_{p} \quad
+			&&\ge \hat{uu}_{1p} - p\_ue_{p} - ul_{p} \quad
 			&& \forall p \\
 		& uv_{1p} 
-		&& \le  (\hat{uu}_{1p} - p\_ue_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
+		&& \le  (\hat{uu}_{1p} - p\_ue_{p} - ul_{p}) + M(1-uvb_{tp}) \quad
 		&& \forall p \\
 		& uv_{tp} 
-			&&\ge \hat{uu}_{tp} - p\_ue_{tp} \quad
+			&&\ge \hat{uu}_{tp} - p\_ue_{p} \quad
 			&& \forall t \in \{2..T \} p \\
 		& uv_{tp} 
-		&& \le  (\hat{uu}_{tp} - p\_ue_{tp}) + M(1-uvb_{tp}) \quad
+		&& \le  (\hat{uu}_{tp} - p\_ue_{p}) + M(1-uvb_{tp}) \quad
 		&& \forall t \in \{ 2..T \} p \\
@@
 		& \hat{ul}_{p} 
-			&& = max \{0, p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \}
+			&& = max \{0, p\_ue_{p} + ul_{p} - \hat{uu}_{1p} \}
 			&& \forall p \in \{p_co\} \\ \\
@@
 		& \hat{ul}_{p} 
-			&& \ge p\_ue_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
+			&& \ge p\_ue_{p} + ul_{p} - \hat{uu}_{1p} \quad 
 			&& \forall p  \in p\_co\\
 		& \hat{ul}_{p} 
-			&& \le (p\_ue_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
+			&& \le (p\_ue_{p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
 			&& \forall p  \in p\_co
+	\end{alignat}
+
+	\item Define Resource Underutilized
+	\begin{alignat}{10}
+		& uu_{1p} 
+			&& = max\{0 , p\_ue_{p} + ul_{p} - \hat{uu}_{1p}\} \quad 
+			&& \forall p \in {\text{Admissions}} \\ 
+		& uu_{tp} 
+			&& = max\{0 , p\_ue_{p} - \hat{uu}_{tp}\} \quad
+			&& \forall t \in \{2..T\} p \in {\text{Admissions}} \\ \\
+		& uu_{tp} 
+			&&\ge 0 \quad
+			&& \forall tp \\
+		& uu_{tp} 
+			&& \le  M(uub_{tp}) \quad
+			&& \forall tp \\
+		& uu_{1p} 
+			&&\ge p\_ue_{p} + ul_{p} - \hat{uu}_{1p} \quad
+			&& \forall p \\
+		& uu_{1p} 
+		&& \le  (p\_ue_{p} + ul_{p} - \hat{uu}_{1p}) + M(1-uub_{tp}) \quad
+		&& \forall p \\
+		& uu_{tp} 
+			&&\ge p\_ue_{p} - \hat{uu}_{tp}\ \quad
+			&& \forall t \in \{2..T \} p \\
+		& uu_{tp} 
+		&& \le  (p\_ue_{p} - \hat{uu}_{tp}\ + M(1-uub_{tp}) \quad
+		&& \forall t \in \{ 2..T \} p \\
 	\end{alignat}
@@
 		& \hat{uu}_{1p} 
-			&& \le p\_ue_{1p} + ul_{p} + uv_{1p} \quad 
+			&& \le p\_ue_{p} + ul_{p} + uv_{1p} \quad 
 			&& \forall p \\
 		& \hat{uu}_{tp} 
-			&& \le p\_ue_{tp} + uv_{tp} \quad
+			&& \le p\_ue_{p} + uv_{tp} \quad
 			&& \forall t \in \{ 2..T \}p 
@@
 
-	\item Bounds on states
+	\item Bounds on states (not sure about the rationale on that)
 	\begin{alignat}{10}
@@
 	\item $cs_{tk} = \sum_t (\alpha^t * cw_{k})$
+	\item $cuu = 0$ if R3 not used, $M$ otherwise
 \end{itemize}
@@
 		& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
-		&& 
-		\overbrace{ \sum_{mdkc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
-			cost of waiting}  + 
-		\overbrace{
+			&& 	\overbrace{
+					\sum_{mdkc} cw_{k} (\hat{pw}_{mdkc}) 
+				}^\text{ Cost of waiting} 
+				+ \overbrace{ 
 					\sum_{tmdkc} cs_{tk} (sc_{tmdkc}) 
 				}^\text{Prefer earlier appointments} \\ 
-		&	&&  +
-		\overbrace{
-			\sum_{
-				\substack{tt`mdkc \\ t' > t}} 
-			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
-		\overbrace{ 
-			\sum_{
-				\substack{tt`mdkc \\ t' < t}}
-			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
-		M \sum_{tp} uv_{tp}
+		&	&& 	+ \overbrace{ 
+					\sum_{ \substack{tt`mdkc \\ t' > t}} 
+					(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})
+				}^\text{Bad reschedule} 
+				- \overbrace{ 
+					\sum_{ \substack{tt`mdkc \\ t' < t}} 
+					(cs_{t-t', k} - cc) * (rsc_{tt'mdc})
+				}^\text{Good reschedule} \\
+		& 	&& 	+ \overbrace{
+					cv \sum_{tp} uv_{tp}
+				}^\text{Unit violation}
+			 	+ \overbrace{
+					cuu \sum_{tp} (uu_{tp})
+				}^\text{(R3) Underutilization}
 \end{alignedat}\end{equation}

### 2023-05-06 New-Implementation/job-smaller-full1.sh

@@ -1,6 +1,0 @@
-#!/bin/bash
-#SBATCH --time=07-00
-#SBATCH --mem-per-cpu=16G
-#SBATCH --job-name=smaller-full1
-#SBATCH --output=optim-smaller-full1.out
-python3 main-smaller-full1.py

### 2023-05-06 New-Implementation/main-smaller-full.py

@@ -1,50 +1,0 @@
-#%%
-import optimization_new
-import simulation_new    
-import time
-import sys
-
-# Test Type
-# test_modifier = f"cw{sys.argv[1]}-cc{sys.argv[2]}-cv{sys.argv[3]}-gam{sys.argv[4]}-"
-test_modifier = "cw1-cc5-cv10-gam99-"
-data_type = "smaller-full"
-
-# Optimization Paramers
-iter_lims = 1000000
-beta_fun = [
-    (0,0.9),
-    (10000,0.99)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-nopri-data.xlsx"
-export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-nopri-optimal-R1R2.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-nopri-p2-R1R2.mps"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 30
-warm_up = 250
-duration = 1250
-show_policy = True
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res-nopri-R1R2.txt"
-export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res-nopri-R1R2.html"
-export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my-nopri-R1R2.txt"
-export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md-nopri-R1R2.txt"
-export_cost_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-cost-my-nopri-R1R2.txt"
-export_cost_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-cost-md-nopri-R1R2.txt"
-export_util_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-util-my-nopri-R1R2.txt"
-export_util_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-util-md-nopri-R1R2.txt"
[…]

### 2023-05-06 New-Implementation/main.py

@@ -1,62 +1,0 @@
-#%%
-import optimization_new
-import simulation_new
-import time
-#%%
-# Test Type
-test_modifier_list = [
-    'cw1-cc1-cv10-gam95-',
-    'cw1-cc1-cv100-gam95-',
-    'cw1-cc5-cv10-gam95-',
-    'cw1-cc5-cv100-gam95-',
-    'cw1-cc10-cv10-gam95-',
-    'cw1-cc10-cv100-gam95-'
-    # 'cw1-cc1-cv10-gam99-',
-    # 'cw1-cc1-cv10-gam999-',
-]
-
-# for i in test_modifier_list:
-#     test_modifier = i
-#     data_type = 'simple'
-        
-
-test_modifier = "cw1-cc1-cv10-gam95-"
-data_type = "complex"
-
-# Optimization Paramers
-iter_lims = 50000
-beta_fun = [
-    (0,0.75)
-    # (500,0.9),
-    # (5000,0.95),
-    # (20000,0.95)
-    # (50000,0.999)
-    # (10,0.8),
-    # (100,0.9),
-    # (500,0.95),
-    # (10000,0.99)
-]
-sub_mip_gap = 0.001
-import_data_opt = f"sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
-export_data_opt = f"sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
-export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.lp"
-import_data_p2 = export_data_p2
-
-# Simulation Parameters
-replications = 3
-warm_up = 1000
-duration = 3000
-show_policy = False
-import_data_sim = import_data_opt
-import_betas_sim = export_data_opt
-export_txt_sim = f"sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
-export_pic_sim = f"sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
-
-# Execute
-start_time_opt = time.time()
-optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
-end_time_opt = time.time()
-simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim)
-end_time_sim = time.time()
[…]

### 2023-05-06 New-Implementation/optimization_new.py

@@ -1,563 +1,0 @@
-##### Initialization & Changeable Parameters ######
-#%%
-#region
-from os import close, linesep
-from Modules import data_import
-
-from gurobipy import *
-import itertools
-import os.path
-import pickle
-import time
-#endregion
-
-
-def main_func(iter_lims, beta_fun, sub_mip_gap, import_data, export_data, export_model, import_model=False):
-
-    ##### Read Data #####
-    #region
-    my_path = os.getcwd()
-    input_data = data_import.read_data(os.path.join(my_path, import_data))
-
-    # Quick Assess to Various Parameters
-    TL = input_data.transition.wait_limit
-    BM = 10000
-    U = input_data.usage
-    p_dat = input_data.ppe_data
-    pea = input_data.arrival
-    gam = input_data.model_param.gamma
-    ptp_d = input_data.transition.transition_rate_comp
-    ptp_k = input_data.transition.transition_rate_pri
-    cw = input_data.model_param.cw
-    cs = input_data.model_param.cs
-    cc = input_data.model_param.cc
-    cv = input_data.model_param.cv
-    cuu = 1000
-
-    ##### Generating Sets #####
-    T = input_data.indices['t']
-    M = input_data.indices['m']
-    P = input_data.indices['p']
-    D = input_data.indices['d']
-    K = input_data.indices['k']
-    C = input_data.indices['c']
-
-    # Sub Sets
-    PCO = []
-    PNCO = []
-    for k, v in input_data.ppe_data.items(): 
-        if v.ppe_type == "non-carry-over": PNCO.append(k) 
-        else: PCO.append(k)
-        
-    mTLdkc = [(m, d, k, c) for c in C for m in M[1:input_data.transition.wait_limit[c]] for d in D for k in K ]
[…]

### 2023-05-06 implementation/compute_canada/job-complex.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+#SBATCH --time=02-00
+#SBATCH --mem-per-cpu=8G
+#SBATCH --job-name=complex1
+#SBATCH --output=optim-complex1.out
+python3 ../main-complex1.py

### 2023-05-06 implementation/main-smaller-full-full.py

@@ -1,0 +1,44 @@
+import optimization_new
+import simulation_new
+import time
+import sys
+
+# Test Type
+test_modifier = f"exp-full-cw{sys.argv[1]}-cc{sys.argv[2]}-cv{sys.argv[3]}-gam{sys.argv[4]}-"
+test_modifier = "cw1-cc5-cv10-gam99-"
+data_type = "smaller-full"
+
+# Optimization Paramers
+iter_lims = 100000
+beta_fun = [(0,0.75),
+            (500,0.9),
+            (5000,0.95),]
+
+sub_mip_gap = 0.001
+import_data_opt = f"Data/sens-data/{data_type}/{test_modifier}{data_type}-data.xlsx"
+export_data_opt = f"Data/sens-data/{data_type}/betas/{test_modifier}{data_type}-optimal.pkl"
+export_data_p2 = f"Data/sens-data/{data_type}/full-model/{test_modifier}{data_type}-p2.mps"
+import_data_p2 = export_data_p2
+
+# Simulation Parameters
+replications = 10
+warm_up = 3000
+duration = 6000
+show_policy = True
+import_data_sim = import_data_opt
+import_betas_sim = export_data_opt
+export_txt_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.txt"
+export_pic_sim = f"Data/sens-res/{data_type}/{test_modifier}{data_type}-optimal-res.html"
+export_state_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-my.txt"
+export_state_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-state-md.txt"
+export_cost_my = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-cost-my.txt"
+export_cost_md = f"Data/sens-res/{data_type}/state-action/{test_modifier}{data_type}-cost-md.txt"
+
+#%% Execute
+start_time_opt = time.time()
+# optimization_new.main_func(iter_lims, beta_fun, sub_mip_gap, import_data_opt, export_data_opt, export_data_p2, import_data_p2)
+end_time_opt = time.time()
+simulation_new.main_func(replications, warm_up, duration, show_policy, import_data_sim, import_betas_sim, export_txt_sim, export_pic_sim, export_state_my, export_state_md, export_cost_my, export_cost_md)
+end_time_sim = time.time()
[…]

### 2023-05-06 implementation/modules/data_import.py

@@ -1,0 +1,172 @@
+# Imports packages
+import openpyxl
+from typing import Dict, Tuple, List, Callable
+from dataclasses import dataclass
+
+from modules.data_classes import ppe_data_class, model_param_class, transition_data_class, input_data_class
+
+# Reads All input data from excel
+def read_data(data_file_path):
+
+    #Opens the excel book
+    book = openpyxl.load_workbook(data_file_path, data_only=True)
+
+
+    # Generates Indices
+    indices_sheet = book.get_sheet_by_name('Indices Data')
+
+    # Generates T
+    t = []
+    for t_row in indices_sheet.iter_rows(min_row=2, min_col=1, max_col=1, values_only=True):
+        if t_row[0] == None: break
+        t.append(t_row[0])
+    # Generates M
+    m = []
+    for m_row in indices_sheet.iter_rows(min_row=2, min_col=2, max_col=2, values_only=True):
+        if m_row[0] == None: break
+        m.append(m_row[0])
+    # Generates P
+    p = []
+    for ppe_row in indices_sheet.iter_rows(min_row=2, min_col=3, max_col=3, values_only=True):
+        if ppe_row[0] == None: break
+        p.append(ppe_row[0])
+    # Generates D
+    d = []
+    for comp_row in indices_sheet.iter_rows(min_row=2, min_col=4, max_col=4, values_only=True):
+        if comp_row[0] == None: break
+        d.append(comp_row[0])
+    # Generates K
+    k = []
+    for prio_row in indices_sheet.iter_rows(min_row=2, min_col=5, max_col=5, values_only=True):
+        if prio_row[0] == None: break
+        k.append(prio_row[0])
+    # Generates C
+    c = []
+    for cpu_row in indices_sheet.iter_rows(min_row=2, min_col=6, max_col=6, values_only=True):
+        if cpu_row[0] == None: break
+        c.append(cpu_row[0])
+
+    # Saves Indices
+    indices = {'t': t, 'm': m, 'p': p, 'd': d, 'k': k, 'c': c }
+    
+
+    # PPE Data
+    ppe_data_sheet = book.get_sheet_by_name('PPE Data')
+
+    ppe_data = {}
+    for ppe_row in ppe_data_sheet.iter_rows(min_row=2, min_col=1, max_col=4, values_only=True):
+        if ppe_row[0] == None: break
+        ppe_type = ""
+        if ppe_row[1] == True: ppe_type = "carry-over"
[…]

### 2023-05-06 implementation/modules/simulation_new.py

@@ -1,0 +1,1243 @@
+##### Initialization & Changeable Parameters #####
+from modules import data_import
+from gurobipy import *
+import gurobipy as gp
+import itertools
+import os.path
+import pickle
+from copy import deepcopy
+import numpy as np
+from tqdm.auto import trange
+import plotly.express as px
+from plotly.subplots import make_subplots
+import plotly.graph_objects as go
+import pandas as pd
+
+class simulation_handler:
+ 
+    ##### Initialize #####
+    def __init__(self, sim_param, sim_paths):
+        self.replications = sim_param['replications']
+        self.warm_up = sim_param['warm_up']
+        self.duration = sim_param['duration']
+        
+        self.import_data = sim_paths['import_params']
+        self.import_beta = sim_paths['import_betas']
+
+        self.export_txt = sim_paths['export_summary_costs']
+        self.export_pic = sim_paths['export_summary_picture']
+
+        self.export_state_my = sim_paths['export_state_myopic']
+        self.export_state_md = sim_paths['export_state_mdp']
+        self.export_cost_my = sim_paths['export_cost_myopic']
+        self.export_cost_md = sim_paths['export_cost_mdp']
+        self.export_util_my = sim_paths['export_util_myopic']
+        self.export_util_md = sim_paths['export_util_mdp']
+        self.export_sa_my = sim_paths['export_sa_myopic']
+        self.export_sa_md = sim_paths['export_sa_mdp']
+        self.my_path = os.getcwd()
+        
+
+    ##### Read Data #####
+    def read_data(self):
+        self.input_data = data_import.read_data(os.path.join(self.my_path, self.import_data))
+        
+        self.export_state_my = os.path.join(self.my_path,self.export_state_my)
+        self.export_state_md = os.path.join(self.my_path,self.export_state_md)
+
+        # Quick Assess to Various Parameters
+        self.TL = self.input_data.transition.wait_limit
+        self.BM = 10000
+        self.U = self.input_data.usage
+        self.p_dat = self.input_data.ppe_data
+        self.pea = self.input_data.arrival
[…]

### 2023-05-12 implementation/Report.Rmd
updating report

@@
 ---
-title: "Dynamic Knapsack Model Report"
+title: "Report"
 date: "`r Sys.Date()`"
 output: 
-  rmdformats::robobook:
-    highlight: kate
-    toc_depth: 3
-    lightbox: TRUE
-    gallery: TRUE
+  flexdashboard::flex_dashboard:
+    orientation: rows
+    social: menu
+    source_code: embed
 ---
 
-```{r setup, include=FALSE, cache=FALSE}
+```{r setup, include=FALSE, cache=TRUE}
 ## Global options
@@
 library(knitr)
-
+library(flexdashboard)
 library(scales)
@@
 library(tidyverse)
+knitr::opts_chunk$set(cache = TRUE)
+source(here('modules','data_funcs.R'))
 
-knitr::opts_chunk$set(cache = TRUE)
-reticulate::use_condaenv('uOttawa-dyn-knap-R', required=TRUE)
-source_python("z_factor.py")
-source(here('Report_Stuff/data_funcs.R'))
+# PARAMS
+warm <- 250
+dur <- 1000
+repl <- 30
+path <- here('data','full-sm')
 
-### Generate Data
-warm <- 250
-dur <- 1250
-repl <- 30
+# NO CUU - OR * 1
+modif <- '0-1'
+dt_pl_n10 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_n10 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_n10 <- generate_summary_zs(path, modif, FALSE)
 
-path <- "R1R2"
-R1R2 <- generate_summary(path, dur, warm, repl)
-R1R2_sa <- generate_summary_sa(path, dur, warm, repl)
-R1R2_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2.pkl"
-return_data(R1R2_beta_file, FALSE, FALSE)
-return_data(R1R2_beta_file, FALSE, TRUE)
-temp1 <- read_csv("Report_Stuff/R2_basic.csv") %>% mutate(type = 'basic')
-temp2 <- read_csv("Report_Stuff/R2_prio.csv") %>% mutate(type = 'prio')
-R1R2_beta_data_mdp <- bind_rows(temp1, temp2) %>% mutate(pol = 'mdp')
-temp1 <- read_csv("Report_Stuff/R2_basic_myopic.csv") %>% mutate(type = 'basic')
-temp2 <- read_csv("Report_Stuff/R2_prio_myopic.csv") %>% mutate(type = 'prio')
-R1R2_beta_data_myopic <- bind_rows(temp1, temp2) %>% mutate(pol = 'myopic')
-R1R2_beta_data <- bind_rows(R1R2_beta_data_mdp, R1R2_beta_data_myopic)
+# # NO CUU - OR * 1.1
+# modif <- '0-1.1'
+# dt_pl_n11 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_n11 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_n11 <- generate_summary_zs(path, modif, FALSE)
+# 
+# # NO CUU - OR * 1.2
+# modif <- '0-1.2'
+# dt_pl_n12 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_n12 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_n12 <- generate_summary_zs(path, modif, FALSE)
+# 
+# # NO CUU - OR * 1.3
+# modif <- '0-1.3'
+# dt_pl_n13 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_n13 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_n13 <- generate_summary_zs(path, modif, FALSE)
+# 
+# 
+# 
+# # CUU - OR * 1
+# modif <- '1000-1'
+# dt_pl_y10 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_y10 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_y10 <- generate_summary_zs(path, modif, TRUE)
+# 
+# # CUU - OR * 1.1
+# modif <- '1000-1.1'
+# dt_pl_y11 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_y11 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_y11 <- generate_summary_zs(path, modif, TRUE)
+# 
+# # CUU - OR * 1.2
+# modif <- '1000-1.2'
+# dt_pl_y12 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_y12 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_y12 <- generate_summary_zs(path, modif, TRUE)
+# 
+# # CUU - OR * 1.3
+# modif <- '1000-1.3'
+# dt_pl_y13 <- generate_summary(path, modif, dur, warm, repl)
+# dt_sa_y13 <- generate_summary_sa(path, modif, dur, warm, repl)
+# dt_zs_y13 <- generate_summary_zs(path, modif, TRUE)
 
-path <- "R1R2R3"
-R1R2R3 <- generate_summary(path, dur, warm, repl)
-R1R2R3_sa <- generate_summary_sa(path, dur, warm, repl)
-R1R2R3_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2R3.pkl"
-return_data(R1R2R3_beta_file, TRUE, FALSE)
-return_data(R1R2R3_beta_file, TRUE, TRUE)
-temp1 <- read_csv("Report_Stuff/R3_basic.csv") %>% mutate(type = 'basic')
-temp2 <- read_csv("Report_Stuff/R3_prio.csv") %>% mutate(type = 'prio')
-R1R2R3_beta_data_mdp <- bind_rows(temp1, temp2) %>% mutate(pol = 'mdp')
-temp1 <- read_csv("Report_Stuff/R3_basic_myopic.csv") %>% mutate(type = 'basic')
-temp2 <- read_csv("Report_Stuff/R3_prio_myopic.csv") %>% mutate(type = 'prio')
-R1R2R3_beta_data_myopic <- bind_rows(temp1, temp2) %>% mutate(pol = 'myopic')
-R1R2R3_beta_data <- bind_rows(R1R2R3_beta_data_mdp, R1R2R3_beta_data_myopic)
-
+# MODEL DATA SUMMARY
 arrival_rate <- data.frame(
-  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 4', 'Surgery 4', 'Surgery 6', 'Surgery 6'),
-  Complexity = c('Complexity 1', 'Complexity 2', 'Complexity 1', 'Complexity 2', 'Complexity 1', 'Complexity 2'),
-  "Arrival_Adjusted" = c(1.231988473, 0.615994236, 0.143731988, 0.102665706, 1.231988473, 0.615994236),
+  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 4', 
+              'Surgery 4', 'Surgery 6', 'Surgery 6'),
+  Complexity = c('Complexity 1', 'Complexity 2', 'Complexity 1', 
+                 'Complexity 2', 'Complexity 1', 'Complexity 2'),
+  "Arrival_Adjusted" = c(1.23, 0.62, 0.14, 0.10, 1.23, 0.62),
   "Arrival_Original" = c(1, 0.5, 0.0833, 0.0625, 1, 0.5), 
-  Rationale = c("once per week", "once per two weeks", "once per 3 months", "once per 4 months", "once per week", "once per 2 weeks")
+  Rationale = c("once per week", "once per two weeks", "once per 3 months", 
+                "once per 4 months", "once per week", "once per 2 weeks")
 )
@@
 resource_usage <- data.frame(
-  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 6', 'Surgery 6', 'Surgery 6', 'Surgery 6'),
-  Complexity = c('Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2', 'Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2', 'Complexity 1', 'Complexity 1', 'Complexity 2', 'Complexity 2'),
-  Resource_Type = c('Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time','Admissions', 'OR_Time'), 
-  Usage = c(0, 3, 1,4,1,4,1,5.5,0,1.5,0,2.5)
+  Surgery = c('Surgery 1', 'Surgery 1', 'Surgery 1', 'Surgery 1', 
+              'Surgery 4', 'Surgery 4', 'Surgery 4', 'Surgery 4', 
+              'Surgery 6', 'Surgery 6', 'Surgery 6', 'Surgery 6'),
+  Complexity = c('Complexity 1', 'Complexity 1', 'Complexity 2', 
+                 'Complexity 2', 'Complexity 1', 'Complexity 1', 
+                 'Complexity 2', 'Complexity 2', 'Complexity 1', 
+                 'Complexity 1', 'Complexity 2', 'Complexity 2'),
+  Resource_Type = c('Admissions', 'OR_Time','Admissions', 'OR_Time',
+                    'Admissions', 'OR_Time','Admissions', 'OR_Time',
+                    'Admissions', 'OR_Time','Admissions', 'OR_Time'), 
+  Usage = c(0,3,1,4,1,4,1,5.5,0,1.5,0,2.5)
 )
@@
 )
-
-### Generate Plots
-R1R2_policy <- (ggplot(R1R2_beta_data %>% filter(M == 0), aes(x=T, y=Val, color=C, shape=D, linetype=D)) +
-    geom_line() + geom_point() +
-    facet_wrap(pol ~ type, scales='free') +
-    scale_x_continuous(breaks=seq(0,10), limits = c(1,10))) %>% ggplotly()
-
-R1R2R3_policy <- (ggplot(R1R2R3_beta_data %>% filter(M == 0), aes(x=T, y=Val, color=C, shape=D, linetype=D)) +
-    geom_line() + geom_point() +
-    facet_wrap(pol ~ type, scales='free') +
-    scale_x_continuous(breaks=seq(0,10), limits = c(1,10))) %>% ggplotly()
 ```
 
-# Parameters
+Model Parameters
+=======================================================================
 
-## Model Parameters
-This model is a smaller instance of the full problem:
+Row
+-----------------------------------------------------------------------
+
+### Model Parameters
+**Model Instance**
 
@@
 
-## Simulation Parameters
+**Simulation Parameters**
+
 * 30 Replications
-* 1250 weeks duration
+* 1000 weeks duration
 * 250 weeks warm up
 
-## Surgeries
-1) **Surgery 1** - 1. SPINE POSTERIOR DECOMPRESSION/LAMINECTOMY LUMBAR
-2) **Surgery 4** - 4. SPINE POST CERV DECOMPRESSION AND FUSION W INSTR
-3) **Surgery 6** - 6. SPINE POSTERIOR DISCECTOMY LUMBAR
+**Surgeries**
 
-## Arrival Rate
+* Surgery 1 - 1. SPINE POSTERIOR DECOMPRESSION/LAMINECTOMY LUMBAR
+* Surgery 4 - 4. SPINE POST CERV DECOMPRESSION AND FUSION W INSTR
+* Surgery 6 - 6. SPINE POSTERIOR DISCECTOMY LUMBAR
+
+### Arrival Rate
 It was set to be 95% of the capacity, however due to transitions, the resource usage should be higher than 95%
@@
 
-## Resource Usage
-Usage of the resources
+Row
+-----------------------------------------------------------------------
+
+### Resource Usage
 ```{r echo=FALSE, cache=FALSE}
@@
 
-## Resource Capacity
+### Resource Capacity
 ```{r echo=FALSE, cache=FALSE}
@@
 
-# R1R2 Report
-This model is the default model that does not penalize bed under utilization
+nPen, OR*1
+=======================================================================
 
-## Policy Description
-The description will be based on the following graphs (both of them are for M of 0 only):
-```{r echo=FALSE, cache=FALSE}
-R1R2_policy
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+```{r echo=FALSE}
+dt_zs_n10$zf_plt %>% ggplotly()
 ```
 
-The top graphs show MDP policy, and the graphs below show Myopic policy.
+### Policy Description
 
-The graph on the left shows in which days the policy will allow scheduling.
+nPen, OR*1.1
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+nPen, OR*1.2
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+nPen, OR*1.3
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+Pen, OR*1
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+Pen, OR*1.1
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+Pen, OR*1.2
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+Pen, OR*1.3
+=======================================================================
+
+Row
+-----------------------------------------------------------------------
+
+### Policy Graph
+
+### Policy Description
+
+<!-- # R1R2 Report -->
+<!-- This model is the default model that does not penalize bed under utilization -->
+
+<!-- ## Policy Description -->
+<!-- The description will be based on the following graphs (both of them are for M of 0 only): -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2_policy -->
+<!-- ``` -->
+
+<!-- The top graphs show MDP policy, and the graphs below show Myopic policy. -->
+
+<!-- The graph on the left shows in which days the policy will allow scheduling.
 If the value is below 0 - the model will allow scheduling, otherwise the model will keep patients in the waitlist.
@@
 The lower the surgery is on the list the more likely it is to be scheduled first.
-The following is the order:
+The following is the order: -->
 
-- Surgery 6, Complexity 2
-- Surgery 6, Complexity 1
-- Surgery 1, Complexity 1
-- Surgery 1, Complexity 2
-- Surgery 4, Complexity 1
-- Surgery 4, Complexity 2
+<!-- - Surgery 6, Complexity 2 -->
+<!-- - Surgery 6, Complexity 1 -->
+<!-- - Surgery 1, Complexity 1 -->
+<!-- - Surgery 1, Complexity 2 -->
+<!-- - Surgery 4, Complexity 1 -->
+<!-- - Surgery 4, Complexity 2 -->
 
-For Myopic, it is changed such that the entire horizon is filled. And the graph on the right shows the approximate order of scheduling priority. It appears to be very similar to MDP.
+<!-- For Myopic, it is changed such that the entire horizon is filled. And the graph on the right shows the approximate order of scheduling priority. It appears to be very similar to MDP. -->
 
-Additionally the following graphs give some insights on how the policy makes decision
-```{r echo=FALSE, cache=FALSE}
-R1R2_sa$res_plot$sched_plt
-```
+<!-- Additionally the following graphs give some insights on how the policy makes decision -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2_sa$res_plot$sched_plt -->
+<!-- ``` -->
 
-## Policy Results
-### Wait Times in weeks
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2$results$pw)
-```
+<!-- ## Policy Results -->
+<!-- ### Wait Times in weeks -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2$results$pw) -->
+<!-- ``` -->
 
-### Wait List Size
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2$results$wtl)
-```
-```{r echo=FALSE, cache=FALSE}
-R1R2_sa$res_plot$waitlist_plt
-```
+<!-- ### Wait List Size -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2$results$wtl) -->
+<!-- ``` -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2_sa$res_plot$waitlist_plt -->
+<!-- ``` -->
 
-### Utilization
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2$results$util)
-```
+<!-- ### Utilization -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2$results$util) -->
+<!-- ``` -->
 
-### Reschedules as percentage of arrivals & Total Reschedules
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2$results$rsc)
-```
-```{r echo=FALSE, cache=FALSE}
-R1R2_sa$res_plot$rsc_plt %>% ggplotly()
-```
+<!-- ### Reschedules as percentage of arrivals & Total Reschedules -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2$results$rsc) -->
+<!-- ``` -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2_sa$res_plot$rsc_plt %>% ggplotly() -->
+<!-- ``` -->
 
-### Transitions per week
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2$results$tr)
-```
+<!-- ### Transitions per week -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2$results$tr) -->
+<!-- ``` -->
 
-# R1R2R3 Report
-In addition to the parameters above, this model penalizes bed under utilization in the first period
+<!-- # R1R2R3 Report -->
+<!-- In addition to the parameters above, this model penalizes bed under utilization in the first period -->
 
-## Policy Description
-<!-- The description will be based on the following graphs: -->
-```{r echo=FALSE, cache=FALSE}
-R1R2R3_policy
-```
+<!-- ## Policy Description -->
+<!-- <!-- The description will be based on the following graphs: --> -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2R3_policy -->
+<!-- ``` -->
 
-Additionally the following graphs give some insights on how the policy makes decision
-```{r echo=FALSE, cache=FALSE}
-R1R2R3_sa$res_plot$sched_plt
-```
+<!-- Additionally the following graphs give some insights on how the policy makes decision -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2R3_sa$res_plot$sched_plt -->
+<!-- ``` -->
 
-## Policy Results
+<!-- ## Policy Results -->
 
-### Wait Times in weeks
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2R3$results$pw)
-```
+<!-- ### Wait Times in weeks -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2R3$results$pw) -->
+<!-- ``` -->
 
-### Wait List Size
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2R3$results$wtl)
-```
-```{r echo=FALSE, cache=FALSE}
-R1R2R3_sa$res_plot$waitlist_plt
-```
+<!-- ### Wait List Size -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2R3$results$wtl) -->
+<!-- ``` -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2R3_sa$res_plot$waitlist_plt -->
+<!-- ``` -->
 
-### Utilization
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2R3$results$util)
-```
+<!-- ### Utilization -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2R3$results$util) -->
+<!-- ``` -->
 
-### Reschedules as percentage of arrivals & Total Reschedules
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2R3$results$rsc)
-```
-```{r echo=FALSE, cache=FALSE}
-R1R2R3_sa$res_plot$rsc_plt %>% ggplotly()
-```
+<!-- ### Reschedules as percentage of arrivals & Total Reschedules -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2R3$results$rsc) -->
+<!-- ``` -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- R1R2R3_sa$res_plot$rsc_plt %>% ggplotly() -->
+<!-- ``` -->
 
-### Transitions per week
-```{r echo=FALSE, cache=FALSE}
-kable(R1R2R3$results$tr)
-```
+<!-- ### Transitions per week -->
+<!-- ```{r echo=FALSE, cache=FALSE} -->
+<!-- kable(R1R2R3$results$tr) -->
+<!-- ``` -->

### 2023-05-12 implementation/Report_Stuff/data_funcs.R

@@ -1,401 +1,0 @@
-library(tidyverse)
-library(here)
-
-# Generate Summary From Patient Level Data
-generate_summary <- function(path, dur, warm, repl) {
-  
-  # Data
-  data <- read_data(path)
-  
-  # Generate Wait Time
-  avg_pw <- analyse_wait(data, dur, warm, repl)
-  # Generate Wait List
-  avg_wtl <- analyse_wait_list(data, dur, warm, repl)
-  # Generate Utilization
-  avg_util <- analyse_util(data, dur, warm, repl)
-  # Generate Reschedules
-  avg_rsc <- analyse_resch(data, dur, warm, repl)
-  # Generate Transitions
-  avg_tr <- analyse_trans(data, dur, warm, repl)
-  
-  results <- list(
-    'data' = data,
-    'results' = list(
-      'pw' = avg_pw, 
-      'wtl' = avg_wtl, 
-      'util' = avg_util, 
-      'rsc' = avg_rsc,
-      'tr' = avg_tr
-    )
-  )
-  
-  return (results)
-}
-### Reads all relevant data
-read_data <- function(path) {
-  
-  # Patient Transition Data
-  state_md <- read_csv(here("simulation_data",paste0('STATE-md-',path,'.txt')), col_types = cols(
-    id = col_double(), repl=col_double(), period=col_double(), arrived_on=col_double(), 
-    sched_to=col_double(), resch_from=col_double(), resch_to=col_double())) %>% filter(!is.na(id))
-  state_my <- read_csv(here("simulation_data",paste0('STATE-my-',path,'.txt')), col_types = cols(
-    id = col_double(), repl=col_double(), period=col_double(), arrived_on=col_double(), 
-    sched_to=col_double(), resch_from=col_double(), resch_to=col_double())) %>% filter(!is.na(id))
-  state <- bind_rows(state_md, state_my)
-
-  # Cost Data
-  cost_md <- read_csv(here("simulation_data",paste0('COST-md-',path,'.txt'))) %>% mutate(policy = 'MDP')
-  cost_my <- read_csv(here("simulation_data",paste0('COST-my-',path,'.txt'))) %>% mutate(policy = 'myopic')
[…]

### 2023-05-12 implementation/Report_Stuff/generate_report.R

@@ -1,7 +1,0 @@
-library(reticulate)
-reticulate::use_condaenv('uOttawa-dyn-knap-R', required=TRUE)
-source_python("z_factor.py")
-
-R1R2_beta_file <- "Data/sens-data/smaller-full/betas/cw1-cc5-cv10-gam99-smaller-full-nopri-optimal-R1R2.pkl"
-R1R2R3_beta_file <- 
-pickle_data <- return_plots(R1R2_beta_file, FALSE)

### 2023-05-13 implementation/Report.Rmd
finalized the report for 8 scenarios

@@
 
-```{r setup, include=FALSE, cache=TRUE}
+```{r setup, include=FALSE}
 ## Global options
@@
 
-# # NO CUU - OR * 1.1
-# modif <- '0-1.1'
-# dt_pl_n11 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_n11 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_n11 <- generate_summary_zs(path, modif, FALSE)
-# 
-# # NO CUU - OR * 1.2
-# modif <- '0-1.2'
-# dt_pl_n12 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_n12 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_n12 <- generate_summary_zs(path, modif, FALSE)
-# 
-# # NO CUU - OR * 1.3
-# modif <- '0-1.3'
-# dt_pl_n13 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_n13 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_n13 <- generate_summary_zs(path, modif, FALSE)
-# 
-# 
-# 
-# # CUU - OR * 1
-# modif <- '1000-1'
-# dt_pl_y10 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_y10 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_y10 <- generate_summary_zs(path, modif, TRUE)
-# 
-# # CUU - OR * 1.1
-# modif <- '1000-1.1'
-# dt_pl_y11 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_y11 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_y11 <- generate_summary_zs(path, modif, TRUE)
-# 
-# # CUU - OR * 1.2
-# modif <- '1000-1.2'
-# dt_pl_y12 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_y12 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_y12 <- generate_summary_zs(path, modif, TRUE)
-# 
-# # CUU - OR * 1.3
-# modif <- '1000-1.3'
-# dt_pl_y13 <- generate_summary(path, modif, dur, warm, repl)
-# dt_sa_y13 <- generate_summary_sa(path, modif, dur, warm, repl)
-# dt_zs_y13 <- generate_summary_zs(path, modif, TRUE)
+# NO CUU - OR * 1.1
+modif <- '0-1.1'
+dt_pl_n11 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_n11 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_n11 <- generate_summary_zs(path, modif, FALSE)
+
+# NO CUU - OR * 1.2
+modif <- '0-1.2'
+dt_pl_n12 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_n12 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_n12 <- generate_summary_zs(path, modif, FALSE)
+
+# NO CUU - OR * 1.3
+modif <- '0-1.3'
+dt_pl_n13 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_n13 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_n13 <- generate_summary_zs(path, modif, FALSE)
+
+# CUU - OR * 1
+modif <- '1000-1'
+dt_pl_y10 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_y10 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_y10 <- generate_summary_zs(path, modif, TRUE)
+
+# CUU - OR * 1.1
+modif <- '1000-1.1'
+dt_pl_y11 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_y11 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_y11 <- generate_summary_zs(path, modif, TRUE)
+
+# CUU - OR * 1.2
+modif <- '1000-1.2'
+dt_pl_y12 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_y12 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_y12 <- generate_summary_zs(path, modif, TRUE)
+
+# CUU - OR * 1.3
+modif <- '1000-1.3'
+dt_pl_y13 <- generate_summary(path, modif, dur, warm, repl)
+dt_sa_y13 <- generate_summary_sa(path, modif, dur, warm, repl)
+dt_zs_y13 <- generate_summary_zs(path, modif, TRUE)
 
@@
 
-nPen, OR*1
+NP, 1
 =======================================================================
 
-Row
+Row {data-height=650}
 -----------------------------------------------------------------------
 
-### Policy Graph
+### Policy Description
+The policy description is based on a graph to the right
+
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
+
+Additionally the far right graph shows the approximate decision making
+
+### Policy Math Graph
 
@@
 
-### Policy Description
+### Policy Evidence Graph
 
-nPen, OR*1.1
-=======================================================================
+```{r echo=FALSE}
+dt_sa_n10$res_plot$sched_plt %>% ggplotly()
+```
 
@@
 
-### Policy Graph
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n10$results$pw)
+```
 
-### Policy Description
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n10$results$wtl)
+```
 
-nPen, OR*1.2
-=======================================================================
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n10$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n10$results$util)
+```
 
@@
 
-### Policy Graph
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n10$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n10$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n10$res_plot$rsc_plt %>% ggplotly()
+```
+
+NP, 1.1
+=======================================================================
+
+Row {data-height=650}
+-----------------------------------------------------------------------
 
 ### Policy Description
+The policy description is based on a graph to the right
 
-nPen, OR*1.3
-=======================================================================
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
+
+Additionally the far right graph shows the approximate decision making
+
+### Policy Math Graph
+
+```{r echo=FALSE}
+dt_zs_n11$zf_plt %>% ggplotly()
+```
+
+### Policy Evidence Graph
+
+```{r echo=FALSE}
+dt_sa_n11$res_plot$sched_plt %>% ggplotly()
+```
 
@@
 
-### Policy Graph
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n11$results$pw)
+```
 
-### Policy Description
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n11$results$wtl)
+```
 
-Pen, OR*1
-=======================================================================
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n11$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n11$results$util)
+```
 
@@
 
-### Policy Graph
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n11$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n11$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n11$res_plot$rsc_plt %>% ggplotly()
+```
+
+NP, 1.2
+=======================================================================
+
+Row {data-height=650}
+-----------------------------------------------------------------------
 
 ### Policy Description
+The policy description is based on a graph to the right
 
-Pen, OR*1.1
-=======================================================================
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
+
+Additionally the far right graph shows the approximate decision making
+
+### Policy Math Graph
+
+```{r echo=FALSE}
+dt_zs_n12$zf_plt %>% ggplotly()
+```
+
+### Policy Evidence Graph
+
+```{r echo=FALSE}
+dt_sa_n12$res_plot$sched_plt %>% ggplotly()
+```
 
@@
 
-### Policy Graph
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n12$results$pw)
+```
 
-### Policy Description
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n12$results$wtl)
+```
 
-Pen, OR*1.2
-=======================================================================
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n12$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n12$results$util)
+```
 
@@
 
-### Policy Graph
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n12$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n12$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n12$res_plot$rsc_plt %>% ggplotly()
+```
+
+NP, 1.3
+=======================================================================
+
+Row {data-height=650}
+-----------------------------------------------------------------------
 
 ### Policy Description
+The policy description is based on a graph to the right
 
-Pen, OR*1.3
-=======================================================================
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
+
+Additionally the far right graph shows the approximate decision making
+
+### Policy Math Graph
+
+```{r echo=FALSE}
+dt_zs_n13$zf_plt %>% ggplotly()
+```
+
+### Policy Evidence Graph
+
+```{r echo=FALSE}
+dt_sa_n13$res_plot$sched_plt %>% ggplotly()
+```
 
@@
 
-### Policy Graph
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n13$results$pw)
+```
+
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n13$results$wtl)
+```
+
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n13$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n13$results$util)
+```
+
+Row
+-----------------------------------------------------------------------
+
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_n13$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n13$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_n13$res_plot$rsc_plt %>% ggplotly()
+```
+
+P, 1
+=======================================================================
+
+Row {data-height=650}
+-----------------------------------------------------------------------
 
 ### Policy Description
+The policy description is based on a graph to the right
 
-<!-- # R1R2 Report -->
-<!-- This model is the default model that does not penalize bed under utilization -->
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
 
-<!-- ## Policy Description -->
-<!-- The description will be based on the following graphs (both of them are for M of 0 only): -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2_policy -->
-<!-- ``` -->
+Additionally the far right graph shows the approximate decision making
 
-<!-- The top graphs show MDP policy, and the graphs below show Myopic policy. -->
+### Policy Math Graph
 
-<!-- The graph on the left shows in which days the policy will allow scheduling.
-If the value is below 0 - the model will allow scheduling, otherwise the model will keep patients in the waitlist.
-Thus this policy **will only schedule into week 1 and week 2**.
-The plot on the right shows the approximate priority of different surgeries.
-The lower the surgery is on the list the more likely it is to be scheduled first.
-The following is the order: -->
+```{r echo=FALSE}
+dt_zs_y10$zf_plt %>% ggplotly()
+```
 
-<!-- - Surgery 6, Complexity 2 -->
-<!-- - Surgery 6, Complexity 1 -->
-<!-- - Surgery 1, Complexity 1 -->
-<!-- - Surgery 1, Complexity 2 -->
-<!-- - Surgery 4, Complexity 1 -->
-<!-- - Surgery 4, Complexity 2 -->
+### Policy Evidence Graph
 
-<!-- For Myopic, it is changed such that the entire horizon is filled. And the graph on the right shows the approximate order of scheduling priority. It appears to be very similar to MDP. -->
+```{r echo=FALSE}
+dt_sa_y10$res_plot$sched_plt %>% ggplotly()
+```
 
-<!-- Additionally the following graphs give some insights on how the policy makes decision -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2_sa$res_plot$sched_plt -->
-<!-- ``` -->
+Row 
+-----------------------------------------------------------------------
 
-<!-- ## Policy Results -->
-<!-- ### Wait Times in weeks -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2$results$pw) -->
-<!-- ``` -->
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y10$results$pw)
+```
 
-<!-- ### Wait List Size -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2$results$wtl) -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2_sa$res_plot$waitlist_plt -->
-<!-- ``` -->
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y10$results$wtl)
+```
 
-<!-- ### Utilization -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2$results$util) -->
-<!-- ``` -->
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y10$results$tr)
+```
 
-<!-- ### Reschedules as percentage of arrivals & Total Reschedules -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2$results$rsc) -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2_sa$res_plot$rsc_plt %>% ggplotly() -->
-<!-- ``` -->
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y10$results$util)
+```
 
-<!-- ### Transitions per week -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2$results$tr) -->
-<!-- ``` -->
+Row
+-----------------------------------------------------------------------
 
-<!-- # R1R2R3 Report -->
-<!-- In addition to the parameters above, this model penalizes bed under utilization in the first period -->
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y10$results$rsc)
+```
 
-<!-- ## Policy Description -->
-<!-- <!-- The description will be based on the following graphs: --> -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2R3_policy -->
-<!-- ``` -->
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y10$res_plot$waitlist_plt %>% ggplotly()
+```
 
-<!-- Additionally the following graphs give some insights on how the policy makes decision -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2R3_sa$res_plot$sched_plt -->
-<!-- ``` -->
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y10$res_plot$rsc_plt %>% ggplotly()
+```
 
-<!-- ## Policy Results -->
+P, 1.1
+=======================================================================
 
-<!-- ### Wait Times in weeks -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2R3$results$pw) -->
-<!-- ``` -->
+Row {data-height=650}
+-----------------------------------------------------------------------
 
-<!-- ### Wait List Size -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2R3$results$wtl) -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2R3_sa$res_plot$waitlist_plt -->
-<!-- ``` -->
+### Policy Description
+The policy description is based on a graph to the right
 
-<!-- ### Utilization -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2R3$results$util) -->
-<!-- ``` -->
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
 
-<!-- ### Reschedules as percentage of arrivals & Total Reschedules -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2R3$results$rsc) -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- R1R2R3_sa$res_plot$rsc_plt %>% ggplotly() -->
-<!-- ``` -->
+Additionally the far right graph shows the approximate decision making
 
-<!-- ### Transitions per week -->
-<!-- ```{r echo=FALSE, cache=FALSE} -->
-<!-- kable(R1R2R3$results$tr) -->
-<!-- ``` -->
+### Policy Math Graph
+
+```{r echo=FALSE}
+dt_zs_y11$zf_plt %>% ggplotly()
+```
+
+### Policy Evidence Graph
+
+```{r echo=FALSE}
+dt_sa_y11$res_plot$sched_plt %>% ggplotly()
+```
+
+Row 
+-----------------------------------------------------------------------
+
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y11$results$pw)
+```
+
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y11$results$wtl)
+```
+
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y11$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y11$results$util)
+```
+
+Row
+-----------------------------------------------------------------------
+
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y11$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y11$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y11$res_plot$rsc_plt %>% ggplotly()
+```
+
+P, 1.2
+=======================================================================
+
+Row {data-height=650}
+-----------------------------------------------------------------------
+
+### Policy Description
+The policy description is based on a graph to the right
+
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
+
+Additionally the far right graph shows the approximate decision making
+
+### Policy Math Graph
+
+```{r echo=FALSE}
+dt_zs_y12$zf_plt %>% ggplotly()
+```
+
+### Policy Evidence Graph
+
+```{r echo=FALSE}
+dt_sa_y12$res_plot$sched_plt %>% ggplotly()
+```
+
+Row 
+-----------------------------------------------------------------------
+
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y12$results$pw)
+```
+
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y12$results$wtl)
+```
+
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y12$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y12$results$util)
+```
+
+Row
+-----------------------------------------------------------------------
+
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y12$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y12$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y12$res_plot$rsc_plt %>% ggplotly()
+```
+
+P, 1.3
+=======================================================================
+
+Row {data-height=650}
+-----------------------------------------------------------------------
+
+### Policy Description
+The policy description is based on a graph to the right
+
+* The left column shows MDP policy, the right column shows Myopic Policy
+* The top row shows scheduling costs, adjusted for resource usage, the bottom is not adjusted
+* The bottom row shows in which days the policy will allow scheduling.
+* The top row shows approximate order of patient scheduling.
+
+Additionally the far right graph shows the approximate decision making
+
+### Policy Math Graph
+
+```{r echo=FALSE}
+dt_zs_y13$zf_plt %>% ggplotly()
+```
+
+### Policy Evidence Graph
+
+```{r echo=FALSE}
+dt_sa_y13$res_plot$sched_plt %>% ggplotly()
+```
+
+Row 
+-----------------------------------------------------------------------
+
+### Wait Times in weeks
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y13$results$pw)
+```
+
+### Wait List Size
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y13$results$wtl)
+```
+
+### Transitions per week
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y13$results$tr)
+```
+
+### Utilization
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y13$results$util)
+```
+
+Row
+-----------------------------------------------------------------------
+
+### Reschedules
+```{r echo=FALSE, cache=FALSE}
+kable(dt_pl_y13$results$rsc)
+```
+
+### Wait List Size by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y13$res_plot$waitlist_plt %>% ggplotly()
+```
+
+### Reschedules by Group
+```{r echo=FALSE, cache=FALSE}
+dt_sa_y13$res_plot$rsc_plt %>% ggplotly()
+```

### 2023-05-13 implementation/modules/z_factor.py

@@ -1,300 +1,0 @@
-#%%|
-from copy import deepcopy
-from modules import data_import
-
-import os.path
-import pickle
-import itertools
-
-import gurobipy as gp
-import numpy as np
-import pandas as pd
-
-from pprint import pprint
-import plotly.express as px
-from plotly.subplots import make_subplots
-import plotly.graph_objects as go
-
-
-#%%
-def generate_z_score(path, modifier, myopic, cuu):
-    # path = '/Users/konstantin/Documents/Projects/uOttawa/UOttawa-Dynamic-Knapsack-Problem-Python/implementation/data/full-sm'
-    # modifier = '0-1'
-    # myopic = True
-    # cuu = False
-
-
-    ##### READ DATA #####
-    # IMPORT    
-    input_path = os.path.join(path, 'input')
-    output_path = os.path.join(path, 'res')
-    cuu_val = float(modifier.split('-')[1])
-    import_data = os.path.join(input_path, 'full-sm-np-dt.xlsx')
-    import_beta = os.path.join(input_path, 'betas', f'full-sm-np-opt-{modifier}.pkl')
-    input_data = data_import.read_data(os.path.join(import_data))
-
-    # QUICK ACCESS
-    TL = input_data.transition.wait_limit
-    U = input_data.usage
-    ptp_d = input_data.transition.transition_rate_comp
-    ptp_k = input_data.transition.transition_rate_pri
-    cw = input_data.model_param.cw
-    cs = input_data.model_param.cs
-    cv = input_data.model_param.cv
-
-    # SETS
-    T = input_data.indices['t']
-    M = input_data.indices['m']
-    P = input_data.indices['p']
-    D = input_data.indices['d']
-    K = input_data.indices['k']
-    C = input_data.indices['c']
-
-
-    ##### BETAS #####
[…]

### 2023-05-26 implementation/Report.Rmd
updates

@@
 library(tidyverse)
+library(here)
 knitr::opts_chunk$set(cache = TRUE)
@@
 
-Additionally the far right graph shows the approximate decision making
+Additionally the far right graph shows the approximate decision making.
+
+Policy:
+
+* MDP will schedule into the first 2 days only. 
+* In this approximate order:
+
+  * Surgery 6, Complexity 1
+  * Surgery 1, Complexity 1
+  * Surgery 6, Complexity 2
+  * Surgery 4, Complexity 2
+  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
 
@@
 
+Policy:
+
+* MDP will schedule into the first 2 days only. 
+* In this approximate order:
+
+  * Surgery 6, Complexity 1
+  * Surgery 6, Complexity 2
+  * Surgery 1, Complexity 1
+  * Surgery 4, Complexity 2
+  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
+
 ### Policy Math Graph
@@
 Additionally the far right graph shows the approximate decision making
+
+Policy:
+
+* MDP will schedule into the first 2 days only. 
+* In this approximate order:
+
+  * Surgery 6, Complexity 1
+  * Surgery 6, Complexity 2
+  * Surgery 1, Complexity 1
+  * Surgery 4, Complexity 2
+  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
 
@@
 Additionally the far right graph shows the approximate decision making
+
+Policy:
+
+* MDP will schedule S6 and S1C1 into the first 2 days only. S4 and S1C2 will be scheduled into the entire planning horizon.
+* In this approximate order:
+
+  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
+  * Surgery 4, Complexity 2
+  * Surgery 6, Complexity 1
+  * Surgery 6, Complexity 2
+  * Surgery 1, Complexity 1
 
@@
 
+Policy:
+
+* MDP will schedule S6 and S1C1 into the first 2 days only. S4 and S1C2 will be scheduled into the entire planning horizon.
+* In this approximate order:
+
+  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
+  * Surgery 4, Complexity 2
+  * Surgery 6, Complexity 1
+  * Surgery 1, Complexity 1
+  * Surgery 6, Complexity 2
+
 ### Policy Math Graph
@@
 Additionally the far right graph shows the approximate decision making
+
+Policy:
+
+* MDP will schedule S6 and S1C1 into the first 2 days only. S4 and S1C2 will be scheduled into the entire planning horizon.
+* In this approximate order:
+
+  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
+  * Surgery 4, Complexity 2
+  * Surgery 6, Complexity 1
+  * Surgery 1, Complexity 1
+  * Surgery 6, Complexity 2
 
